### 2013-07-18 dit-paper.tex
First commit

\documentclass[a4paper,10pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{charter}
\usepackage{color}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{url}

\definecolor{grey}{rgb}{0.9,0.9,0.9}

\lstset{
language=Python,
basicstyle=\footnotesize\fontfamily{pcr},
backgroundcolor=\color{grey},
numbers=left,
numberstyle=\tiny,
numbersep=5pt,
showstringspaces=false,
tabsize=2,
breaklines=true
}

\setlength{\parindent}{0pt}

%opening
\sloppy

\newcommand{\dbf}[1]{\operatorname{dbf}(#1)}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

\newtheorem*{remarks}{Remarks}

\begin{document}

\title{Using DIT to simplify the DBF feasibility test}
\author{Thomas Chapeaux \\ ~ \\ \emph{Supervisor} \\ Laurent George, ECE Paris \\ ~ \\ \emph{Thanks to} \\ Paul Rodriguez}

\date{July 2013}

\maketitle

\tableofcontents

\newpage

\section{Real-Time Systems}

$\tau = \{ \tau_1, \cdots, \tau_n \}$

$\tau_i = (O_i, C_i, D_i, T_i)$

$H = LCM(T_i)$

\section{The demand-bound function feasibility test}
\label{sct:DBF}

\subsection{Definition of the demand-bound function}

\begin{definition}
 The \textbf{demand-bound function (DBF)} (\cite{baruah1999generalized} and \cite{baruah1990algorithms}), defined for a task set $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\

 Mathematically,
 $$\dbf{t} = \max_{\{t_1, t_2 \; : \; t_2 - t_1 = t\}} \sum_{i=1}^n C_i \; h_i(t_1, t_2)$$
 where $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
\end{definition}

As the synchronous arrival pattern is known to be the worst case, in that particular case we can only consider the interval $[0, t]$. In an asynchronous arrival pattern, it is sufficient to check only intervals where $t_1 < O_{max} + H$, as the values will be periodic after it.\\

In the sequel a closed form expression of the DBF is given in the synchronous case. Intuitively, in that case, it will be a step-function whose increase will occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\

Starting from the definition, it remains to find a method to compute the values of $h_i(t)$. In the synchronous case, these values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} : k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
$$k T_i + D_i \leq t$$
$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e. $h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\

This is generalized by the final definition of $h_i(t)$: $$h_i(t) = \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \}$$

With this result, a closed form of the DBF function in the synchronous case is obtained $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$

\subsection{Feasibility test for EDF}

In \cite{baruah1990algorithms}, the authors show that the DBF can be used to derive the following feasibility condition for EDF\footnote{And thus, EDF being optimal, for all optimal schedulers} on sporadic task sets. An adapted proof is given here.

\begin{theorem}
$$\text{$(\tau_1, ..., \tau_n)$ is feasible} \iff \dbf{t} \leq t \; \forall t$$
\end{theorem}

\begin{proof}
	We first show that the condition is \emph{necessary}. Indeed, if the condition is not fulfilled (i.e. $\exists t^* \; s.t. \; \dbf{t^*} > t^*$), it means that in an interval of $t^*$ time units, the total execution time of the jobs whose arrival and deadline occurs within the interval is superior to $t^*$. The system is thus not feasible if the condition is not fulfilled.\\

	Now, we prove that the condition is \emph{sufficient}. For that, suppose that $\dbf{t} \leq t \; \forall t$.\\

	... (The idea is to look at each interval beginning at an arrival time and finishing at a deadline (not necessarily of the same job). Then we can prove that if there is only those two tasks, they can execute. If there are other tasks, we can look at a greater interval in which they can all execute)

\end{proof}

Furthermore, the authors show that in the synchronous case, it is sufficient to consider intervals of the form $[0, t_d]$, where the $t_d$ correspond to job deadlines (i.e. the increases the demand-bound function) in the interval $\left[ D_{min}, H \right]$.\\

For constrained deadline set, it is sufficient to consider intervals $[0, t_d]$ with $t_d \leq L$, where $L$ is the first busy period and is the solution to the following recursive equation $$L = \sum_{i=1}^{n} \lceil \frac{L}{T_i} \rceil C_i$$ which can be computed through fixed-point iteration $$w_0 = \sum_{i=1}^{n} C_i$$ $$w_{k+1} = \sum_{i=1}^{n} \lceil \frac{w_k}{T_i} \rceil C_i$$

Even so, this test requires to check a number of instant which is exponential in the number of tasks, making the general determination of feasibility a NP-hard problem.

\section{Definitive idle time approach}
\label{sct:DIT}

\begin{definition}
An \textbf{idle time} is a time $t$ such that every job released strictly before instant $t$ finishes its execution before  or at instant $t$.\\
\end{definition}

\begin{definition}
A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.\\
\end{definition}

Remarks
 \begin{itemize}
  \item If the system is feasible, every DIT is an idle time.
  \item Contrary to the idle times, the DITs are independent of the scheduling or the execution times of the jobs.
  \item $t=0$ is always a DIT.
  \item There are no DITs strictly after the first arrival of an arbitrary deadline task. In the following we only consider the constrained deadline case.
 \end{itemize}

 An example of the DITs of a system is given in Fig. \ref{fig:ditExample}.

 \begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{figs/dit_example.png}
\caption{The block of colors represents the arrival time and deadline of a job. DITs are represented by a green line below}
\label{fig:ditExample}
\end{center}
\end{figure}

While the definition is applicable to both synchronous and asynchronous tasks system, the following only consider the synchronous case (which is the worst-case for non-concrete tasks). The difficulties arising with asynchronous tasks are described in a later section.\\

In the synchronous case, $t=0$ and $t=H$ are DITs but there might be others in-between. The following notion is thus defined:

\begin{definition}
The earliest DIT occurring in the system strictly after $t=0$ is called the \textbf{first DIT} and is noted $t_d$.
\end{definition}

If the first DIT is $H$, then the only DITs of the system are multiple of $H$ as the occurrence of DITs is periodic.\\

The following section explains the methods to determine the value of the first DIT. Then section \ref{sct:ditsynchfeastest} will explain a method to reduce the complexity of the DBF feasibility test if the first DIT occurs before $H$.

\subsection{Existence and value}

In synchronous systems, $H$ is always a DIT, so the first DIT $t_d$ exists and is such that $t_d \leq H$. In the constrained deadline case ($D_i \leq T_i \; \forall i$), it is possible that other DITs occur before it, in which case $t_d < H$.\\

The problem of the existence of a DIT can be written with modular equations as
$$
\exists ? \; t_d \; s.t. \; \forall i : \exists a_i \in [D_i, T_i] \; s.t. \; t_d \equiv a_i \; (mod \; T_i) \\
$$

For fixed values of $a_i$, this is a case of the Generalized Chinese Remainder Theorem (see Appendix \ref{sct:appCRT}). However, in our case, each $a_i$ can take every value in the interval $[D_i, T_i]$. Observe that the particular case $a_1 \cdots a_n = 0 \cdots 0$ is always a solution, which confirm the previous result that both 0 and $H$ are always DIT.\\

If the value returned by the Chinese Remainder Theorem with a particular set of $a_i$ values is called $t_{idle} (a_1, \cdots, a_n)$\footnote{If the values are such that there are no solution, we set $t_{idle}$ to $\infty$}, the first DIT is given by $$t_d = \operatorname*{min}_{a_i \in [D_i, T_i], \; i = 1 \cdots n} t_{idle} (a_1, \cdots, a_n)$$ which require to consider a number of combinations which is exponential in the number of tasks.

\subsection{Feasibility test}
\label{sct:ditsynchfeastest}

\begin{theorem}
 Let $t_1$ be a DIT, it is sufficient to check the DBF condition at job deadlines in the interval $[0, t_1]$ to determine feasibility.
\end{theorem}

\begin{proof}
Let $t_1$ be any DIT of a synchronous task set such that $\forall t \leq t_1 : \dbf{t} \leq t$. We want to show that $\forall t > t_1 : \dbf{t} \leq t$.\\

As we are in the synchronous case, $t=0$ is a critical instant, which mean we have the earliest next job deadline for each task. Thus the DBF increase faster than in any other configuration of arrival times.\\

A DIT for some task set is similar (w.r.t. the increase of the DBF) to the initial time of the same system in the asynchronous case. In other words, after the DIT, the increase of the DBF will be slower than it was at the initial time. Which gives us, with $t_1$ being the DIT:
$$\forall t > t_1 : \dbf{t} \leq \dbf{t_1} + \dbf{t-t_1}$$

~\\

We now prove by induction that $\dbf{t-t_1} \leq t - t_1$.\\

\emph{Initial case} : We consider $t = t_1 + 1$. Thus, $\dbf{t-t_1} = \dbf{t_1 + 1 - t_1} = \dbf{1}$. As $1 \leq t_1$, we know that $\dbf{1} \leq 1$.\\

\emph{Inductive case} : We consider any $t > t_1 + 1$ and we suppose that $\forall t' < t : \dbf{t'} \leq t'$. Then, we have $\dbf{t - t_1} \leq t - t_1$ as $t - t_1 < t$.\\

And thus we have that $\dbf{t-t_1} \leq t - t_1$. As we also have $\dbf{t_1} \leq t_1$, the previous inequality becomes
$$\forall t > t_1 : \dbf{t} \leq \dbf{t_1} + \dbf{t-t_1} \leq t_1 + t - t_1 = t$$
$$\iff \forall t > t_1 : \dbf{t} \leq t$$
\end{proof}

If there exists a DIT earlier than $H$, it can be used to reduce the interval used in the DBF feasibility test.

\subsection{Results in the asynchronous case}

\begin{definition}
The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the arrival of at least one job of each task.
\end{definition}

Note that the first periodic DIT will be the first DIT in the synchronous case.\\

In the synchronous case, $t = H$ is always a DIT. This is no longer true in the asynchronous case. In fact, the first periodic DIT could happen at a time $t_d > H$, or there could be no first periodic DIT at all, as seen in Fig. \ref{fig:asyncNoDit}.

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.75\textwidth]{figs/dit_asynchronousNoDit.png}
\caption{An asynchronous task system with no DITs after $t=0$}
\label{fig:asyncNoDit}
\end{center}
\end{figure}

\subsubsection{Existence and value}

The first periodic DIT cannot happen at a time $t > O_{max} + H$, or else it would have happened previously.\\

Similarly to the synchronous case, the problem of existence of the first periodic DIT can be written as a system of modular equation:
$$
\begin{array}{l}
	\exists ? \; t_d \; s.t. \; \forall i \; :\\
	\left\{
		\begin{array}{l}
		t_d > O_i \\
		t_d - O_i \equiv a_i \; (mod \; T_i) \\
		a_i \in [D_i, T_i]
	\end{array}
\right.
\end{array}
$$
which can, again, be solved by testing every combination of the $a_i$ and solving the corresponding equation with the Generalized Chinese Remainder Theorem. If a solution $t < O_{max}$ is found, recall that $t + k \, H, k \in \mathbb{N}$ is also a solution. Note that this time, it is possible for the system to not have any solution (e.g. Fig \ref{fig:asyncNoDit}).

\subsubsection{Feasibility test}

To understand feasibility tests in the asynchronous case, one must first understand how an asynchronous system behaves under, for example, EDF.\\

\begin{figure}[h]
$$
\begin{array}{r|c|c|c|c|l}
	 & \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
	 & \text{period} & \text{period} & \text{period} & \text{period} & \\
	\hline
	t & 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
\end{array}
$$
\begin{center}
\caption{Behavior of an asynchronous system under EDF. The value of $t$ indicates the time at which each period starts}
\label{fig:asyncBehavior}
\end{center}
\end{figure}

As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the \emph{incomplete period}, where all tasks are not in the system. Then, after $O_{max}$ time units, every tasks is in the system and the \emph{transitive period} begins. Then, after $O_{max} + H$ time units, the system is faced with the same pattern of arrival as in $O_{max}$. However, because in $O_{max} + H$ every task is in the system and in $O_{max}$ some were missing, the state of the system will be different. The \emph{stationary period} then begins. It is only after $O_{max} + 2H$ time units that the system comes back into a state in which it was before.\\

For this reason, as explained in \cite{leung1982complexity}, most feasibility test for asynchronous task system (e.g. the DBF test) are restricted to the interval $[0, O_{max} + 2H]$, which has an exponential length in the number of tasks.\\

However, using DIT, we have the following property:

\begin{theorem}
Let $t_d$ be the first periodic DIT of an asynchronous system $\tau$ (supposing it exists). Then it is sufficient to check the DBF test in the interval $[0, t_d + H]$
\end{theorem}

\begin{proof}
???\\

(basically at $t_d + H$ we know that the behavior will be the same as in $t_d$)
\end{proof}

\section{Simulation}

As was shown previously, the DBF condition must be true on all instant to prove that a system is feasible. It is necessary and sufficient to check only instants where a deadline occurs, and it is also necessary and sufficient to check only instants before the hyper-period, the end of the first busy period (for constrained system only), or the first DIT. While the test itself will be shorter if the smallest of those values is used as an upper limit, the time needed to compute the value must be taken into consideration as well.\\

The DBF feasibility test was simulated on a set of synchronous system with constrained deadline. For all of those systems, the value of the hyper-period, the end of the first busy period and the first DIT is computed. Then the DBF feasibility test is applied using those upper limits. The times each methods took to complete are compared.

\subsection{Implementation model}

\subsubsection{Tasks system generation}

The method used to generate the system consisted of
\begin{itemize}
	\item Generating the $U_i$ with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
	\begin{itemize}
		\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
		\item $n$ (number of tasks) chosen uniformly between 1 and 4
	\end{itemize}
	\item Generating the $T_i$ from a list of divisors (see \ref{sct:simuRemarks}). This also gives the $C_i = \lfloor U_i \, T_i \rfloor$
	\item $O_i$ (...)
	\item And finally, choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i)$, where the value of $e$ is discussed in \ref{sct:simuRemarks}.
\end{itemize}

\subsubsection{General remarks}
\label{sct:simuRemarks}
\begin{itemize}
	\item The interval used for the generation of $D_i$ can be explained by looking at the final formula for the DIT $$t_d = \operatorname*{min}_{a_i \in [D_i, T_i], \; i = 1 \cdots n} t_{idle} (a_1, \cdots, a_n)$$ The necessary number of combination of $a_i$ values to considerr is equal to the cardinality of $[D_1, T_1] \times [D_2, T_2] \times \cdots \times [D_n, T_n]$, which gives an exponential time in the number of tasks. This constraint aims to allow the DIT algorithm to terminate in an acceptable time but it also gives it a considerable advantage.
	\item The $T_i$ are not generated uniformly, but from a list of divisors of 554400\footnote{LCM of $2^5$, $3^2$, $5^2$, 7 and 11}. This prevents the value of the hyper-period from growing exponentially. Similarly, this is giving the hyper-period method an advantage.
	\item During the DBF test, the deadline are considered chronologically. The order is not important for feasible tasks set, but can change the duration of the test for unfeasible task set (where the DBF test can stop when it finds an instant where the test does not hold).
\end{itemize}

\subsubsection{Source code}

Am I allowed to make it available on GitHub? License problem with ECE?

\subsection{Results}

Fig. \ref{fig:simuTextResult} gives us the precise timing with a value of $e = 5$. While the DIT and the hyper-period methods achieve similar results, the busy period method is clearly ahead. This can be explained by the relative simplicity of its algorithm.\\

Looking more closely at the values, the trade-off offered by the DIT method compared to the hyper-period method becomes apparent. While the preprocessing time is longer for the DIT, the interval to consider for the DBF test is greatly reduced.\\

\begin{figure}[h]
\begin{center}

\begin{lstlisting}[language=]
== Test Results (on 1000 tasks system)
	Algorithms performance (upper limit computation + dbf test)
		Time with busy period: 0.02 + 0.01  =  0.03 s
		Time with DIT: 0.84 + 0.83  =  1.67 s
		Time with hyperT: 0.02 + 1.64  =  1.66 s
	Feasible? 432 , or about 43 %
\end{lstlisting}

\caption{Comparison of performance of different upper limit for the DBF feasibility test} with $e=5$
\label{fig:simuTextResult}
\end{center}
\end{figure}

~\\

Fig. \ref{fig:simuGraphE} shows the influence of the $e$ parameter, which describes the restriction imposed on the deadline parameter. Observe the exponential growth to the left. While we could think that the hyper-period curve should not be affected by $e$, this figure shows otherwise. This is explained by the fact that higher value of $e$ means more feasibility, and as was shown previously more feasibility means longer feasibility tests.

\begin{figure}[h]
\begin{center}

\includegraphics[width=0.75\textwidth]{dit-simulation/plots/001_137389818886_princess.png}

\caption{Comparison of performance for different values of $e$. The plain line represent the total time, while the dotted line represent only the upper limit computation time.}
\label{fig:simuGraphE}
\end{center}
\end{figure}

\newpage
\appendix

\huge APPENDIX
\normalsize

\section{Generalized Chinese Remainder Theorem}
\label{sct:appCRT}

First let us recall the Chinese Remainder Theorem, proven in \cite{leiserson2001introduction}.

\begin{theorem}
 \textbf{Chinese Remainder Theorem} Suppose $M_1, \cdots, M_n$ are positive integers which are pairwise co-prime. Then, for any given sequence of integers $a_1, \cdots, a_n$ there exists one integer $x$ modulo $M = M_1 \cdots M_n$ solving the following system
 $$
 \left\{
	\begin{array}{llcl}
		x \equiv a_1 \; (mod \; M_1) \\
		x \equiv a_2 \; (mod \; M_2) \\
		\vdots \\
		x \equiv a_n \; (mod \; M_n)
	\end{array}
\right.
 $$

This value is given by
$$x = \sum_{i=1}^{n} a_i \frac{M}{M_i} \left[ \frac{M}{M_i} \right]_{M_i}^{-1}$$
where $[a]^{-1}_{b}$ is the modular multiplicative inverse of $a$ (mod $b$)
\end{theorem}

We can see that a requirement of the theorem is that the values of $M_i$ need to be pairwise co-prime. When this is not the case, the system is not guaranteed to have a solution. Indeed, a previous result in \cite{leiserson2001introduction} is that the system has one solution modulo $M$ if and only if $\forall \; i,j \; s.t. \; a_i \equiv a_j \; (mod \; gcd(M_i, M_j) )$ (which is clearly true when all the $M_i$ are pairwise co-prime).\\

A method to find this solution, which we will call the Generalized Chinese Remainder Theorem, is given in \cite{mathNonPairwiseCoprime}. The method consists of transforming the system into an equivalent one where the moduli are pairwise co-prime, which we can then solve using the Chinese Remainder Theorem. Another method would be the method of successive substitution.

\newpage
\nocite{*}
\bibliographystyle{plain}
\bibliography{stateoftheart}

\end{document}

### 2013-07-18 slides/dbf_dit_pres.tex
First commit

--- 2013-07-18 dit-paper.tex
@@
-\documentclass[a4paper,10pt]{article}
+\documentclass{beamer}
+\mode<presentation>
+{
+    \usetheme{Warsaw}      % or try Darmstadt, Madrid, Warsaw, ...
+    \usecolortheme{beaver} % or try albatross, beaver, crane, ...
+    \usefonttheme{default}  % or try serif, structurebold, ...
+    \setbeamertemplate{navigation symbols}{}
+    \setbeamertemplate{caption}[numbered]
+    \setbeamertemplate{footline}[frame number]
+}
 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{charter}
+\usepackage[english]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage{pgfpages}
 \usepackage{color}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage[utf8]{inputenc}
 \usepackage{listings}
-\usepackage{url}
 
@@
 
-\lstset{
-language=Python,
-basicstyle=\footnotesize\fontfamily{pcr},
-backgroundcolor=\color{grey},
-numbers=left,
-numberstyle=\tiny,
-numbersep=5pt,
-showstringspaces=false,
-tabsize=2,
-breaklines=true
-}
-
-\setlength{\parindent}{0pt}
-
-%opening
-\sloppy
-
 \newcommand{\dbf}[1]{\operatorname{dbf}(#1)}
 
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}{Theorem}
-
-\newtheorem*{remarks}{Remarks}
+\title {Using DIT in the DBF feasibility test}
+\author {Thomas Chapeaux}
+\institute {ECE Paris}
+\date {July 2013}
 
@@
 
-\title{Using DIT to simplify the DBF feasibility test}
-\author{Thomas Chapeaux \\ ~ \\ \emph{Supervisor} \\ Laurent George, ECE Paris \\ ~ \\ \emph{Thanks to} \\ Paul Rodriguez}
+\begin{frame}
+    \titlepage
+\end{frame}
 
-\date{July 2013}
+\begin{frame}{Outline}
+    \tableofcontents
+\end{frame}
 
-\maketitle
+\section{Demand Bound Function (DBF)}
 
-\tableofcontents
+\begin{frame}{Outline}
+    \tableofcontents[currentsection]
+\end{frame}
 
-\newpage
+\subsection{Definition}
 
-\section{Real-Time Systems}
-
-$\tau = \{ \tau_1, \cdots, \tau_n \}$
-
-$\tau_i = (O_i, C_i, D_i, T_i)$
-
-$H = LCM(T_i)$
-
-\section{The demand-bound function feasibility test}
-\label{sct:DBF}
-
-\subsection{Definition of the demand-bound function}
-
+\begin{frame}{Definition}
     \begin{definition}
- The \textbf{demand-bound function (DBF)} (\cite{baruah1999generalized} and \cite{baruah1990algorithms}), defined for a task set $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\
-
- Mathematically,
- $$\dbf{t} = \max_{\{t_1, t_2 \; : \; t_2 - t_1 = t\}} \sum_{i=1}^n C_i \; h_i(t_1, t_2)$$
- where $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
+    The \textbf{demand-bound function (DBF)}, defined for a task set $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.
     \end{definition}
 
-As the synchronous arrival pattern is known to be the worst case, in that particular case we can only consider the interval $[0, t]$.
-In an asynchronous arrival pattern, it is sufficient to check only intervals where $t_1 < O_{max} + H$, as the values will be periodic after it.\\
+    In the synchronous case, a closed form expression is $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$
+\end{frame}
 
-In the sequel a closed form expression of the DBF is given in the synchronous case.
-Intuitively, in that case, it will be a step-function whose increase will occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\
+\subsection{Feasibility test}
 
-Starting from the definition, it remains to find a method to compute the values of $h_i(t)$.
-In the synchronous case, these values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} : k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc.
-The maximal value of $k$ can be explicitly stated by rearranging the condition:
-$$k T_i + D_i \leq t$$
-$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
-The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$.
-If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e.
-$h_i(t) = 0$.
-Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\
-
-This is generalized by the final definition of $h_i(t)$: $$h_i(t) = \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \}$$
-
-With this result, a closed form of the DBF function in the synchronous case is obtained $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$
-
-\subsection{Feasibility test for EDF}
-
-In \cite{baruah1990algorithms}, the authors show that the DBF can be used to derive the following feasibility condition for EDF\footnote{And thus, EDF being optimal, for all optimal schedulers} on sporadic task sets.
-An adapted proof is given here.
-
+\begin{frame}{Feasibility test}
     \begin{theorem}
@@
 
-\begin{proof}
-	We first show that the condition is \emph{necessary}.
-Indeed, if the condition is not fulfilled (i.e.
-$\exists t^* \; s.t.
-\; \dbf{t^*} > t^*$), it means that in an interval of $t^*$ time units, the total execution time of the jobs whose arrival and deadline occurs within the interval is superior to $t^*$.
-The system is thus not feasible if the condition is not fulfilled.\\
+    \begin{itemize}
+      \item In the synchronous case, it is sufficient to consider intervals of the form $[0, t_d]$, where the $t_d$ correspond to job deadlines in the interval $\left[ D_{min}, H \right]$
+      \item For constrained deadline set, it is sufficient to consider intervals with $t_d \leq L$
+    \end{itemize}
+\end{frame}
 
-	Now, we prove that the condition is \emph{sufficient}. For that, suppose that $\dbf{t} \leq t \; \forall t$.\\
+\section{Definitive Idle Time (DIT)}
 
-	...
-(The idea is to look at each interval beginning at an arrival time and finishing at a deadline (not necessarily of the same job).
-Then we can prove that if there is only those two tasks, they can execute.
-If there are other tasks, we can look at a greater interval in which they can all execute)
+\begin{frame}{Outline}
+    \tableofcontents[currentsection]
+\end{frame}
 
-\end{proof}
+\subsection{Definition}
 
-Furthermore, the authors show that in the synchronous case, it is sufficient to consider intervals of the form $[0, t_d]$, where the $t_d$ correspond to job deadlines (i.e.
-the increases the demand-bound function) in the interval $\left[ D_{min}, H \right]$.\\
-
-For constrained deadline set, it is sufficient to consider intervals $[0, t_d]$ with $t_d \leq L$, where $L$ is the first busy period and is the solution to the following recursive equation $$L = \sum_{i=1}^{n} \lceil \frac{L}{T_i} \rceil C_i$$ which can be computed through fixed-point iteration $$w_0 = \sum_{i=1}^{n} C_i$$ $$w_{k+1} = \sum_{i=1}^{n} \lceil \frac{w_k}{T_i} \rceil C_i$$
-
-Even so, this test requires to check a number of instant which is exponential in the number of tasks, making the general determination of feasibility a NP-hard problem.
-
-\section{Definitive idle time approach}
-\label{sct:DIT}
-
+\begin{frame}{Definition}
     \begin{definition}
@@
 
-Remarks
     \begin{itemize}
       \item If the system is feasible, every DIT is an idle time.
-  \item Contrary to the idle times, the DITs are independent of the scheduling or the execution times of the jobs.
+      \item The DITs are independent of the scheduling or the execution times of the jobs.
       \item $t=0$ is always a DIT.
-  \item There are no DITs strictly after the first arrival of an arbitrary deadline task. In the following we only consider the constrained deadline case.
+      \item There are no DITs strictly after the first arrival of an arbitrary deadline task.
     \end{itemize}
+\end{frame}
 
- An example of the DITs of a system is given in Fig. \ref{fig:ditExample}.
+\subsection{Synchronous case}
 
- \begin{figure}[h]
-\begin{center}
-\includegraphics[width=\textwidth]{figs/dit_example.png}
-\caption{The block of colors represents the arrival time and deadline of a job. DITs are represented by a green line below}
-\label{fig:ditExample}
-\end{center}
-\end{figure}
+\begin{frame}{Outline}
+    \tableofcontents[currentsection, currentsubsection]
+\end{frame}
 
-While the definition is applicable to both synchronous and asynchronous tasks system, the following only consider the synchronous case (which is the worst-case for non-concrete tasks).
-The difficulties arising with asynchronous tasks are described in a later section.\\
-
-In the synchronous case, $t=0$ and $t=H$ are DITs but there might be others in-between. The following notion is thus defined:
-
+\begin{frame}{Feasibility test}
     \begin{definition}
@@
 
-If the first DIT is $H$, then the only DITs of the system are multiple of $H$ as the occurrence of DITs is periodic.\\
-
-The following section explains the methods to determine the value of the first DIT.
-Then section \ref{sct:ditsynchfeastest} will explain a method to reduce the complexity of the DBF feasibility test if the first DIT occurs before $H$.
-
-\subsection{Existence and value}
-
-In synchronous systems, $H$ is always a DIT, so the first DIT $t_d$ exists and is such that $t_d \leq H$.
-In the constrained deadline case ($D_i \leq T_i \; \forall i$), it is possible that other DITs occur before it, in which case $t_d < H$.\\
-
-The problem of the existence of a DIT can be written with modular equations as
-$$
-\exists ? \; t_d \; s.t. \; \forall i : \exists a_i \in [D_i, T_i] \; s.t. \; t_d \equiv a_i \; (mod \; T_i) \\
-$$
-
-For fixed values of $a_i$, this is a case of the Generalized Chinese Remainder Theorem (see Appendix \ref{sct:appCRT}).
-However, in our case, each $a_i$ can take every value in the interval $[D_i, T_i]$.
-Observe that the particular case $a_1 \cdots a_n = 0 \cdots 0$ is always a solution, which confirm the previous result that both 0 and $H$ are always DIT.\\
-
-If the value returned by the Chinese Remainder Theorem with a particular set of $a_i$ values is called $t_{idle} (a_1, \cdots, a_n)$\footnote{If the values are such that there are no solution, we set $t_{idle}$ to $\infty$}, the first DIT is given by $$t_d = \operatorname*{min}_{a_i \in [D_i, T_i], \; i = 1 \cdots n} t_{idle} (a_1, \cdots, a_n)$$ which require to consider a number of combinations which is exponential in the number of tasks.
-
-\subsection{Feasibility test}
-\label{sct:ditsynchfeastest}
+    We have
+    $$t_d = \operatorname*{min}_{a_i \in [D_i, T_i], \; i = 1 \cdots n} t_{idle} (a_1, \cdots, a_n)$$
+    with
+    $$ t_{idle}(a_1, \cdots, a_n) \equiv a_i (mod \; T_i) \; \forall i $$
+    which can be solved with a generalized form of the Chinese Remainder Theorem
 
@@
     \end{theorem}
+\end{frame}
 
-\begin{proof}
-Let $t_1$ be any DIT of a synchronous task set such that $\forall t \leq t_1 : \dbf{t} \leq t$. We want to show that $\forall t > t_1 : \dbf{t} \leq t$.\\
+\subsection{Asynchronous case}
 
-As we are in the synchronous case, $t=0$ is a critical instant, which mean we have the earliest next job deadline for each task.
-Thus the DBF increase faster than in any other configuration of arrival times.\\
+\begin{frame}{Outline}
+    \tableofcontents[currentsection, currentsubsection]
+\end{frame}
 
-A DIT for some task set is similar (w.r.t.
-the increase of the DBF) to the initial time of the same system in the asynchronous case.
-In other words, after the DIT, the increase of the DBF will be slower than it was at the initial time.
-Which gives us, with $t_1$ being the DIT:
-$$\forall t > t_1 : \dbf{t} \leq \dbf{t_1} + \dbf{t-t_1}$$
-
-~\\
-
-We now prove by induction that $\dbf{t-t_1} \leq t - t_1$.\\
-
-\emph{Initial case} : We consider $t = t_1 + 1$. Thus, $\dbf{t-t_1} = \dbf{t_1 + 1 - t_1} = \dbf{1}$. As $1 \leq t_1$, we know that $\dbf{1} \leq 1$.\\
-
-\emph{Inductive case} : We consider any $t > t_1 + 1$ and we suppose that $\forall t' < t : \dbf{t'} \leq t'$. Then, we have $\dbf{t - t_1} \leq t - t_1$ as $t - t_1 < t$.\\
-
-And thus we have that $\dbf{t-t_1} \leq t - t_1$. As we also have $\dbf{t_1} \leq t_1$, the previous inequality becomes
-$$\forall t > t_1 : \dbf{t} \leq \dbf{t_1} + \dbf{t-t_1} \leq t_1 + t - t_1 = t$$
-$$\iff \forall t > t_1 : \dbf{t} \leq t$$
-\end{proof}
-
-If there exists a DIT earlier than $H$, it can be used to reduce the interval used in the DBF feasibility test.
-
-\subsection{Results in the asynchronous case}
-
+\begin{frame}{First periodic DIT}
     \begin{definition}
@@
 
-Note that the first periodic DIT will be the first DIT in the synchronous case.\\
-
-In the synchronous case, $t = H$ is always a DIT.
-This is no longer true in the asynchronous case.
-In fact, the first periodic DIT could happen at a time $t_d > H$, or there could be no first periodic DIT at all, as seen in Fig.
-\ref{fig:asyncNoDit}.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.75\textwidth]{figs/dit_asynchronousNoDit.png}
-\caption{An asynchronous task system with no DITs after $t=0$}
-\label{fig:asyncNoDit}
-\end{center}
-\end{figure}
-
-\subsubsection{Existence and value}
-
-The first periodic DIT cannot happen at a time $t > O_{max} + H$, or else it would have happened previously.\\
-
-Similarly to the synchronous case, the problem of existence of the first periodic DIT can be written as a system of modular equation:
+    Its value is given by the system of equation
     $$
-\begin{array}{l}
-	\exists ? \; t_d \; s.t. \; \forall i \; :\\
       \left\{
@@
       \right.
-\end{array}
     $$
-which can, again, be solved by testing every combination of the $a_i$ and solving the corresponding equation with the Generalized Chinese Remainder Theorem.
-If a solution $t < O_{max}$ is found, recall that $t + k \, H, k \in \mathbb{N}$ is also a solution.
-Note that this time, it is possible for the system to not have any solution (e.g.
-Fig \ref{fig:asyncNoDit}).
+    which require to test every possible combination of the $a_i$
+\end{frame}
 
-\subsubsection{Feasibility test}
+\begin{frame}{Feasibility Test}
 
-To understand feasibility tests in the asynchronous case, one must first understand how an asynchronous system behaves under, for example, EDF.\\
-
-\begin{figure}[h]
     $$
@@
     $$
-\begin{center}
-\caption{Behavior of an asynchronous system under EDF. The value of $t$ indicates the time at which each period starts}
-\label{fig:asyncBehavior}
-\end{center}
-\end{figure}
-
-As shown in Fig.
-\ref{fig:asyncBehavior}, the system begins in the \emph{incomplete period}, where all tasks are not in the system.
-Then, after $O_{max}$ time units, every tasks is in the system and the \emph{transitive period} begins.
-Then, after $O_{max} + H$ time units, the system is faced with the same pattern of arrival as in $O_{max}$.
-However, because in $O_{max} + H$ every task is in the system and in $O_{max}$ some were missing, the state of the system will be different.
-The \emph{stationary period} then begins.
-It is only after $O_{max} + 2H$ time units that the system comes back into a state in which it was before.\\
-
-For this reason, as explained in \cite{leung1982complexity}, most feasibility test for asynchronous task system (e.g.
-the DBF test) are restricted to the interval $[0, O_{max} + 2H]$, which has an exponential length in the number of tasks.\\
-
-However, using DIT, we have the following property:
 
@@
     \end{theorem}
-
-\begin{proof}
-???\\
-
-(basically at $t_d + H$ we know that the behavior will be the same as in $t_d$)
-\end{proof}
+\end{frame}
 
@@
 
-As was shown previously, the DBF condition must be true on all instant to prove that a system is feasible.
-It is necessary and sufficient to check only instants where a deadline occurs, and it is also necessary and sufficient to check only instants before the hyper-period, the end of the first busy period (for constrained system only), or the first DIT.
-While the test itself will be shorter if the smallest of those values is used as an upper limit, the time needed to compute the value must be taken into consideration as well.\\
+\begin{frame}{Outline}
+    \tableofcontents[currentsection]
+\end{frame}
 
-The DBF feasibility test was simulated on a set of synchronous system with constrained deadline.
-For all of those systems, the value of the hyper-period, the end of the first busy period and the first DIT is computed.
-Then the DBF feasibility test is applied using those upper limits.
-The times each methods took to complete are compared.
+\subsection{Model}
 
-\subsection{Implementation model}
+\begin{frame}{Simulation}
+    The simulation consisted of
+    \begin{itemize}
+      \item Generating $N$ tasks system
+      \item Computing
+        \begin{itemize}
+          \item The busy period
+          \item The first periodic DIT
+          \item The hyper-period (LCM of periods)
+        \end{itemize}
+      \item Applying three DBF tests using each of those values as upper limit (synchr case only)
+    \end{itemize}
+\end{frame}
 
-\subsubsection{Tasks system generation}
+\subsection{Implementation}
 
-The method used to generate the system consisted of
+\begin{frame}{Task system generation}
     \begin{itemize}
-	\item Generating the $U_i$ with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
+      \item $U_i$: \texttt{UUniSort} algorithm, with parameters
       \begin{itemize}
@@
       \end{itemize}
-	\item Generating the $T_i$ from a list of divisors (see \ref{sct:simuRemarks}). This also gives the $C_i = \lfloor U_i \, T_i \rfloor$
-	\item $O_i$ (...)
-	\item And finally, choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i)$, where the value of $e$ is discussed in \ref{sct:simuRemarks}.
+      \item $T_i$: from a list of divisors. This also gives the $    C_i = \lfloor U_i \, T_i \rfloor$
+      \item $D_i$: uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i)$.
     \end{itemize}
-
-\subsubsection{General remarks}
-\label{sct:simuRemarks}
-\begin{itemize}
-	\item The interval used for the generation of $D_i$ can be explained by looking at the final formula for the DIT $$t_d = \operatorname*{min}_{a_i \in [D_i, T_i], \; i = 1 \cdots n} t_{idle} (a_1, \cdots, a_n)$$ The necessary number of combination of $a_i$ values to considerr is equal to the cardinality of $[D_1, T_1] \times [D_2, T_2] \times \cdots \times [D_n, T_n]$, which gives an exponential time in the number of tasks.
-This constraint aims to allow the DIT algorithm to terminate in an acceptable time but it also gives it a considerable advantage.
-	\item The $T_i$ are not generated uniformly, but from a list of divisors of 554400\footnote{LCM of $2^5$, $3^2$, $5^2$, 7 and 11}.
-This prevents the value of the hyper-period from growing exponentially.
-Similarly, this is giving the hyper-period method an advantage.
-	\item During the DBF test, the deadline are considered chronologically.
-The order is not important for feasible tasks set, but can change the duration of the test for unfeasible task set (where the DBF test can stop when it finds an instant where the test does not hold).
-\end{itemize}
-
-\subsubsection{Source code}
-
-Am I allowed to make it available on GitHub? License problem with ECE?
+\end{frame}
 
@@
 
-Fig.
-\ref{fig:simuTextResult} gives us the precise timing with a value of $e = 5$.
-While the DIT and the hyper-period methods achieve similar results, the busy period method is clearly ahead.
-This can be explained by the relative simplicity of its algorithm.\\
+\begin{frame}{Results (I)}
+    \begin{block}{Results with $e=4$ and $N=1000$}
+    Algorithms performance (upper limit computation + dbf test)
+    \begin{itemize}
+    \item Time with busy period: 0.02 + 0.01  =  0.03 s
+    \item Time with DIT: 0.84 + 0.83  =  1.67 s
+    \item Time with hyperT: 0.02 + 1.64  =  1.66 s
+    \end{itemize}
+    \end{block}
 
-Looking more closely at the values, the trade-off offered by the DIT method compared to the hyper-period method becomes apparent.
-While the preprocessing time is longer for the DIT, the interval to consider for the DBF test is greatly reduced.\\
+    \begin{itemize}
+      \item Busy period is clearly ahead
+      \item DIT seems to offer an interesting trade-off to the hyperT method
+    \end{itemize}
+\end{frame}
 
-\begin{figure}[h]
+\begin{frame}{Results (II)}
     \begin{center}
-
-\begin{lstlisting}[language=]
-== Test Results (on 1000 tasks system)
-	Algorithms performance (upper limit computation + dbf test)
-		Time with busy period: 0.02 + 0.01  =  0.03 s
-		Time with DIT: 0.84 + 0.83  =  1.67 s
-		Time with hyperT: 0.02 + 1.64  =  1.66 s
-	Feasible? 432 , or about 43 %
-\end{lstlisting}
-
-\caption{Comparison of performance of different upper limit for the DBF feasibility test} with $e=5$
-\label{fig:simuTextResult}
+      \includegraphics[width=0.9\textwidth]{../dit-simulation/plots/001_137389818886_princess.png}
     \end{center}
-\end{figure}
-
-~\\
-
-Fig.
-\ref{fig:simuGraphE} shows the influence of the $e$ parameter, which describes the restriction imposed on the deadline parameter.
-Observe the exponential growth to the left.
-While we could think that the hyper-period curve should not be affected by $e$, this figure shows otherwise.
-This is explained by the fact that higher value of $e$ means more feasibility, and as was shown previously more feasibility means longer feasibility tests.
-
-\begin{figure}[h]
-\begin{center}
-
-\includegraphics[width=0.75\textwidth]{dit-simulation/plots/001_137389818886_princess.png}
-
-\caption{Comparison of performance for different values of $e$. The plain line represent the total time, while the dotted line represent only the upper limit computation time.}
-\label{fig:simuGraphE}
-\end{center}
-\end{figure}
-
-\newpage
-\appendix
-
-\huge APPENDIX
-\normalsize
-
-\section{Generalized Chinese Remainder Theorem}
-\label{sct:appCRT}
-
-First let us recall the Chinese Remainder Theorem, proven in \cite{leiserson2001introduction}.
-
-\begin{theorem}
- \textbf{Chinese Remainder Theorem} Suppose $M_1, \cdots, M_n$ are positive integers which are pairwise co-prime.
-Then, for any given sequence of integers $a_1, \cdots, a_n$ there exists one integer $x$ modulo $M = M_1 \cdots M_n$ solving the following system
- $$
- \left\{
-	\begin{array}{llcl}
-		x \equiv a_1 \; (mod \; M_1) \\
-		x \equiv a_2 \; (mod \; M_2) \\
-		\vdots \\
-		x \equiv a_n \; (mod \; M_n)
-	\end{array}
-\right.
- $$
-
-This value is given by
-$$x = \sum_{i=1}^{n} a_i \frac{M}{M_i} \left[ \frac{M}{M_i} \right]_{M_i}^{-1}$$
-where $[a]^{-1}_{b}$ is the modular multiplicative inverse of $a$ (mod $b$)
-\end{theorem}
-
-We can see that a requirement of the theorem is that the values of $M_i$ need to be pairwise co-prime.
-When this is not the case, the system is not guaranteed to have a solution.
-Indeed, a previous result in \cite{leiserson2001introduction} is that the system has one solution modulo $M$ if and only if $\forall \; i,j \; s.t.
-\; a_i \equiv a_j \; (mod \; gcd(M_i, M_j) )$ (which is clearly true when all the $M_i$ are pairwise co-prime).\\
-
-A method to find this solution, which we will call the Generalized Chinese Remainder Theorem, is given in \cite{mathNonPairwiseCoprime}.
-The method consists of transforming the system into an equivalent one where the moduli are pairwise co-prime, which we can then solve using the Chinese Remainder Theorem.
-Another method would be the method of successive substitution.
-
-\newpage
-\nocite{*}
-\bibliographystyle{plain}
-\bibliography{stateoftheart}
+\end{frame}
 

### 2013-07-18 dit-paper.tex
Fixed broken links

@@
 Even so, this test requires to check a number of instant which is exponential in the number of tasks, making the general determination of feasibility a NP-hard problem.
+
+\section{C-space}
+When developing an application, it often happens that the platform is not known in advance, in which case the value of the $C_i$ are not known.
+Then, it can be useful to have a description of the possible values of the $C_i$ for which the system would be feasible.
+
+\subsection{Definition}
+
+The authors of \cite{george2009characterization} give the following definition of the C-space:
+\begin{definition}
+For a given task system $\tau$ in which the $C_i$ are not known, the \textbf{C-space} is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_n\}$ in the C-space, $\tau$ is feasible.
+\end{definition}
+
+Thus, with a good description of the C-space, it is easy to check if a given vector of $C_i$ value (given e.g.
+when deploying the application on a specific platform) allows the system to be scheduled or not.
+
+\subsection{Description using DBF}
+
+A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing bounds of the convex hull of the admissible points.
+In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
+
+For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are
+$$\dbf{t} = \sum_{i=1}^{n} h_i(t) C_i \leq t \; \forall t$$
+Note that for a given $t$, we have that the $h_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus effectively linear.\\
+
+While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.
+As was shown previously, the equations corresponding to job deadlines are necessary and sufficient to test the feasibility, so only those can be considered.
+In \cite{lipariaverage}, the authors use the simplex algorithms to further reduce the number of equation to consider.\\
 
@@
 
-\includegraphics[width=0.75\textwidth]{dit-simulation/plots/001_137389818886_princess.png}
+\includegraphics[width=0.75\textwidth]{figs/001_137389818886_princess.png}
 
@@
 \bibliographystyle{plain}
-\bibliography{stateoftheart}
+\bibliography{dit-paper}
 

### 2013-07-18 dit-paper.tex
Added details on removing redundancy Notation consistency Made a title smaller (to save internet trees)

@@
 
-\section{The demand-bound function feasibility test}
+\section{The DBF feasibility test}
 \label{sct:DBF}
@@
 
-Starting from the definition, it remains to find a method to compute the values of $h_i(t)$.
+Starting from the definition, it remains to find a method to compute the values of $h_i(0, t)$ (noted $h_i(t)$ from now on).
 In the synchronous case, these values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} : k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc.
@@
 
-While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.
-As was shown previously, the equations corresponding to job deadlines are necessary and sufficient to test the feasibility, so only those can be considered.
-In \cite{lipariaverage}, the authors use the simplex algorithms to further reduce the number of equation to consider.\\
+\subsection{Removing redundancy}
+
+While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.\\
+
+As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered.
+For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used.
+In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.
+
+In \cite{lipariaverage}, the authors use the simplex algorithm to further reduce the number of equation to consider.\\
 

### 2013-07-18 dit-paper.tex
Removes trailing \newline

@@
 For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used.
-In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.
+In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.\\
 
-In \cite{lipariaverage}, the authors use the simplex algorithm to further reduce the number of equation to consider.\\
+In \cite{lipariaverage}, the authors use the simplex algorithm to further reduce the number of equation to consider.
 

### 2013-07-19 dit-paper.tex
fixed multi-cite and dbf t_1 t_2 sum formula

@@
 \begin{definition}
- The \textbf{demand-bound function (DBF)} (\cite{baruah1999generalized} and \cite{baruah1990algorithms}), defined for a task set $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\
+ The \textbf{demand-bound function (DBF)}
+ \cite{baruah1999generalized, baruah1990algorithms} defined for a task set
+ $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\
 
  Mathematically,
- $$\dbf{t} = \max_{\{t_1, t_2 \; : \; t_2 - t_1 = t\}} \sum_{i=1}^n C_i \; h_i(t_1, t_2)$$
- where $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
+ $$\dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
+ \leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot h_i(t_1, t_2)$$ where
+ $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
 \end{definition}

### 2013-07-19 dit-paper.tex
minor changes

@@
 
+\begin{definition}
+	A system is \textbf{synchronous} if all its tasks have no offset, and
+	\textbf{asynchronous} otherwise.
+\end{definition}
+
 \section{The DBF feasibility test}
@@
 
-As the synchronous arrival pattern is known to be the worst case, in that particular case we can only consider the interval $[0, t]$.
-In an asynchronous arrival pattern, it is sufficient to check only intervals where $t_1 < O_{max} + H$, as the values will be periodic after it.\\
+As the synchronous arrival pattern is known to be the worst case
+\cite{liu1973scheduling}, in that particular case we can only consider the
+interval $[0, t]$. In an asynchronous arrival pattern, it is sufficient to check
+only intervals where $t_2 < O_{max} + 2H$, as the system will be
+periodic starting from $O_{max} + H$ or sooner \cite{leung1982complexity}.\\
 
-In the sequel a closed form expression of the DBF is given in the synchronous case.
-Intuitively, in that case, it will be a step-function whose increase will occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\
+In the sequel a closed form expression of the DBF is given in the synchronous
+case. Intuitively, in this case it will be a step-function whose increases will
+occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\
 
-Starting from the definition, it remains to find a method to compute the values of $h_i(0, t)$ (noted $h_i(t)$ from now on).
-In the synchronous case, these values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} : k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc.
-The maximal value of $k$ can be explicitly stated by rearranging the condition:
+Starting from the definition, it remains to find a method to compute the values
+of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
+values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
+k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k =
+1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
 $$k T_i + D_i \leq t$$

### 2013-07-19 python-simulation/algorithms.py
Added more general dbf function + added completedJobCnt(task, t1, t2)

@@ -69,12 +69,22 @@ def findBusyPeriod(tau):
 
 	return wNew
 
-def dbf(tau, t):
+
+def dbf_synchr(tau, t):
+	return dbf(tau, 0, t)
+
+
+def dbf(tau, t1, t2):
 	dbfSum = 0
 	for task in tau.tasks:
-		completedJobCnt = max(0, math.ceil((t - task.D - task.O) / task.T)) + 1
-		dbfSum += completedJobCnt * task.C
+		dbfSum += completedJobCount(task, t1, t2) * task.C
 	return dbfSum
+
+
+def completedJobCount(task, t1, t2):
+	jobBeforeT2 = math.floor(1.0 * (t2 - task.O - task.D) / task.T)
+	jobBeforeT1 = math.ceil(1.0 * (t1 - task.O) / task.T)
+	return max(0, jobBeforeT2 - jobBeforeT1 + 1)
 
 
 def dbf_test(tau, upperLimit="def"):
@@ -95,7 +105,7 @@ def dbf_test(tau, upperLimit="def"):
 		tup = heapq.heappop(deadlineHeap)
 		deadline = tup[0]
 		task = tup[1]
-		testResult = dbf(tau, deadline) <= deadline
+		testResult = dbf_synchr(tau, deadline) <= deadline
 		if testResult is False:
 			return False
 		# add next deadline of this task to the heap

### 2013-07-19 dit-paper_ieee.tex
Added template for IEEE

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$
%
%  $Author: ienne, modified by Laurent George $
%  $Date: 2012/02/02 15:20:59 $
%  $Revision: 1.5 $

\documentclass[times, 10pt,twocolumn, a4paper]{article}
\usepackage{latex8}
\usepackage{epsfig, hhline}
\usepackage{amssymb}
\usepackage{vmargin,array,multirow,float,shadow,times, euscript}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{pdftricks}

\newtheorem{property}{Property}
\newtheorem{assumption}{Assumption}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\newtheorem{constraint}{Constraint}
\newtheorem{corollary}{Corollary}
\newtheorem{condition}{Condition}

\def\QED{\mbox{\rule[0pt]{1.5ex}{1.5ex}}}
\def\proof{\noindent{{\textbf{Proof}: }}}
\def\endproof{\hspace*{\fill}~\QED\par\endtrivlist\unskip \vspace{1\baselineskip}}
\newenvironment{accolade}{\begin{centering} $$ \left\{ \begin{array}{l}}{\end{array} \right. $$ \end{centering}}

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
\pagestyle{empty}

%-------------------------------------------------------------------------
\begin{document}

\title{Describing the C-space of asynchronous periodic task using DIT}

\author{Thomas Chapeaux, Paul Rodriguez\\
Universit\'e Libre de Bruxelles\\ tchapeau@ulb.ac.be, paurodri@ulb.ac.be \\
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
\and
Laurent George\\
ECE Paris\\
First line of institution2 address\\ Second line of institution2 address\\
lgeorge@ece.fr\\
}

\maketitle
\thispagestyle{empty}

\begin{abstract}
   Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel turpis ultricies vulputate vel at arcu. Curabitur lectus metus, rutrum sed malesuada ut, mollis sit amet mauris. Integer dapibus in risus et porttitor. In hac habitasse platea dictumst. Maecenas dolor libero, suscipit porta consequat eu, consequat non orci. Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum. Aenean tempor est nisl, at dictum metus elementum iaculis. Sed iaculis magna erat, sit amet congue dolor dignissim accumsan. Duis sit amet luctus sem, non interdum purus. Vestibulum at eros sit amet magna malesuada faucibus nec in nisi. Sed et varius nibh. Suspendisse auctor mattis ultricies.
\end{abstract}

\section{Introduction}

  \subsection{Model}

  \subsection{The DBF feasibility test for EDF}

  In general, ...\\

  In the synchronous case, this can be simplified to...

  \subsection{Using DIT to describe the C-space}

  \subsection{Our work}

\section{DIT in asynchronous systems}

  \subsection{Definition}

  \subsection{Existence condition}

  \subsection{EDF Feasibility test}

  \subsection{Simulation}

  `e' factor...

\section{Description of the C-space of asynchronous system}

\section{Example}

\section{Conclusion}

\bibliographystyle{latex8}
\bibliography{dit-paper}

\end{document}

### 2013-07-19 dit-paper.tex
minor changes renamed baruah pdf

@@
 
+\renewcommand{\arraystretch}{1.4}
 \newcommand{\dbf}[1]{\operatorname{dbf}(#1)}
@@
 	Mathematically,
- $$\dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
- \leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot h_i(t_1, t_2)$$ where
- $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
+	\[ 
+		\dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
+		\leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot h_i(t_1, t_2) 
+	\] 
+	where $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and
+	deadline are in (non-strict) the interval $[t_1, t_2]$.
 \end{definition}
@@
 In the sequel a closed form expression of the DBF is given in the synchronous
-case. Intuitively, in this case it will be a step-function whose increases will
+case. Intuitively, in this case it will be a step-function which increases will
 occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\
@@
 of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
-values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
-k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k =
-1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
-$$k T_i + D_i \leq t$$
-$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
-The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$.
-If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e.
-$h_i(t) = 0$.
-Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\
+values can be obtained as 
+\[
+	h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
+	k T_i  + D_i \leq t \} + 1
+\]
+Indeed, $k = 0$ corresponds to the first task, $k = 1$ to the second task, etc.
+The maximal value of $k$ can be explicitly stated by rearranging the condition:
+\[
+	\begin{array}{c}
+		k T_i + D_i \leq t \\
+		\iff 0 \leq k \leq \left\lfloor \frac{t - D_i}{T_i} \right\rfloor
+	\end{array}
+\]
+The highest value is $k = \left\lfloor \frac{t - D_i}{T_i} \right\rfloor$. If
+this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e.
+that $h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) =
+\left\lfloor \frac{t - D_i}{T_i} \right\rfloor + 1$\\
 
-This is generalized by the final definition of $h_i(t)$: $$h_i(t) = \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \}$$
+This is generalized by the final definition of $h_i(t)$: 
+\[
+	h_i(t) = \operatorname{max} \{ 0, \left\lfloor \frac{t - D_i}{T_i}
+	\right\rfloor + 1\}
+\]
 
-With this result, a closed form of the DBF function in the synchronous case is obtained $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$
+With this result, a closed form of the DBF function in the synchronous case is
+obtained 
+\[
+	\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \left\lfloor \frac{t -
+	D_i}{T_i} \right\rfloor + 1 \} \cdot C_i
+\]
 
@@
 
-In \cite{baruah1990algorithms}, the authors show that the DBF can be used to derive the following feasibility condition for EDF\footnote{And thus, EDF being optimal, for all optimal schedulers} on sporadic task sets.
-An adapted proof is given here.
+In \cite{baruah1990algorithms} it is shown that the DBF can be used to
+derive the following feasibility condition for EDF (and thus, EDF being
+optimal, for all other optimal schedulers) on sporadic task sets. An adapted
+proof is given here.
 
 \begin{theorem}
-$$\text{$(\tau_1, ..., \tau_n)$ is feasible} \iff \dbf{t} \leq t \; \forall t$$
+\[
+	(\tau_1, ..., \tau_n) \: \text{is feasible} \iff \dbf{t} \leq t \; \forall t
+\]
 \end{theorem}
@@
 \begin{proof}
-	We first show that the condition is \emph{necessary}.
-Indeed, if the condition is not fulfilled (i.e.
-$\exists t^* \; s.t.
-\; \dbf{t^*} > t^*$), it means that in an interval of $t^*$ time units, the total execution time of the jobs whose arrival and deadline occurs within the interval is superior to $t^*$.
-The system is thus not feasible if the condition is not fulfilled.\\
+	We first show that the condition is \emph{necessary}. Indeed, if the condition
+	is not fulfilled (i.e. $\exists t^* \; s.t. \; \dbf{t^*} > t^*$), it means that
+	in an interval of $t^*$ time units, the total execution time of the jobs which
+	arrival and deadline occurs within the interval is superior to $t^*$, but the
+	processor can only execute $t^*$. The system is thus not feasible if the
+	condition is not fulfilled.\\
 
@@
 
-	...
-(The idea is to look at each interval beginning at an arrival time and finishing at a deadline (not necessarily of the same job).
-Then we can prove that if there is only those two tasks, they can execute.
-If there are other tasks, we can look at a greater interval in which they can all execute)
+	... (The idea is to look at each interval beginning at an arrival time and
+	finishing at a deadline (not necessarily of the same job). Then we can prove
+	that if there is only those two tasks, they can execute. If there are other
+	tasks, we can look at a greater interval in which they can all execute)
 

### 2013-07-19 dit-paper.tex

--- 2013-07-19 dit-paper.tex
@@
 of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
-values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
-k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k =
-1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
-$$k T_i + D_i \leq t$$
-$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
-The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$.
-If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e.
-$h_i(t) = 0$.
-Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\
+values can be obtained as 
+\[
+	h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
+	k T_i  + D_i \leq t \} + 1
+\]
+Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc.
+The maximal value of $k$ can be explicitly stated by rearranging the condition:
+\[
+	\begin{array}{c}
+		k T_i + D_i \leq t \\
+		\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor
+	\end{array}
+\]
+The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is
+negative, it means that no job of task $\tau_i$ respects the condition, i.e.
+$h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\
 
@@
 
-With this result, a closed form of the DBF function in the synchronous case is obtained $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$
+With this result, a closed form of the DBF function in the synchronous case is
+obtained $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$
 
@@
 
-In \cite{baruah1990algorithms}, the authors show that the DBF can be used to derive the following feasibility condition for EDF\footnote{And thus, EDF being optimal, for all optimal schedulers} on sporadic task sets.
-An adapted proof is given here.
+In \cite{baruah1990algorithms} it is shown that the DBF can be used to
+derive the following feasibility condition for EDF (and thus, EDF being
+optimal, for all other optimal schedulers) on sporadic task sets. An adapted
+proof is given here.
 

### 2013-07-19 python-simulation/algorithms.py
Added more unit test

@@ -122,6 +122,9 @@ if __name__ == '__main__':
 	tasks.append(Task.Task(0, 1, 3, 6))
 	tasks.append(Task.Task(0, 1, 3, 3))
 	tau = Task.TaskSystem(tasks)
+	assert completedJobCount(tau.tasks[0], 15, 25) == 1
+	assert completedJobCount(tau.tasks[0], 0, 33) == 6
+	assert completedJobCount(tau.tasks[1], 0, 33) == 11, "returned: " + str(completedJobCount(tau.tasks[1], 0, 33))
 	assert findBusyPeriod(tau) == 2, "Unit Test FAIL : findBusyPeriod"
 	assert findFirstDIT(tau) == 3, "Unit Test FAIL : findFirstDIT, returned: " + str(findFirstDIT(tau))
 	assert findSynchronousInstant(tau) == 0, "Unit Test FAIL : findSynchronousInstant; returned: " + str(findSynchronousInstant(tau))

### 2013-07-19 dit-paper.tex

--- 2013-07-19 dit-paper.tex
@@
 
-Furthermore, the authors show that in the synchronous case, it is sufficient to consider intervals of the form $[0, t_d]$, where the $t_d$ correspond to job deadlines (i.e.
-the increases the demand-bound function) in the interval $\left[ D_{min}, H \right]$.\\
+Furthermore, it is shown in \cite{baruah1990algorithms} that in the synchronous case, it is
+sufficient to consider intervals of the form $[0, t_d]$, where values of
+$t_d$ correspond to job deadlines (i.e. instants at which the demand-bound
+function increases) in the interval $\left[ D_{min}, H \right]$.\\
 
-For constrained deadline set, it is sufficient to consider intervals $[0, t_d]$ with $t_d \leq L$, where $L$ is the first busy period and is the solution to the following recursive equation $$L = \sum_{i=1}^{n} \lceil \frac{L}{T_i} \rceil C_i$$ which can be computed through fixed-point iteration $$w_0 = \sum_{i=1}^{n} C_i$$ $$w_{k+1} = \sum_{i=1}^{n} \lceil \frac{w_k}{T_i} \rceil C_i$$
-
-Even so, this test requires to check a number of instant which is exponential in the number of tasks, making the general determination of feasibility a NP-hard problem.
+For constrained deadline task sets, it is sufficient to consider intervals $[0,
+t_d]$ with $t_d \leq L$, where $L$ is the length of the first busy period and is
+the solution to the following recursive equation
+\[
+	L = \sum_{i=1}^{n} \left\lceil \frac{L}{T_i} \right\rceil C_i
+\]
+which can be computed through the following fixed-point iteration
+\[
+	\begin{array}{rl}
+		w_0 = 		& \sum\limits_{i=1}^{n} C_i \\
+		w_{k+1} = 	& \sum\limits_{i=1}^{n} \left\lceil \frac{w_k}{T_i} \right\rceil
+		C_i
+		\\
+	\end{array}
+\]
+Even so, this test requires to check a number of time instants in $[0,
+t_d]$ which is exponential in the number of tasks, making the general
+determination of feasibility an NP problem.
 
 \section{C-space}
-When developing an application, it often happens that the platform is not known in advance, in which case the value of the $C_i$ are not known.
-Then, it can be useful to have a description of the possible values of the $C_i$ for which the system would be feasible.
+When developing an application, it often happens that the platform is not known
+in advance, in which case the value of the $C_i$ are not known. It can be
+useful in those situations to have a description of the possible values of
+the $C_i$ for which the system would be feasible.
 
@@
 
-The authors of \cite{george2009characterization} give the following definition of the C-space:
+A definition is given in \cite{george2009characterization} :
+
 \begin{definition}
-For a given task system $\tau$ in which the $C_i$ are not known, the \textbf{C-space} is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_n\}$ in the C-space, $\tau$ is feasible.
+	For a given task system $\tau$ in which the $C_i$ are not known, the
+\textbf{C-space} is a region of $n = |\tau|$ dimensions (where each dimension
+denotes the range of possible values of $C_i$ for a task $\tau_i$) such that
+for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in the C-space, $\tau$ is
+feasible.
 \end{definition}
 
-Thus, with a good description of the C-space, it is easy to check if a given vector of $C_i$ value (given e.g.
-when deploying the application on a specific platform) allows the system to be scheduled or not.
+Thus, with a good description of the C-space, it is easy to check if a given
+vector of $C_i$ values (given e.g. when deploying the application on a specific platform) allows the system to be scheduled or not.
 
@@
 
-A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing bounds of the convex hull of the admissible points.
-In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
+A region of $\mathbb{N}^n$ can be described by a list of parametric linear
+inequations describing the convex hull of the admissible points. In
+other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
 
 For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are
-$$\dbf{t} = \sum_{i=1}^{n} h_i(t) C_i \leq t \; \forall t$$
-Note that for a given $t$, we have that the $h_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus effectively linear.\\
+\[
+	\dbf{t} = \sum_{i=1}^{n} C_i \cdot h_i(t) \leq t \; \forall t
+\]
+Note that for a given $t$, we have that the $h_i(t)$ are constants (w.r.t. the
+$C_i$). Those equations are thus effectively linear.\\
 
@@
 
-While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.\\
+While redundant constraints are not a problem in theory, a short description is
+always preferred as it can greatly reduce the complexity of calculating
+whether a given vector of $C_i$ values is feasible.\\
 
-As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered.
-For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used.
-In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.\\
+As was shown previously, the equations corresponding to job deadlines happening
+before $H$ are necessary and sufficient to test the feasibility of the system
+and are therefore the only ones which have to be considered. For
+constrained deadline systems, the end of the first busy period has been proven
+to be an acceptable upper bound for the DBF test as well, but this value depends
+on the $C_i$ and therefore cannot be used. In section \ref{sct:DIT}, a similar
+concept which does not depend on the value of $C_i$ is presented.\\
 

### 2013-07-19 dit-paper_ieee.tex
Begun to copypaste some text

@@
 \def\endproof{\hspace*{\fill}~\QED\par\endtrivlist\unskip \vspace{1\baselineskip}}
-\newenvironment{accolade}{\begin{centering} $$ \left\{ \begin{array}{l}}{\end{array} \right. $$ \end{centering}}
+
+\newcommand{\dbf}[1]{\operatorname{dbf}(#1)}
+
+%\newenvironment{accolade}{\begin{centering} $$ \left\{ \begin{array}{l}}{\end{array} \right. $$ \end{centering}}
 
@@
 
-  \subsection{The DBF feasibility test for EDF}
+  We consider systems of periodic tasks with constrained deadline, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period.
+The constrained deadline property implies that $D_i \leq T_i$.\\
 
-  In general, ...\\
+  For those type of systems, the \emph{Earliest Deadline First} (EDF) algorithm has been shown to be optimal on uniprocessor platform [citation needed], i.e.
+this scheduling algorithm is able to schedule any feasible system.
+
+  \subsection{The DBF feasibility test}
+
+  We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms}, based on the demand-bound function.
+
+  \begin{definition}
+  The \textbf{demand-bound function (DBF)}
+  \cite{baruah1999generalized, baruah1990algorithms} defined for a task set
+  $\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\
+
+  Mathematically,
+  \[
+    \dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
+    \leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot n_i(t_1, t_2)
+  \]
+  where $n_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and
+  deadline are in (non-strict) the interval $[t_1, t_2]$.
+\end{definition}
+
+A closed form of the DBF function is given in \cite{baruah1990algorithms}
+\[
+  \dbf{t_1, t_2} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \left\lfloor \frac{t_2 - O_i -
+  D_i}{T_i} \right\rfloor - \left\lceil \frac{t_1 - O_i}{T_i} \right\rceil + 1 \} \cdot C_i
+\]
+
+Furthermore, a feasibility test for EDF is given
+
+\begin{theorem}
+\[
+  (\tau_1, ..., \tau_n) \: \text{is feasible} \iff \dbf{t_1, t_2} \leq t_2 - t_1 \; \forall 0 \leq t_1 \leq t_2
+\]
+\end{theorem}
 
@@
 
+When developing an application, it often happens that the platform is not known in advance, in which case the value of the $C_i$ are not known.
+Then, it can be useful to have a description of the possible values of the $C_i$ for which the system would be feasible.
+
+    \subsubsection{Definition}
+
+The authors of \cite{george2009characterization} give the following definition of the C-space:
+\begin{definition}
+For a given task system $\tau$ in which the $C_i$ are not known, the \textbf{C-space} is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_n\}$ in the C-space, $\tau$ is feasible.
+\end{definition}
+
+Thus, with a good description of the C-space, it is easy to check if a given vector of $C_i$ value (given e.g.
+when deploying the application on a specific platform) allows the system to be scheduled or not.
+
+  \subsubsection{Description using DBF}
+
+A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing the convex hull of the admissible points.
+In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
+
+For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are
+$$\dbf{t} = \sum_{i=1}^{n} n_i(t) C_i \leq t \; \forall t$$
+Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus effectively linear.\\
+
+\subsection{Removing redundancy using DIT}
+
+While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.\\
+
+As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered.
+For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used.
+
+\begin{definition}
+A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.\\
+\end{definition}
+
   \subsection{Our work}
 
+  In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case.
+In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT, along with an algorithm to find its value and an EDF feasibility condition based on it.
+In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[O_{max}, O_{max} + 2 H]$ is sufficient to consider.
+
 \section{DIT in asynchronous systems}
+  \label{sct:asyncDIT}
 
   \subsection{Definition}
+
+  \begin{definition}
+  The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the arrival of at least one job of each task.
+  \end{definition}
 
@@
 \section{Description of the C-space of asynchronous system}
+  \label{sct:asyncCspace}
 

### 2013-07-22 dit-paper_ieee.tex
Big rewrite of what was already there

--- 2013-07-19 dit-paper_ieee.tex
@@
 Aenean tempor est nisl, at dictum metus elementum iaculis.
-Sed iaculis magna erat, sit amet congue dolor dignissim accumsan.
-Duis sit amet luctus sem, non interdum purus.
-Vestibulum at eros sit amet magna malesuada faucibus nec in nisi.
-Sed et varius nibh.
-Suspendisse auctor mattis ultricies.
 \end{abstract}
@@
 
+Abstract models for real-time systems often require the determination of the (worst-case) computation time of a job, a value highly dependent on the platform on which the application will be deployed.\\
+
+The \emph{C-space} of a real-time system is, intuitively, the set of execution times value for which this system would be feasible.
+A precise and efficient description of its C-space would allow to quickly decide if a system is feasible on a given platform.\\
+
+This section review the current description of the C-space of synchronous constrained systems, mostly studied by \cite{george2009characterization}.
+
   \subsection{Model}
 
-  \subsection{The DBF feasibility test for EDF}
+  We consider systems of periodic concrete tasks with constrained deadline on uniprocessor platform, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period.
+The constrained deadline property implies that $D_i \leq T_i \; \forall i$.
+In the following, we differentiate between \emph{synchronous systems} (where $O_i = 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\
 
-  In general, ...\\
+  For those systems, the \emph{Earliest Deadline First} (EDF) algorithm, in which jobs are prioritized according to their absolute deadline, has been shown to be optimal [citation needed], that is it schedules any feasible system.\\
 
-  In the synchronous case, this can be simplified to...
+  Furthermore, the following notations are used:
+  \begin{itemize}
+    \item $\tau = (\tau_0, \cdots, \tau_{n-1})$
+    \item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
+    \item $O_{max} = \max (O_0, \cdots, O_{n-1})$
+    \item idle time...
+    \item busy period...
+  \end{itemize}
 
-  \subsection{Using DIT to describe the C-space}
+  \subsection{The DBF feasibility test}
+
+  We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms}, based on the demand-bound function.
+
+  \begin{definition}
+  The \textbf{demand-bound function (DBF)}
+  \cite{baruah1999generalized, baruah1990algorithms} defined for a task set
+  $\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in the interval $[t_1, t_2]$.
+  \end{definition}
+
+  Mathematically,
+  \[
+    \dbf{t_1, t_2} = \sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i
+  \]
+  where $n_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and
+  deadline both are in the interval $[t_1, t_2]$.\\
+
+The values of the $n_i$ are given by
+\[
+  n_i(t_1, t_2) = \left( \left\lfloor \frac{t_2 - O_i -
+  D_i}{T_i} \right\rfloor - \left\lceil \frac{t_1 - O_i}{T_i} \right\rceil + 1 \right)^{+}
+\]
+where $(x)^+$ stands for $\max \{ 0, x \}$.\\
+
+The DBF allows to give a necessary and sufficient condition of feasibility:
+
+\begin{theorem}
+\[
+  \begin{array}{c}
+    (\tau_1, ..., \tau_n) \: \text{is feasible}  \iff \\
+    \dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+  \end{array}
+\]
+\end{theorem}
+
+  \subsection{C-space of synchronous systems}
+
+    \subsubsection{Definition}
+
+The authors of \cite{george2009characterization} give the following definition of the C-space:
+\begin{definition}
+For a given task system $\tau$ in which the $C_i$ are not known, the \textbf{C-space} is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in the C-space, $\tau$ is feasible.
+\end{definition}
+
+%Thus, with a good description of the C-space, it is easy to check if a given vector of $C_i$ value (given e.g.
+when deploying the application on a specific platform) allows the system to be scheduled or not.
+
+  \subsubsection{Description using DBF}
+
+A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing the convex hull of the admissible points.
+In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
+
+For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are:
+$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
+Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus indeed linear.\\
+
+However, this description contains an infinite number of equations, most of which are redundant.
+While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times.
+The next section gives a method to reduce the size of the description.
+
+\subsection{Removing redundancy}
+
+In the synchronous case, is has been shown that the equations corresponding to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are necessary and sufficient to test the feasibility.\\
+
+Even then, the number of equations to consider is exponential in the number of tasks.
+While it has been shown that intervals ending after the end of the busy period are also redundant, this value depends on the $C_i$ and is therefore not usable.
+The following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.
+
+\begin{definition}
+A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.\\
+\end{definition}
 
@@
 
+  In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case.
+In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT, along with an algorithm to find its value and an EDF feasibility condition based on it.
+In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[O_{max}, O_{max} + 2 H]$ is sufficient to consider.
+
 \section{DIT in asynchronous systems}
+  \label{sct:asyncDIT}
 
@@
 
+  \begin{definition}
+  The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the arrival of at least one job of each task.
+  \end{definition}
+
   \subsection{Existence condition}
 
-  \subsection{EDF Feasibility test}
+As in the synchronous case, the problem of existence of the first periodic DIT can be written as a system of modular equation:
+$$
+\begin{array}{l}
+  \exists ? \; t_d \; s.t. \; \forall i \; :\\
+  \left\{
+    \begin{array}{l}
+    t_d > O_i \\
+    t_d - O_i \equiv a_i \; (mod \; T_i) \\
+    a_i \in [D_i, T_i]
+  \end{array}
+\right.
+\end{array}
+$$
+
+This system is guaranteed to have at least one solution modulo $H$ if the following condition is respected $$a_i + O_i \equiv a_j + O_j \; (mod \; \operatorname{gcd}(T_i, T_j))$$
 

### 2013-07-22 dit-paper_ieee.tex
Completed Section on Asynchronous DIT

@@
 
-  We consider systems of periodic concrete tasks with constrained deadline on uniprocessor platform, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period.
+  We consider a discrete time and systems of periodic concrete tasks with constrained deadline on uniprocessor platform, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period.
 The constrained deadline property implies that $D_i \leq T_i \; \forall i$.
@@
     \item $O_{max} = \max (O_0, \cdots, O_{n-1})$
-    \item idle time...
-    \item busy period...
+    \item An \emph{idle time} is an instant $t$ at which each job that arrived strictly before $t$ has finished its execution.
+    \item The interval between the initial time and the first idle time is called the \emph{busy period}.
   \end{itemize}
@@
 \begin{definition}
-A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.\\
+A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.
 \end{definition}
+
+\begin{definition}
+The earliest DIT occurring in the system strictly after $t=0$ is called the \textbf{first DIT} and is noted $t_d$.
+\end{definition}
+
+The value of the first DIT can be found by solving the following equation:
+\[
+  t_d = \min \left( t \; s.t. \; \forall i:
+  \left\{
+  \begin{array}{c}
+    t \equiv a_i \; (mod \; T_i) \\
+    a_i \in [D_i, T_i]
+  \end{array}
+  \right.
+  \right)
+\]
+
+\begin{remark} (from the definition):
+ \begin{itemize}
+  \item Contrary to the idle times, the DITs are independent of the scheduling or the execution times of the jobs.
+  \item In feasible system, every DIT is an idle time.
+  \item In feasible system, the first DIT happens after the end of the busy period.
+  \item As $H$ is always a DIT, we have $t_d \leq H$.
+ \end{itemize}
+\end{remark}
+
+Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously.
+Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\
+
+To summarize, we reduced the description of the C-space from an infinite number of equations to only the equations where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job.
+Note that this is still exponential in the number of tasks.
 
@@
   In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case.
-In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT, along with an algorithm to find its value and an EDF feasibility condition based on it.
-In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[O_{max}, O_{max} + 2 H]$ is sufficient to consider.
+In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT ($t_d$), along with an algorithm to find its value.
+In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is sufficient to consider.
 
@@
 
-This system is guaranteed to have at least one solution modulo $H$ if the following condition is respected $$a_i + O_i \equiv a_j + O_j \; (mod \; \operatorname{gcd}(T_i, T_j))$$
+This system is guaranteed to have at least one solution modulo $H$ for given values of $a_i$ if the following condition is respected $$a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i, j$$
 
@@
 
+\nocite{*}
 \bibliographystyle{latex8}

### 2013-07-22 python-simulation/mainAsynchr.py
Show more detailed results

@@ -26,11 +26,14 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 
 if __name__ == '__main__':
 	NUMBER_OF_SYSTEMS = 1000
-	for constrDeadlineFactor in range(5, 15):
+	for constrDeadlineFactor in range(1, 10):
 		print "CONSTR DEAD FACTOR", constrDeadlineFactor
 		systemArray = generateSystemArray(NUMBER_OF_SYSTEMS, constrDeadlineFactor)
+		successCount = 0
 		start = time.clock()
-		for tau in systemArray:
-			algorithms.findFirstDIT(tau)
+		for i, tau in enumerate(systemArray):
+			if constrDeadlineFactor == 1 and i % 100 == 0:
+				print i, "/", NUMBER_OF_SYSTEMS, "..."
+			successCount += 1 if algorithms.findFirstDIT(tau) else 0
 		stop = time.clock()
-		print "Found", NUMBER_OF_SYSTEMS, "DITs in ", stop - start, "seconds."
+		print "Found", successCount, "/", NUMBER_OF_SYSTEMS, "DITs in ", stop - start, "seconds."

### 2013-07-22 dit-paper_ieee.tex
minor changes

@@
 
-Abstract models for real-time systems often require the determination of the (worst-case) computation time of a job, a value highly dependent on the platform on which the application will be deployed.\\
+Abstract models for real-time systems often require the determination of the
+(worst-case) computation time of a job (WCET), a value highly dependent on the
+platform on which the application will be deployed.\\
 
-The \emph{C-space} of a real-time system is, intuitively, the set of execution times value for which this system would be feasible.
-A precise and efficient description of its C-space would allow to quickly decide if a system is feasible on a given platform.\\
+The \emph{C-space} of a real-time system is, intuitively,
+the set of WCET values for which this system would be feasible. A
+precise and efficient description of its C-space would allow to quickly decide
+if a system is feasible on a given platform.\\
 
-This section review the current description of the C-space of synchronous constrained systems, mostly studied by \cite{george2009characterization}.
+In this section the current description of the C-space of synchronous
+constrained systems is reviewed, mostly through
+\cite{george2009characterization}.
 
@@
 
-  We consider a discrete time and systems of periodic concrete tasks with constrained deadline on uniprocessor platform, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period.
-The constrained deadline property implies that $D_i \leq T_i \; \forall i$.
-In the following, we differentiate between \emph{synchronous systems} (where $O_i = 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\
+We consider a discrete timeline and systems comprised of periodic concrete
+tasks with constrained deadlines on uniprocessor platforms, where each task
+  $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
+  $C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
+  The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
+  the following, we differentiate between \emph{synchronous systems} (where $O_i
+  = 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\
 
-  For those systems, the \emph{Earliest Deadline First} (EDF) algorithm, in which jobs are prioritized according to their absolute deadline, has been shown to be optimal [citation needed], that is it schedules any feasible system.\\
+  For those systems, the \emph{Earliest Deadline First} (EDF) algorithm, in
+  which jobs are prioritized according to their absolute deadline, has been
+  shown to be optimal \cite{liu1973scheduling}, which means it
+  correctly schedules any feasible system within that group.\\
 
@@
   \begin{itemize}
-    \item $\tau = (\tau_0, \cdots, \tau_{n-1})$
+    \item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
     \item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
     \item $O_{max} = \max (O_0, \cdots, O_{n-1})$
-    \item An \emph{idle time} is an instant $t$ at which each job that arrived strictly before $t$ has finished its execution.
-    \item The interval between the initial time and the first idle time is called the \emph{busy period}.
+    \item An \emph{idle time} is an instant $t$ at which each job that arrived
+    \emph{strictly} before $t$ has finished its execution.
+    \item A \emph{busy period} is a time interval during which there is always
+    at least one job available and not finished in the system and maximal
+    (in interval length) with this property. Any busy period starts and ends
+    with an idle time.
+    \item The interval between the initial time and the first
+    idle time is called the \emph{first busy period}.
   \end{itemize}
@@
   \cite{baruah1999generalized, baruah1990algorithms} defined for a task set
-  $\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in the interval $[t_1, t_2]$.
+  $\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution
+  time of jobs of $\tau$ contained in the closed interval $[t_1, t_2]$.
   \end{definition}
@@
 
-\nocite{*}
+% \nocite{*}
 \bibliographystyle{latex8}

### 2013-07-22 dit-paper_ieee.tex
Added section on CSPACE asynchr

--- 2013-07-22 dit-paper_ieee.tex
@@
 
+  \label{sct:cspaceDescr}
+
 A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing the convex hull of the admissible points.
@@
 
-\section{Description of the C-space of asynchronous system}
+\section{C-space of asynchronous systems}
   \label{sct:asyncCspace}
+
+  \subsection{Description using DBF}
+
+  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant: $$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
+
+  The method used to remove redundancy, however, assumed the synchronous case. A more general approach is presented in the following section.
+
+  \subsection{Removing redundancy}
+
+\subsubsection{Job arrival and deadline}
+
+Consider an interval $[t_1, t_2]$.
+If $t_2$ is an instant without any job deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to $\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.\\
+
+A similar argument can be made if $t_1$ is an instant without any job arrival (and $t_1^*$ is the earliest arrival after $t_1$).
+We can thus restricts ourselves to intervals where $t_1$ is an instant with at least one job arrival, and $t_2$ is an instant with at least one job deadline.
+
+  \subsubsection{Feasibility interval}
+
+  First let us recall how an asynchronous system behaves under, for example, EDF.\\
+
+\begin{figure}[h]
+$$
+\begin{array}{|c|c|c|c|l}
+   \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
+   \text{period} & \text{period} & \text{period} & \text{period} & \\
+  \hline
+  t > 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
+\end{array}
+$$
+\begin{center}
+\caption{Behavior of an asynchronous system under EDF.}
+\label{fig:asyncBehavior}
+\end{center}
+\end{figure}
+
+As shown in Fig.
+\ref{fig:asyncBehavior}, the system begins in the \emph{incomplete period}, where all tasks are not in the system.
+Then, after $O_{max}$ time units, every tasks is in the system and the \emph{transitive period} begins.
+Then, after $O_{max} + H$ time units, the system is faced with the same pattern of arrival as in $O_{max}$.
+However, because in $O_{max} + H$ every task is in the system and in $O_{max}$ some were missing, the state of the system will be different.
+The \emph{stationary period} then begins.
+It is only after $O_{max} + 2H$ time units that the system comes back into a state in which it was before.\\
+
+For this reason, as explained in \cite{leung1982complexity}, it is sufficient to check for intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length in the number of tasks.
+
+\subsubsection{Using the first periodic DIT}
+
+The first periodic DIT happen...
 

### 2013-07-22 dit-paper_ieee.tex
indent fix
By a small abuse of slight notation....

@@
 
+  In an asynchronous system, the first DIT could happen before the arrival of at least one job of each task. We thus introduce the following notion:
+
   \begin{definition}
-  The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the arrival of at least one job of each task.
+  The \textbf{first periodic DIT} of a system is the earliest DIT occurring strictly after the arrival of at least one job of each task.
   \end{definition}
+
+  By a slight abuse of notation, it will also be noted $t_d$. Note that in the synchronous case the first periodic DIT is also the first DIT.
 
@@
 
-The first periodic DIT happen...
+The first periodic DIT, if it exists, must occur in the transitive period.
+Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in a stationary period, another DIT should have occurred in the transitive period (a contradiction).\\
 

### 2013-07-22 dit-paper_ieee.tex
Added explanation on DIT to remove redundancy

@@
 
+  \label{sct:FPDITexist}
+
 As in the synchronous case, the problem of existence of the first periodic DIT can be written as a system of modular equation:
@@
   \subsection{Simulation}
+
+  (Work in Progress...)
 
@@
 The first periodic DIT, if it exists, must occur in the transitive period.
-Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in a stationary period, another DIT should have occurred in the transitive period (a contradiction).\\
+Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).\\
+
+We show (...) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists.
+This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\
+
+To summarize, we reduced the number of equation from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
 

### 2013-07-22 dit-paper_ieee.tex
indent fix

--- 2013-07-22 dit-paper_ieee.tex
@@
 \begin{abstract}
-   Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nulla lobortis mi vel turpis ultricies vulputate vel at arcu.
+	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel
+turpis ultricies vulputate vel at arcu.
 Curabitur lectus metus, rutrum sed malesuada ut, mollis sit amet mauris.
@@
 	\]
-  where $n_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and
-  deadline both are in the interval $[t_1, t_2]$.\\
+	where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
+	and deadlines are both in the closed interval $[t_1, t_2]$.\\
 
@@
 		\begin{array}{c}
-    (\tau_1, ..., \tau_n) \: \text{is feasible}  \iff \\
+			\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
 			\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
@@
 			\begin{definition}
-For a given task system $\tau$ in which the $C_i$ are not known, the \textbf{C-space} is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in the C-space, $\tau$ is feasible.
+				For a given task system $\tau$ in which the $C_i$ are not known, the
+				\textbf{C-space} is a region of $n$ dimensions (where each dimension denotes
+				the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in the C-space, $\tau$ is feasible.
 			\end{definition}
@@
 		\subsubsection{Description using DBF}
-
 			\label{sct:cspaceDescr}
@@
 \begin{definition}
-  The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the arrival of at least one job of each task.
+	The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the
+	arrival of at least one job of each task.
 \end{definition}
@@
 \subsection{Existence condition}
-
-As in the synchronous case, the problem of existence of the first periodic DIT can be written as a system of modular equation:
-$$
+	As in the synchronous case, the problem of existence of the first periodic DIT
+	can be written as a system of modular equations:
+	\[
 		\begin{array}{l}
@@
 		\end{array}
-$$
+	\]
 
-This system is guaranteed to have at least one solution modulo $H$ for given values of $a_i$ if the following condition is respected $$a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i, j$$
+	This system is guaranteed to have at least one solution modulo $H$ for given
+	values of $a_i$ if the following condition is respected :
+	\[
+		a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
+		T_j)) \; \forall i,j
+	\]
 

### 2013-07-22 dit-paper_ieee.tex

@@
 
+		In an asynchronous system, the first DIT could happen before the arrival of at
+		least one job of each task. We thus introduce the following notion:
+
 		\begin{definition}
-	The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the
-	arrival of at least one job of each task.
+			The \textbf{first periodic DIT} of a system is the earliest DIT occurring
+			strictly after the arrival of at least one job of each task.
 		\end{definition}
+
+		By a slight abuse of notation, it will also be noted $t_d$. Note that in the
+		synchronous case the first periodic DIT is also the first DIT.
 
@@
 
-The first periodic DIT happen...
+The first periodic DIT, if it exists, must occur in the transitive period.
+Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).\\
+
+We show (...) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists.
+This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\
+
+To summarize, we reduced the number of equation from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
 

### 2013-07-22 dit-paper_ieee.tex
Repaired broken reference (thanks Paul)

@@
 	\subsection{Existence condition}
+  \label{sct:FPDITexist}
 		As in the synchronous case, the problem of existence of the first periodic DIT

### 2013-07-23 dit-paper_ieee.tex
small typos and rewrite

@@
 	In this section the current description of the C-space of synchronous
-	constrained systems is reviewed, mostly through
-	\cite{george2009characterization}.
+	constrained systems, which has been mostly covered by \cite{george2009characterization}, is reviewed.
 
@@
 
-		We consider a discrete timeline and systems comprised of periodic concrete
-		tasks with constrained deadlines on uniprocessor platforms, where each task
+		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic concrete
+		tasks with constrained deadlines on uniprocessor platforms. Each task
 		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
@@
 			\item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
-			\item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
+			\item $H = \operatorname{lcm}(T_0, \cdots, T_{n-1})$
 			\item $O_{max} = \max (O_0, \cdots, O_{n-1})$
@@
 			\item A \emph{busy period} is a time interval during which there is always
-			at least one job available and not finished in the system and maximal
-			(in interval length) with this property. Any busy period starts and ends
+			at least one unfinished job available in the system and maximal
+			with this property. Any busy period starts and ends
 			with an idle time.
@@
 		The \textbf{demand-bound function (DBF)}
-		\cite{baruah1999generalized, baruah1990algorithms} defined for a task set
-		$\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution
-		time of jobs of $\tau$ contained in the closed interval $[t_1, t_2]$.
+		defined for a task set $\tau$ and noted $\dbf{t_1, t_2}$, is equal to
+		the maximal cumulated execution time of jobs of $\tau$ contained in the
+		closed interval $[t_1, t_2]$.
 	\end{definition}

### 2013-07-23 dit-paper_ieee.tex
beautifying

@@
 			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
-			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus indeed linear.\\
+			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The equations are thus indeed linear.\\
 
@@
 
-\subsection{Removing redundancy}
+			\subsubsection{Removing redundancy}
 
@@
 			Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously.
-Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\
+Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to consider every interval $[0, t]$ with $t$ being a deadline before the first DIT.\\
 
@@
 
-		In an asynchronous system, the first DIT could happen before the arrival of at
-		least one job of each task. We thus introduce the following notion:
+		In an asynchronous system, the first DIT may happen before $O_{max}$, i.e. before all tasks are in the system. We thus introduce the following notion:
 
@@
 			The \textbf{first periodic DIT} of a system is the earliest DIT occurring
-			strictly after the arrival of at least one job of each task.
+			strictly after $O_{max}$.
 		\end{definition}
@@
 $$
-\begin{array}{|c|c|c|c|l}
-   \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
-   \text{period} & \text{period} & \text{period} & \text{period} & \\
+\begin{array}{r||c|c|c|l}
+    & \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
+   \text{Name} & \text{period} & \text{period} & \text{period}  & \\
   \hline
-  t > 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
+  \text{size} & O_{max} & H & H & \cdots \\
+  \hline
+  t \geqslant & 0 & O_{max} & O_{max} + H & \cdots
 \end{array}

### 2013-07-23 dit-paper_ieee.tex
equation > constraint

@@
 
-			A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing the convex hull of the admissible points.
+			A region of $\mathbb{N}^n$ can be described by a list of parametric linear constraints describing the convex hull of the admissible points.
 In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
 
-			For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are:
+			For the synchronous case, the DBF test gives us a list of constraints which, taken together, are a necessary and sufficient condition of feasibility. Those are:
 			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
-			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The equations are thus indeed linear.\\
+			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The constraints are thus indeed linear.\\
 
-			However, this description contains an infinite number of equations, most of which are redundant.
+			However, this description contains an infinite number of constraints, most of which are redundant.
 While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times.
@@
 
-			In the synchronous case, is has been shown that the equations corresponding to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are necessary and sufficient to test the feasibility.\\
+			In the synchronous case, is has been shown that the constraints corresponding to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are necessary and sufficient to test the feasibility.\\
 
-			Even then, the number of equations to consider is exponential in the number of tasks.
+			Even then, the number of constraints to consider is exponential in the number of tasks.
 While it has been shown that intervals ending after the end of the busy period are also redundant, this value depends on the $C_i$ and is therefore not usable.
@@
 
-			To summarize, we reduced the description of the C-space from an infinite number of equations to only the 			equations where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job.
+			To summarize, we reduced the description of the C-space from an infinite number of constraints to only the 			constraints where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job.
 Note that this is still 			exponential in the number of tasks.
@@
 
-To summarize, we reduced the number of equation from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
+To summarize, we reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
 

### 2013-07-23 dit-paper_ieee.tex
style changes, typo fixes

--- 2013-07-23 dit-paper_ieee.tex
@@
 	In this section the current description of the C-space of synchronous
-	constrained systems, which has been mostly covered by \cite{george2009characterization}, is reviewed.
+	constrained systems is reviewed, mostly through
+	\cite{george2009characterization}.
 
@@
 
-		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic concrete
-		tasks with constrained deadlines on uniprocessor platforms. Each task
+		We consider a discrete timeline and systems comprised of periodic concrete
+		tasks with constrained deadlines on uniprocessor platforms, where each task
 		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
@@
 			\item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
-			\item $H = \operatorname{lcm}(T_0, \cdots, T_{n-1})$
+			\item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
 			\item $O_{max} = \max (O_0, \cdots, O_{n-1})$
@@
 			\item A \emph{busy period} is a time interval during which there is always
-			at least one unfinished job available in the system and maximal
-			with this property. Any busy period starts and ends
+			at least one job available and not finished in the system and maximal
+			(in interval length) with this property. Any busy period starts and ends
 			with an idle time.
@@
 		The \textbf{demand-bound function (DBF)}
-		defined for a task set $\tau$ and noted $\dbf{t_1, t_2}$, is equal to
-		the maximal cumulated execution time of jobs of $\tau$ contained in the
-		closed interval $[t_1, t_2]$.
+		\cite{baruah1999generalized, baruah1990algorithms} defined for a task set
+		$\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution
+		time of jobs of $\tau$ contained in the closed interval $[t_1, t_2]$.
 	\end{definition}
@@
 
-			A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing the convex hull of the admissible points.
-In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
+			A region of $\mathbb{N}^n$ can be described by a list of parametric linear
+			constraints describing the convex hull of that region. In other words, a
+			list of conditions which can unequivocally decide if a point is included in the region or not.\\
 
-			For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are:
-			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
-			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus indeed linear.\\
+			For the synchronous case, the DBF test gives us a list of inequations
+			on the WCET values of the task set which together are a necessary and
+			sufficient condition of feasibility. They can all be written in the
+			following way:
+			\[
+				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
+				t_1 \leq t_2
+			\]
+			Note that for a given $t$, we have that the $n_i(t)$ are
+			constant (w.r.t. the $C_i$). Those equations are thus indeed linear.\\
 
-			However, this description contains an infinite number of equations, most of which are redundant.
-While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times.
-The next section gives a method to reduce the size of the description.
+			However, this description contains an infinite number of equations, most of
+			which are redundant. While this does not harm the precision of the
+			test, the smallest description is preferred as it can greatly
+			reduce the computation time of practical feasibility tests using this system
+			of constraints. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of inequations is given.
 
 	\subsection{Removing redundancy}
+		\label{sct:removeRedundancy}
 
@@
 	\[
-  t_d = \min \left( t \; s.t. \; \forall i:
+		t_d = \min 
+		\left( t \; s.t. \; \forall i:
 			\left\{
@@
 		\begin{itemize}
-		\item Contrary to the idle times, the DITs are independent of the scheduling or the execution times of the jobs.
-		\item In feasible system, every DIT is an idle time.
-		\item In feasible system, the first DIT happens after the end of the busy period.
-		\item As $H$ is always a DIT, we have $t_d \leq H$.
+			\item Contrary to other idle times, DITs are independent of the
+			scheduling or the execution times of the jobs.
+			\item In a feasible system, every DIT is an idle time.
+			\item In a feasible system, the first DIT happens after the end of the
+			first busy period.
+			\item As $H$ is always a DIT in synchronous systems, we have $t_d \leq H$ in
+			this case.
 		\end{itemize}
@@
 
-Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously.
-Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\
+	Every DIT being an idle instant, the execution of the system after a DIT does
+	not depend on what happened before. Because the synchronous arrival pattern is
+	the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\
 
-To summarize, we reduced the description of the C-space from an infinite number of equations to only the equations where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job.
-Note that this is still exponential in the number of tasks.
+	To summarize, we reduced the description of the C-space from an infinite number
+	of constraints to only the inequations where $t_1 = 0$, $t_2 \leqslant t_d$ and
+	values of $t_2$ correspond to job deadlines. Note that the number of
+	constraints is still exponential in the number of tasks.
 
@@
 
-  In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case.
-In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT ($t_d$), along with an algorithm to find its value.
-In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is sufficient to consider.
+		In this paper, we extend the work of \cite{george2009characterization} to the
+		asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
+		the concept of DIT adapted to the asynchronous case called first periodic DIT
+		($t_d$), along with an algorithm to find its value. In Section
+		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
+		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
+		sufficient to consider.
 
@@
 \begin{figure}[h]
-$$
+\[
 	\begin{array}{|c|c|c|c|l}
-   \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
+		\text{Incomplete} & \text{Transitive} & \text{Stationary} & 2^{nd}
+		\text{Stationary} & \cdots \\
 		\text{period} & \text{period} & \text{period} & \text{period} & \\
@@
 	\end{array}
-$$
+\]
 \begin{center}

### 2013-07-23 dit-paper_ieee.tex
small rephrasing

--- 2013-07-23 dit-paper_ieee.tex
@@
 Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum.
-Aenean tempor est nisl, at dictum metus elementum iaculis.
+Aenean tempor est nisl, at dictum metus elementum iaculis.\\
+
+Keywords: Real-time systems, C-space, WCET
+
+Buzzword: sensitivity analysis
 \end{abstract}
@@
 
-  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant: $$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
+  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant.
+Therefore the C-space is still described by the following infinite number of constraints:$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
 
-  The method used to remove redundancy, however, assumed the synchronous case. A more general approach is presented in the following section.
+  However, the method used in the synchronous case to remove redundancy does not apply here. A more general approach is presented in the following section.
 
@@
 
-  First let us recall how an asynchronous system behaves under, for example, EDF.\\
+  First let us recall how an asynchronous system behaves under an optimal scheduler, for example EDF.\\
 
@@
 The \emph{stationary period} then begins.
-It is only after $O_{max} + 2H$ time units that the system comes back into a state in which it was before.\\
+It is only after $O_{max} + 2H$ time units that the system comes back into a state in which we can be sure it has been before.\\
 

### 2013-07-23 dit-paper_ieee.tex

--- 2013-07-23 dit-paper_ieee.tex
@@
 
-			A region of $\mathbb{N}^n$ can be described by a list of parametric linear constraints describing the convex hull of the admissible points.
-In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
+			A region of $\mathbb{N}^n$ can be described by a list of parametric linear
+			constraints describing the convex hull of that region. In other words, a
+			list of conditions which can unequivocally decide if a point is included in the region or not.\\
 
-			For the synchronous case, the DBF test gives us a list of constraints which, taken together, are a necessary and sufficient condition of feasibility. Those are:
-			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
-			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The constraints are thus indeed linear.\\
+			For the synchronous case, the DBF test gives us a list of inequations
+			on the WCET values of the task set which together are a necessary and
+			sufficient condition of feasibility. They can all be written in the
+			following way:
+			\[
+				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
+				t_1 \leq t_2
+			\]
+			Note that for a given $t$, we have that the $n_i(t)$ are
+			constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.\\
 
-			However, this description contains an infinite number of constraints, most of which are redundant.
-While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times.
-The next section gives a method to reduce the size of the description.
+			However, this description contains an infinite number of constraints, most of
+			which are redundant. While this does not harm the precision of the
+			test, the smallest description is preferred as it can greatly
+			reduce the computation time of practical feasibility tests using this system
+			of inequations. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of constraints is given.
 
-			\subsubsection{Removing redundancy}
+	\subsection{Removing redundancy}
+		\label{sct:removeRedundancy}
 
-			In the synchronous case, is has been shown that the constraints corresponding to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are necessary and sufficient to test the feasibility.\\
+	In the synchronous case, is has been shown that the inequations corresponding
+	to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are
+	necessary and sufficient to test the feasibility of a system.\\
 
-			Even then, the number of constraints to consider is exponential in the number of tasks.
-While it has been shown that intervals ending after the end of the busy period are also redundant, this value depends on the $C_i$ and is therefore not usable.
-The following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.
+	Even then, the number of inequations to consider is exponential in the number
+	of tasks. While it has been shown that constraints that cover intervals ending
+	after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
+	therefore not usable, or at least not for the purposes of this paper. The
+	following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.
 
 	\begin{definition}
-			A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$			 has its absolute deadline before or at instant $t$.
+		A \textbf{definitive idle time} (DIT) is a time $t$ such that every job
+		released strictly before instant $t$ has its absolute deadline before or at instant $t$.
 	\end{definition}
@@
 	\begin{definition}
-			The earliest DIT occurring in the system strictly after $t=0$ is called the \textbf{first DIT} and is noted 			$t_d$.
+		The earliest DIT occurring in the system strictly after $t=0$ is called the
+		\textbf{first DIT} and is noted $t_d$.
 	\end{definition}
@@
 	\[
-			  t_d = \min \left( t \; s.t. \; \forall i:
+		t_d = \min 
+		\left( t \; s.t. \; \forall i:
 			\left\{
@@
 		\begin{itemize}
-					\item Contrary to the idle times, the DITs are independent of the scheduling or the execution times 			of the jobs.
-					\item In feasible system, every DIT is an idle time.
-					\item In feasible system, the first DIT happens after the end of the busy period.
-					\item As $H$ is always a DIT, we have $t_d \leq H$.
+			\item Contrary to other idle times, DITs are independent of the
+			scheduling or the execution times of the jobs.
+			\item In a feasible system, every DIT is an idle time.
+			\item In a feasible system, the first DIT happens at the end of the
+			first busy period.
+			\item As $H$ is always a DIT in synchronous systems, we have at least $t_d
+			\leqslant H$ in this case.
 		\end{itemize}
@@
 
-			Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously.
-Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to consider every interval $[0, t]$ with $t$ being a deadline before the first DIT.\\
+	Every DIT being an idle instant, the execution of the system after a DIT does
+	not depend on what happened before. Because the synchronous arrival pattern is
+	the worst case [citation needed], it is sufficient for the DBF test to only
+	consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\
 
-			To summarize, we reduced the description of the C-space from an infinite number of constraints to only the 			constraints where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job.
-Note that this is still 			exponential in the number of tasks.
+	To summarize, we reduced the description of the C-space from an infinite number
+	of constraints to only the inequations where $t_1 = 0$, $t_2 \leqslant t_d$ and
+	values of $t_2$ correspond to job deadlines. Note that the number of
+	constraints is still exponential in the number of tasks.
 
 	\subsection{Our work}
-
-  In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case.
-In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT ($t_d$), along with an algorithm to find its value.
-In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is sufficient to consider.
+		In this paper, we extend the work of \cite{george2009characterization} to the
+		asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
+		the concept of DIT adapted to the asynchronous case called first periodic DIT
+		($t_d$), along with an algorithm to find its value. In Section
+		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
+		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
+		sufficient to consider.
 
@@
 \begin{figure}[h]
-$$
+	\[
 		\begin{array}{r||c|c|c|l}
@@
 		\end{array}
-$$
+	\]
 	\begin{center}

### 2013-07-23 dit-paper_ieee.tex
max(0,x)

@@
 \usepackage{pdftricks}
+\usepackage{stmaryrd}
 
@@
 	\[
-		n_i(t_1, t_2) = \left( \left\lfloor \frac{t_2 - O_i -
-		D_i}{T_i} \right\rfloor - \left\lceil \frac{t_1 - O_i}{T_i} \right\rceil + 1 \right)^{+}
+		n_i(t_1, t_2) = 
+		\left\llbracket
+			\left\lfloor
+				\frac{t_2 - O_i - D_i}{T_i}
+			\right\rfloor - 
+			\left\lceil 
+				\frac{t_1 - O_i}{T_i} 
+			\right\rceil + 1 
+		\right\rrbracket_0
 	\]
-	where $(x)^+$ stands for $\max \{ 0, x \}$.\\
+	where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.\\
 

### 2013-07-23 dit-paper_ieee.tex
tabs and caret return

@@
 		This system is guaranteed to have at least one solution modulo $H$ for given
-		values of $a_i$ if the following condition is respected :
+		values of $a_i$ if the following condition is respected:
 		\[
@@
 		\]
+		which means that there could be systems with no first periodic DIT.
 

### 2013-07-23 python-simulation/TaskGenerator.py
new tests

@@ -58,7 +58,7 @@ def generateTasksFrom(utilizations, T_LCM, Tmin, Tmax, synchronous, constrDeadli
 
 	tasks = []
 	for u in utilizations:
-		O = 0 if synchronous else max(0, int(random.normalvariate(Tmin, Tmax)))
+		O = 0 if synchronous else max(0, int(random.normalvariate(Tmin, (Tmax-Tmin)/2)))
 		T = random.randrange(Tmin, Tmax) if T_LCM == -1 else random.choice(divisors)
 		C = max(1, int(round(math.floor(u*T))))
 		D = random.randint(T-(T-C)/constrDeadlineFactor, T)

### 2013-07-23 python-simulation/mainAsynchr.py

@@ -17,7 +17,7 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 		maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
 		# maxHyperT = -1
 		Tmin = 5
-		Tmax = 50
+		Tmax = 20
 		tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
 		if (verbose and numberOfSystems <= 10):
 			print "Generated task system # ", i
@@ -27,25 +27,38 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 	return systemArray
 
 if __name__ == '__main__':
-	NUMBER_OF_SYSTEMS = 10
-	for constrDeadlineFactor in range(3, 8):
-		print "CONSTR DEAD FACTOR", constrDeadlineFactor
+	NUMBER_OF_SYSTEMS = 100
+	for constrDeadlineFactor in range(1,3):
+		#print "CONSTR DEAD FACTOR", constrDeadlineFactor
 		systemArray = generateSystemArray(NUMBER_OF_SYSTEMS, constrDeadlineFactor)
+		firstDITs = []
+		upLs = []
 		for i, tau in enumerate(systemArray):
 			start = time.clock()
 			print "\t", tau
 
-			firstDIT = algorithms.findFirstPeriodicDIT(tau)
-			upL = max([task.O for task in tau.tasks]) + 2 * tau.hyperPeriod()
-			print "\tLimit :", firstDIT if firstDIT is None else firstDIT + tau.hyperPeriod(), "/", upL
+			firstDITs.append(algorithms.findFirstPeriodicDIT(tau))
+			if firstDITs[-1] is not None:
+				firstDITs[-1] += tau.hyperPeriod()
+			upLs.append(max([task.O for task in tau.tasks]) + 2 * tau.hyperPeriod())
+			print "\t", i, "Limit :", firstDITs[-1] if firstDITs[-1] is None else firstDITs[-1], "/", upLs[-1]
 
-			sizeWithDIT = len(cspace.Cspace(tau, upperLimit="def"))  # will use first DIT if it exists
-			if firstDIT is None:
-				sizeWithoutDIT = sizeWithDIT
-			else:
[…]

### 2013-07-23 dit-paper.tex
Begun to copypaste some text

--- 2013-07-19 dit-paper.tex
@@
 	\item $O_i$ (...)
-	\item And finally, choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i)$, where the value of $e$ is discussed in \ref{sct:simuRemarks}.
+	\item And finally, choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i]$, where the value of $e$ is discussed in \ref{sct:simuRemarks}.
 \end{itemize}

### 2013-07-23 dit-paper_ieee.tex

@@
 		which means that there could be systems with no first periodic DIT.
+		We now present an example of such a system.\\
+
+		\begin{center}
+		\begin{tabular}{|r|c|c|c|c|}
+		 \hline
+		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
+		 \hline
+		 $\tau_1$ & 0 & $C_1$ & 3 & 4\\
+		 \hline
+		 $\tau_2$ & 2 & $C_2$ & 7 & 8\\
+		 \hline
+		\end{tabular}
+		\end{center}
+		~\\
+
+		Here, the possible values of $a_1$ are 3 and 4, and the possible values
+		of $a_2$ are 7 and 8. For a first periodic DIT to exist, one of those
+		condition must be fulfilled:
+		\[
+		\left[
+		\begin{array}{c}
+			3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
+			3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
+			4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
+			4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
+		\end{array}
+		\right.
+		\]
+		However those four conditions are false, so the system has no first
+		periodic DIT (and no other DIT than $t=0$).
 
@@
 
-  (Work in Progress...)
+	We wanted to quantify how much systems has a first periodic DIT........
 
-  `e' factor...
+	We generated task systems by
+	\begin{itemize}
+		\item Generating utilization values with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
+		\begin{itemize}
+			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
+			\item $n$ (number of tasks) equal to 3
+		\end{itemize}
+		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
+		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
+		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
+	\end{itemize}
+	and then computed the value of the first periodic DIT.\\
+
+	We use the CDF because........
+
+	The result are represented in Fig. \ref{fig:noFPDIT}
+
+	\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit.png}
+	\end{center}
+	\label{fig:noFPDIT}
+	\end{figure}
 

### 2013-07-23 dit-paper_ieee.tex
First Periodic DIT -> FPDIT
+ removed joke

@@
 
-Keywords: Real-time systems, C-space, WCET
-
-Buzzword: sensitivity analysis
+Keywords: Real-time systems, C-space, WCET, sensitivity analysis
 \end{abstract}
@@
 		\begin{definition}
-			The \textbf{first periodic DIT} of a system is the earliest DIT occurring
+			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
 			strictly after $O_{max}$.
@@
   \label{sct:FPDITexist}
-		As in the synchronous case, the problem of existence of the first periodic DIT
+		As in the synchronous case, the problem of existence of the FPDIT
 		can be written as a system of modular equations:
@@
 		\]
-		which means that there could be systems with no first periodic DIT.
+		which means that there could be systems with no FPDIT.
 		We now present an example of such a system.\\
@@
 		Here, the possible values of $a_1$ are 3 and 4, and the possible values
-		of $a_2$ are 7 and 8. For a first periodic DIT to exist, one of those
+		of $a_2$ are 7 and 8. For a FPDIT to exist, one of those
 		condition must be fulfilled:
@@
 		\]
-		However those four conditions are false, so the system has no first
-		periodic DIT (and no other DIT than $t=0$).
+		However those four conditions are false, so the system has no FPDIT
+		(and no other DIT than $t=0$).
 
@@
 
-	We wanted to quantify how much systems has a first periodic DIT........
+	We wanted to quantify how much systems have a FPDIT........
 
@@
 	\end{itemize}
-	and then computed the value of the first periodic DIT.\\
+	and then computed the value of the FPDIT.\\
 
-	We use the CDF because........
-
-	The result are represented in Fig. \ref{fig:noFPDIT}
+	We use the CDF because........\\
 
@@
 	\end{center}
+	\caption{Evolution of the existence of FPDIT with the CDF}
 	\label{fig:noFPDIT}
 	\end{figure}
+
+	The result are represented in Fig. \ref{fig:noFPDIT}. We observe that the more we are close to the implicit deadline case, the less systems have FPDIT.
 
@@
 
+!!! (Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par 4 le nombre de contraintes)
+
 \section{Conclusion}

### 2013-07-25 python-simulation/cspace.py
More thorough second pass

@@ -75,25 +75,27 @@ def removeRedundancy(cspace):
 	# Idea:
 	# start with an empty list of cstr,
 	# add each cstr only if it is not redundant
+	# THEN test every remaining cstr against the others
 
-	# THEN do the same with what is left
-	# but in reversed order
-
-	newCspace = [cspace[0]]
-	print "first cstr : ", cspace[0]
-	for i, cstr in enumerate(cspace[1:]):
-		print "\t", i, "/", len(cspace), "\tLP with ", len(newCspace), "cstrs of size", len(newCspace[0]), ":", cstr
+	# first pass - filter against previous cstr
+	newCspace = []
+	for i, cstr in enumerate(cspace):
 		if not isRedundant(cstr, newCspace):
+			print "\tNon-redundant at step ", i, ":", cstr
 			newCspace.append(cstr)
 
-	reversedCspace = [newCspace[0]]
-	print "first cstr : ", newCspace[0]
-	for i, cstr in enumerate(newCspace[1:]):
-		print "\t", i, "/", len(newCspace), "\tLP with ", len(reversedCspace), "cstrs of size", len(reversedCspace[0]), cstr
-		if not isRedundant(cstr, reversedCspace):
-			reversedCspace.append(cstr)
+	# second pass - filter against all cstr
+	# Note that the number of cstr should be small
+	i = 0
+	while i < len(newCspace):
+		cstr = newCspace.pop(i)
+		if not isRedundant(cstr, newCspace):
+			newCspace.insert(i, cstr)
+			i += 1
+		else:
+			print "\t", cstr, "was redundant against", newCspace
 
-	return reversedCspace
+	return newCspace
 
 
 def isRedundant(cstr, cspace):
@@ -106,6 +108,8 @@ def isRedundant(cstr, cspace):
 	# 	AX <= b
 	# 	C X <= d + 1
 	# If the optimal value of the LP is > d, the
+	if len(cspace) == 0:
+		return False
 	toGLPSOLData(cspace, cstr, "redundant_temp.dat")
 	p = subprocess.Popen(["glpsol", "-m", "GLPK/redundant.mod", "-d", "redundant_temp.dat"], stdout=subprocess.PIPE)
 	(output, err) = p.communicate()

### 2013-07-25 dit-paper_ieee.tex
Description of the LIP

@@
 
-We show (...) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists.
+We show (???) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists.
 This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\
 
-To summarize, we reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
+\subsubsection{Redundancy as an integer linear problem}
+
+The general problem of redundancy of a new linear constraint $C \, X \leq d$ w.r.t. a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the following ILP:
+
+\begin{figure}[h]
+$$z = \max C \, X$$
+s.t.
+\[
+\begin{array}{rccc}
+	A & X &\leq & B \\
+	C & X &\leq & d + 1
+\end{array}
+\]
+with
+\[
+	\begin{array}{ccc}
+		A & : & [k,n] \text{ matrix}\\
+		B & : & [1,n] \text{ matrix}\\
+		C & : & [k,1] \text{ matrix}\\
+		X & : & [1,n] \text{ matrix}\\
+		d & : & \text{integer}
+	\end{array}
+\]
+\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as a ILP}
+\end{figure}
+
+Indeed, if the maximization returns $z=d+1$, it means that there are some integer values accessible with the previous constraints that the new constraint forbids.
+On the other hands, if the maximization returns $z \leq d$, it means that the limitation expressed in the new constraint is already enforced by the previous constraints.
+Therefore $z \leq d$ is a necessary and sufficient condition of redundancy of the new constraint.\\
+
+Such a linear problem can be solved by the simplex algorithm.
+However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within.
+The naive method would be to test each constraints against the set of all the others, we present an efficient preprocessing slightly more efficient approach in Algorithm \ref{alg:prunRedun}.
+
+\begin{algorithm}
+\caption{Removing redundancy - first pass}
+\label{alg:prunRedun}
+	\begin{algorithmic}[1]
+		\STATE $CSPACE$ : set of constraints
+		\STATE $S \leftarrow \emptyset$
+		\FOR{$cstr$ \textbf{in} $CSPACE$}
+			\IF {$cstr$ is not redundant w.r.t. $S$}
+				\STATE $S \leftarrow cstr$
+			\ENDIF
+		\ENDFOR
+
+		\STATE $S_2 \leftarrow \emptyset$
+		\FOR{$cstr$ \textbf{in} $S$}
+
+	\end{algorithmic}
+\end{algorithm}
+
+After doing this, no redundant constraints are left.
+However, this algorithm takes an exponential time in the number of constraints.
+An efficient initial description of $CSPACE$, as described in previous sections, is therefore preferred.\\
+
+To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
+This gives us a first correct description of the C-SPACE which is not efficient.
+We then solve a linear integer problem per constraint which allow us to determine redundancy.
 
@@
 
-!!! (Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par 4 le nombre de contraintes)
+!!! (Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par 4 le nombre de contraintes ??)
 

### 2013-07-25 dit-paper_ieee.tex
Better description of the linear problem

@@
 However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within.
-The naive method would be to test each constraints against the set of all the others, we present an efficient preprocessing slightly more efficient approach in Algorithm \ref{alg:prunRedun}.
+The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.
 
 \begin{algorithm}
-\caption{Removing redundancy - first pass}
+\caption{Removing redundancy from CSPACE}
 \label{alg:prunRedun}
@@
 		\STATE $S \leftarrow \emptyset$
+		\STATE \COMMENT{First pass - test $cstr$ against previous ones}
 		\FOR{$cstr$ \textbf{in} $CSPACE$}
@@
 		\ENDFOR
-
-		\STATE $S_2 \leftarrow \emptyset$
+		\STATE \COMMENT{Second pass - test $cstr$ against every other}
 		\FOR{$cstr$ \textbf{in} $S$}
-
+			\STATE Remove $cstr$ from $S$
+			\IF {$cstr$ is not redundant w.r.t. $S$}
+				\STATE Put $cstr$ back into $S$
+			\ENDIF
+		\ENDFOR
 	\end{algorithmic}
@@
 To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
-This gives us a first correct description of the C-SPACE which is not efficient.
-We then solve a linear integer problem per constraint which allow us to determine redundancy.
+After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.
 

### 2013-07-26 dit-paper_ieee.tex
uunisort > uunifast
More rigorous explanation of formulation & added numerical example

@@
 			\begin{definition}
-				For a given task system $\tau$ in which the $C_i$ are not known, the
-				\textbf{C-space} is a region of $n$ dimensions (where each dimension denotes
-				the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in the C-space, $\tau$ is feasible.
+				The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in it, $\tau$ is feasible.
 			\end{definition}
@@
 
-			A region of $\mathbb{N}^n$ can be described by a list of parametric linear
-			constraints describing the convex hull of that region. In other words, a
-			list of conditions which can unequivocally decide if a point is included in the region or not.\\
+			As explained in \cite{wolsey2000integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}).
+The constraints must be conditions which can unequivocally decide if a point is included in the region or not.
+In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$\footnote{For a formulation in $\mathbb{N}^n$ rather than in $\mathbb{N}_0^n$, the following inequations can be added to the formulation \[ C_i \geqslant 1 \; \forall i \]}.\\
 
-			For the synchronous case, the DBF test gives us a list of inequations
-			on the WCET values of the task set which together are a necessary and
-			sufficient condition of feasibility. They can all be written in the
-			following way:
+			The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility. They can all be written in the following way:
 			\[
@@
 
-	The value of the first DIT can be found by solving the following equation:
+	\begin{remark} (from the definitions):
+		\begin{itemize}
+			\item Contrary to other idle times, DITs are independent of the
+			scheduling or the execution times of the jobs.
+			\item In a feasible system, every DIT is an idle time.
+			\item In a feasible system, the first DIT happens after the end of the
+			first busy period.
+			\item As any $kH$ with $k \geqslant 0$ is a DIT in synchronous systems, we have at least $t_d
+			\leqslant H$ in this case.
+		\end{itemize}
+	\end{remark}
+
+	The value of the first DIT can be found by solving the following modular equation system:
 	\[
@@
 				\begin{array}{c}
+					t > 0 \\
 					t \equiv a_i \; (mod \; T_i) \\
@@
 	\]
-
-	\begin{remark} (from the definition):
-		\begin{itemize}
-			\item Contrary to other idle times, DITs are independent of the
-			scheduling or the execution times of the jobs.
-			\item In a feasible system, every DIT is an idle time.
-			\item In a feasible system, the first DIT happens at the end of the
-			first busy period.
-			\item As $H$ is always a DIT in synchronous systems, we have at least $t_d
-			\leqslant H$ in this case.
-		\end{itemize}
-	\end{remark}
+	The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.\\
 
 	Every DIT being an idle instant, the execution of the system after a DIT does
-	not depend on what happened before. Because the synchronous arrival pattern is
+	not depend on the execution before it. Because the synchronous arrival pattern is
 	the worst case [citation needed], it is sufficient for the DBF test to only
@@
 	To summarize, we reduced the description of the C-space from an infinite number
-	of constraints to only the inequations where $t_1 = 0$, $t_2 \leqslant t_d$ and
+	of constraints to only those where $t_1 = 0$, $t_2 \leqslant t_d$ and
 	values of $t_2$ correspond to job deadlines. Note that the number of
@@
 		the concept of DIT adapted to the asynchronous case called first periodic DIT
-		($t_d$), along with an algorithm to find its value. In Section
+		($t_d$), along with an algorithm to find its value for any period values. In Section
 		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
 		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
-		sufficient to consider.
+		sufficient to consider. In section ???, we present a simulation where we find that........
 
@@
 
+	\subsection{Solving the modular system}
+
+	PAUL PAUL PAUL ?
+
 	\subsection{Simulation}
@@
 	\begin{itemize}
-		\item Generating utilization values with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
+		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters
 		\begin{itemize}
@@
   The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant.
-Therefore the C-space is still described by the following infinite number of constraints:$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
+Therefore the C-space is still accurately described by the following infinite number of constraints:$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
 
@@
 		B & : & [1,n] \text{ matrix}\\
-		C & : & [k,1] \text{ matrix}\\
+		C & : & [n,1] \text{ matrix}\\
 		X & : & [1,n] \text{ matrix}\\
@@
 \]
-\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as a ILP}
+\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
 \end{figure}
@@
 However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within.
-The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.
+The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.\\
 
@@
 		\STATE $S \leftarrow \emptyset$
-		\STATE \COMMENT{First pass - test $cstr$ against previous ones}
+		\STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
 		\FOR{$cstr$ \textbf{in} $CSPACE$}
@@
 		\ENDFOR
-		\STATE \COMMENT{Second pass - test $cstr$ against every other}
+		\STATE \COMMENT{$2^{nd}$ pass: test each $cstr$ against every other}
 		\FOR{$cstr$ \textbf{in} $S$}
@@
 		\ENDFOR
+		\RETURN{S}
 	\end{algorithmic}
@@
 However, this algorithm takes an exponential time in the number of constraints.
-An efficient initial description of $CSPACE$, as described in previous sections, is therefore preferred.\\
+An efficient initial description of $CSPACE$, as given by the methods described in previous sections, is therefore preferred.\\
 
@@
 After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.
+Note that
+
+\subsection{Numerical Example}
+
+Consider the following task system
+
+		\begin{center}
+		\begin{tabular}{|r|c|c|c|c|}
+		 \hline
+		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
+		 \hline
+		 $\tau_1$ & 5 & $C_1$ & 4 & 9\\
+		 \hline
+		 $\tau_2$ & 0 & $C_2$ & 12 & 14\\
+		 \hline
+		\end{tabular}
+		\end{center}
+		~\\
+
+The FPDIT happens at $t=12$ and $H = 126$.
+The study interval using the FPDIT is thus $[12, 138]$, which contains 261 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $12 \leqslant a < d \leqslant 138$.
+For comparison, the more pessimistic study interval is $[5, 257]$ which yields 1006 intervals.\\
+
+We now apply the
 

### 2013-07-26 dit-paper_ieee.tex
corrected reference to the Wolsey book

@@
 
-			As explained in \cite{wolsey2000integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}).
+			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}).
 The constraints must be conditions which can unequivocally decide if a point is included in the region or not.

### 2013-07-26 dit-paper_ieee.tex
- multiprocess : killing workers when the parent dies - tex : typo

--- 2013-07-25 dit-paper_ieee.tex
@@
 
-	The DBF allows to give a necessary and sufficient condition of feasibility:
+	A necessary and sufficient condition of feasibility can easily be written
+	based on the DBF:
 

### 2013-07-26 python-simulation/main.py

@@ -18,7 +18,7 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 		maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
 		# maxHyperT = -1
 		Tmin = 2
-		Tmax = 50
+		Tmax = 25
 		tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
 		if (verbose and numberOfSystems <= 10):
 			print "Generated task system # ", i

### 2013-07-26 python-simulation/multithread.py

@@ -1,10 +1,23 @@
+import main
+import algorithms
+
 import multiprocessing
 import array
-import main
 import time
-import algorithms
 import pylab	
 import sys
+import atexit
+import os
+import signal
+
+def cleanup():
+	pList = multiprocessing.active_children()
+	for p in pList:
+		os.kill(p.pid(),signal.SIGKILL)
+# 		p.terminate()
+		
+atexit.register(cleanup)
+	
 
 class WorkThread(object):
 	def __init__(self, cdfIndex, numSystems, numCdfValues):
@@ -31,6 +44,8 @@ class WorkThread(object):
 			
 	def runSystems(self,numberOfSystems, constrDeadlineFactor):
 		systemArray = main.generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False)
+		print "systems generated"
+		sys.stdout.flush()
 		verbose = False
 	
 		# Upper Limit Arrays
@@ -54,12 +69,15 @@ class WorkThread(object):
  		bpStop = time.clock()
 	
 	
-# 		print "Thread", self.cdfIndex, "starting DIT value computation..."
+		print "CDF Index", self.cdfIndex, "starting hyperperiod computation..."
+		sys.stdout.flush()
 		hyperTStart = time.clock()
 		for i, tau in enumerate(systemArray):
 			hyperTs.append(tau.hyperPeriod())
 		hyperTMedium = time.clock()
 		for i, tau in enumerate(systemArray):
+			print "CDF Index", self.cdfIndex, "system", i
+			sys.stdout.flush()
 			hyperTResults.append(algorithms.dbfTest(tau))
 		hyperTStop = time.clock()
 
@@ -92,10 +110,17 @@ class WorkThread(object):
 # 		self.outLock.release()
 	
 		return bpStop - bpMedium, bpMedium - bpStart, ditStop - ditMedium, ditMedium - ditStart, hyperTStop - hyperTMedium, hyperTMedium - hyperTStart
-	
+
 def processRun(cdfIndex, numSystems, numCdfValues, resQueue, globalCdfIndex, cdfArray, resLock, outLock):
 	work = WorkThread(cdfIndex, numSystems, numCdfValues)
 	work.run(resQueue, globalCdfIndex, cdfArray, resLock, outLock)
+	
+# def zombieKiller(masterQueue, workerPidList):
+# 	master = masterQueue.get()
[…]

### 2013-07-26 dit-paper_ieee.tex
Added numerical example

--- 2013-07-26 dit-paper_ieee.tex
@@
 			\[
-				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
-				t_1 \leq t_2
+				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
 			\]
@@
 	the worst case [citation needed], it is sufficient for the DBF test to only
-	consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\
+	consider intervals $[0, t]$ with $t$ being a deadline before or at the first DIT.\\
 
@@
 		the concept of DIT adapted to the asynchronous case called first periodic DIT
-		($t_d$), along with an algorithm to find its value for any period values. In Section
+		($t_d$), along with an algorithm to determine its existence and value for any system. In Section
 		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
@@
 
-	PAUL PAUL PAUL ?
+	(Paul ?)
 
@@
 
+(Remarque : Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par exactement 4 le nombre de contraintes ??)
+
 \subsubsection{Redundancy as an integer linear problem}
@@
 		 \hline
-		 $\tau_1$ & 5 & $C_1$ & 4 & 9\\
+		 $\tau_1$ & 8 & $C_1$ & 7 & 15\\
 		 \hline
-		 $\tau_2$ & 0 & $C_2$ & 12 & 14\\
+		 $\tau_2$ & 0 & $C_2$ & 2 & 5\\
 		 \hline
@@
 
-The FPDIT happens at $t=12$ and $H = 126$.
-The study interval using the FPDIT is thus $[12, 138]$, which contains 261 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $12 \leqslant a < d \leqslant 138$.
-For comparison, the more pessimistic study interval is $[5, 257]$ which yields 1006 intervals.\\
+The FPDIT happens at $t=15$ and we have $H = 15$.
+The study interval using the FPDIT is thus $[15, 30]$, which contains 11 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $15 \leqslant a < d \leqslant 30$.
+Those intervals are
+$[15, 17]$, $[15, 22]$, $[15, 27]$, $[15, 30]$, $[20, 22]$, $[20, 27]$, $[20, 30]$, $[23, 27]$, $[23, 30]$, $[25, 27]$ and $[25, 30]$.
+For comparison, the more pessimistic study interval is $[8, 38]$ which yields 57 intervals.\\
 
-We now apply the
+For each $[a, d]$, we have a constraint $$\sum_{i=0}^{n-1} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.\\
+
+We now apply algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
+$$
+\left\{
+	\begin{array}{ccccc}
+		& & C_2 & \leqslant & 2 \\
+		C_1 & + & C_2 & \leqslant & 7
+	\end{array}
+\right.
+$$
+The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.\\
+
+Let us now consider the same system but with a synchronous pattern of arrival.
+
+		\begin{center}
+		\begin{tabular}{|r|c|c|c|c|}
+		 \hline
+		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
+		 \hline
+		 $\tau_1$ & 0 & $C_1$ & 7 & 15\\
+		 \hline
+		 $\tau_2$ & 0 & $C_2$ & 2 & 5\\
+		 \hline
+		\end{tabular}
+		\end{center}
+		~\\
+
+The first DIT happens at time $t_d = 7$.
+The intervals to consider are thus of the form $[0, t]$ where $t$ is a deadline happening before or at time $t_d$.
+This yields 2 intervals ($[0, 2]$ and $[0, 7]$) and the following constraints describing the C-space, none of them being redundant:
+$$
+\left\{
+	\begin{array}{ccccc}
+		& & C_2 & \leqslant & 2 \\
+		C_1 & + & 2 C_2 & \leqslant & 7
+	\end{array}
+\right.
+$$
+This time, the C-space only contains 8 points: $(1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$.\\
+
+Fig. \ref{fig:cspaceComp} shows the two C-spaces in the plane.
+
+\begin{figure}[h]
+\begin{center}
+	\includegraphics[width=0.5\textwidth]{figs/cspace_example.png}
+	\caption{C-space of an asynchronous system and its corresponding synchronous system}
+	\label{fig:cspaceComp}
+\end{center}
+\end{figure}
 
 \section{Example}
-
-!!! (Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par 4 le nombre de contraintes ??)
 

### 2013-07-26 python-simulation/cspace.py

@@ -190,7 +190,7 @@ if __name__ == '__main__':
 	assert len(tau_Cspace) > len(tau_Cspace_noredun) == 2, str(tau_Cspace_noredun)
 
 	# RANDOM TEST
-	NUMBER_OF_SYSTEMS = 1
+	NUMBER_OF_SYSTEMS = 10
 	systemArray = generateSystemArray(NUMBER_OF_SYSTEMS, 1)
 	for tau in systemArray:
 		print tau
@@ -201,7 +201,10 @@ if __name__ == '__main__':
 		cspace_noredun = removeRedundancy(cspace)
 		print len(cspace), "=>", len(cspace_noredun), "equations left"
 		print ""
-		assert testCVector(cspace_noredun, [task.C for task in tau.tasks]) == testCVector(cspace, [task.C for task in tau.tasks]) == algorithms.dbf_test(tau)
+		resultCSPACE = testCVector(cspace_noredun, [task.C for task in tau.tasks])
+		resultCSPACENOREDUN = testCVector(cspace, [task.C for task in tau.tasks])
+		resultDBF = algorithms.dbf_test(tau)
+		assert resultCSPACE == resultCSPACENOREDUN == resultDBF, str(resultCSPACE) + str(resultCSPACENOREDUN) + str(resultDBF)
 		print "redundancy (necessary) condition ok"
 		print "synchronous instant", algorithms.findSynchronousInstant(tau)
 		print "cspacesize", CspaceSize(tau, cspace_noredun)

### 2013-07-26 dit-paper_ieee.tex
- FPDIT calculation method

--- 2013-07-26 dit-paper_ieee.tex
@@
 		Here, the possible values of $a_1$ are 3 and 4, and the possible values
-		of $a_2$ are 7 and 8. For a FPDIT to exist, one of those
-		condition must be fulfilled:
+		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
+		conditions must be fulfilled:
 		\[
@@
 		\]
-		However those four conditions are false, so the system has no FPDIT
-		(and no other DIT than $t=0$).
+		However those four conditions cannot be satisfied, which means the system has
+		no FPDIT (and no other DIT than $t=0$).
 
 	\subsection{Solving the modular system}
+		Finding the FPDIT of a system is similar to finding a synchronous instant of
+		this system (an instant at which all tasks release a job simultaneously), but
+		with weaker constraints. That is, the FPDIT is an instant after the last
+		deadline of all tasks, but before the next arrival time of all tasks. Finding
+		a synchronous instant is equivalent to finding a solution $t$ for the
+		following set of constraints :
+		\[
+			\left\{
+			\begin{array}{l}
+				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
+				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
+			\end{array}
+			\right.
+		\]
+		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
+		is not possible to directly use a solver for the CRP as in a task system,
+		$T_i$ values could have common factors. However, the instance can be modified
+		(each constraint with a non-prime period can be split into powers of primes
+		without changing the solution if there is one) in order to make the problem
+		solvable through applying a solution for the CRP. \\
 
-	PAUL PAUL PAUL ?
+		Now that we have a solver for the problem of finding a synchronous instant, we
+		actually also have a solver for finding the FPDIT. The problem of finding the
+		first DIT is the same as finding all the possible DIT then taking the minimum.
+		Each of those DIT corresponds to a unique combination of $a_i$ values (one
+		for each task). Finding one of such DIT is the same problem as finding a
+		synchronous instant :
+		\[
+			\left\{
+			\begin{array}{l}
+				t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
+				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
+			\end{array}
+			\right.
+		\]
+		all DITs can be found by solving the equivalent CRP problem for all
+		combinations of $a_i$ values. This is however very inefficient as there are
+		exponentially many different combinations of $a_i$ values in the number of
+		tasks.\\
+
+		A better method for finding the FPDIT consists in splitting the algorithm that
+		is used to solve the CRP in two separate parts. The algorithm requires
+		calculating one modular inverse for each task.
 

### 2013-07-26 dit-paper_ieee.tex

--- 2013-07-26 dit-paper_ieee.tex
@@
 		\]
-		However those four conditions are false, so the system has no FPDIT
-		(and no other DIT than $t=0$).
+		However those four conditions cannot be satisfied, which means the system has
+		no FPDIT (and no other DIT than $t=0$).
 
 	\subsection{Solving the modular system}
+		Finding the FPDIT of a system is similar to finding a synchronous instant of
+		this system (an instant at which all tasks release a job simultaneously), but
+		with weaker constraints. That is, the FPDIT is an instant after the last
+		deadline of all tasks, but before the next arrival time of all tasks. Finding
+		a synchronous instant is equivalent to finding a solution $t$ for the
+		following set of constraints :
+		\[
+			\left\{
+			\begin{array}{l}
+				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
+				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
+			\end{array}
+			\right.
+		\]
+		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
+		is not possible to directly use a solver for the CRP as in a task system,
+		$T_i$ values could have common factors. However, the instance can be modified
+		(each constraint with a non-prime period can be split into powers of primes
+		without changing the solution if there is one) in order to make the problem
+		solvable through applying a solution for the CRP. \\
 
-	(Paul ?)
+		Now that we have a solver for the problem of finding a synchronous instant, we
+		actually also have a solver for finding the FPDIT. The problem of finding the
+		first DIT is the same as finding all the possible DIT then taking the minimum.
+		Each of those DIT corresponds to a unique combination of $a_i$ values (one
+		for each task). Finding one of such DIT is the same problem as finding a
+		synchronous instant :
+		\[
+			\left\{
+			\begin{array}{l}
+				t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
+				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
+			\end{array}
+			\right.
+		\]
+		all DITs can be found by solving the equivalent CRP problem for all
+		combinations of $a_i$ values. This is however very inefficient as there are
+		exponentially many different combinations of $a_i$ values in the number of
+		tasks.\\
+
+		A better method for finding the FPDIT consists in splitting the algorithm that
+		is used to solve the CRP in two separate parts. The algorithm requires
+		calculating one modular inverse for each task. %TODO continue
 

### 2013-07-26 dit-paper_ieee.tex
- tex: new CRP

@@
 \newcommand{\dbf}[1]{\operatorname{dbf}(#1)}
+
+\algsetup{
+	indent=2em,
+	linenosize=\small,
+	linenodelimiter=\ 
+}
 
@@
 	therefore not usable, or at least not for the purposes of this paper. The
-	following concept is thus introduced, which is similar to the end of the busy period but which does not depend on the execution times.
+	following concept is thus introduced, which is similar to the end of the busy period but does not depend on the execution times.
 
@@
 		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
-		is not possible to directly use a solver for the CRP as in a task system,
-		$T_i$ values could have common factors. However, the instance can be modified
-		(each constraint with a non-prime period can be split into powers of primes
+		is not possible to directly use a solver for the CRP (such as Gauss's
+		algorithm) as in a task system, $T_i$ values could have common factors.
+		However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
 		without changing the solution if there is one) in order to make the problem
@@
 
-		A better method for finding the FPDIT consists in splitting the algorithm that
-		is used to solve the CRP in two separate parts. The algorithm requires
-		calculating one modular inverse for each task. %TODO continue
+		A better method for finding the FPDIT consists in splitting Gauss's algorithm
+		into two separate parts. The global structure is simply a sum of factors, each
+		term being dependant on which $a_i$ value is chosen. A major speedup can
+		be acheived by first computing all possible terms for each task (only one
+		modular inverse must be computed per task that way) then creating all possible DIT values
+		by summing the terms in all possible ways. The number of results is still
+		exponential in the number of tasks, but the only operation that is repeated
+		exponentially many times is now a sum.
 

### 2013-07-26 dit-paper_ieee.tex
i dunno

--- 2013-07-26 dit-paper_ieee.tex
@@
 
-The first periodic DIT, if it exists, must occur in the transitive period.
+The FPDIT, if it exists, must occur in the transitive period.
 Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).\\
 
+As the FPDIT happened when all tasks were in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$)
 We show (???) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists.
@@
 Such a linear problem can be solved by the simplex algorithm.
-However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within.
-The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.\\
+However, in our case the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within.
+A naive method would be to test each constraint against all the others.
+We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.\\
 
@@
 
-\subsection{Numerical Example}
+\section{Numerical Example}
 
@@
 
-We now apply algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
+We now apply Algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
 $$
@@
 
-\section{Example}
-
 \section{Conclusion}

### 2013-07-26 dit-paper_ieee.tex

@@
 \newcommand{\dbf}[1]{\operatorname{dbf}(#1)}
+
+\algsetup{
+	indent=2em,
+	linenosize=\small,
+	linenodelimiter=\
+}
 

### 2013-07-29 dit-paper_ieee.tex
- title
small changes

@@
 The constraints must be conditions which can unequivocally decide if a point is included in the region or not.
-In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$\footnote{For a formulation in $\mathbb{N}^n$ rather than in $\mathbb{N}_0^n$, the following inequations can be added to the formulation \[ C_i \geqslant 1 \; \forall i \]}.\\
+In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ to the formulation).\\
 
@@
 
-As the FPDIT happened when all tasks were in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$)
-We show (???) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists.
+As the FPDIT happens when all tasks are in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$).
+We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the FPDIT exists.
 This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\

### 2013-07-29 dit-paper_ieee.tex
typos and citations

@@
 
-\title{Describing the C-space of asynchronous periodic task using DIT}
+\title{Describing the C-Space of Asynchronous Periodic Task Systems using
+Definitive Idle Times}
 
@@
 The constraints must be conditions which can unequivocally decide if a point is included in the region or not.
-In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ to the formulation).\\
+In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ in the list of constraints).\\
 
@@
 		\]
-		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
+		which is very similar to an instance of the Chinese Remainder Problem (CRP). It
 		is not possible to directly use a solver for the CRP (such as Gauss's
-		algorithm) as in a task system, $T_i$ values could have common factors.
+		algorithm \cite{gauss1965disquisitiones}) as in a task system, $T_i$ values could have common factors.
 		However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
@@
 		into two separate parts. The global structure is simply a sum of factors, each
-		term being dependant on which $a_i$ value is chosen. A major speedup can
-		be acheived by first computing all possible terms for each task (only one
+		term being dependent on which $a_i$ value is chosen. A major speedup can
+		be achieved by first computing all possible terms for each task (only one
 		modular inverse must be computed per task that way) then creating all possible DIT values

### 2013-07-29 dit-paper_ieee.tex
Corrected matrix size

@@
 
-(Remarque : Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par exactement 4 le nombre de contraintes ??)
+(Remarque : Avec seulement cette méthode, si un DIT existe on divisera toujours par exactement 4 le nombre de contraintes par rapport à $O_{max} + 2H$)
 
@@
 	\begin{array}{ccc}
-		A & : & [k,n] \text{ matrix}\\
-		B & : & [1,n] \text{ matrix}\\
+		A & : & [n,k] \text{ matrix}\\
+		B & : & [n,1] \text{ matrix}\\
 		C & : & [n,1] \text{ matrix}\\
@@
 
-Such a linear problem can be solved by the simplex algorithm.
+Such a linear problem can be solved by e.g.
+the simplex algorithm and a branch-and-cut approach.
 However, in our case the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within.
@@
 After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.
-Note that
 
@@
 $[15, 17]$, $[15, 22]$, $[15, 27]$, $[15, 30]$, $[20, 22]$, $[20, 27]$, $[20, 30]$, $[23, 27]$, $[23, 30]$, $[25, 27]$ and $[25, 30]$.
-For comparison, the more pessimistic study interval is $[8, 38]$ which yields 57 intervals.\\
+For comparison, the original study interval of $[O_{max}, O_{max} + 2H]$ is $[8, 38]$ which yields 57 intervals.\\
 

### 2013-07-29 dit-paper_ieee.tex
- shortened FPDIT calculation text

--- 2013-07-29 dit-paper_ieee.tex
@@
 	\subsection{Solving the modular system}
-		Finding the FPDIT of a system is similar to finding a synchronous instant of
-		this system (an instant at which all tasks release a job simultaneously), but
-		with weaker constraints. That is, the FPDIT is an instant after the last
-		deadline of all tasks, but before the next arrival time of all tasks. Finding
-		a synchronous instant is equivalent to finding a solution $t$ for the
-		following set of constraints :
-		\[
-			\left\{
-			\begin{array}{l}
-				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
-				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
-			\end{array}
-			\right.
-		\]
-		which is very similar to an instance of the Chinese Remainder Problem (CRP). It
-		is not possible to directly use a solver for the CRP (such as Gauss's
-		algorithm \cite{gauss1965disquisitiones}) as in a task system, $T_i$ values could have common factors.
-		However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
-		without changing the solution if there is one) in order to make the problem
-		solvable through applying a solution for the CRP. \\
+		Finding the FPDIT of a system is similar to finding at least one synchronous
+		instant (an instant at which all tasks release a job simultaneously) out of a
+		collection of systems with different offsets. The existence conditions can
+		directly be used to calculate the value of the FPDIT (if there is one),
+		because for a given set of $a_i$ values they are very similar to an instance
+		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
+		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}. \\
 
-		Now that we have a solver for the problem of finding a synchronous instant, we
-		actually also have a solver for finding the FPDIT. The problem of finding the
-		first DIT is the same as finding all the possible DIT then taking the minimum.
-		Each of those DIT corresponds to a unique combination of $a_i$ values (one
-		for each task). Finding one of such DIT is the same problem as finding a
-		synchronous instant :
-		\[
-			\left\{
-			\begin{array}{l}
-				t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
-				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
-			\end{array}
-			\right.
-		\]
-		all DITs can be found by solving the equivalent CRP problem for all
-		combinations of $a_i$ values. This is however very inefficient as there are
-		exponentially many different combinations of $a_i$ values in the number of
-		tasks.\\
-
-		A better method for finding the FPDIT consists in splitting Gauss's algorithm
-		into two separate parts. The global structure is simply a sum of factors, each
-		term being dependent on which $a_i$ value is chosen. A major speedup can
-		be achieved by first computing all possible terms for each task (only one
-		modular inverse must be computed per task that way) then creating all possible DIT values
-		by summing the terms in all possible ways. The number of results is still
+		However this is very inefficient as there are exponentially many different
+		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
+		algorithm into two separate parts. Its global structure is simply a sum of
+		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
+		be achieved by first computing all possible terms for each task then creating all
+		possible DIT values by summing the terms in all possible ways. The number of results is still
 		exponential in the number of tasks, but the only operation that is repeated

### 2013-07-29 dit-paper_ieee.tex
- small changes
- ilovetabs.gif

@@
 	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel
-turpis ultricies vulputate vel at arcu.
-Curabitur lectus metus, rutrum sed malesuada ut, mollis sit amet mauris.
-Integer dapibus in risus et porttitor.
-In hac habitasse platea dictumst.
-Maecenas dolor libero, suscipit porta consequat eu, consequat non orci.
-Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum.
-Aenean tempor est nisl, at dictum metus elementum iaculis.\\
+	turpis ultricies vulputate vel at arcu. Curabitur lectus metus, rutrum sed
+	malesuada ut, mollis sit amet mauris. Integer dapibus in risus et porttitor. In
+	hac habitasse platea dictumst. Maecenas dolor libero, suscipit porta consequat
+	eu, consequat non orci. Sed tortor neque, tincidunt congue cursus sit amet,
+	luctus id ipsum. Aenean tempor est nisl, at dictum metus elementum iaculis.\\
 
@@
 	precise and efficient description of its C-space would allow to quickly decide
-	if a system is feasible on a given platform.\\
+	whether or not a system is feasible on a given platform.\\
 
@@
 				\hline
-		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
-		 \hline
-		 $\tau_1$ & 0 & $C_1$ & 3 & 4\\
-		 \hline
-		 $\tau_2$ & 2 & $C_2$ & 7 & 8\\
-		 \hline
+							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
+				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
+				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
 			\end{tabular}
@@
 
-  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant.
-Therefore the C-space is still accurately described by the following infinite number of constraints:$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
+		The description we presented in Section \ref{sct:cspaceDescr} was general, and
+		is thus still relevant. Therefore the C-space is still accurately described by
+		the following infinite number of constraints:
 
-  However, the method used in the synchronous case to remove redundancy does not apply here. A more general approach is presented in the following section.
+		\[
+			\sum_{i=0}^{n-1} n_i(t_1, t_2)
+			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+		\]
+
+		However, the method used in the synchronous case to remove redundancy does not
+		apply here. A more general approach is presented in the following section.
 
@@
 		\subsubsection{Job arrival and deadline}
+			Consider an interval $[t_1, t_2]$. If $t_2$ is an instant without any job
+			deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to
+			$\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.\\
 
-Consider an interval $[t_1, t_2]$.
-If $t_2$ is an instant without any job deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to $\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.\\
-
-A similar argument can be made if $t_1$ is an instant without any job arrival (and $t_1^*$ is the earliest arrival after $t_1$).
-We can thus restricts ourselves to intervals where $t_1$ is an instant with at least one job arrival, and $t_2$ is an instant with at least one job deadline.
+			A similar argument can be made if $t_1$ is an instant without any job arrival
+			(and $t_1^*$ is the earliest arrival after $t_1$). We can thus restricts
+			ourselves to intervals where $t_1$ is an instant with at least one job
+			arrival, and $t_2$ is an instant with at least one job deadline.
 
 		\subsubsection{Feasibility interval}
-
-  First let us recall how an asynchronous system behaves under an optimal scheduler, for example EDF.\\
+			First let us recall how an asynchronous system behaves under an optimal
+			scheduler, for example EDF.\\
 
@@
 									& \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
-			\text{Name} & \text{period} & \text{period} & \text{period}  & \\
-			\hline
-			\text{size} & O_{max} & H & H & \cdots \\
-			\hline
+						\text{Name} & \text{period} 	& \text{period} 	& \text{period}  	& \\ \hline
+						\text{size} & O_{max} 			& H 				& H 				& \cdots \\ \hline
 						t \geqslant & 0 				& O_{max} 			& O_{max} + H 		& \cdots

### 2013-07-29 python-simulation/multiprocess.py
- refactor multiprocess

@@ -19,7 +19,7 @@ def cleanup():
 atexit.register(cleanup)
 	
 
-class WorkThread(object):
+class Worker(object):
 	def __init__(self, cdfIndex, numSystems, numCdfValues):
 		self.cdfIndex = cdfIndex
 		self.numCdfValues = numCdfValues
@@ -112,7 +112,7 @@ class WorkThread(object):
 		return bpStop - bpMedium, bpMedium - bpStart, ditStop - ditMedium, ditMedium - ditStart, hyperTStop - hyperTMedium, hyperTMedium - hyperTStart
 
 def processRun(cdfIndex, numSystems, numCdfValues, resQueue, globalCdfIndex, cdfArray, resLock, outLock):
-	work = WorkThread(cdfIndex, numSystems, numCdfValues)
+	work = Worker(cdfIndex, numSystems, numCdfValues)
 	work.run(resQueue, globalCdfIndex, cdfArray, resLock, outLock)
 	
 # def zombieKiller(masterQueue, workerPidList):
@@ -122,15 +122,15 @@ def processRun(cdfIndex, numSystems, numCdfValues, resQueue, globalCdfIndex, cdf
 # 		os.kill(worker, signal.SIGKILL)
 # 	sys.exit()
 		
-class ThreadManager(object):
+class ProcessManager(object):
 	def __init__(self,cdf,threadCountLimit,numSystems):
 		self.resultsQueue = multiprocessing.Queue()
 		self.stdoutLock = multiprocessing.Lock()
 		self.numSystems = numSystems
 		self.cdf = multiprocessing.Array('d', cdf)
 		self.numCdfValues = len(self.cdf)
-		self.threadCountLimit = min(threadCountLimit,self.numCdfValues)
-		self.threadList = []
+		self.processCountLimit = min(threadCountLimit,self.numCdfValues)
+		self.workerList = []
 		self.bpValue = array.array('f',[0.0])*self.numCdfValues
 		self.bpTest = array.array('f',[0.0])*self.numCdfValues
 		self.bpAll = array.array('f',[0.0])*self.numCdfValues
@@ -146,16 +146,16 @@ class ThreadManager(object):
 		resLock = multiprocessing.Lock()
 		outLock = multiprocessing.Lock()
 		resLock.acquire()
-		for i in range(self.threadCountLimit):
+		for i in range(self.processCountLimit):
[…]

### 2013-07-29 python-simulation/algorithms.py
Change call to function dbfTest with new name

@@ -161,7 +161,7 @@ if __name__ == '__main__':
 	# No busy period test as it does not make sense in asynchronous system
 	assert findFirstPeriodicDIT(tau) == 6, "Unit Test FAIL : findFirstDIT (4a); " + "returned: " + str(findFirstDIT(tau))
 	assert findSynchronousInstant(tau) == 8, "Unit Test FAIL : findSynchronousInstant (4a); " + "returned: " + str(findSynchronousInstant(tau))
-	#assert dbf_test(tau) is True
+	#assert dbfTest(tau) is True
 
 	tasks = []
 	#                      0, C, D, T

### 2013-07-29 python-simulation/cspace.py

@@ -128,6 +128,7 @@ def toGLPSOLData(cspace, cstr, filename):
 		f.write(str(cstr[-1]))
 		f.write(";\n")
 
+
 def CspaceSize(tau, cspace=None):
 	if cspace is None:
 		cspace = Cspace(tau)
@@ -135,6 +136,7 @@ def CspaceSize(tau, cspace=None):
 	for task in tau.tasks:
 		cValues.append((c for c in range(1, task.D + 1)))
 	return len(filter(lambda cvector: testCVector(cspace, cvector), itertools.product(*cValues)))
+
 
 def testCVector(cspace, cvector):
 	for i, equation in enumerate(cspace):
@@ -153,7 +155,7 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 		Umin = 0.25
 		Umax = 0.75
 		Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
-		n = 2
+		n = 3
 		# maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
 		maxHyperT = -1
 		Tmin = 5
@@ -202,7 +204,7 @@ if __name__ == '__main__':
 		print ""
 		resultCSPACE = testCVector(cspace_noredun, [task.C for task in tau.tasks])
 		resultCSPACENOREDUN = testCVector(cspace, [task.C for task in tau.tasks])
-		resultDBF = algorithms.dbf_test(tau)
+		resultDBF = algorithms.dbfTest(tau)
 		assert resultCSPACE == resultCSPACENOREDUN == resultDBF, str(resultCSPACE) + str(resultCSPACENOREDUN) + str(resultDBF)
 		print "redundancy (necessary) condition ok"
 		print "synchronous instant", algorithms.findSynchronousInstant(tau)

### 2013-07-29 dit-paper_ieee.tex
new latex template

--- 2013-07-29 dit-paper_ieee.tex
@@
+%% bare_conf.tex
+%% V1.3
+%% 2007/01/11
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE!
+%% User assumes all risk.
+%% In no event shall IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%
+%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
+%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. IEEE's font choices can trigger bugs that do  ***
+% *** not appear when using other class files.                            ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
 %
-%  $Description: Author guidelines and sample document in LaTeX 2.09$
-%
-%  $Author: ienne, modified by Laurent George $
-%  $Date: 2012/02/02 15:20:59 $
-%  $Revision: 1.5 $
+\documentclass[conference]{IEEEtran}
+\usepackage{cite}
+\ifCLASSINFOpdf
+  \usepackage[pdftex]{graphicx}
+\fi
+\usepackage[cmex10]{amsmath}
+\usepackage{algorithmic}
+\usepackage{array}
+\usepackage{fixltx2e}
+\usepackage{url}
 
-\documentclass[times, 10pt,twocolumn, a4paper]{article}
-\usepackage{latex8}
-\usepackage{epsfig, hhline}
+% added
 \usepackage{amssymb}
-\usepackage{vmargin,array,multirow,float,shadow,times, euscript}
-\usepackage{amsmath}
-\usepackage{algorithmic}
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage{pdftricks}
-\usepackage{stmaryrd}
 
@@
 
-%\newenvironment{accolade}{\begin{centering} $$ \left\{ \begin{array}{l}}{\end{array} \right. $$ \end{centering}}
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
-%-------------------------------------------------------------------------
-% take the % away on next line to produce the final camera-ready version
-\pagestyle{empty}
-
-%-------------------------------------------------------------------------
 \begin{document}
-
+%
+% paper title
+% can use linebreaks \\ within to get better formatting as desired
 \title{Describing the C-Space of Asynchronous Periodic Task Systems using
@@
 
-\author{Thomas Chapeaux, Paul Rodriguez\\
-Universit\'e Libre de Bruxelles\\ tchapeau@ulb.ac.be, paurodri@ulb.ac.be \\
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
+% author names and affiliations
+% use a multiple column layout for up to three different
+% affiliations
+\author{
+\IEEEauthorblockN{Thomas Chapeaux\\ and Paul Rodriguez}
+\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
+Adresse\\
+Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
 \and
-Laurent George\\
-ECE Paris\\
-First line of institution2 address\\ Second line of institution2 address\\
-lgeorge@ece.fr\\
+\IEEEauthorblockN{Laurent George\\ and Jean-Fran\c{c}ois Hermant}
+\IEEEauthorblockA{ECE Paris\\
+Adresse\\
+Email}
 }
-
+% make the title area
 \maketitle
-\thispagestyle{empty}
 
 \begin{abstract}
+%\boldmath
   Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel
@@
 Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum.
-Aenean tempor est nisl, at dictum metus elementum iaculis.\\
+Aenean tempor est nisl, at dictum metus elementum iaculis
+\end{abstract}
+% no keywords
 
-Keywords: Real-time systems, C-space, WCET, sensitivity analysis
-\end{abstract}
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
@@
     n_i(t_1, t_2) =
-		\left\llbracket
+    \left(
       \left\lfloor
@@
       \right\rceil + 1
-		\right\rrbracket_0
+    \right)_0
   \]
-	where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.\\
+  where $( x )_0$ stands for $\max \{ 0, x \}$.\\
 
@@
 
-			The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility. They can all be written in the following way:
+      The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility.
+They can all be written in the following way:
       \[
@@
   \subsection{Solving the modular system}
-		Finding the FPDIT of a system is similar to finding at least one synchronous
-		instant (an instant at which all tasks release a job simultaneously) out of a
-		collection of systems with different offsets. The existence conditions can
-		directly be used to calculate the value of the FPDIT (if there is one),
-		because for a given set of $a_i$ values they are very similar to an instance
-		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
-		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}. \\
+    Finding the FPDIT of a system is similar to finding a synchronous instant of
+    this system (an instant at which all tasks release a job simultaneously), but
+    with weaker constraints. That is, the FPDIT is an instant after the last
+    deadline of all tasks, but before the next arrival time of all tasks. Finding
+    a synchronous instant is equivalent to finding a solution $t$ for the
+    following set of constraints :
+    \[
+      \left\{
+      \begin{array}{l}
+        t \geqslant O_i \: \forall \: \tau_i \in \tau \\
+        t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
+      \end{array}
+      \right.
+    \]
+    which is very similar to an instance of the Chinese Remainder Problem (CRP). It
+    is not possible to directly use a solver for the CRP (such as Gauss's
+    algorithm \cite{gauss1965disquisitiones}) as in a task system, $T_i$ values could have common factors.
+    However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
+    without changing the solution if there is one) in order to make the problem
+    solvable through applying a solution for the CRP. \\
 
-		However this is very inefficient as there are exponentially many different
-		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
-		algorithm into two separate parts. Its global structure is simply a sum of
-		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
-		be achieved by first computing all possible terms for each task then creating all
-		possible DIT values by summing the terms in all possible ways. The number of results is still
+    Now that we have a solver for the problem of finding a synchronous instant, we
+    actually also have a solver for finding the FPDIT. The problem of finding the
+    first DIT is the same as finding all the possible DIT then taking the minimum.
+    Each of those DIT corresponds to a unique combination of $a_i$ values (one
+    for each task). Finding one of such DIT is the same problem as finding a
+    synchronous instant :
+    \[
+      \left\{
+      \begin{array}{l}
+        t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
+        t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
+      \end{array}
+      \right.
+    \]
+    all DITs can be found by solving the equivalent CRP problem for all
+    combinations of $a_i$ values. This is however very inefficient as there are
+    exponentially many different combinations of $a_i$ values in the number of
+    tasks.\\
+
+    A better method for finding the FPDIT consists in splitting Gauss's algorithm
+    into two separate parts. The global structure is simply a sum of factors, each
+    term being dependent on which $a_i$ value is chosen. A major speedup can
+    be achieved by first computing all possible terms for each task (only one
+    modular inverse must be computed per task that way) then creating all possible DIT values
+    by summing the terms in all possible ways. The number of results is still
     exponential in the number of tasks, but the only operation that is repeated
@@
 
-% \nocite{*}
-\bibliographystyle{latex8}
-\bibliography{dit-paper}
+% conference papers do not normally have an appendix
 
+% use section* for acknowledgement
+\section*{Acknowledgment}
+
+The authors would like to thank...
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+\begin{thebibliography}{1}
+
+\bibitem{IEEEhowto:kopka}
+H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+\end{thebibliography}
+
+% that's all folks
 \end{document}

### 2013-07-29 dit-paper_ieee.tex

@@
 \usepackage[ruled,vlined]{algorithm2e}
+\usepackage{stmaryrd}
 
@@
 \end{abstract}
-% no keywords
 
@@
 	precise and efficient description of its C-space would allow to quickly decide
-  if a system is feasible on a given platform.\\
+	whether or not a system is feasible on a given platform.\\
 
@@
 		n_i(t_1, t_2) =
-    \left(
+		\left\llbracket
 			\left\lfloor
@@
 			\right\rceil + 1
-    \right)_0
+		\right\rrbracket_0
 	\]
-  where $( x )_0$ stands for $\max \{ 0, x \}$.\\
+	where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.\\
 
@@
 			\end{definition}
-
-%Thus, with a good description of the C-space, it is easy to check if a given vector of $C_i$ value (given e.g.
-when deploying the application on a specific platform) allows the system to be scheduled or not.
 
@@
   \label{sct:FPDITexist}
+
 		As in the synchronous case, the problem of existence of the FPDIT
@@
 				\hline
-      & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
-     \hline
-     $\tau_1$ & 0 & $C_1$ & 3 & 4\\
-     \hline
-     $\tau_2$ & 2 & $C_2$ & 7 & 8\\
-     \hline
+							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
+				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
+				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
 			\end{tabular}
@@
 	\subsection{Solving the modular system}
-    Finding the FPDIT of a system is similar to finding a synchronous instant of
-    this system (an instant at which all tasks release a job simultaneously), but
-    with weaker constraints. That is, the FPDIT is an instant after the last
-    deadline of all tasks, but before the next arrival time of all tasks. Finding
-    a synchronous instant is equivalent to finding a solution $t$ for the
-    following set of constraints :
-    \[
-      \left\{
-      \begin{array}{l}
-        t \geqslant O_i \: \forall \: \tau_i \in \tau \\
-        t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
-      \end{array}
-      \right.
-    \]
-    which is very similar to an instance of the Chinese Remainder Problem (CRP). It
-    is not possible to directly use a solver for the CRP (such as Gauss's
-    algorithm \cite{gauss1965disquisitiones}) as in a task system, $T_i$ values could have common factors.
-    However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
-    without changing the solution if there is one) in order to make the problem
-    solvable through applying a solution for the CRP. \\
+		Finding the FPDIT of a system is similar to finding at least one synchronous
+		instant (an instant at which all tasks release a job simultaneously) out of a
+		collection of systems with different offsets. The existence conditions can
+		directly be used to calculate the value of the FPDIT (if there is one),
+		because for a given set of $a_i$ values they are very similar to an instance
+		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
+		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}. \\
 
-    Now that we have a solver for the problem of finding a synchronous instant, we
-    actually also have a solver for finding the FPDIT. The problem of finding the
-    first DIT is the same as finding all the possible DIT then taking the minimum.
-    Each of those DIT corresponds to a unique combination of $a_i$ values (one
-    for each task). Finding one of such DIT is the same problem as finding a
-    synchronous instant :
-    \[
-      \left\{
-      \begin{array}{l}
-        t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
-        t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
-      \end{array}
-      \right.
-    \]
-    all DITs can be found by solving the equivalent CRP problem for all
-    combinations of $a_i$ values. This is however very inefficient as there are
-    exponentially many different combinations of $a_i$ values in the number of
-    tasks.\\
-
-    A better method for finding the FPDIT consists in splitting Gauss's algorithm
-    into two separate parts. The global structure is simply a sum of factors, each
-    term being dependent on which $a_i$ value is chosen. A major speedup can
-    be achieved by first computing all possible terms for each task (only one
-    modular inverse must be computed per task that way) then creating all possible DIT values
-    by summing the terms in all possible ways. The number of results is still
+		However this is very inefficient as there are exponentially many different
+		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
+		algorithm into two separate parts. Its global structure is simply a sum of
+		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
+		be achieved by first computing all possible terms for each task then creating all
+		possible DIT values by summing the terms in all possible ways. The number of results is still
 		exponential in the number of tasks, but the only operation that is repeated
@@
 									& \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
-      \text{Name} & \text{period} & \text{period} & \text{period}  & \\
-      \hline
-      \text{size} & O_{max} & H & H & \cdots \\
-      \hline
+						\text{Name} & \text{period} 	& \text{period} 	& \text{period}  	& \\ \hline
+						\text{size} & O_{max} 			& H 				& H 				& \cdots \\ \hline
 						t \geqslant & 0 				& O_{max} 			& O_{max} + H 		& \cdots

### 2013-07-29 dit-paper_ieee.tex
Mainly upgraded the nofpdit simulation

@@
 \IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
-Adresse\\
 Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
@@
 \IEEEauthorblockA{ECE Paris\\
-Adresse\\
 Email}
@@
 %\boldmath
-  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel
-turpis ultricies vulputate vel at arcu.
-Curabitur lectus metus, rutrum sed malesuada ut, mollis sit amet mauris.
-Integer dapibus in risus et porttitor.
-In hac habitasse platea dictumst.
-Maecenas dolor libero, suscipit porta consequat eu, consequat non orci.
-Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum.
-Aenean tempor est nisl, at dictum metus elementum iaculis
+Sensitivity analysis for real-time systems asks for efficient methods to determine feasibility
+after small changes of execution times, such as when porting a system to a different platform.
+The C-space, presented in \cite{bini2004schedulability,george2009characterization}, describes the
+set of execution times for which a system is feasible. This paper extends previous works to
+generalize the description of the C-space for Earliest Deadline First scheduling to asynchronous
+systems and non-pairwise coprime periods. The feasibility gain offered by offsets is then
+expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
+synchronous system.
 \end{abstract}
@@
 	(worst-case) computation time of a job (WCET), a value highly dependent on the
-	platform on which the application will be deployed.\\
+	platform on which the application is deployed.
 
@@
 	precise and efficient description of its C-space would allow to quickly decide
-	whether or not a system is feasible on a given platform.\\
+	whether or not a system is feasible on a given platform.
 
@@
 		the following, we differentiate between \emph{synchronous systems} (where $O_i
-		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\
+		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).
 
@@
 		shown to be optimal \cite{liu1973scheduling}, which means it
-		correctly schedules any feasible system within that group.\\
+		correctly schedules any feasible system within that group.
 
@@
 
-	We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms}, based on the demand-bound function.
+	We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms,pellizzoni2005feasibility}, based on the demand-bound function.
 
@@
 	where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
-	and deadlines are both in the closed interval $[t_1, t_2]$.\\
+	and deadlines are both in the closed interval $[t_1, t_2]$.
 
@@
 	\]
-	where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.\\
+	where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.
 
@@
 
-			The authors of \cite{george2009characterization} give the following definition of the C-space:
+			The authors of \cite{george2009characterization} give the following definition of the C-space (based on \cite{bini2004schedulability}):
 			\begin{definition}
@@
 The constraints must be conditions which can unequivocally decide if a point is included in the region or not.
-In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ in the list of constraints).\\
+In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ to the list of constraints).
 
@@
       Note that for a given $t$, we have that the $n_i(t)$ are
-      constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.\\
+      constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.
 
@@
       test, the smallest description is preferred as it can greatly
-      reduce the computation time of practical feasibility tests using this system
-      of inequations. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of constraints is given.
+      reduce the computation time of practical feasibility tests. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of constraints is given.
 
@@
 
-  In the synchronous case, is has been shown that the inequations corresponding
+  In the synchronous case, is has been shown in \cite{baruah1990algorithms} that the constraints corresponding
   to every interval $[0, t]$ (with $t$ a job deadline happening before $H$) are
-  necessary and sufficient to test the feasibility of a system.\\
+  necessary and sufficient to test the feasibility of a system.
 
-  Even then, the number of inequations to consider is exponential in the number
+  Even then, the number of constraints to consider is exponential in the number
   of tasks. While it has been shown that constraints that cover intervals ending
   after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
-  therefore not usable, or at least not for the purposes of this paper. The
+  therefore not usable for the purposes of this paper. The
   following concept is thus introduced, which is similar to the end of the busy period but does not depend on the execution times.
@@
   \]
-  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.\\
+  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.
 
-  Every DIT being an idle instant, the execution of the system after a DIT does
-  not depend on the execution before it. Because the synchronous arrival pattern is
-  the worst case [citation needed], it is sufficient for the DBF test to only
-  consider intervals $[0, t]$ with $t$ being a deadline before or at the first DIT.\\
+  For synchronous systems in which the execution times are not known, the first DIT $t_d$
+  is our ``best guess'' at an upper limit for the end of the busy period. As it was sufficient
+  to check the DBF test in intervals $[0, t]$ before the end of the busy period, it is
+  slightly more pessimistic but still correct to use the following condition:
+  \[
+  	\begin{array}{c}
+  		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d \\
+  		\iff \text{The system is feasible}
+  	\end{array}
+  \]
 
@@
 		\end{center}
-		~\\
 
@@
 		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
-		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}. \\
+		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}.
 
@@
 
-	We wanted to quantify how much systems have a FPDIT........
+	This simulation aims to quantify how much system have a FPDIT and which factor can influence this quantity.
 
-	We generated task systems by
+	We thus checked the existence condition on systems generated by:
 	\begin{itemize}
@@
 	\end{itemize}
-	and then computed the value of the FPDIT.\\
 
-	We use the CDF because........\\
+	The number of tasks and the constrained Deadline Factor is shown to have a direct influence on the density of FPDIT.
+Indeed, Fig~\ref{fig:noFPDIT} show the percentage of systems having no FPDIT for different values of CDF.
 
@@
 
-	The result are represented in Fig. \ref{fig:noFPDIT}. We observe that the more we are close to the implicit deadline case, the less systems have FPDIT.
+	We observe that the more we are close to the implicit deadline case, the less systems have FPDIT.
+This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen.
+Similarly, as all tasks must be synchronized for a DIT to happen, a higher number of tasks results in a decrease in FPDIT density.
 
@@
 			deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to
-			$\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.\\
+			$\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.
 
@@
 			First let us recall how an asynchronous system behaves under an optimal
-			scheduler, for example EDF.\\
+			scheduler, for example EDF.
 
@@
 The \emph{stationary period} then begins.
-It is only after $O_{max} + 2H$ time units that the system comes back into a state in which we can be sure it has been before.\\
+It is only after $O_{max} + 2H$ time units that the system comes back into a state in which we can be sure it has been before.
 
@@
 The FPDIT, if it exists, must occur in the transitive period.
-Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).\\
+Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).
 
@@
 We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the FPDIT exists.
-This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\
+This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.
 
@@
 A naive method would be to test each constraint against all the others.
-We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.\\
+We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.
 
@@
 However, this algorithm takes an exponential time in the number of constraints.
-An efficient initial description of $CSPACE$, as given by the methods described in previous sections, is therefore preferred.\\
+An efficient initial description of $CSPACE$, as given by the methods described in previous sections, is therefore preferred.
 
@@
 
-For each $[a, d]$, we have a constraint $$\sum_{i=0}^{n-1} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.\\
+For each $[a, d]$, we have a constraint $$\sum_{i=0}^{n-1} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.
 
@@
 $$
-The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.\\
+The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.
 
@@
     \end{center}
-    ~\\
 
@@
 $$
-This time, the C-space only contains 8 points: $(1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$.\\
+This time, the C-space only contains 8 points: $(1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$.
 
@@
 % use section* for acknowledgement
-\section*{Acknowledgment}
+% \section*{Acknowledgment}
 
-The authors would like to thank...
+% The authors would like to thank...
 
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
+% \nocite{*}
+\bibliographystyle{plain}
+\bibliography{dit-paper}
 

### 2013-07-29 python-simulation/mainNoFPDIT.py

@@ -8,13 +8,13 @@ import Task
 import TaskGenerator
 
 
-def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
+def generateSystemArray(numberOfSystems, constrDeadlineFactor, tasksCnt, verbose=False):
 	systemArray = []
 	for i in range(numberOfSystems):
 		Umin = 0.25
 		Umax = 0.75
 		Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
-		n = 3
+		n = tasksCnt
 		# maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
 		maxHyperT = -1
 		Tmin = 5
@@ -29,39 +29,34 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 
 if __name__ == '__main__':
 	NUMBER_OF_SYSTEMS = 10000
-	noFPDITpcts = []
+	noFPDITpcts2 = []
+	noFPDITpcts3 = []
+	noFPDITpcts4 = []
 	CDFvalues = []
-	for constrDeadlineFactor in [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 15, 20]:
-		#print "CONSTR DEAD FACTOR", constrDeadlineFactor
-		systemArray = generateSystemArray(NUMBER_OF_SYSTEMS, constrDeadlineFactor)
-		firstDITs = []
-		upLs = []
-		for i, tau in enumerate(systemArray):
-			start = time.clock()
-
-			firstDITs.append(algorithms.findFirstPeriodicDIT(tau))
-			if firstDITs[-1] is not None:
-				firstDITs[-1] += tau.hyperPeriod()
-			upLs.append(max([task.O for task in tau.tasks]) + 2 * tau.hyperPeriod())
-			# print "\t", i, "Limit :", firstDITs[-1] if firstDITs[-1] is None else firstDITs[-1], "/", upLs[-1]
-
-			# sizeWithDIT = len(cspace.Cspace(tau, upperLimit="def"))  # will use first DIT if it exists
-			# if firstDIT is None:
-			# 	sizeWithoutDIT = sizeWithDIT
-			# else:
-			# 	sizeWithoutDIT = len(cspace.Cspace(tau, upperLimit=upL))
-			# print "\tsize with DIT\t", sizeWithDIT
[…]

### 2013-07-29 dit-paper_ieee_old.tex

--- 2013-07-29 dit-paper_ieee.tex
@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
+%
+%  $Description: Author guidelines and sample document in LaTeX 2.09$
+%
+%  $Author: ienne, modified by Laurent George $
+%  $Date: 2012/02/02 15:20:59 $
+%  $Revision: 1.5 $
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-%
-\documentclass[conference]{IEEEtran}
-\usepackage{cite}
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-\fi
-\usepackage[cmex10]{amsmath}
+\documentclass[times, 10pt,twocolumn, a4paper]{article}
+\usepackage{latex8}
+\usepackage{epsfig, hhline}
+\usepackage{amssymb}
+\usepackage{vmargin,array,multirow,float,shadow,times, euscript}
+\usepackage{amsmath}
 \usepackage{algorithmic}
-\usepackage{array}
-\usepackage{fixltx2e}
-\usepackage{url}
-
-% added
-\usepackage{amssymb}
 \usepackage[ruled,vlined]{algorithm2e}
+\usepackage{pdftricks}
+\usepackage{stmaryrd}
 
@@
 
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+%\newenvironment{accolade}{\begin{centering} $$ \left\{ \begin{array}{l}}{\end{array} \right. $$ \end{centering}}
 
+%-------------------------------------------------------------------------
+% take the % away on next line to produce the final camera-ready version
+\pagestyle{empty}
+
+%-------------------------------------------------------------------------
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
+
 \title{Describing the C-Space of Asynchronous Periodic Task Systems using
@@
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{
-\IEEEauthorblockN{Thomas Chapeaux\\ and Paul Rodriguez}
-\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
-Adresse\\
-Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
+\author{Thomas Chapeaux, Paul Rodriguez\\
+Universit\'e Libre de Bruxelles\\ tchapeau@ulb.ac.be, paurodri@ulb.ac.be \\
+% For a paper whose authors are all at the same institution,
+% omit the following lines up until the closing ``}''.
+% Additional authors and addresses can be added with ``\and'',
+% just like the second author.
 \and
-\IEEEauthorblockN{Laurent George\\ and Jean-Fran\c{c}ois Hermant}
-\IEEEauthorblockA{ECE Paris\\
-Adresse\\
-Email}
+Laurent George\\
+ECE Paris\\
+First line of institution2 address\\ Second line of institution2 address\\
+lgeorge@ece.fr\\
 }
-% make the title area
+
 \maketitle
+\thispagestyle{empty}
 
 \begin{abstract}
-%\boldmath
 	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel
@@
 Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum.
-Aenean tempor est nisl, at dictum metus elementum iaculis
+Aenean tempor est nisl, at dictum metus elementum iaculis.\\
+
+Keywords: Real-time systems, C-space, WCET, sensitivity analysis
 \end{abstract}
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 
@@
 
-      The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility.
-They can all be written in the following way:
+			The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility. They can all be written in the following way:
 			\[
@@
 
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgement
-\section*{Acknowledgment}
-
-The authors would like to thank...
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
-
-% that's all folks
+% \nocite{*}
+\bibliographystyle{latex8}
+\bibliography{dit-paper}
 \end{document}

### 2013-07-29 dit-paper_ieee.tex
Updated noFPDIT plot

@@
 		\]
-		However those four conditions cannot be satisfied, which means the system has
+		However neither is, which means the system has
 		no FPDIT (and no other DIT than $t=0$).
@@
 
-	We thus checked the existence condition on systems generated by:
+	We thus checked the existence condition on 10000 systems generated by:
 	\begin{itemize}
@@
 			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
-			\item $n$ (number of tasks) equal to 3
+			\item $n$ (number of tasks) equal to 3, 4 and 5.
 		\end{itemize}
@@
 
-(Remarque : Avec seulement cette méthode, si un DIT existe on divisera toujours par exactement 4 le nombre de contraintes par rapport à $O_{max} + 2H$)
-
 \subsubsection{Redundancy as an integer linear problem}
@@
 On the other hands, if the maximization returns $z \leq d$, it means that the limitation expressed in the new constraint is already enforced by the previous constraints.
-Therefore $z \leq d$ is a necessary and sufficient condition of redundancy of the new constraint.\\
+Therefore $z \leq d$ is a necessary and sufficient condition of redundancy of the new constraint.
 
@@
 $[15, 17]$, $[15, 22]$, $[15, 27]$, $[15, 30]$, $[20, 22]$, $[20, 27]$, $[20, 30]$, $[23, 27]$, $[23, 30]$, $[25, 27]$ and $[25, 30]$.
-For comparison, the original study interval of $[O_{max}, O_{max} + 2H]$ is $[8, 38]$ which yields 57 intervals.\\
+For comparison, the original study interval of $[O_{max}, O_{max} + 2H]$ is $[8, 38]$ which yields 57 intervals.
 

### 2013-07-29 python-simulation/mainNoFPDIT.py

@@ -55,7 +55,7 @@ if __name__ == '__main__':
 
 	pylab.figure()
 	pylab.plot(CDFvalues, noFPDITpcts2, "g-s", label="2 Tasks")
-	pylab.plot(CDFvalues, noFPDITpcts3, "r-o", label="3 Tasks")
+	pylab.plot(CDFvalues, noFPDITpcts3, "k-o", label="3 Tasks")
 	pylab.plot(CDFvalues, noFPDITpcts4, "b-^", label="4 Tasks")
 	pylab.ylabel("%")
 	pylab.xlabel("CDF")

### 2013-07-29 dit-paper_ieee.tex
our work updated

@@
     the concept of DIT adapted to the asynchronous case called first periodic DIT
-    ($t_d$), along with an algorithm to determine its existence and value for any system. In Section
+    ($t_d$) along with an algorithm to determine its existence and value for any system,
+    then we show the influence of some factors on its existence. In Section
     \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
-    system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
-    sufficient to consider. In section ???, we present a simulation where we find that........
+    system based on the DBF test, we show why the interval $[t_d, t_d + H]$ is
+    sometimes sufficient to consider and we give a numerical example.
+    Finally, in section ???, we present a simulation where we find that........
 

### 2013-07-29 python-simulation/Task.py
pepepep

@@ -35,7 +35,6 @@ class TaskSystem(object):
 		self.tasks = tasks
 		self.hyperperiod = None
 		#self.hyperT = self.hyperPeriod()
-		
 
 	def hyperPeriod(self):
 		if not self.hyperperiod:
@@ -43,40 +42,33 @@ class TaskSystem(object):
 			self.hyperperiod = myAlgebra.lcmArray(Tset)
 		return self.hyperperiod
 
-
 	def hasConstrainedDeadline(self):
 		ok = True
 		for task in self.tasks:
 			ok = ok and task.D <= task.T
 		return ok
 
-
 	def isSynchronous(self):
 		return max([task.O for task in self.tasks]) == 0
-
 
 	def systemUtilization(self):
 		u = 0
 		for task in self.tasks:
 			u += task.utilization()
 		return u
-	
-	
+
 	def omax(self):
 		return reduce(max,[task.O for task in self.tasks])
-	
-	
+
 	def util(self):
 		return self.systemUtilization()
-	
 
 	def __repr__(self):
 		tauString = "TASK SYSTEM"
 		for task in self.tasks:
 			tauString += "\n\t" + str(task)
 		return tauString
-	
-	
+
 	def synchronousEquivalent(self):
 		if self.isSynchronous():
 			return self
@@ -85,8 +77,7 @@ class TaskSystem(object):
 			for t in sync.tasks:
 				t.O = 0
 			return sync
-	
-	
+
 	def firstSynchronousInstant(self):
 		if(self.isSynchronous()):
 			return 0
@@ -101,7 +92,6 @@ class TaskSystem(object):
 				while tSync < Omax:
 					tSync += H
 			return tSync
-
 
 	def dbf_intervals(self, lowerLimit, upperLimit):
 		starts = {}  # will contain all tasks first arrival
@@ -161,26 +151,21 @@ class TestTask(unittest.TestCase):
 		self.tau2 = TaskSystem(self.tasks[0:2])
 		self.tau3 = TaskSystem(self.tasks2)
 
-
 	def test_isSynchronous(self):
 		self.assertFalse(self.tau.isSynchronous())
 		self.assertTrue(self.tau2.isSynchronous())
 		self.assertTrue(self.tau3.isSynchronous())
-
 
 	def test_hasConstrainedDeadline(self):
 		self.assertFalse(self.tau.hasConstrainedDeadline())
[…]

### 2013-07-29 dit-paper_ieee.tex
- cspace size ratio computation and text

--- 2013-07-29 dit-paper_ieee.tex
@@
 
+\section{Experimental C-space size gain of asynchronous systems}
+	One of the advantages of asynchronous systems over synchronous systems in the
+	context of periodic tasks is that the critical instants of asynchronous systems
+	cannot be more constraining for the C-space than synchronous instants. For this
+	reason, it has long been known that modifying task offsets when possible during
+	the design of a real-time system is a useful trick to fit a heavy but periodic task set
+	into a given platform.
+
+	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets without
+	synchronous instants were generated and the size of their C-space was
+	calculated and compared with the size of the C-space of the same
+	task sets with all task offsets set to zero. In other words, this figure
+	evaluates the feasibility gain of adding random offsets to a synchronous task
+	set. It is assumed that a more advanced strategy to assign these offsets
+	would yield a greater difference.
+
+	\begin{figure}[h]
+		\begin{center}
+			\includegraphics[width=0.5\textwidth]{figs/sizeRatio.png}
+			\caption{C-space size ratio between asynchronous and equivalent synchronous
+			systems}
+			\label{fig:sizeRatio}
+		\end{center}
+	\end{figure}
+
 \section{Conclusion}

### 2013-07-29 dit-paper_ieee.tex
- size ratio discussion

@@
 
-	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets without
-	synchronous instants were generated and the size of their C-space was
-	calculated and compared with the size of the C-space of the same
+	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
+	three tasks without synchronous instants were generated. The size of their
+	C-space was calculated and compared with the size of the C-space of the same
 	task sets with all task offsets set to zero. In other words, this figure
@@
 	\end{figure}
+
+	The ratio between the size of the synchronous and asynchronous C-spaces of
+	these systems roughly range from 0.95 in the worst case (high utilization, high
+	CDF) to 0.85 in the best case (low utilization, low CDF). Note that the value
+	of the CDF has a greater influence on this ratio than the system's total
+	utilization, but less so when the CDF is lower. It is also important to note
+	that even though a 0.95 ratio may not seem much, the synchronous C-spaces of
+	the systems contain many dominated WCET vectors, and only those that are
+	pareto-optimal (i.e. non-dominated) actually matter to the system's engineer.
+	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
+	solutions that will dominate solutions that were previous non-dominated,
+	increasing the quality of the WCET pareto-front.
 
@@
 % \nocite{*}
-\bibliographystyle{plain}
+\bibliographystyle{IEEEtran}
 \bibliography{dit-paper}

### 2013-07-29 dit-paper_ieee.tex
- size ratio discussion
conclusion initial draft

--- 2013-07-29 dit-paper_ieee.tex
@@
 
-\section{Experimental C-space size gain of asynchronous systems}
-	One of the advantages of asynchronous systems over synchronous systems in the
-	context of periodic tasks is that the critical instants of asynchronous systems
-	cannot be more constraining for the C-space than synchronous instants. For this
-	reason, it has long been known that modifying task offsets when possible during
-	the design of a real-time system is a useful trick to fit a heavy but periodic task set
-	into a given platform.
+\section{Conclusion}
 
-	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets without
-	synchronous instants were generated and the size of their C-space was
-	calculated and compared with the size of the C-space of the same
-	task sets with all task offsets set to zero. In other words, this figure
-	evaluates the feasibility gain of adding random offsets to a synchronous task
-	set. It is assumed that a more advanced strategy to assign these offsets
-	would yield a greater difference.
+In this paper, we presented a general approach to define the C-space of a constrained periodic task set for EDF on uniform platform.
+Possible future works includes an extension to multiprocessor platforms or including preemption costs, in which case EDF is no longer an optimal algorithm, meaning that another algorithm could be studied.
 
-	\begin{figure}[h]
-		\begin{center}
-			\includegraphics[width=0.5\textwidth]{figs/sizeRatio.png}
-			\caption{C-space size ratio between asynchronous and equivalent synchronous
-			systems}
-			\label{fig:sizeRatio}
-		\end{center}
-	\end{figure}
-
-\section{Conclusion}
+(...)
 

### 2013-07-29 dit-paper_ieee.tex

--- 2013-07-29 dit-paper_ieee.tex
@@
 
+In this paper, we presented a general approach to define the C-space of a constrained periodic task set for EDF on uniform platform.
+Possible future works includes an extension to multiprocessor platforms or including preemption costs, in which case EDF is no longer an optimal algorithm, meaning that another algorithm could be studied.
+
+(...)
+
 % conference papers do not normally have an appendix

### 2013-07-30 dit-paper_ieee.tex
Changes after discussion w/ LG

@@
 %% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
 %%
@@
 %%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
 
@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
 \title{Describing the C-Space of Asynchronous Periodic Task Systems using
@@
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
 \author{
@@
 \and
-\IEEEauthorblockN{Laurent George\\ and Jean-Fran\c{c}ois Hermant}
+\IEEEauthorblockN{Laurent George\\ and ???}
 \IEEEauthorblockA{ECE Paris\\
@@
 }
-% make the title area
 \maketitle
@@
 \begin{abstract}
-%\boldmath
 Sensitivity analysis for real-time systems asks for efficient methods to determine feasibility
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+%\IEEEpeerreviewmaketitle
+
+\section*{TODO}
+
+\begin{itemize}
+	\item changer CDF
+	\item Expliquer simulation plus en d\'etail (GLPK)
+	\item Donner un algo pour CRP
+	\item fix bibliography
+\end{itemize}
 
@@
       which are redundant. While this does not harm the precision of the
-      test, the smallest description is preferred as it can greatly
+      test, a smaller description is preferred as it can greatly
       reduce the computation time of practical feasibility tests. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of constraints is given.
 
-  \subsection{Removing redundancy}
+  \subsection{Removing redundant constraints}
     \label{sct:removeRedundancy}
@@
   For synchronous systems in which the execution times are not known, the first DIT $t_d$
-  is our ``best guess'' at an upper limit for the end of the busy period. As it was sufficient
+  is our ``best guess'' at an upper limit on the end of the busy period. As it was sufficient
   to check the DBF test in intervals $[0, t]$ before the end of the busy period, it is
@@
     sometimes sufficient to consider and we give a numerical example.
-    Finally, in section ???, we present a simulation where we find that........
+    Finally, in section \ref{sct:expCspaceGain}, we use a simulation to quantify the feasibility
+    gain of asynchronous system in terms of volume of the C-space.
 
@@
 
-	\subsection{Removing redundancy}
+	\subsection{Removing redundant constraints}
+
+		The first two following sections contain well-known results of feasibility analysis.
+		The third one is a new result based on the FPDIT and the last section contains a general
+		but heavy method for removing constraints redundancies.
 
@@
 
-Fig. \ref{fig:cspaceComp} shows the two C-spaces in the plane.
+Fig.
+\ref{fig:cspaceComp} shows the two C-spaces in the plane.
+The dark grey region is the C-space of the synchronous system and the light grey region is the surface gain given by the asynchronous system.
 
@@
 \section{Experimental C-space size gain of asynchronous systems}
+\label{sct:expCspaceGain}
 	One of the advantages of asynchronous systems over synchronous systems in the
 	context of periodic tasks is that the critical instants of asynchronous systems
-	cannot be more constraining for the C-space than synchronous instants. For this
-	reason, it has long been known that modifying task offsets when possible during
-	the design of a real-time system is a useful trick to fit a heavy but periodic task set
+	are at most as constraining for the C-space as a synchronous instant. For this
+	reason, modifying task offsets when possible during
+	the design of a real-time system is a useful trick to fit a heavy periodic task set
 	into a given platform.
@@
 	three tasks without synchronous instants were generated. The size of their
-	C-space was calculated and compared with the size of the C-space of the same
-	task sets with all task offsets set to zero. In other words, this figure
+	C-space (number of valid WCET vectors) was calculated and compared with that of the same
+	task sets with all offsets set to zero. In other words, this figure
 	evaluates the feasibility gain of adding random offsets to a synchronous task
@@
 	the systems contain many dominated WCET vectors, and only those that are
-	pareto-optimal (i.e. non-dominated) actually matter to the system's engineer.
+	pareto-optimal (i.e. non-dominated) actually matter to the designer of the system.
 	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
-	solutions that will dominate solutions that were previous non-dominated,
+	solutions that will dominate solutions that were previously non-dominated,
 	increasing the quality of the WCET pareto-front.
@@
 In this paper, we presented a general approach to define the C-space of a constrained periodic task set for EDF on uniform platform.
-Possible future works includes an extension to multiprocessor platforms or including preemption costs, in which case EDF is no longer an optimal algorithm, meaning that another algorithm could be studied.
+Possible future works includes an extension to the study of systems with preemption costs or running on multiprocessor platforms, as the value of the DIT does not depend on preemptions or the number of processors.
 
-(...)
+Future works could also study the shape of the C-space and how it is affected by some factors.
+An interesting path would be the effect of the CDF on the number of constraints describing the C-space, as we know that in the implicit case this description is simple ($U_{tot} \leqslant 1$).
+While we quantified the feasibility gain by looking at the ratio between sizes of C-space, another approach would be to look at the ratio between the minimal distance of the pareto front of the C-space, which would give a lower bound of the gain given by the offsets.
 
@@
 % \nocite{*}
-\bibliographystyle{IEEEtran}
+\bibliographystyle{plain}
 \bibliography{dit-paper}

### 2013-07-30 dit-paper_ieee.tex

@@
 		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
-		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
+		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}.
+It allows us to generate systems where the deadlines are closer to the period.
 	\end{itemize}

### 2013-07-30 dit-paper_ieee.tex
New plot for CDF (better)

@@
 \author{
-\IEEEauthorblockN{Thomas Chapeaux\\ and Paul Rodriguez}
+\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
 \IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
@@
 \and
-\IEEEauthorblockN{Laurent George\\ and ???}
+\IEEEauthorblockN{Laurent George and ???}
 \IEEEauthorblockA{ECE Paris\\
@@
 	\begin{center}
-		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit.png}
+		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.eps}
 	\end{center}
@@
 	the systems contain many dominated WCET vectors, and only those that are
-	pareto-optimal (i.e. non-dominated) actually matter to the designer of the system.
+	in the border (i.e. non-dominated) actually matter to the designer of the system.
 	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
 	solutions that will dominate solutions that were previously non-dominated,
-	increasing the quality of the WCET pareto-front.
+	increasing the quality of the C-space border.
 

### 2013-07-30 python-simulation/mainRedunComp.py

@@ -1,0 +1,63 @@
+import Task
+import TaskGenerator
+import algorithms
+import cspace
+
+import random
+import time
+
+def testSystem(tau):
+	print "TESTING SYSTEM"
+	print tau
+
+	Omax = max([task.O for task in tau.tasks])
+	fpdit = algorithms.findFirstDIT(tau)
+	H = tau.hyperPeriod()
+	tau_cspace = cspace.Cspace(tau)
+
+	print "firstDIT", fpdit
+	print "H", H
+	print "#cstr of cspace", len(tau_cspace)
+
+	if len(tau_cspace) <= 2000:
+		twoPassStart = time.clock()
+		cspacePruned = cspace.removeRedundancy(tau_cspace)
+		twoPassStop = time.clock()
+
+		onePassStart = time.clock()
+		cspacepruned_onePass = cspace.removeRedundancy(tau_cspace, firstPass=False)
+		onePassStop = time.clock()
+
+		print "#cstr of cspace in 2 passes ", len(cspacePruned), "(time", twoPassStop - twoPassStart, ")"
+		print "#cstr of cspace in 1 pass ", len(cspacepruned_onePass), "(time", onePassStop - onePassStart, ")"
+		print "comparison of sizes", cspace.CspaceSize(tau, cspacepruned_onePass), "|", cspace.CspaceSize(tau, cspacePruned)
+		return len(tau_cspace), twoPassStop - twoPassStart, onePassStop - onePassStart
+	else:
+		return None
+
+
+def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
+	systemArray = []
+	for i in range(numberOfSystems):
+		Umin = 0.25
+		Umax = 0.75
+		Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
+		n = 3
+		# maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
+		maxHyperT = -1
+		Tmin = 5
+		Tmax = 20
+		tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
+		if (verbose and numberOfSystems <= 10):
+			print "Generated task system # ", i
+			for task in tasks:
+					print "\t", task
[…]

### 2013-07-30 dit-paper_ieee.tex
algo gaussssssss

--- 2013-07-30 dit-paper_ieee.tex
@@
 \algsetup{
-  indent=2em,
+  indent=1em,
   linenosize=\small,
@@
 	\subsection{Solving the modular system}
-		Finding the FPDIT of a system is similar to finding at least one synchronous
-		instant (an instant at which all tasks release a job simultaneously) out of a
-		collection of systems with different offsets. The existence conditions can
-		directly be used to calculate the value of the FPDIT (if there is one),
-		because for a given set of $a_i$ values they are very similar to an instance
-		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
-		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}.
+		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
+		the FPDIT (if there is one), because for a given set of $a_i$ values they are
+		very similar to an instance of the Chinese Remainder Problem (CRP), which is
+		easily solved using Gauss's CRP solving method for non-coprime moduli
+		\cite{gauss1965disquisitiones}.
 
 		However this is very inefficient as there are exponentially many different
-		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
-		algorithm into two separate parts. Its global structure is simply a sum of
-		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
-		be achieved by first computing all possible terms for each task then creating all
-		possible DIT values by summing the terms in all possible ways. The number of results is still
-		exponential in the number of tasks, but the only operation that is repeated
-		exponentially many times is now a sum.
+		combinations of $a_i$ values in the number of tasks, and resolving
+		exponentially many CRP is prohibitively slow. A better method for finding the
+		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
+		shown in Algorithm~\ref{alg:multiACRP}.
+
+		\begin{algorithm}
+			\caption{Modified Gauss Algorithm}
+			\label{alg:multiACRP}
+			\begin{algorithmic}[1]
+				\REQUIRE $A$ is a list of the sets of possible $a_i$ per task
+				\REQUIRE $H$ is the hyperperiod of the system
+
+				\STATE $sumchunks \leftarrow \text{empty list}$
+				\FORALL{$\tau_j \in \tau$}
+					\STATE $taskTerms \leftarrow \text{empty list}$ 
+					\STATE $Mj \leftarrow \frac{H}{T_j}$
+					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
+					\FORALL{$a_i \in A(\tau_j)$}
+						\STATE $\text{append} \; (a_i \cdot Mj \cdot invMj) \; \text{to} \; taskTerms$
+					\ENDFOR
+					\STATE $\text{append} \; taskTerms \; \text{to} \; sumchunks$
+				\ENDFOR
+
+				\STATE $results \leftarrow \text{empty list}$
+				\STATE append $0$ to $results$
+				\FORALL{$\tau_j \in \tau$}
+					\STATE $newresults \leftarrow \text{empty list}$
+					\FORALL{$a_i \in A(\tau_j)$}
+						\FORALL{$r \in results$}
+							\STATE $\text{append} \; (r + sumchunks(\tau_j,i)) \; \text{to} \; newresults$
+						\ENDFOR
+					\ENDFOR
+					\STATE $results \leftarrow newresults$
+				\ENDFOR
+				\RETURN $r \; (mod \; H)$ for all $r \in results$
+			\end{algorithmic}
+		\end{algorithm}
+
+		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
+		speedup is achieved by first computing all possible terms for each task
+		then creating all possible DIT values by summing the terms in all possible
+		ways. The number of results is still exponential in the number of tasks, but
+		the only operation that is repeated exponentially many times is now a sum.
+		This allows us to profit from the high chance of having DITs when the CDF
+		factor is close to one, but with only a slight increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.
 

### 2013-07-30 dit-paper_ieee.tex
go go gadgeto commit

--- 2013-07-30 dit-paper_ieee.tex
@@
 	\subsection{Simulation}
+	\label{sct:noFPDITsimu}
 
@@
 
-	We observe that the more we are close to the implicit deadline case, the less systems have FPDIT.
+	We observe that the more we are close to the implicit deadline case ($CDF = 0$), the less systems have FPDIT.
 This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen.
@@
 	three tasks without synchronous instants were generated. The size of their
-	C-space (number of valid WCET vectors) was calculated and compared with that of the same
-	task sets with all offsets set to zero. In other words, this figure
+	C-space (number of valid WCET vectors) was compared with that of the same
+	task sets with all offsets set to zero. The systems were generated as in section~\ref{sct:noFPDITsimu}
+	and the integer linear problems used to remove redundancies were solved via the GLPK tool\footnote{\url{http://www.gnu.org/software/glpk/}}.
+
+	In other words, this figure
 	evaluates the feasibility gain of adding random offsets to a synchronous task

### 2013-07-30 python-simulation/mainRedunComp.py

@@ -3,10 +3,12 @@ import TaskGenerator
 import algorithms
 import cspace
 
+import pylab
+
 import random
 import time
 
-def testSystem(tau):
+def testSystem(tau, maxCstrcnt=1000):
 	print "TESTING SYSTEM"
 	print tau
 
@@ -19,7 +21,7 @@ def testSystem(tau):
 	print "H", H
 	print "#cstr of cspace", len(tau_cspace)
 
-	if len(tau_cspace) <= 2000:
+	if len(tau_cspace) <= maxCstrcnt:
 		twoPassStart = time.clock()
 		cspacePruned = cspace.removeRedundancy(tau_cspace)
 		twoPassStop = time.clock()
@@ -56,8 +58,27 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 	return systemArray
 
 if __name__ == '__main__':
-	systemArray = generateSystemArray(10, 1)
+	systemArray = generateSystemArray(100, 1)
+	cstrSizes = []
+	twoTimes = []
+	oneTimes = []
 
 	for i, tau in enumerate(systemArray):
 		print "TEST NUMBER", i
-		cstrSize, twoPassTime, onePassTime
+		returnTuple = testSystem(tau, maxCstrcnt=1000)
+		if returnTuple is not None:
+			cstrSize, twoPassTime, onePassTime = returnTuple[0], returnTuple[1], returnTuple[2]
+			cstrSizes.append(cstrSize)
+			twoTimes.append(twoPassTime)
+			oneTimes.append(onePassTime)
+
+	pylab.figure()
+	pylab.plot(cstrSize, twoTimes, "g-s", label="Two passes")
+	pylab.plot(cstrSize, oneTimes, "b-r", label="One pass")
+	pylab.ylabel("s")
+	pylab.xlabel("cstr number")
+	pylab.title("Comparison of redundancy removal techniques")
+	pylab.legend(loc=0)
+	# pylab.axis()
+	# pylab.savefig("./plots/001_" + str(time.time()).replace(".", "") + ".png")
+	pylab.show()

### 2013-07-30 python-simulation/cspace.py
Cspace class

@@ -9,64 +9,111 @@ import math
 import os.path
 import re
 
-def Cspace(tau, upperLimit="def", lowerLimit = 0):
-	# return a system of inequations of the form
-	# cst_1 * C_1 + cst_2 * C_2 + ... + cst_n * C_n <= CST
-	# encoded as a list
-	# [cst_1, cst_2, ..., cst_n, CST]
+class Cspace(object):
+	def __init__(self, tau, upperLimit='def', lowerLimit=0, fromList=False):
+# 	 return a system of inequations of the form
+		# cst_1 * C_1 + cst_2 * C_2 + ... + cst_n * C_n <= CST
+		# encoded as a list
+		# [cst_1, cst_2, ..., cst_n, CST]
+		
+		if fromList:
+			self.equations = tau
+		else:		
+			Omax = tau.omax()
+			isSynchronous = (Omax == 0)
+		
+			if upperLimit == "def":
+				firstDIT = algorithms.findFirstDIT(tau)
+				if isSynchronous:
+					upperLimit = firstDIT
+					lowerLimit = 0
+				else:
+					if firstDIT is not None:
+						upperLimit = firstDIT + tau.hyperPeriod()
+						lowerLimit = firstDIT
+					else:
+						upperLimit = Omax + 2 * tau.hyperPeriod()
+						lowerLimit = Omax
+		
+			# for each arrival and each deadline, create an equation
+			self.equations = []
+			for a, d in tau.dbf_intervals(lowerLimit, upperLimit):
+				self.equations.append([algorithms.completedJobCount(t, a, d) for t in tau.tasks] + [d - a])
+		
+			
+	def __getitem__(self,key):
+		return self.equations.__getitem__(key)
 
-	Omax = max([task.O for task in tau.tasks])
-	isSynchronous = (Omax == 0)
 
-	if upperLimit == "def":
-		firstDIT = algorithms.findFirstDIT(tau)
-		if isSynchronous:
-			upperLimit = firstDIT
-			lowerLimit = 0
+	def __setitem__(self,key,val):
+		return self.equations.__getitem__(key,val)
+
+
+	def __delitem__(self,key):
+		return self.equations.__getitem__(key)
+	
+	
+	def __len__(self):
+		return self.equations.__len__()
+
+# def Cspace(tau, upperLimit="def", lowerLimit = 0):
[…]

### 2013-07-30 dit-paper_ieee.tex
removed TODO
style changes

@@
 %\IEEEpeerreviewmaketitle
-
-\section*{TODO}
-
-\begin{itemize}
-	\item changer CDF
-	\item Expliquer simulation plus en d\'etail (GLPK)
-	\item Donner un algo pour CRP
-	\item fix bibliography
-\end{itemize}
 
@@
 		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
-		the FPDIT (if there is one), because for a given set of $a_i$ values they are
+		the FPDIT (if any), because for a given set of $a_i$ values they are
 		very similar to an instance of the Chinese Remainder Problem (CRP), which is
@@
 		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
-		shown in Algorithm~\ref{alg:multiACRP}.
+		shown in Algorithm~\ref{alg:multiACRP} (note that $x^{-1} \; (mod \; y)$
+		means the modular inverse of $x$ in the naturals modulo $y$).
 
@@
 		the only operation that is repeated exponentially many times is now a sum.
-		This allows us to profit from the high chance of having DITs when the CDF
-		factor is close to one, but with only a slight increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.
+		This allows us to profit from a high chance of having DITs when the deadlines
+		are close to the WCETs (and far from the periods), but with only a slight
+		increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.
 
@@
 	\begin{center}
-		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.eps}
+		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.png}
 	\end{center}
@@
 	these systems roughly range from 0.95 in the worst case (high utilization, high
-	CDF) to 0.85 in the best case (low utilization, low CDF). Note that the value
-	of the CDF has a greater influence on this ratio than the system's total
-	utilization, but less so when the CDF is lower. It is also important to note
-	that even though a 0.95 ratio may not seem much, the synchronous C-spaces of
-	the systems contain many dominated WCET vectors, and only those that are
-	in the border (i.e. non-dominated) actually matter to the designer of the system.
-	Using the asynchronous C-space instead will relax some constraints and therefore add new acceptable
-	solutions that will dominate solutions that were previously non-dominated,
+	CDF) to 0.85 in the best case (low utilization, low CDF). As calculating those
+	sizes is rather long, the number of systems used to obtain average
+	results was rather low (1000), which is the likely cause of the spikes in the
+	data. Note that the value of the CDF has a greater influence on this ratio than
+	the system's total utilization, but less so when the CDF is lower. It is also
+	important to note that even though a 0.95 ratio may not seem much, the
+	synchronous C-spaces of the systems contain many dominated WCET vectors, and
+	only those that are in the border (i.e. non-dominated) actually matter to the
+	designer of the system. Using the asynchronous C-space instead will relax some
+	constraints and therefore add new acceptable solutions that will dominate solutions that were previously non-dominated,
 	increasing the quality of the C-space border.

### 2013-07-30 dit-paper_ieee.tex
typos, style

@@
 
-	We observe that the more we are close to the implicit deadline case ($CDF = 0$), the less systems have FPDIT.
-This is easily explained by the fact that a lower CDF means more idle instant for each task, and thus more opportunities for DITs to happen.
-Similarly, as all tasks must be synchronized for a DIT to happen, a higher number of tasks results in a decrease in FPDIT density.
+	We observe that the closer we are to the implicit deadline case ($CDF =
+	0$), the fewer systems have a FPDIT. This is easily explained by the fact that
+	a lower CDF means more idle instants for each task, and thus more opportunities
+	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
+	happen, a higher number of tasks results in a decrease in FPDIT density.
 
@@
 		\subsubsection{Job arrival and deadline}
-			Consider an interval $[t_1, t_2]$. If $t_2$ is an instant without any job
-			deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to
+			Consider a time interval $[t_1, t_2]$. If $t_2$ is an instant without any
+			job deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to
 			$\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.
@@
 			A similar argument can be made if $t_1$ is an instant without any job arrival
-			(and $t_1^*$ is the earliest arrival after $t_1$). We can thus restricts
+			(and $t_1^*$ is the earliest arrival after $t_1$). We can thus restrict
 			ourselves to intervals where $t_1$ is an instant with at least one job
@@
 					\begin{array}{r||c|c|c|l}
-									& \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
+									& \text{Incomplete} & \text{Transient}	& \text{Stationary} & \cdots \\
 						\text{Name} & \text{period} 	& \text{period} 	& \text{period}  	& \\ \hline
@@
 
-As shown in Fig.
-\ref{fig:asyncBehavior}, the system begins in the \emph{incomplete period}, where all tasks are not in the system.
-Then, after $O_{max}$ time units, every tasks is in the system and the \emph{transitive period} begins.
-Then, after $O_{max} + H$ time units, the system is faced with the same pattern of arrival as in $O_{max}$.
-However, because in $O_{max} + H$ every task is in the system and in $O_{max}$ some were missing, the state of the system will be different.
-The \emph{stationary period} then begins.
-It is only after $O_{max} + 2H$ time units that the system comes back into a state in which we can be sure it has been before.
+			As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the
+			\emph{incomplete period}, where all tasks are not in the system. Then, after
+			$O_{max}$ time units, every tasks is in the system and the \emph{transient
+			period} begins. Then, after $O_{max} + H$ time units, the system is faced
+			with the same pattern of arrival as in $O_{max}$. However, because in
+			$O_{max} + H$ every task is in the system and in $O_{max}$ some were missing,
+			the state of the system will be different. The \emph{stationary period} then
+			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
+			exact same situation it was at instant $O_{max} + H$ (however it may be
+			possible to find earlier intervals with the same property).
 

### 2013-07-30 dit-paper_ieee.tex
changes by LG

--- 2013-07-30 dit-paper_ieee.tex
@@
 \algsetup{
-  indent=1em,
+  indent=2em,
   linenosize=\small,
@@
 \begin{document}
-\title{Describing the C-Space of Asynchronous Periodic Task Systems using
+\title{The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using
 Definitive Idle Times}
@@
 \begin{abstract}
-Sensitivity analysis for real-time systems asks for efficient methods to determine feasibility
-after small changes of execution times, such as when porting a system to a different platform.
-The C-space, presented in \cite{bini2004schedulability,george2009characterization}, describes the
+Sensitivity analysis for real-time systems provides for efficient methods to determine feasibility
+conditions  in the case of small changes in task parameters, such as when porting a system to a
+different platform. The C-space, presented in \cite{bini2004schedulability,george2009characterization}, describes the
 set of execution times for which a system is feasible. This paper extends previous works to
-generalize the description of the C-space for Earliest Deadline First scheduling to asynchronous
-systems and non-pairwise coprime periods. The feasibility gain offered by offsets is then
+generalize the description of the C-space for Earliest Deadline First scheduling to
+systems with initial offset. The feasibility gain offered by offsets is then
 expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
@@
 
-\section*{TODO}
-
-\begin{itemize}
-	\item changer CDF
-	\item Expliquer simulation plus en d\'etail (GLPK)
-	\item Donner un algo pour CRP
-	\item fix bibliography
-\end{itemize}
-
 \section{Introduction}
@@
 	Abstract models for real-time systems often require the determination of the
-	(worst-case) computation time of a job (WCET), a value highly dependent on the
+	(worst-case) execution time of a job (WCET), a value highly dependent on the
 	platform on which the application is deployed.
+
+	Feasibility conditions...
 
@@
 
-	In this section the current description of the C-space of synchronous
-	constrained systems, which has been mostly covered by \cite{george2009characterization}, is reviewed.
+    In section~\ref{sct:relatedWorks}, the description of the C-space of synchronous
+	constrained systems, which has been mostly covered by \cite{george2009characterization}, is revisited.
+	This description is based on the DBF feasibility condition described in
+	\cite{baruah1999generalized,baruah1990algorithms} and is found with exponential complexity using
+	the notion of definitive idle times (DIT).
 
+	In section~\ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the
+	asynchronous case called first periodic DIT
+    ($t_d$) along with an algorithm to determine its existence and value for any system,
+    then we show the influence of some factors on its existence.
+
+    In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
+    system based on the DBF test, we show why the interval $[t_d, t_d + H]$ is
+    sometimes sufficient to consider and we give a numerical example.
+
+    Finally, in section~\ref{sct:expCspaceGain}, we use a simulation to quantify the feasibility
+    gain of asynchronous system in terms of volume of the C-space.
+
+\section{Related works}
+\label{sct:relatedWorks}
 	\subsection{Model}
@@
 		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
-		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
+		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
 		the following, we differentiate between \emph{synchronous systems} (where $O_i
@@
 
-		For those systems, the \emph{Earliest Deadline First} (EDF) algorithm, in
+		For those systems, the preemptive \emph{Earliest Deadline First} (EDF) algorithm, in
 		which jobs are prioritized according to their absolute deadline, has been
@@
 		\begin{itemize}
-			\item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
-			\item $H = \operatorname{lcm}(T_0, \cdots, T_{n-1})$
-			\item $O_{max} = \max (O_0, \cdots, O_{n-1})$
+			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$
+			\item $H = \operatorname{lcm}(T_1, \cdots, T_{n})$
+			\item $O_{max} = \max (O_1, \cdots, O_{n})$
 			\item An \emph{idle time} is an instant $t$ at which each job that arrived
 			\emph{strictly} before $t$ has finished its execution.
-			\item A \emph{busy period} is a time interval during which there is always
-			at least one unfinished job available in the system and maximal
-			with this property. Any busy period starts and ends
-			with an idle time.
-			\item The interval between the initial time and the first
+			\item A \emph{busy period} is a time interval between two consecutive idle times in
+			which at least one job is executing.
+			\item The interval between the initial time ($t=0$) and the first
 			idle time is called the \emph{first busy period}.
@@
 
-	We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms,pellizzoni2005feasibility}, based on the demand-bound function.
+	We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms}, based on the demand-bound function.
 
@@
 		The \textbf{demand-bound function (DBF)}
-		defined for a task set $\tau$ and noted $\dbf{t_1, t_2}$, is equal to
-		the maximal cumulated execution time of jobs of $\tau$ contained in the
+		defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
+		equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
 		closed interval $[t_1, t_2]$.
@@
 
-	The values of the $n_i$ are given by
+	The values of the $n_i$ are given by \cite{baruah1999generalized}
 	\[
@@
 	A necessary and sufficient condition of feasibility can easily be written
-	based on the DBF:
+	based on the DBF \cite{baruah1999generalized}
 
@@
 	\subsection{C-space of synchronous systems}
-
-		\subsubsection{Definition}
+	\label{sct:cspaceDescr}
 
@@
 			\begin{definition}
-				The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_0, \cdots, C_{n-1}\}$ in it, $\tau$ is feasible.
+				The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
 			\end{definition}
-
-    \subsubsection{Description using DBF}
-      \label{sct:cspaceDescr}
 
@@
 
-  \subsection{Our work}
-    In this paper, we extend the work of \cite{george2009characterization} to the
-    asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
-    the concept of DIT adapted to the asynchronous case called first periodic DIT
-    ($t_d$) along with an algorithm to determine its existence and value for any system,
-    then we show the influence of some factors on its existence. In Section
-    \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
-    system based on the DBF test, we show why the interval $[t_d, t_d + H]$ is
-    sometimes sufficient to consider and we give a numerical example.
-    Finally, in section \ref{sct:expCspaceGain}, we use a simulation to quantify the feasibility
-    gain of asynchronous system in terms of volume of the C-space.
-
 \section{DIT in asynchronous systems}
@@
 	\subsection{Solving the modular system}
-		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
-		the FPDIT (if there is one), because for a given set of $a_i$ values they are
-		very similar to an instance of the Chinese Remainder Problem (CRP), which is
-		easily solved using Gauss's CRP solving method for non-coprime moduli
-		\cite{gauss1965disquisitiones}.
+		Finding the FPDIT of a system is similar to finding at least one synchronous
+		instant (an instant at which all tasks release a job simultaneously) out of a
+		collection of systems with different offsets. The existence conditions can
+		directly be used to calculate the value of the FPDIT (if there is one),
+		because for a given set of $a_i$ values they are very similar to an instance
+		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
+		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}.
 
 		However this is very inefficient as there are exponentially many different
-		combinations of $a_i$ values in the number of tasks, and resolving
-		exponentially many CRP is prohibitively slow. A better method for finding the
-		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
-		shown in Algorithm~\ref{alg:multiACRP}.
-
-		\begin{algorithm}
-			\caption{Modified Gauss Algorithm}
-			\label{alg:multiACRP}
-			\begin{algorithmic}[1]
-				\REQUIRE $A$ is a list of the sets of possible $a_i$ per task
-				\REQUIRE $H$ is the hyperperiod of the system
-
-				\STATE $sumchunks \leftarrow \text{empty list}$
-				\FORALL{$\tau_j \in \tau$}
-					\STATE $taskTerms \leftarrow \text{empty list}$ 
-					\STATE $Mj \leftarrow \frac{H}{T_j}$
-					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
-					\FORALL{$a_i \in A(\tau_j)$}
-						\STATE $\text{append} \; (a_i \cdot Mj \cdot invMj) \; \text{to} \; taskTerms$
-					\ENDFOR
-					\STATE $\text{append} \; taskTerms \; \text{to} \; sumchunks$
-				\ENDFOR
-
-				\STATE $results \leftarrow \text{empty list}$
-				\STATE append $0$ to $results$
-				\FORALL{$\tau_j \in \tau$}
-					\STATE $newresults \leftarrow \text{empty list}$
-					\FORALL{$a_i \in A(\tau_j)$}
-						\FORALL{$r \in results$}
-							\STATE $\text{append} \; (r + sumchunks(\tau_j,i)) \; \text{to} \; newresults$
-						\ENDFOR
-					\ENDFOR
-					\STATE $results \leftarrow newresults$
-				\ENDFOR
-				\RETURN $r \; (mod \; H)$ for all $r \in results$
-			\end{algorithmic}
-		\end{algorithm}
-
-		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
-		speedup is achieved by first computing all possible terms for each task
-		then creating all possible DIT values by summing the terms in all possible
-		ways. The number of results is still exponential in the number of tasks, but
-		the only operation that is repeated exponentially many times is now a sum.
-		This allows us to profit from the high chance of having DITs when the CDF
-		factor is close to one, but with only a slight increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.
+		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
+		algorithm into two separate parts. Its global structure is simply a sum of
+		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
+		be achieved by first computing all possible terms for each task then creating all
+		possible DIT values by summing the terms in all possible ways. The number of results is still
+		exponential in the number of tasks, but the only operation that is repeated
+		exponentially many times is now a sum.
 
@@
 The intervals to consider are thus of the form $[0, t]$ where $t$ is a deadline happening before or at time $t_d$.
-This yields 2 intervals ($[0, 2]$ and $[0, 7]$) and the following constraints describing the C-space, none of them being redundant:
+This yields two intervals ($[0, 2]$ and $[0, 7]$) and the following constraints describing the C-space, none of them being redundant:
 $$
@@
 \ref{fig:cspaceComp} shows the two C-spaces in the plane.
-The dark grey region is the C-space of the synchronous system and the light grey region is the surface gain given by the asynchronous system.
+The dark gray region is the C-space of the synchronous system and the light gray region is the surface gain given by the asynchronous system.
 
@@
 
-Future works could also study the shape of the C-space and how it is affected by some factors.
-An interesting path would be the effect of the CDF on the number of constraints describing the C-space, as we know that in the implicit case this description is simple ($U_{tot} \leqslant 1$).
-While we quantified the feasibility gain by looking at the ratio between sizes of C-space, another approach would be to look at the ratio between the minimal distance of the pareto front of the C-space, which would give a lower bound of the gain given by the offsets.
+Future works could also study the shape of the C-space and how it is affected by some factors. An
+interesting path would be the effect of the CDF on the number of constraints describing the C-space,
+as we know that in the implicit case this description is simple ($U_{tot} \leqslant 1$). While we
+quantified the feasibility gain by looking at the ratio between sizes of C-space, another approach
+would be to look at the ratio between the minimal distance of the border of the C-space, which would
+give a lower bound of the gain given by the offsets.
 

### 2013-07-30 dit-paper_ieee.tex

@@
 	\subsection{Solving the modular system}
-		Finding the FPDIT of a system is similar to finding at least one synchronous
-		instant (an instant at which all tasks release a job simultaneously) out of a
-		collection of systems with different offsets. The existence conditions can
-		directly be used to calculate the value of the FPDIT (if there is one),
-		because for a given set of $a_i$ values they are very similar to an instance
-		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
-		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}.
+		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
+		the FPDIT (if any), because for a given set of $a_i$ values they are
+		very similar to an instance of the Chinese Remainder Problem (CRP), which is
+		easily solved using Gauss's CRP solving method for non-coprime moduli
+		\cite{gauss1965disquisitiones}.
 
 		However this is very inefficient as there are exponentially many different
-		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
-		algorithm into two separate parts. Its global structure is simply a sum of
-		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
-		be achieved by first computing all possible terms for each task then creating all
-		possible DIT values by summing the terms in all possible ways. The number of results is still
-		exponential in the number of tasks, but the only operation that is repeated
-		exponentially many times is now a sum.
+		combinations of $a_i$ values in the number of tasks, and resolving
+		exponentially many CRP is prohibitively slow. A better method for finding the
+		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
+		shown in Algorithm~\ref{alg:multiACRP} (note that $x^{-1} \; (mod \; y)$
+		means the modular inverse of $x$ in the naturals modulo $y$).
+
+		\begin{algorithm}
+			\caption{Modified Gauss Algorithm}
+			\label{alg:multiACRP}
+			\begin{algorithmic}[1]
+				\REQUIRE $A$ is a list of the sets of possible $a_i$ per task
+				\REQUIRE $H$ is the hyperperiod of the system
+
+				\STATE $sumchunks \leftarrow \text{empty list}$
+				\FORALL{$\tau_j \in \tau$}
+					\STATE $taskTerms \leftarrow \text{empty list}$
+					\STATE $Mj \leftarrow \frac{H}{T_j}$
+					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
+					\FORALL{$a_i \in A(\tau_j)$}
+						\STATE $\text{append} \; (a_i \cdot Mj \cdot invMj) \; \text{to} \; taskTerms$
+					\ENDFOR
+					\STATE $\text{append} \; taskTerms \; \text{to} \; sumchunks$
+				\ENDFOR
+
+				\STATE $results \leftarrow \text{empty list}$
+				\STATE append $0$ to $results$
+				\FORALL{$\tau_j \in \tau$}
+					\STATE $newresults \leftarrow \text{empty list}$
+					\FORALL{$a_i \in A(\tau_j)$}
+						\FORALL{$r \in results$}
+							\STATE $\text{append} \; (r + sumchunks(\tau_j,i)) \; \text{to} \; newresults$
+						\ENDFOR
+					\ENDFOR
+					\STATE $results \leftarrow newresults$
+				\ENDFOR
+				\RETURN $r \; (mod \; H)$ for all $r \in results$
+			\end{algorithmic}
+		\end{algorithm}
+
+		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
+		speedup is achieved by first computing all possible terms for each task
+		then creating all possible DIT values by summing the terms in all possible
+		ways. The number of results is still exponential in the number of tasks, but
+		the only operation that is repeated exponentially many times is now a sum.
+		This allows us to profit from a high chance of having DITs when the deadlines
+		are close to the WCETs (and far from the periods), but with only a slight
+		increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.
 

### 2013-07-30 dit-paper_ieee.tex
PULL

--- 2013-07-30 dit-paper_ieee.tex
@@
 
-After doing this, no redundant constraints are left.
-However, this algorithm takes an exponential time in the number of constraints.
-An efficient initial description of $CSPACE$, as given by the methods described in previous sections, is therefore preferred.
+After doing this, no redundant constraints are left. However, this algorithm
+takes an exponential time in the number of constraints. An efficient initial
+description of $CSPACE$, as given by the methods described in previous
+sections, is therefore preferred.
 
-To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise.
-After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.
+To summarize, we first reduced the number of constraints from every possible
+interval $[t_1, t_2]$ to the intervals where $t_1$ is an arrival time and
+$t_2$ is a deadline in $[t_d, t_d + H]$ if $t_d$ exists, or in
+$[O_{max}, O_{max} + 2H]$ otherwise. This set of constraints is a
+correct description of the C-Space, but it is not efficient. Redundant
+contraints are removed through a linear integer approach.
 

### 2013-07-31 dit-paper_ieee.tex
feasibility conditions
Final touches (hopefully)

@@
 	Abstract models for real-time systems often require the determination of the
-	(worst-case) execution time of a job (WCET), a value highly dependent on the
-	platform on which the application is deployed.
-
-	Feasibility conditions...
+	worst-case execution time of a job (WCET), a value highly dependent on the
+	platform on which the application is deployed. Feasibility conditions allow to
+	decide whether a system can be scheduled correctly (i.e. without violating any
+	timeliness constraint) based on task parameters, including the WCET.
 
@@
 	the set of WCET values for which this system would be feasible. A
-	precise and efficient description of its C-space would allow to quickly decide
-	whether or not a system is feasible on a given platform.
+	precise and efficient description of the C-space of a system would allow to quickly decide
+	whether or not it is feasible on a given platform.
 
@@
 			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
-			exact same situation it was at instant $O_{max} + H$ (however it may be
-			possible to find earlier intervals with the same property).
+			exact same situation it was at instant $O_{max} + H$.
 
-For this reason, as explained in \cite{leung1982complexity}, it is sufficient to check for intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length in the number of tasks.
+			For this reason, as shown by \cite{leung1982complexity}, it is sufficient (but pessimistic) to
+			check for
+			intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length
+			in the number of tasks. A better interval is given in \cite{choquet2004minimal} using the
+			notion of cyclic idle times (denoted $t_c$), which are dependent of the execution
+			time and therefore cannot be used directly. The interval is $[0, t_c + H]$ and is valid for
+			every $t_c$.
+
+			In the following section, we extend the latter interval using the previously defined notion
+			of periodic DIT, a particular case of cyclic idle times which does not depend on the execution
+			times.
 
@@
 
-The FPDIT, if it exists, must occur in the transitive period.
-Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transitive period at instant $t_d - k H$ (a contradiction).
+The FPDIT, if it exists, must occur in the transient period.
+Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transient period at instant $t_d - k H$ (a contradiction).
 
-As the FPDIT happens when all tasks are in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$).
-We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the FPDIT exists.
+As the FPDIT happens when all tasks are in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$) (A rigorous proof is given in \cite{choquet2004minimal} for any cyclic idle time).
+We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$ if the FPDIT exists.
 This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.
@@
 		\begin{center}
-			\includegraphics[width=0.5\textwidth]{figs/sizeRatio.png}
+			\includegraphics[width=0.5\textwidth]{figs/sizeratio.png}
 			\caption{C-space size ratio between asynchronous and equivalent synchronous

### 2013-07-31 python-simulation/Task.py
OO C-Space size

@@ -1,5 +1,6 @@
 import math
 import myAlgebra
+import cspace
 
 import array
 import heapq
@@ -129,6 +130,12 @@ class TaskSystem(object):
 			if not self.isSynchronous() and nextArrival + task.D <= upperLimit:
 				heapTuple = (nextArrival, task)
 				heapq.heappush(arrivals, heapTuple)
+				
+	
+	def cSpaceSize(self, acspace=None):
+		if acspace is None:
+			acspace = cspace.Cspace(self)
+		return acspace.size(self)
 
 
 import unittest

### 2013-07-31 python-simulation/cspace.py

@@ -17,7 +17,7 @@ class Cspace(object):
 		# [cst_1, cst_2, ..., cst_n, CST]
 		
 		if fromList:
-			self.equations = tau
+			self.constraints = tau
 		else:		
 			Omax = tau.omax()
 			isSynchronous = (Omax == 0)
@@ -36,25 +36,26 @@ class Cspace(object):
 						lowerLimit = Omax
 		
 			# for each arrival and each deadline, create an equation
-			self.equations = []
+			self.constraints = []
 			for a, d in tau.dbf_intervals(lowerLimit, upperLimit):
-				self.equations.append([algorithms.completedJobCount(t, a, d) for t in tau.tasks] + [d - a])
+				constraint = CSpaceConstraint([algorithms.completedJobCount(t, a, d) for t in tau.tasks], d - a)
+				self.constraints.append(constraint)
 		
 			
 	def __getitem__(self,key):
-		return self.equations.__getitem__(key)
+		return self.constraints.__getitem__(key)
 
 
 	def __setitem__(self,key,val):
-		return self.equations.__getitem__(key,val)
+		return self.constraints.__getitem__(key,val)
 
 
 	def __delitem__(self,key):
-		return self.equations.__getitem__(key)
+		return self.constraints.__getitem__(key)
 	
 	
 	def __len__(self):
-		return self.equations.__len__()
+		return self.constraints.__len__()
 
 # def Cspace(tau, upperLimit="def", lowerLimit = 0):
 # 	# return a system of inequations of the form
@@ -79,11 +80,11 @@ class Cspace(object):
 # 				lowerLimit = Omax
 # 
 # 	# for each arrival and each deadline, create an equation
-# 	equations = []
+# 	constraints = []
 # 	for a, d in tau.dbf_intervals(lowerLimit, upperLimit):
-# 		equations.append([algorithms.completedJobCount(t, a, d) for t in tau.tasks] + [d - a])
+# 		constraints.append([algorithms.completedJobCount(t, a, d) for t in tau.tasks] + [d - a])
 # 
-# 	return equations
+# 	return constraints
 
 
 	def removeRedundancy(self, firstPass=True, verbose=False):
@@ -96,105 +97,69 @@ class Cspace(object):
[…]

### 2013-07-31 python-simulation/sizeRatio.py

@@ -8,7 +8,7 @@ import time
 if __name__ == "__main__":
 	UTIL_BINS = [f/10.0 for f in range(1,11)]
 	CDF_BINS = [e/1.0 for e in range(1,5)]
-	NUMBER_OF_SYSTEMS = 1000
+	NUMBER_OF_SYSTEMS = 10
 	results = []
 	for cdf in CDF_BINS:
 		resCdf = []
@@ -23,10 +23,10 @@ if __name__ == "__main__":
 				tSync = tau.firstSynchronousInstant()
 				if not tSync:
 					asyncCSpace = cspace.Cspace(tau)
-					asyncCSpaceSize = cspace.CspaceSize(tau,asyncCSpace)
+					asyncCSpaceSize = asyncCSpace.size(tau)
 					if asyncCSpaceSize > 0:
 						syncTau = tau.synchronousEquivalent()
-						syncCSpaceSize = cspace.CspaceSize(syncTau)
+						syncCSpaceSize = syncTau.cSpaceSize()
 						resUtil += float(syncCSpaceSize)/asyncCSpaceSize
 						trueAsyncCnt += 1
 			if(trueAsyncCnt > 0):

### 2013-07-31 dit-paper_ieee.tex
made the bibliography style ieeetran
Added reference to Navet paper

@@
 \IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
-Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
+tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
 \and
@@
 \IEEEauthorblockA{ECE Paris\\
-Email}
+lgeorge@ece.fr}
 }
@@
 
-Future works could also study the shape of the C-space and how it is affected by some factors. An
+Future works could also repeat the simulation of section~\ref{sct:expCspaceGain} with the algorithm described in \cite{grenier2008pushing}, which determine offset values with optimal feasibility. The
+feasibility gain could then be expressed using the C-space.
+
+Another direction is to study the shape of the C-space and how it is affected by some factors. An
 interesting path would be the effect of the CDF on the number of constraints describing the C-space,

### 2013-07-31 dit-paper_ieee.tex
changed one sentence

@@
 
-	We observe that the closer we are to the implicit deadline case ($CDF =
-	0$), the fewer systems have a FPDIT. This is easily explained by the fact that
-	a lower CDF means more idle instants for each task, and thus more opportunities
+	We observe that when the $CDF$ tends to zero, few systems have a FPDIT.
+	This is easily explained by the fact that
+	a high CDF means more idle instants for each task, and thus more opportunities
 	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to

### 2013-07-31 python-simulation/algorithms.py
??? removed and task refactor

@@ -71,26 +71,16 @@ def findBusyPeriod(tau):
 		assert wOld > wNew, "findBusyPeriod: wOld <= wNew. Old:" + str(wOld) + ", new:" + str(wNew)
 		for task in tau.tasks:
 			wNew += int(math.ceil(wOld*1.0 / task.T)*task.C)
-
 	return wNew
 
-
 def dbf_synchr(tau, t):
-	return dbf(tau, 0, t)
-
+	return tau.dbf(0, t)
 
 def dbf(tau, t1, t2):
-	dbfSum = 0
-	for task in tau.tasks:
-		dbfSum += completedJobCount(task, t1, t2) * task.C
-	return dbfSum
-
+	return tau.dbf(t1, t2)
 
 def completedJobCount(task, t1, t2):
-	jobBeforeT2 = int(math.floor(1.0 * (t2 - task.O - task.D) / task.T))
-	jobBeforeT1 = int(math.ceil(1.0 * (t1 - task.O) / task.T))
-	return max(0, jobBeforeT2 - jobBeforeT1 + 1)
-
+	return task.completedJobCount(t1, t2)
 
 def dbfTest(tau, firstDIT=None):
 	# TODO : add lowerLimit (already present in all subfunctions)

### 2013-07-31 dit-paper_ieee.tex
??? removed and task refactor
remarks of the last mail of LG

@@
 	\[
-		\dbf{t_1, t_2} = \sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i
+		\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
 	\]
@@
       \[
-        \sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+        \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
       \]
@@
   therefore not usable for the purposes of this paper. The
-  following concept is thus introduced, which is similar to the end of the busy period but does not depend on the execution times.
+  following concept, initially described by \cite{lipariaverage}, is thus introduced. It is similar to the end of the busy period but does not depend on the execution times.
 
   \begin{definition}
-    A \textbf{definitive idle time} (DIT) is a time $t$ such that every job
+    A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
     released strictly before instant $t$ has its absolute deadline before or at instant $t$.
@@
 		\[
-			\sum_{i=0}^{n-1} n_i(t_1, t_2)
+			\sum_{i=1}^{n} n_i(t_1, t_2)
 			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
@@
 			notion of cyclic idle times (denoted $t_c$), which are dependent of the execution
-			time and therefore cannot be used directly. The interval is $[0, t_c + H]$ and is valid for
-			every $t_c$.
+			time and therefore cannot be used directly. Their interval is $[0, t_c + H]$ and is valid for
+			every cyclic idle time $t_c$.
 
@@
 
-For each $[a, d]$, we have a constraint $$\sum_{i=0}^{n-1} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.
+For each $[a, d]$, we have a constraint $$\sum_{i=1}^{n} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.
 

### 2013-08-05 dit-paper_ieee.tex
Figure 5 correction moved figure 1 to /figs directory cleanup
Added Mr. Goossens as an authors small typos

@@
 \begin{document}
-\title{The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using
-Definitive Idle Times}
+\title{The Space of Feasible Execution Times for Asynchronous Periodic Task
+Systems using Definitive Idle Times}
 
@@
 \and
-\IEEEauthorblockN{Laurent George and ???}
+\IEEEauthorblockN{Laurent George}
 \IEEEauthorblockA{ECE Paris\\
 lgeorge@ece.fr}
+\and
+\IEEEauthorblockN{Jo\e"l Goossens}
+\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
+joel.goossens@ulb.ac.be}
 }
@@
 \begin{abstract}
-Sensitivity analysis for real-time systems provides for efficient methods to determine feasibility
+Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
 conditions  in the case of small changes in task parameters, such as when porting a system to a
@@
   values of $t_2$ correspond to job deadlines. Note that the number of
-  constraints is still exponential in the number of tasks.
+  constraints is still exponential in the number of tasks in the worst-case ($t_d = H$).
 
@@
 	\begin{center}
-		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit_3.png}
+		\includegraphics[width=0.5\textwidth]{figs/nofpdit_3.png}
 	\end{center}
@@
 
-The general problem of redundancy of a new linear constraint $C \, X \leq d$ w.r.t. a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the following ILP:
+The general problem of redundancy of a new linear constraint $C \, X \leq d$ w.r.t.
+a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the ILP presented in Fig.~\ref{fig:redILP}.
 
@@
 \caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
+\label{fig:redILP}
 \end{figure}

### 2013-09-04 dit-paper_ieee.tex
no idea
Small changes from Joël Goossens's remarks

@@
 			\item The interval between the initial time ($t=0$) and the first
-			idle time is called the \emph{first busy period}.
+			idle time after $t=0$ is called the \emph{first busy period}.
 		\end{itemize}
@@
 
-	We recall the necessary and sufficient condition explained in \cite{baruah1999generalized, baruah1990algorithms}, based on the demand-bound function.
+	We recall the necessary and sufficient feasability condition on monoprocessor platform given in \cite{baruah1999generalized, baruah1990algorithms} and based on the demand-bound function.
 
@@
 	\]
-	where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
+	where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ which arrival times
 	and deadlines are both in the closed interval $[t_1, t_2]$.
@@
   therefore not usable for the purposes of this paper. The
-  following concept, initially described by \cite{lipariaverage}, is thus introduced. It is similar to the end of the busy period but does not depend on the execution times.
+  following concept, initially described by \cite{lipariaverage}, is thus introduced. It gives an upper bound for to the end of the busy period and does not depend on the execution times.
 
@@
   \[
-  	\begin{array}{c}
-  		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d \\
+  		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d
   		\iff \text{The system is feasible}
-  	\end{array}
   \]

### 2013-09-05 beamer/dit-paper-presentation.tex
?

\documentclass{beamer}
\mode<presentation>
{
  \usetheme{Warsaw}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{beaver} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
  \setbeamertemplate{footline}[frame number]
}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}

\title {Real-Time Systems}
\subtitle {The Space of Feasible Execution Times for Asynchronous Periodic Task
Systems using Definitive Idle Times}
\author{Thomas Chapeaux \inst{1} \and Paul Rodriguez \inst{1} \and Laurent George \inst{2} \and Joël Goossens \inst{1}}
\institute[shortinst]{\inst{1} Université Libre de Bruxelles \and %
                      \inst{2} ECE Paris}
\date{July 2013}

\newcommand{\dbf}[1]{\operatorname{dbf}(#1)}

\begin{document}

\maketitle{}

\begin{frame}
	\tableofcontents
\end{frame}

\section{Introduction}

	\subsection{Real-time systems}

	\begin{frame}{Model}
		Tasks, jobs, OCDT
	\end{frame}

	\begin{frame}{Feasibility}
		We define feasibility...
	\end{frame}

	\begin{frame}{DBF test}
		\begin{block}{Definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{block}

		Mathematically,
		\[
			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
		\]
		where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
		and deadlines are both in the closed interval $[t_1, t_2]$.

		The values of the $n_i$ are given by \cite{baruah1999generalized}

		CNS of feasibility: $\dbf{t1, t2} \leqslant t2 - t1$
	\end{frame}

	\subsection{Related works}

	\begin{frame}{Related Works}
	This one and this one
	\end{frame}

	\subsection{Our work}

	\begin{frame}{Our work}

	Extension of the previous results

	\end{frame}

\section{First Periodic DIT}

	\subsection{Definition}

	\begin{frame}{Definition of the FPDIT}
		Even without knowing the WCETs in advance, we can define the following notions:
		\begin{block}{Definition}
			A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
			released strictly before instant $t$ has its absolute deadline before or at instant $t$.
		\end{block}
		\begin{block}{Definition}
			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{block}

	\end{frame}

	\subsection{Existence and value}

	\begin{frame}{Existence and value}
		The FPDIT is a time $t_d$ for which
		\[
			\begin{array}{l}
				\forall i \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]

		Note that in the synchronous case $t_d = H$ is always a solution ($a_i = T_i$)
	\end{frame}

\section{C-space}

	\subsection{Definition}

	\begin{frame}{Definition of the C-space}
		\begin{block}{Definition}
			The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
		\end{block}

		A region of $\mathbb{N}_0^n$ such as the C-space can be described by a list of parametric linear constraints (called the \emph{formulation}).
	\end{frame}

	\subsection{Redundancies}

		\subsubsection{General approach}

		\begin{frame}{Redundancies}
			Infinite number of constraints...

			However: arrival and deadlines, feasibility interval, ILP

			The sequel will concentrate on obtaining a short feasibility interval
		\end{frame}

		\subsubsection{Synchronous systems}

		\begin{frame}{Redundancy in synchronous systems}
			[0, t] is a critical instant, 0 is the worst-case
		\end{frame}

		\subsubsection{Asynchronous systems}

		\begin{frame}{Redundancy in asynchronous systems}
			[$t_d$, $t_d + H$] is a feasibility interval
		\end{frame}

	\subsection{Numerical Example}

	\begin{frame}{Example}
		Table, OCDT, figure
	\end{frame}

\end{document}

### 2013-09-05 python-simulation/Model/Task.py

@@ -1,5 +1,6 @@
 import math
 from Helper import myAlgebra
+from Model import Job
 
 import array
 import heapq
@@ -34,6 +35,10 @@ class Task(object):
         jobBeforeT2 = int(math.floor(1.0 * (t2 - self.O - self.D) / self.T))
         jobBeforeT1 = int(math.ceil(1.0 * (t1 - self.O) / self.T))
         return max(0, jobBeforeT2 - jobBeforeT1 + 1)
+
+    def getJob(self, arrival):
+        assert (arrival - self.O) % self.T == 0
+        return Job.Job(self, arrival)
 
 
 class TaskSystem(object):

### 2013-09-05 python-simulation/Simulator/PALLF.py

@@ -25,7 +25,7 @@ class PALLF(Scheduler.SchedulerDP):
             if t < task.O:
                 nextArrival = task.O
             else:
-                nextArrival = (t - task.O) + (task.T - (t - task.O) % task.T) + task.O
+                nextArrival = t + (task.T - (t - task.O) % task.T)
             # expected priorities (based on lax)
             jobExecLeftAtArrival = max(0, finishTime - nextArrival)
             arrivalLax = task.D - task.C
@@ -36,7 +36,7 @@ class PALLF(Scheduler.SchedulerDP):
     def priority(self, job, simu):
         lax = self.getLaxity(job, simu)
         if self.isJobExecuting(job, simu):
-            return 1.0/(self.prioOffset + lax - job.alpha())
+            return 1/(self.prioOffset + lax - job.alpha())
         if job.alpha() > 1:
             # If executing now is sure to result in costly preemption, idle
             epa = self.earliestPreempArrival(job, simu)
@@ -46,4 +46,4 @@ class PALLF(Scheduler.SchedulerDP):
         lpbCPU = simu.leastPrioritaryCPU()
         if lpbCPU and lpbCPU.job and lpbCPU.job.computationLeft() <= lax:
             return -1 * float("inf")
-        return 1.0/(self.prioOffset + lax)
+        return 1/(self.prioOffset + lax)

### 2013-09-05 python-simulation/Simulator/Scheduler.py

@@ -41,7 +41,7 @@ class SpotlightEDF(SchedulerDP):
 
 
 class SchedulerFJP(SchedulerDP):
-    def priority(self, job, simu):
+    def priority(self, job, simu=None):
         if job.priority is not None:
             return job.priority
 
@@ -50,9 +50,9 @@ class SchedulerFJP(SchedulerDP):
 
 
 class EDF(SchedulerFJP):
-    def priority(self, job, simu):
+    def priority(self, job, simu=None):
         super(SchedulerFJP, self).priority(job, simu)
-        return 1.0/job.deadline
+        return 1 / job.deadline
 
 
 class SchedulerFTP(SchedulerFJP):
@@ -64,7 +64,7 @@ class SchedulerFTP(SchedulerFJP):
         # return priorities array in priority order (decreasing)
         pass
 
-    def priority(self, job, simu):
+    def priority(self, job, simu=None):
         super(SchedulerFTP, self).priority(job, simu)
         for i, task in enumerate(reversed(self.priorities)):  # priorities is decreasing
             if job.task is task:

### 2013-09-05 python-simulation/Simulator/Simulator.py

@@ -1,9 +1,8 @@
 from heapq import heapify, heappop, heappush
-import pdb
+# import pdb
 
 from Model.CPU import CPU
 from Model import algorithms
-from Model.Job import Job
 from . import Drawer
 from .JobConfiguration import JobConfiguration
 
@@ -13,7 +12,7 @@ def heappeek(heap):
 
 
 class Simulator(object):  # Global multiprocessing only
-    def __init__(self, tau, stop, nbrCPUs, scheduler, abortAndRestart, verbose=False):
+    def __init__(self, tau, stop, nbrCPUs, scheduler, abortAndRestart, verbose=False, drawing=True):
         """stop can be set to None for default value"""
         self.verbose = verbose
         self.system = tau
@@ -46,7 +45,10 @@ class Simulator(object):  # Global multiprocessing only
         self.activeJobsHeap = []
         heapify(self.activeJobsHeap)
 
-        self.drawer = Drawer.Drawer(self, stop)
+        if drawing:
+            self.drawer = Drawer.Drawer(self, stop)
+        else:
+            self.drawer = Drawer.EmptyDrawer(self, stop)
 
     def saveConfiguration(self):
         jobs = self.getCurrentJobs()
@@ -142,9 +144,10 @@ class Simulator(object):  # Global multiprocessing only
     def checkJobArrival(self):
         for task in self.system.tasks:
             if self.t >= task.O and self.t % task.T == task.O % task.T:
-                newJob = Job(task, self.t)
+                newJob = task.getJob(self.t)
                 newJob.priority = self.scheduler.priority(newJob, self)
-                if self.verbose: print("\tarrival of job", newJob)
+                if self.verbose:
+                    print("\tarrival of job", newJob)
                 heappush(self.activeJobsHeap, (-1 * newJob.priority, newJob))
 
     def handlePreemptions(self):
@@ -204,9 +207,11 @@ class Simulator(object):  # Global multiprocessing only
     def incrementTime(self):
         self.t += 1
         if self.verbose: print("t=", self.t)
-        if (self.t - self.system.omax()) % self.system.hyperPeriod() == 0:
+        if self.t > self.system.omax() and (self.t - self.system.omax()) % self.system.hyperPeriod() == 0:
             if self.lastConfig is not None and self.checkConfig() is True:
                 self.isStable = True
+                if self.verbose:
+                    print("Stable Config !")
             else:
                 self.isStable = False
             self.saveConfiguration()

### 2013-09-05 python-simulation/mainSimu.py

@@ -1,13 +1,13 @@
-from .Model import algorithms
-from .Simulator import Simulator
-from .Simulator import Scheduler, ChooseKeepEDF, PALLF
-from . import systems
+from Model import algorithms
+from Simulator import Simulator
+from Simulator import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
+import systems
 
 import subprocess
 import sys
 
 # tau = systems.generateSystemArray(1, 1)[0]
-tau = systems.ULessThanOneImplicitUnfeasible
+tau = systems.test
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()
@@ -25,9 +25,12 @@ if fpdit:
 print(("stop", stop))
 
 # scheduler = Scheduler.EDF(tau)
-scheduler = Scheduler.SpotlightEDF(tau)
+# scheduler = Scheduler.SpotlightEDF(tau)
 # scheduler = ChooseKeepEDF.ChooseKeepEDF(tau)
 # scheduler = PALLF.PALLF(tau)
+
+scheduler = LBLScheduler.LBLEDF(tau)
+
 # scheduler = Scheduler.FixedPriority(tau, [1, 2, 3])
 # !!! exhaustive: set the parameters right !!!
 # scheduler = Scheduler.ExhaustiveFixedPriority(tau, nbrCPUs=1, abortAndRestart=False)
@@ -36,7 +39,7 @@ scheduler = Scheduler.SpotlightEDF(tau)
 # else:
 #   print "No feasible priorities found !"
 
-simu = Simulator.Simulator(tau, stop=1000, nbrCPUs=1, scheduler=scheduler, abortAndRestart=False, verbose=False)
+simu = Simulator.Simulator(tau, stop=1000, nbrCPUs=1, scheduler=scheduler, abortAndRestart=False, verbose=True)
 
 try:
     simu.run(stopAtDeadlineMiss=True, stopAtStableConfig=True)

### 2013-09-05 python-simulation/mainSimuCompEDF.py

@@ -1,57 +1,64 @@
-from .Model import algorithms
-from .Simulator import Simulator
-from .Simulator import Scheduler, ChooseKeepEDF, PALLF
-from . import systems
+from Model import algorithms
+from Simulator import Simulator
+from Simulator import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
+import systems
 
-import subprocess
+NUMBER_OF_SYSTEMS = 1000
 
-resultsEDF = []
-resultsCK = []
-resultsPALLF = []
+# schedulers = [Scheduler.EDF, ChooseKeepEDF.ChooseKeepEDF, PALLF.PALLF]
+schedulers = [Scheduler.EDF, LBLScheduler.LBLEDF]
 
-edfScore = 0
-ckScore = 0
-pallfScore = 0
+interest = []  # system with weird property
 
-for i in range(1000):
+results = {}
+scores = {}
+for sched in schedulers:
+    results[sched] = []
+    scores[sched] = 0
+
+for i in range(NUMBER_OF_SYSTEMS):
     print(i)
     tau = systems.generateSystemArray(1, 1)[0]
+    if i == 0:
+        tau = systems.CloudAtlas
     # tau = systems.test
-    print(tau)
+    # print(tau)
 
     Omax = max([task.O for task in tau.tasks])
     H = tau.hyperPeriod()
     fpdit = algorithms.findFirstDIT(tau)
-    stop = Omax + 2 * H
+    stop = Omax + 10 * H  # FIXME
     if fpdit:
         stop = fpdit + H
 
-    simuEDF = Simulator.Simulator(tau, stop=stop, nbrCPUs=1, scheduler=Scheduler.EDF(tau), abortAndRestart=False)
-    simuCK = Simulator.Simulator(tau, stop=stop, nbrCPUs=1, scheduler=ChooseKeepEDF.ChooseKeepEDF(tau), abortAndRestart=False)
-    simuPALLF = Simulator.Simulator(tau, stop=stop, nbrCPUs=1, scheduler=PALLF.PALLF(tau), abortAndRestart=False)
+    for sched in schedulers:
+        simu = Simulator.Simulator(tau, stop=stop, nbrCPUs=1, scheduler=sched(tau), abortAndRestart=False, drawing=False)
+        simu.run(stopAtDeadlineMiss=True, stopAtStableConfig=True)
+        results[sched].append(simu.success())
 
[…]

### 2013-09-05 python-simulation/systems.py

@@ -221,7 +221,8 @@ ULessThanOneImplicitUnfeasible = Task.TaskSystem(tasks)
 
 # test
 tasks = []
-tasks.append(Task.Task(0, 5, 11, 11, alpha=1))
-tasks.append(Task.Task(4, 1, 1, 11))
-tasks.append(Task.Task(6, 4, 11, 11))
+tasks.append(Task.Task(32, 1, 15, 15, alpha = 2))
+tasks.append(Task.Task(0, 1, 20, 45, alpha = 2))
+tasks.append(Task.Task(15, 1, 3, 8, alpha = 2))
+tasks.append(Task.Task(45, 7, 14, 15, alpha = 2))
 test = Task.TaskSystem(tasks)

### 2013-09-12 python-simulation/Simulator/Simulator.py
Implicit systems and small things

@@ -1,5 +1,5 @@
 from heapq import heapify, heappop, heappush
-# import pdb
+import pdb
 
 from Model.CPU import CPU
 from Model import algorithms
@@ -95,7 +95,7 @@ class Simulator(object):  # Global multiprocessing only
         if getWaitingJobs:
             waitingJobs = [job for prio, job in self.activeJobsHeap]
         if getBusyJobs:
-            busyJobs = [_f for _f in [cpu.job for cpu in self.CPUs] if _f]
+            busyJobs = [job for job in [cpu.job for cpu in self.CPUs] if job]
         return waitingJobs + busyJobs
 
     def updatePriorities(self, job="all"):
@@ -206,6 +206,8 @@ class Simulator(object):  # Global multiprocessing only
 
     def incrementTime(self):
         self.t += 1
+        # if self.t == 2:
+        #     pdb.set_trace()
         if self.verbose: print("t=", self.t)
         if self.t > self.system.omax() and (self.t - self.system.omax()) % self.system.hyperPeriod() == 0:
             if self.lastConfig is not None and self.checkConfig() is True:

### 2013-09-12 python-simulation/mainSimu.py

@@ -3,11 +3,12 @@ from Simulator import Simulator
 from Simulator import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
 import systems
 
+import random
 import subprocess
 import sys
 
 # tau = systems.generateSystemArray(1, 0)[0]
-tau = systems.test
+tau = systems.LongTransitive
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()
@@ -24,10 +25,11 @@ stop = Omax + 10 * H
 
 print(("stop", stop))
 
-# scheduler = Scheduler.EDF(tau)
+scheduler = Scheduler.EDF(tau)
 # scheduler = Scheduler.SpotlightEDF(tau)
 # scheduler = ChooseKeepEDF.ChooseKeepEDF(tau)
-scheduler = PALLF.PALLF(tau)
+# scheduler = Scheduler.PTEDF(tau)
+# scheduler = PALLF.PALLF(tau)
 # scheduler = Scheduler.ArbitraryScheduler(tau, systems.mpanaSchedule)
 # scheduler = LBLScheduler.LBLEDF(tau)
 

### 2013-09-12 python-simulation/systems.py

@@ -125,7 +125,7 @@ LongTransitive2 = Task.TaskSystem(tasks)
 # FailByTransitive
 tasks = []
 tasks.append(Task.Task(0, 3, 5, 5, alpha=2))
-tasks.append(Task.Task(1, 1, 1, 5))
+tasks.append(Task.Task(0, 1, 1, 5))
 FailByTransitive = Task.TaskSystem(tasks)
 
 
@@ -236,12 +236,25 @@ mpanaSchedule.append(t2)
 mpanaSchedule.append(t1)
 mpanaSchedule.append(t1)
 
+# ImpCumulLaxity
+tasks = []
+tasks.append(Task.Task(0, 1, 12, 12, alpha=2))
+tasks.append(Task.Task(2, 3, 20, 20, alpha=2))
+tasks.append(Task.Task(0, 26, 45, 45, alpha=2))
+ImpCumulLaxity = Task.TaskSystem(tasks)
+
+# ImpFTPNonOptimal
+tasks = []
+tasks.append(Task.Task(0, 1, 3, 3, alpha=1))
+tasks.append(Task.Task(0, 5, 9, 9, alpha=1))
+ImpFTPNonOptimal = Task.TaskSystem(tasks)
+
 # test
 tasks = []
-tasks.append(Task.Task(36, 1, 6, 6, alpha=2))
-tasks.append(Task.Task(41, 1, 4, 4, alpha=2))
-tasks.append(Task.Task(0, 3, 18, 18, alpha=2))
-tasks.append(Task.Task(0, 1, 9, 9, alpha=2))
-tasks.append(Task.Task(26, 3, 24, 24, alpha=2))
-tasks.append(Task.Task(0, 4, 45, 45, alpha=2))
+tasks.append(Task.Task(27, 1, 12, 12, alpha=2))
+tasks.append(Task.Task(0, 6, 20, 20, alpha=2))
+tasks.append(Task.Task(1, 1, 4, 4, alpha=2))
+tasks.append(Task.Task(60, 2, 12, 12, alpha=2))
+tasks.append(Task.Task(0, 1, 6, 6, alpha=2))
+
 test = Task.TaskSystem(tasks)

### 2013-09-12 python-simulation/paper-paedf/paper-paedf.tex
Created files :)

--- 2013-07-19 dit-paper.tex
@@
 \documentclass[a4paper,10pt]{article}
-
+\usepackage[utf8]{inputenc}
+\usepackage{charter}
+\usepackage{listings}
+\usepackage{color}
+\usepackage{url}
+\usepackage{amssymb}
 \usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{charter}
-\usepackage{color}
+\usepackage{hyperref}
 \usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{url}
+%\usepackage[section]{placeins}
 
@@
 
+\title{Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor systems}
 %opening
 \sloppy
-
-\renewcommand{\arraystretch}{1.4}
-\newcommand{\dbf}[1]{\operatorname{dbf}(#1)}
-
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}{Theorem}
-
-\newtheorem*{remarks}{Remarks}
-
 \begin{document}
-
-\title{Using DIT to simplify the DBF feasibility test}
-\author{Thomas Chapeaux \\ ~ \\ \emph{Supervisor} \\ Laurent George, ECE Paris \\ ~ \\ \emph{Thanks to} \\ Paul Rodriguez}
-
-\date{July 2013}
-
 \maketitle
@@
 
-\section{Real-Time Systems}
+\begin{abstract}
 
-$\tau = \{ \tau_1, \cdots, \tau_n \}$
-
-$\tau_i = (O_i, C_i, D_i, T_i)$
-
-$H = LCM(T_i)$
-
-\begin{definition}
-	A system is \textbf{synchronous} if all its tasks have no offset, and
-	\textbf{asynchronous} otherwise.
-\end{definition}
-
-\section{The DBF feasibility test}
-\label{sct:DBF}
-
-\subsection{Definition of the demand-bound function}
-
-\begin{definition}
-	The \textbf{demand-bound function (DBF)}
-	\cite{baruah1999generalized, baruah1990algorithms} defined for a task set
-	$\tau$ and noted $\dbf{t}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in any interval of length $t$.\\
-
-	Mathematically,
-	\[ 
-		\dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
-		\leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot h_i(t_1, t_2) 
-	\] 
-	where $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and
-	deadline are in (non-strict) the interval $[t_1, t_2]$.
-\end{definition}
-
-As the synchronous arrival pattern is known to be the worst case
-\cite{liu1973scheduling}, in that particular case we can only consider the
-interval $[0, t]$. In an asynchronous arrival pattern, it is sufficient to check
-only intervals where $t_2 < O_{max} + 2H$, as the system will be
-periodic starting from $O_{max} + H$ or sooner \cite{leung1982complexity}.\\
-
-In the sequel a closed form expression of the DBF is given in the synchronous
-case. Intuitively, in this case it will be a step-function whose increases will
-occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\
-
-Starting from the definition, it remains to find a method to compute the values
-of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
-values can be obtained as 
-\[
-	h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
-	k T_i  + D_i \leq t \} + 1
-\]
-Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc.
-The maximal value of $k$ can be explicitly stated by rearranging the condition:
-\[
-	\begin{array}{c}
-		k T_i + D_i \leq t \\
-		\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor
-	\end{array}
-\]
-The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is
-negative, it means that no job of task $\tau_i$ respects the condition, i.e.
-$h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\
-
-This is generalized by the final definition of $h_i(t)$: $$h_i(t) = \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \}$$
-
-With this result, a closed form of the DBF function in the synchronous case is
-obtained $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$
-
-\subsection{Feasibility test for EDF}
-
-In \cite{baruah1990algorithms} it is shown that the DBF can be used to
-derive the following feasibility condition for EDF (and thus, EDF being
-optimal, for all other optimal schedulers) on sporadic task sets. An adapted
-proof is given here.
-
-\begin{theorem}
-$$\text{$(\tau_1, ..., \tau_n)$ is feasible} \iff \dbf{t} \leq t \; \forall t$$
-\end{theorem}
-
-\begin{proof}
-	We first show that the condition is \emph{necessary}.
-Indeed, if the condition is not fulfilled (i.e.
-$\exists t^* \; s.t.
-\; \dbf{t^*} > t^*$), it means that in an interval of $t^*$ time units, the total execution time of the jobs whose arrival and deadline occurs within the interval is superior to $t^*$.
-The system is thus not feasible if the condition is not fulfilled.\\
-
-	Now, we prove that the condition is \emph{sufficient}. For that, suppose that $\dbf{t} \leq t \; \forall t$.\\
-
-	...
-(The idea is to look at each interval beginning at an arrival time and finishing at a deadline (not necessarily of the same job).
-Then we can prove that if there is only those two tasks, they can execute.
-If there are other tasks, we can look at a greater interval in which they can all execute)
-
-\end{proof}
-
-Furthermore, the authors show that in the synchronous case, it is sufficient to consider intervals of the form $[0, t_d]$, where the $t_d$ correspond to job deadlines (i.e.
-the increases the demand-bound function) in the interval $\left[ D_{min}, H \right]$.\\
-
-For constrained deadline set, it is sufficient to consider intervals $[0, t_d]$ with $t_d \leq L$, where $L$ is the first busy period and is the solution to the following recursive equation $$L = \sum_{i=1}^{n} \lceil \frac{L}{T_i} \rceil C_i$$ which can be computed through fixed-point iteration $$w_0 = \sum_{i=1}^{n} C_i$$ $$w_{k+1} = \sum_{i=1}^{n} \lceil \frac{w_k}{T_i} \rceil C_i$$
-
-Even so, this test requires to check a number of instant which is exponential in the number of tasks, making the general determination of feasibility a NP-hard problem.
-
-\section{C-space}
-When developing an application, it often happens that the platform is not known in advance, in which case the value of the $C_i$ are not known.
-Then, it can be useful to have a description of the possible values of the $C_i$ for which the system would be feasible.
-
-\subsection{Definition}
-
-The authors of \cite{george2009characterization} give the following definition of the C-space:
-\begin{definition}
-For a given task system $\tau$ in which the $C_i$ are not known, the \textbf{C-space} is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_n\}$ in the C-space, $\tau$ is feasible.
-\end{definition}
-
-Thus, with a good description of the C-space, it is easy to check if a given vector of $C_i$ value (given e.g.
-when deploying the application on a specific platform) allows the system to be scheduled or not.
-
-\subsection{Description using DBF}
-
-A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing bounds of the convex hull of the admissible points.
-In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\
-
-For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are
-$$\dbf{t} = \sum_{i=1}^{n} h_i(t) C_i \leq t \; \forall t$$
-Note that for a given $t$, we have that the $h_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus effectively linear.\\
-
-\subsection{Removing redundancy}
-
-While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.\\
-
-As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered.
-For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used.
-In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.\\
-
-In \cite{lipariaverage}, the authors use the simplex algorithm to further reduce the number of equation to consider.
-
-\section{Definitive idle time approach}
-\label{sct:DIT}
-
-\begin{definition}
-An \textbf{idle time} is a time $t$ such that every job released strictly before instant $t$ finishes its execution before  or at instant $t$.\\
-\end{definition}
-
-\begin{definition}
-A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.\\
-\end{definition}
-
-Remarks
- \begin{itemize}
-  \item If the system is feasible, every DIT is an idle time.
-  \item Contrary to the idle times, the DITs are independent of the scheduling or the execution times of the jobs.
-  \item $t=0$ is always a DIT.
-  \item There are no DITs strictly after the first arrival of an arbitrary deadline task. In the following we only consider the constrained deadline case.
- \end{itemize}
-
- An example of the DITs of a system is given in Fig. \ref{fig:ditExample}.
-
- \begin{figure}[h]
-\begin{center}
-\includegraphics[width=\textwidth]{figs/dit_example.png}
-\caption{The block of colors represents the arrival time and deadline of a job. DITs are represented by a green line below}
-\label{fig:ditExample}
-\end{center}
-\end{figure}
-
-While the definition is applicable to both synchronous and asynchronous tasks system, the following only consider the synchronous case (which is the worst-case for non-concrete tasks).
-The difficulties arising with asynchronous tasks are described in a later section.\\
-
-In the synchronous case, $t=0$ and $t=H$ are DITs but there might be others in-between. The following notion is thus defined:
-
-\begin{definition}
-The earliest DIT occurring in the system strictly after $t=0$ is called the \textbf{first DIT} and is noted $t_d$.
-\end{definition}
-
-If the first DIT is $H$, then the only DITs of the system are multiple of $H$ as the occurrence of DITs is periodic.\\
-
-The following section explains the methods to determine the value of the first DIT.
-Then section \ref{sct:ditsynchfeastest} will explain a method to reduce the complexity of the DBF feasibility test if the first DIT occurs before $H$.
-
-\subsection{Existence and value}
-
-In synchronous systems, $H$ is always a DIT, so the first DIT $t_d$ exists and is such that $t_d \leq H$.
-In the constrained deadline case ($D_i \leq T_i \; \forall i$), it is possible that other DITs occur before it, in which case $t_d < H$.\\
-
-The problem of the existence of a DIT can be written with modular equations as
-$$
-\exists ? \; t_d \; s.t. \; \forall i : \exists a_i \in [D_i, T_i] \; s.t. \; t_d \equiv a_i \; (mod \; T_i) \\
-$$
-
-For fixed values of $a_i$, this is a case of the Generalized Chinese Remainder Theorem (see Appendix \ref{sct:appCRT}).
-However, in our case, each $a_i$ can take every value in the interval $[D_i, T_i]$.
-Observe that the particular case $a_1 \cdots a_n = 0 \cdots 0$ is always a solution, which confirm the previous result that both 0 and $H$ are always DIT.\\
-
-If the value returned by the Chinese Remainder Theorem with a particular set of $a_i$ values is called $t_{idle} (a_1, \cdots, a_n)$\footnote{If the values are such that there are no solution, we set $t_{idle}$ to $\infty$}, the first DIT is given by $$t_d = \operatorname*{min}_{a_i \in [D_i, T_i], \; i = 1 \cdots n} t_{idle} (a_1, \cdots, a_n)$$ which require to consider a number of combinations which is exponential in the number of tasks.
-
-\subsection{Feasibility test}
-\label{sct:ditsynchfeastest}
-
-\begin{theorem}
- Let $t_1$ be a DIT, it is sufficient to check the DBF condition at job deadlines in the interval $[0, t_1]$ to determine feasibility.
-\end{theorem}
-
-\begin{proof}
-Let $t_1$ be any DIT of a synchronous task set such that $\forall t \leq t_1 : \dbf{t} \leq t$. We want to show that $\forall t > t_1 : \dbf{t} \leq t$.\\
-
-As we are in the synchronous case, $t=0$ is a critical instant, which mean we have the earliest next job deadline for each task.
-Thus the DBF increase faster than in any other configuration of arrival times.\\
-
-A DIT for some task set is similar (w.r.t.
-the increase of the DBF) to the initial time of the same system in the asynchronous case.
-In other words, after the DIT, the increase of the DBF will be slower than it was at the initial time.
-Which gives us, with $t_1$ being the DIT:
-$$\forall t > t_1 : \dbf{t} \leq \dbf{t_1} + \dbf{t-t_1}$$
-
-~\\
-
-We now prove by induction that $\dbf{t-t_1} \leq t - t_1$.\\
-
-\emph{Initial case} : We consider $t = t_1 + 1$. Thus, $\dbf{t-t_1} = \dbf{t_1 + 1 - t_1} = \dbf{1}$. As $1 \leq t_1$, we know that $\dbf{1} \leq 1$.\\
-
-\emph{Inductive case} : We consider any $t > t_1 + 1$ and we suppose that $\forall t' < t : \dbf{t'} \leq t'$. Then, we have $\dbf{t - t_1} \leq t - t_1$ as $t - t_1 < t$.\\
-
-And thus we have that $\dbf{t-t_1} \leq t - t_1$. As we also have $\dbf{t_1} \leq t_1$, the previous inequality becomes
-$$\forall t > t_1 : \dbf{t} \leq \dbf{t_1} + \dbf{t-t_1} \leq t_1 + t - t_1 = t$$
-$$\iff \forall t > t_1 : \dbf{t} \leq t$$
-\end{proof}
-
-If there exists a DIT earlier than $H$, it can be used to reduce the interval used in the DBF feasibility test.
-
-\subsection{Results in the asynchronous case}
-
-\begin{definition}
-The \textbf{first periodic DIT} is the earliest DIT to occur strictly after the arrival of at least one job of each task.
-\end{definition}
-
-Note that the first periodic DIT will be the first DIT in the synchronous case.\\
-
-In the synchronous case, $t = H$ is always a DIT.
-This is no longer true in the asynchronous case.
-In fact, the first periodic DIT could happen at a time $t_d > H$, or there could be no first periodic DIT at all, as seen in Fig.
-\ref{fig:asyncNoDit}.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.75\textwidth]{figs/dit_asynchronousNoDit.png}
-\caption{An asynchronous task system with no DITs after $t=0$}
-\label{fig:asyncNoDit}
-\end{center}
-\end{figure}
-
-\subsubsection{Existence and value}
-
-The first periodic DIT cannot happen at a time $t > O_{max} + H$, or else it would have happened previously.\\
-
-Similarly to the synchronous case, the problem of existence of the first periodic DIT can be written as a system of modular equation:
-$$
-\begin{array}{l}
-	\exists ? \; t_d \; s.t. \; \forall i \; :\\
-	\left\{
-		\begin{array}{l}
-		t_d > O_i \\
-		t_d - O_i \equiv a_i \; (mod \; T_i) \\
-		a_i \in [D_i, T_i]
-	\end{array}
-\right.
-\end{array}
-$$
-which can, again, be solved by testing every combination of the $a_i$ and solving the corresponding equation with the Generalized Chinese Remainder Theorem.
-If a solution $t < O_{max}$ is found, recall that $t + k \, H, k \in \mathbb{N}$ is also a solution.
-Note that this time, it is possible for the system to not have any solution (e.g.
-Fig \ref{fig:asyncNoDit}).
-
-\subsubsection{Feasibility test}
-
-To understand feasibility tests in the asynchronous case, one must first understand how an asynchronous system behaves under, for example, EDF.\\
-
-\begin{figure}[h]
-$$
-\begin{array}{r|c|c|c|c|l}
-	 & \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
-	 & \text{period} & \text{period} & \text{period} & \text{period} & \\
-	\hline
-	t & 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
-\end{array}
-$$
-\begin{center}
-\caption{Behavior of an asynchronous system under EDF. The value of $t$ indicates the time at which each period starts}
-\label{fig:asyncBehavior}
-\end{center}
-\end{figure}
-
-As shown in Fig.
-\ref{fig:asyncBehavior}, the system begins in the \emph{incomplete period}, where all tasks are not in the system.
-Then, after $O_{max}$ time units, every tasks is in the system and the \emph{transitive period} begins.
-Then, after $O_{max} + H$ time units, the system is faced with the same pattern of arrival as in $O_{max}$.
-However, because in $O_{max} + H$ every task is in the system and in $O_{max}$ some were missing, the state of the system will be different.
-The \emph{stationary period} then begins.
-It is only after $O_{max} + 2H$ time units that the system comes back into a state in which it was before.\\
-
-For this reason, as explained in \cite{leung1982complexity}, most feasibility test for asynchronous task system (e.g.
-the DBF test) are restricted to the interval $[0, O_{max} + 2H]$, which has an exponential length in the number of tasks.\\
-
-However, using DIT, we have the following property:
-
-\begin{theorem}
-Let $t_d$ be the first periodic DIT of an asynchronous system $\tau$ (supposing it exists). Then it is sufficient to check the DBF test in the interval $[0, t_d + H]$
-\end{theorem}
-
-\begin{proof}
-???\\
-
-(basically at $t_d + H$ we know that the behavior will be the same as in $t_d$)
-\end{proof}
-
-\section{Simulation}
-
-As was shown previously, the DBF condition must be true on all instant to prove that a system is feasible.
-It is necessary and sufficient to check only instants where a deadline occurs, and it is also necessary and sufficient to check only instants before the hyper-period, the end of the first busy period (for constrained system only), or the first DIT.
-While the test itself will be shorter if the smallest of those values is used as an upper limit, the time needed to compute the value must be taken into consideration as well.\\
-
-The DBF feasibility test was simulated on a set of synchronous system with constrained deadline.
-For all of those systems, the value of the hyper-period, the end of the first busy period and the first DIT is computed.
-Then the DBF feasibility test is applied using those upper limits.
-The times each methods took to complete are compared.
-
-\subsection{Implementation model}
-
-\subsubsection{Tasks system generation}
-
-The method used to generate the system consisted of
-\begin{itemize}
-	\item Generating the $U_i$ with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
-	\begin{itemize}
-		\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
-		\item $n$ (number of tasks) chosen uniformly between 1 and 4
-	\end{itemize}
-	\item Generating the $T_i$ from a list of divisors (see \ref{sct:simuRemarks}). This also gives the $C_i = \lfloor U_i \, T_i \rfloor$
-	\item $O_i$ (...)
-	\item And finally, choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i)$, where the value of $e$ is discussed in \ref{sct:simuRemarks}.
-\end{itemize}
-
-\subsubsection{General remarks}
-\label{sct:simuRemarks}
-\begin{itemize}
-	\item The interval used for the generation of $D_i$ can be explained by looking at the final formula for the DIT $$t_d = \operatorname*{min}_{a_i \in [D_i, T_i], \; i = 1 \cdots n} t_{idle} (a_1, \cdots, a_n)$$ The necessary number of combination of $a_i$ values to considerr is equal to the cardinality of $[D_1, T_1] \times [D_2, T_2] \times \cdots \times [D_n, T_n]$, which gives an exponential time in the number of tasks.
-This constraint aims to allow the DIT algorithm to terminate in an acceptable time but it also gives it a considerable advantage.
-	\item The $T_i$ are not generated uniformly, but from a list of divisors of 554400\footnote{LCM of $2^5$, $3^2$, $5^2$, 7 and 11}.
-This prevents the value of the hyper-period from growing exponentially.
-Similarly, this is giving the hyper-period method an advantage.
-	\item During the DBF test, the deadline are considered chronologically.
-The order is not important for feasible tasks set, but can change the duration of the test for unfeasible task set (where the DBF test can stop when it finds an instant where the test does not hold).
-\end{itemize}
-
-\subsubsection{Source code}
-
-Am I allowed to make it available on GitHub? License problem with ECE?
-
-\subsection{Results}
-
-Fig.
-\ref{fig:simuTextResult} gives us the precise timing with a value of $e = 5$.
-While the DIT and the hyper-period methods achieve similar results, the busy period method is clearly ahead.
-This can be explained by the relative simplicity of its algorithm.\\
-
-Looking more closely at the values, the trade-off offered by the DIT method compared to the hyper-period method becomes apparent.
-While the preprocessing time is longer for the DIT, the interval to consider for the DBF test is greatly reduced.\\
-
-\begin{figure}[h]
-\begin{center}
-
-\begin{lstlisting}[language=]
-== Test Results (on 1000 tasks system)
-	Algorithms performance (upper limit computation + dbf test)
-		Time with busy period: 0.02 + 0.01  =  0.03 s
-		Time with DIT: 0.84 + 0.83  =  1.67 s
-		Time with hyperT: 0.02 + 1.64  =  1.66 s
-	Feasible? 432 , or about 43 %
-\end{lstlisting}
-
-\caption{Comparison of performance of different upper limit for the DBF feasibility test} with $e=5$
-\label{fig:simuTextResult}
-\end{center}
-\end{figure}
-
-~\\
-
-Fig.
-\ref{fig:simuGraphE} shows the influence of the $e$ parameter, which describes the restriction imposed on the deadline parameter.
-Observe the exponential growth to the left.
-While we could think that the hyper-period curve should not be affected by $e$, this figure shows otherwise.
-This is explained by the fact that higher value of $e$ means more feasibility, and as was shown previously more feasibility means longer feasibility tests.
-
-\begin{figure}[h]
-\begin{center}
-
-\includegraphics[width=0.75\textwidth]{figs/001_137389818886_princess.png}
-
-\caption{Comparison of performance for different values of $e$. The plain line represent the total time, while the dotted line represent only the upper limit computation time.}
-\label{fig:simuGraphE}
-\end{center}
-\end{figure}
+\end{abstract}
 
 \newpage
-\appendix
 
-\huge APPENDIX
-\normalsize
+\section{Introduction}
 
-\section{Generalized Chinese Remainder Theorem}
-\label{sct:appCRT}
+\section{Related Works}
 
-First let us recall the Chinese Remainder Theorem, proven in \cite{leiserson2001introduction}.
+    \subsection{Model}
 
-\begin{theorem}
- \textbf{Chinese Remainder Theorem} Suppose $M_1, \cdots, M_n$ are positive integers which are pairwise co-prime.
-Then, for any given sequence of integers $a_1, \cdots, a_n$ there exists one integer $x$ modulo $M = M_1 \cdots M_n$ solving the following system
- $$
- \left\{
-	\begin{array}{llcl}
-		x \equiv a_1 \; (mod \; M_1) \\
-		x \equiv a_2 \; (mod \; M_2) \\
-		\vdots \\
-		x \equiv a_n \; (mod \; M_n)
-	\end{array}
-\right.
- $$
+    Present model with per-task $\alpha$
 
-This value is given by
-$$x = \sum_{i=1}^{n} a_i \frac{M}{M_i} \left[ \frac{M}{M_i} \right]_{M_i}^{-1}$$
-where $[a]^{-1}_{b}$ is the modular multiplicative inverse of $a$ (mod $b$)
-\end{theorem}
-
-We can see that a requirement of the theorem is that the values of $M_i$ need to be pairwise co-prime.
-When this is not the case, the system is not guaranteed to have a solution.
-Indeed, a previous result in \cite{leiserson2001introduction} is that the system has one solution modulo $M$ if and only if $\forall \; i,j \; s.t.
-\; a_i \equiv a_j \; (mod \; gcd(M_i, M_j) )$ (which is clearly true when all the $M_i$ are pairwise co-prime).\\
-
-A method to find this solution, which we will call the Generalized Chinese Remainder Theorem, is given in \cite{mathNonPairwiseCoprime}.
-The method consists of transforming the system into an equivalent one where the moduli are pairwise co-prime, which we can then solve using the Chinese Remainder Theorem.
-Another method would be the method of successive substitution.
-
-\newpage
 \nocite{*}
 \bibliographystyle{plain}
-\bibliography{dit-paper}
+\bibliography{paper-paedf}
 

### 2013-09-12 python-simulation/Simulator/Drawer.py
quickfix to have arrivals and deadline even if an exception occurs before termination

@@ -24,6 +24,7 @@ class Drawer(object):
         self.outDraw = draw.Draw(self.outImg)
 
         self.drawGrid(stop)
+        self.drawArrivalsAndDeadlines()
 
     def getTaskNbr(self, task):
         taskNbr = None

### 2013-09-12 python-simulation/Simulator/Simulator.py
priorities are not updated at each preemption, which force Schedulers to be smart and removes possible loops

@@ -151,49 +151,46 @@ class Simulator(object):  # Global multiprocessing only
                 heappush(self.activeJobsHeap, (-1 * newJob.priority, newJob))
 
     def handlePreemptions(self):
-        while True:
-            # update priorities
-            self.updatePriorities()
-            self.updateHeaps()
-            # check for preemptions
+        # update priorities
+        self.updatePriorities()
+        self.updateHeaps()
+        # check for preemptions
+        if self.verbose:
+            print("\t", self.mostPrioritaryJob(), "(", str(self.mostPrioritaryJob().priority if self.mostPrioritaryJob() else None), ") vs.", self.leastPrioritaryCPU(), "(", str(self.leastPrioritaryCPU().priority() if self.leastPrioritaryCPU() else None), ")")
+        if self.mostPrioritaryJob() and self.leastPrioritaryCPU() and self.mostPrioritaryJob().priority >= self.leastPrioritaryCPU().priority():
+            # special case of equal priorities : decided by the scheduler
+            if self.mostPrioritaryJob().priority == self.leastPrioritaryCPU().priority():
+                if self.verbose:
+                    print("equal priority: preemption policy of scheduler :", self.scheduler.preemptEqualPriorities())
+                if not self.scheduler.preemptEqualPriorities():
+                    return
+            if self.verbose:
+                print("\tpremption!")
+            preemptiveJob = heappop(self.activeJobsHeap)[1]
+            preemptedCPU = heappop(self.activeCPUsHeap)
+            preemptedJob = preemptedCPU.job  # may be None
+
+            # assign preemptive job to the CPU and push CPU in the correct heap
+            self.updatePriorities(job=preemptiveJob)
+            preemptedCPU.job = preemptiveJob
+            if preemptiveJob.preempted and preemptiveJob.alpha() > 0:
+                self.preemptedCPUs.add(preemptedCPU)
+            else:
+                heappush(self.activeCPUsHeap, preemptedCPU)
+            if preemptiveJob.preempted:
+                preemptiveJob.preempted = False
+
+            # put the preempted job back in the active job heap
+            if preemptedJob:
+                preemptedJob.preempted = True
+                preemptedJob.preemptionTimeLeft = preemptedJob.alpha()
+                if self.AR:
+                    preemptedJob.computation = 0
+                    self.drawer.drawAbort(preemptedJob.task, self.t)
+                heappush(self.activeJobsHeap, (-1 * preemptedJob.priority, preemptedJob))
[…]

### 2013-09-12 python-simulation/paper-paedf/paper-paedf.tex
structure
abstract++

@@
 \title{Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor systems}
+\author{Thomas Chapeaux}
+\date{Summer 2013}
 %opening
@@
 
+In preemptive scheduling techniques of real-time systems, a task can be interrupted during its execution to allow another task to meet its deadline.
+Previous results, such as the optimality of the EDF scheduler, assume that the added cost of the preemptions (including context saving and restoration, as well as the increase in cache misses) is negligible compared to the tasks execution time.
+In this paper, we show that when the preemption costs are supposed non-negliglbe and constant per-task.
+
 \end{abstract}
@@
 
-\section{Related Works}
+\section{Model}
 
-    \subsection{Model}
+    \subsection{State of the Art}
 
-    Present model with per-task $\alpha$
+        OCDT model with per-task
+
+        Constrained deadline
+
+        EDF is optimal
+
+    \subsection{Preemption Cost}
+
+        Preemption model (add parameters alpha and atomic preemption recovery period)
+
+        Meumeu is FTP-optimal (equivalent to ExhaustiveFTP)
+
+\section{Performance of EDF with preemption cost}
+
+    \subsection{Non-optimality}
+
+    \subsection{Anomalies}
+
+\section{PA-EDF: an amelioration}
 

### 2013-09-12 python-simulation/mainSimu.py
New system

@@ -8,7 +8,7 @@ import subprocess
 import sys
 
 # tau = systems.generateSystemArray(1, 0)[0]
-tau = systems.LongTransitive
+tau = systems.test
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()

### 2013-09-12 python-simulation/mainSimuComp.py

@@ -9,10 +9,10 @@ import pylab
 
 domin_scores = {}
 results = {}
-NUMBER_OF_SYSTEMS = 100
+NUMBER_OF_SYSTEMS = 1000
 nRange = list(range(2, 6))
-schedulers = [PALLF.PALLF, Scheduler.PTEDF]
-names = ["PALLF", "PA-EDF"]
+schedulers = [Scheduler.EDF, Scheduler.PTEDF]
+names = ["EDF", "PA-EDF"]
 
 
 def oneTest(taskCnt):
@@ -24,8 +24,8 @@ def oneTest(taskCnt):
 
     for i in range(NUMBER_OF_SYSTEMS):
         print("n", taskCnt, "\t", i, "/", NUMBER_OF_SYSTEMS)
-        tau = systems.generateSystemArray(1, 0, n=taskCnt)[0]  # 0 is implicit, 1 is constrained
-        # print(tau)
+        tau = systems.generateSystemArray(1, 0, n=taskCnt, preemptionCost=-1)[0]  # 0 is implicit, 1 is constrained
+        print(tau)
 
         Omax = max([task.O for task in tau.tasks])
         H = tau.hyperPeriod()

### 2013-09-12 python-simulation/systems.py

@@ -249,12 +249,18 @@ tasks.append(Task.Task(0, 1, 3, 3, alpha=1))
 tasks.append(Task.Task(0, 5, 9, 9, alpha=1))
 ImpFTPNonOptimal = Task.TaskSystem(tasks)
 
+# DifferentPreemptionCost_PTFNonOptimal
+tasks = []
+tasks.append(Task.Task(1, 11, 18, 18, alpha=2))
+tasks.append(Task.Task(0, 7, 30, 30, alpha=0))
+tasks.append(Task.Task(1, 1, 9, 9, alpha=0))
+DifferentPreemptionCost_PTFNonOptimal = Task.TaskSystem(tasks)
+
+
 # test
 tasks = []
-tasks.append(Task.Task(27, 1, 12, 12, alpha=2))
-tasks.append(Task.Task(0, 6, 20, 20, alpha=2))
-tasks.append(Task.Task(1, 1, 4, 4, alpha=2))
-tasks.append(Task.Task(60, 2, 12, 12, alpha=2))
-tasks.append(Task.Task(0, 1, 6, 6, alpha=2))
+tasks.append(Task.Task(1, 11, 18, 18, alpha=2))
+tasks.append(Task.Task(0, 7, 30, 30, alpha=0))
+tasks.append(Task.Task(1, 1, 9, 9, alpha=0))
 
 test = Task.TaskSystem(tasks)

### 2013-09-16 python-simulation/mainSimuComp.py
graph per utilization rather than number of tasks

@@ -1,31 +1,47 @@
 from Model import algorithms
+from Model import Task, TaskGenerator
 from Simulator import Simulator
 from Simulator import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
 import systems
 
-
+import random
 import pylab
 
 
 domin_scores = {}
 results = {}
 NUMBER_OF_SYSTEMS = 1000
-nRange = list(range(2, 6))
+uRange = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]
 schedulers = [Scheduler.EDF, Scheduler.PTEDF]
 names = ["EDF", "PA-EDF"]
 
+failures = []
 
-def oneTest(taskCnt):
-    domin_scores[taskCnt] = {}
-    results[taskCnt] = {}
+
+def oneTest(utilization):
+    global failureCnt
+    domin_scores[utilization] = {}
+    results[utilization] = {}
     for sched in schedulers:
-        results[taskCnt][sched] = []
-        domin_scores[taskCnt][sched] = 0
+        results[utilization][sched] = []
+        domin_scores[utilization][sched] = 0
 
     for i in range(NUMBER_OF_SYSTEMS):
-        print("n", taskCnt, "\t", i, "/", NUMBER_OF_SYSTEMS)
-        tau = systems.generateSystemArray(1, 0, n=taskCnt, preemptionCost=-1)[0]  # 0 is implicit, 1 is constrained
-        print(tau)
+        print("u = ", utilization, ", i = ", i, "/", NUMBER_OF_SYSTEMS)
+        Umin = 0.55
+        Umax = 0.95
+        # Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
+        Utot = utilization
+        maxHyperT = 360  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
+        # maxHyperT = -1
+        Tmin = 3
+        Tmax = 50
+        n = random.randint(2, 5)
+        preemptionCost = 2
+        constrDeadlineFactor = 0  # 0 is implicit, 1 is constrained
+        tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, preemptionCost=preemptionCost, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
[…]

### 2013-09-16 python-simulation/systems.py
problematic system

@@ -257,10 +257,18 @@ tasks.append(Task.Task(1, 1, 9, 9, alpha=0))
 DifferentPreemptionCost_PTFNonOptimal = Task.TaskSystem(tasks)
 
 
+# ImpPTEFTNonOptimal
+tasks = []
+tasks.append(Task.Task(0, 9, 45, 45, alpha=2))
+tasks.append(Task.Task(0, 1, 6, 6, alpha=2))
+tasks.append(Task.Task(0, 6, 12, 12, alpha=2))
+ImpPTEFTNonOptimal = Task.TaskSystem(tasks)
+
+
 # test
 tasks = []
-tasks.append(Task.Task(1, 11, 18, 18, alpha=2))
-tasks.append(Task.Task(0, 7, 30, 30, alpha=0))
-tasks.append(Task.Task(1, 1, 9, 9, alpha=0))
+tasks.append(Task.Task(0, 9, 45, 45, alpha=2))
+tasks.append(Task.Task(0, 1, 6, 6, alpha=2))
+tasks.append(Task.Task(0, 6, 12, 12, alpha=2))
 
 test = Task.TaskSystem(tasks)

### 2013-09-16 python-simulation/paper-paedf/paper-paedf.tex
extended the abstract

@@
 In preemptive scheduling techniques of real-time systems, a task can be interrupted during its execution to allow another task to meet its deadline.
-Previous results, such as the optimality of the EDF scheduler, assume that the added cost of the preemptions (including context saving and restoration, as well as the increase in cache misses) is negligible compared to the tasks execution time.
-In this paper, we show that when the preemption costs are supposed non-negliglbe and constant per-task.
+Previous results, such as the optimality of the EDF scheduler, assume that the added cost of the preemptions (including context saving and restoration, as well as the increase in cache misses) is negligible compared to the tasks execution times.
+In this paper, we show that within a model taking this cost into account, the optimality of EDF is no longer guaranteed.
+We then propose another algorithm which strictly dominates EDF in the model, and prove that it is also optimal for implicit deadline systems.
 

### 2013-09-16 python-simulation/mainSimu.py
main main

@@ -8,7 +8,7 @@ import subprocess
 import sys
 
 # tau = systems.generateSystemArray(1, 0)[0]
-tau = systems.test
+tau = systems.ImpPTEFTNonOptimal
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()
@@ -25,10 +25,10 @@ stop = Omax + 10 * H
 
 print(("stop", stop))
 
-scheduler = Scheduler.EDF(tau)
+# scheduler = Scheduler.EDF(tau)
 # scheduler = Scheduler.SpotlightEDF(tau)
 # scheduler = ChooseKeepEDF.ChooseKeepEDF(tau)
-# scheduler = Scheduler.PTEDF(tau)
+scheduler = Scheduler.PTEDF(tau)
 # scheduler = PALLF.PALLF(tau)
 # scheduler = Scheduler.ArbitraryScheduler(tau, systems.mpanaSchedule)
 # scheduler = LBLScheduler.LBLEDF(tau)

### 2013-09-16 dit-paper_ieee.tex
review 1

@@
 \and
-\IEEEauthorblockN{Jo\e"l Goossens}
+\IEEEauthorblockN{Jo\"el Goossens}
 \IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
@@
 }
+
 \maketitle
@@
 	conditions in the case of small changes in task parameters, such as when porting a system to a
-different platform. The C-space, presented in \cite{bini2004schedulability,george2009characterization}, describes the
+	different platform. The C-space describes the
 	set of execution times for which a system is feasible. This paper extends previous works to
 	generalize the description of the C-space for Earliest Deadline First scheduling to
-systems with initial offset. The feasibility gain offered by offsets is then
-expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
+	systems with initial task offsets. The feasibility gain offered by offsets is
+	then expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
 	synchronous system.
@@
 	The \emph{C-space} of a real-time system is, intuitively,
-	the set of WCET values for which this system would be feasible. A
-	precise and efficient description of the C-space of a system would allow to quickly decide
+	the set of WCET values for which this system would be feasible
+	\cite{bini2004schedulability,george2009characterization}. A precise and efficient description of the C-space of a system would allow to quickly decide
 	whether or not it is feasible on a given platform.
@@
 	In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
-	system based on the DBF test, we show why the interval $[t_d, t_d + H]$ is
-	sometimes sufficient to consider and we give a numerical example.
+	system based on the demand bound function test. Then we show why applying this
+	test on the interval starting at $t_d$
+	and spanning an hyperperiod when $t_d$ exists is sufficient. A
+	numerical example is also given.
 
@@
 	\subsection{Model}
-
-		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic concrete
+		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
 		tasks with constrained deadlines on uniprocessor platforms. Each task

### 2013-09-16 dit-paper_ieee.tex
review algo 1

@@
 	conditions in the case of small changes in task parameters, such as when porting a system to a
-	different platform. The C-space describes the
-	set of execution times for which a system is feasible. This paper extends previous works to
-	generalize the description of the C-space for Earliest Deadline First scheduling to
-	systems with initial task offsets. The feasibility gain offered by offsets is
-	then expressed as the volume ratio between the C-space of an asynchronous system and its corresponding
-	synchronous system.
+	different platform. The C-space describes the set of execution times for which
+	a system is feasible. This paper extends previous works to generalize the
+	description of the C-space for Earliest Deadline First scheduling to systems
+	with initial task offsets. The feasibility gain offered by offsets is then
+	expressed as the volume ratio between the C-space of an asynchronous system and
+	its corresponding synchronous system. The problem requires solving multiple
+	similar instances of the Chinese Remainder Problem, for which an algorithm
+	efficient in this context is provided.
 \end{abstract}
@@
 
-		For those systems, the preemptive \emph{Earliest Deadline First} (EDF) algorithm, in
-		which jobs are prioritized according to their absolute deadline, has been
+		For both synchronous and asynchronous systems, the preemptive
+		\emph{Earliest Deadline First} (EDF) algorithm, in which jobs are prioritized according to their absolute deadline, has been
 		shown to be optimal \cite{liu1973scheduling}, which means it
@@
 		t_d = \min
-    \left( t \; s.t. \; \forall i:
+		\left( t \; s.t. \; \forall i \; \exists a_i \in [D_i, T_i]:
 			\left\{
@@
 					t \equiv a_i \; (mod \; T_i) \\
-          a_i \in [D_i, T_i]
 				\end{array}
@@
 			\begin{algorithmic}[1]
-				\REQUIRE $A$ is a list of the sets of possible $a_i$ per task
+				\REQUIRE $\forall j: A_j$ is a list of the sets of possible $a_i$ values for
+				task $\tau_j$ 
 				\REQUIRE $H$ is the hyperperiod of the system
@@
 					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
-					\FORALL{$a_i \in A(\tau_j)$}
-						\STATE $\text{append} \; (a_i \cdot Mj \cdot invMj) \; \text{to} \; taskTerms$
+					\FORALL{$a_i \in A_j$}
+						\STATE $taskTerms[i] \leftarrow (a_i \cdot Mj \cdot invMj)$
 					\ENDFOR
-					\STATE $\text{append} \; taskTerms \; \text{to} \; sumchunks$
+					\STATE $sumchunks[j] \leftarrow taskTerms$
 				\ENDFOR
@@
 					\STATE $newresults \leftarrow \text{empty list}$
-					\FORALL{$a_i \in A(\tau_j)$}
+					\FORALL{$a_i \in A_j$}
 						\FORALL{$r \in results$}
-							\STATE $\text{append} \; (r + sumchunks(\tau_j,i)) \; \text{to} \; newresults$
+							\STATE $\text{append} \; (r + sumchunks[j][i]) \; \text{to} \;
+							newresults$
 						\ENDFOR

### 2013-09-16 dit-paper_ieee.tex
added reference
algo 1 review

@@
 			\begin{algorithmic}[1]
-				\REQUIRE $\forall j: A_j$ is a list of the sets of possible $a_i$ values for
-				task $\tau_j$ 
+				\REQUIRE $\forall i: A_i$ is the set of possible $a_i$ values for
+					task $\tau_i$
 				\REQUIRE $H$ is the hyperperiod of the system
@@
 				\STATE $sumchunks \leftarrow \text{empty list}$
-				\FORALL{$\tau_j \in \tau$}
+				\FORALL{$\tau_i \in \tau$}
 					\STATE $taskTerms \leftarrow \text{empty list}$
-					\STATE $Mj \leftarrow \frac{H}{T_j}$
-					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_j)$
-					\FORALL{$a_i \in A_j$}
-						\STATE $taskTerms[i] \leftarrow (a_i \cdot Mj \cdot invMj)$
+					\STATE $Mj \leftarrow \frac{H}{T_i}$
+					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_i)$
+					\FORALL{$a_i \in A_i$}
+						\STATE append $(a_i \cdot Mj \cdot invMj)$ to $taskTerms$
 					\ENDFOR
-					\STATE $sumchunks[j] \leftarrow taskTerms$
+					\STATE $sumchunks[i] \leftarrow taskTerms$
 				\ENDFOR
@@
 				\STATE append $0$ to $results$
-				\FORALL{$\tau_j \in \tau$}
+				\FORALL{$\tau_i \in \tau$}
 					\STATE $newresults \leftarrow \text{empty list}$
-					\FORALL{$a_i \in A_j$}
+					\FORALL{$chunk \in sumchunks[i]$}
 						\FORALL{$r \in results$}
-							\STATE $\text{append} \; (r + sumchunks[j][i]) \; \text{to} \;
-							newresults$
+							\STATE $\text{append} \; (r + chunk) \; \text{to} \; newresults$
 						\ENDFOR
@@
 
-		The description we presented in Section \ref{sct:cspaceDescr} was general, and
+		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
 		is thus still relevant. Therefore the C-space is still accurately described by

### 2013-09-16 dit-paper_ieee.tex
review

@@
 	\subsection{The DBF feasibility test}
-
-	We recall the necessary and sufficient feasability condition on monoprocessor platform given in \cite{baruah1999generalized, baruah1990algorithms} and based on the demand-bound function.
+		We recall the necessary and sufficient feasability condition on monoprocessor
+		platforms based on the demand-bound function \cite{baruah1999generalized,
+		baruah1990algorithms}.
 
@@
 
-		As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}).
-The constraints must be conditions which can unequivocally decide if a point is included in the region or not.
-In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ to the list of constraints).
+			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$
+			such as the C-space can be described by a \emph{polytope}, or a list of
+			parametric linear constraints (called the \emph{formulation}). The
+			constraints must be conditions which can unequivocally decide if a point is
+			included in the region or not. In the sequel we give a formulation for the
+			C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add
+			$C_i \geqslant 1 \; \forall \tau_i \in \tau$ to the list of constraints).
 
@@
       \[
-        \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+     	\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
+      	t_1 \leq t_2
       \]
@@
 					first busy period.
-      \item As any $kH$ with $k \geqslant 0$ is a DIT in synchronous systems, we have at least $t_d
-      \leqslant H$ in this case.
+				\item In synchronous systems any $kH$ with $k \geqslant 0$ is a DIT and we
+					also have at least $t_d \leqslant H$.
 			\end{itemize}
@@
 		t_d = \min
-		\left( t \; s.t. \; \forall i \; \exists a_i \in [D_i, T_i]:
+		\left( t \; s.t. \; \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]:
 			\left\{
@@
 			\begin{array}{l}
-				\exists ? \; t_d \; s.t. \; \forall i \; :\\
+				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau \; :\\
 				\left\{
@@
 
-		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
+		The description we presented in Section \ref{sct:cspaceDescr} was general, and
 		is thus still relevant. Therefore the C-space is still accurately described by

### 2013-09-16 dit-paper_ieee.tex
review 3 : added todo comments, fixed equations

@@
 	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
-	conditions in the case of small changes in task parameters, such as when porting a system to a
-	different platform. The C-space describes the set of execution times for which
-	a system is feasible. This paper extends previous works to generalize the
-	description of the C-space for Earliest Deadline First scheduling to systems
-	with initial task offsets. The feasibility gain offered by offsets is then
-	expressed as the volume ratio between the C-space of an asynchronous system and
-	its corresponding synchronous system. The problem requires solving multiple
-	similar instances of the Chinese Remainder Problem, for which an algorithm
-	efficient in this context is provided.
+	conditions in the case of small changes in task parameters, such as
+	different WCET values when porting a system to a different platform. The C-space describes the set of execution
+	times for which a system is feasible, which allows system designers to quickly
+	find the best platform for a given task set. This paper extends previous works
+	to generalize the description of the C-space for Earliest Deadline First
+	scheduling to systems with initial task offsets. The feasibility gain offered
+	by offsets is then expressed as the volume ratio between the C-space of an
+	asynchronous system and its corresponding synchronous system. The problem
+	requires solving multiple similar instances of the Chinese Remainder Problem,
+	for which an algorithm efficient in this context is provided.
 \end{abstract}
@@
 \label{sct:relatedWorks}
+
+%Review 3 : add map of literature
+
 	\subsection{Model}
@@
 			\begin{array}{l}
-				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau \; :\\
+				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
+				T_i] \; :\\
 				\left\{
@@
 						t_d > O_i \\
-						t_d - O_i \equiv a_i \; (mod \; T_i) \\
-						a_i \in [D_i, T_i]
+						t_d - O_i \equiv a_i \; (mod \;	T_i)
+						\\
 					\end{array}
@@
 		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
-		the FPDIT (if any), because for a given set of $a_i$ values they are
-		very similar to an instance of the Chinese Remainder Problem (CRP), which is
-		easily solved using Gauss's CRP solving method for non-coprime moduli
-		\cite{gauss1965disquisitiones}.
+		the FPDIT (if any), because for a given set of $a_i$ values the problem of
+		finding the corresponding DIT is an instance of the Chinese Remainder Problem
+		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
+		moduli \cite{gauss1965disquisitiones}.
+
+		%Review 3 : explain Gauss algorithm
 
@@
 		means the modular inverse of $x$ in the naturals modulo $y$).
+
+		%Review 3 : add formal complexity assessment of this algorithm
 

### 2013-09-16 dit-paper_ieee.tex
added equation numbering

@@
 		Mathematically,
-		\[
+		\begin{equation}
 			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
-		\]
+		\end{equation}
 		where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ which arrival times
@@
 		The values of the $n_i$ are given by \cite{baruah1999generalized}
-		\[
+		\begin{equation}
 			n_i(t_1, t_2) =
@@
 			\right\rrbracket_0
-		\]
+		\end{equation}
 		where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.
@@
 		\begin{theorem}
-		\[
+			\begin{equation}
 				\begin{array}{c}
@@
 				\end{array}
-		\]
+			\end{equation}
 		\end{theorem}
@@
 
-      The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility.
-They can all be written in the following way:
-      \[
-     	\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
-      	t_1 \leq t_2
-      \]
+		The DBF test gives us a list of inequations on the WCET values of the task set
+		which together are a necessary and sufficient condition of feasibility. They
+		can all be written in the following way:
+		\begin{equation}
+			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+		\end{equation}
 		Note that for a given $t$, we have that the $n_i(t)$ are
@@
 
-  The value of the first DIT can be found by solving the following modular equation system:
-	\[
+		The value of the first DIT can be found by solving the following modular
+		equation system:
+
+		%TODO : change format so that the equation number is displayed correctly
+
+		\begin{equation}
 			t_d = \min
@@
 			\right)
-	\]
+		\end{equation}
   The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.
@@
   slightly more pessimistic but still correct to use the following condition:
-  \[
+  \begin{equation}
   		\dbf{0,t} \leqslant t \; \forall t \leqslant t_d
   		\iff \text{The system is feasible}
-  \]
+  \end{equation}
 
@@
 		can be written as a system of modular equations:
-		\[
+		\begin{equation}
 			\begin{array}{l}
@@
 			\end{array}
-		\]
+		\end{equation}
 
@@
 		values of $a_i$ if the following condition is respected:
-		\[
-			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
-			T_j)) \; \forall i,j
-		\]
+
+		%Review 3 : use ref to justify this formula
+		%TODO : change format so that the equation number is displayed correctly
+
+		\begin{equation}
+			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i,j
+		\end{equation}
 		which means that there could be systems with no FPDIT.
@@
 
-	We observe that when the $CDF$ tends to zero, few systems have a FPDIT.
+	We observe that when the CDF tends to zero, few systems have a FPDIT.
 	This is easily explained by the fact that
@@
 
-		\[
+		\begin{equation}
 			\sum_{i=1}^{n} n_i(t_1, t_2)
 			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
-		\]
+		\end{equation}
 
@@
 We now apply Algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
-$$
+	\begin{equation}
 		\left\{
@@
 		\right.
-$$
+	\end{equation}
 The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.

### 2013-09-17 dit-paper_ieee.tex
fixed equation 5
explained gauss CRP algorithm

@@
 		equation system:	
-
-		%TODO : change format so that the equation number is displayed correctly
-
 		\begin{equation}
-			t_d = \min
-			\left( t \; s.t. \; \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]:
-				\left\{
-					\begin{array}{c}
-						t > 0 \\
-						t \equiv a_i \; (mod \; T_i) \\
-					\end{array}
-				\right.
-			\right)
+			\begin{split}
+				 t_d = \min(& \{ t \; s.t. \; t > 0 \; and \\ 
+						& \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]: t \equiv a_i \;
+						(mod \; T_i) \})
+			\end{split}
 		\end{equation}
@@
 		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
-		moduli \cite{gauss1965disquisitiones}.
+		moduli \cite{gauss1965disquisitiones}. (note that $x^{-1} \; (mod \; y)$
+		means the modular inverse of $x$ in the naturals modulo $y$)
+
+		\begin{algorithm}
+			\caption{Gauss's CRP Algorithm}
+			\label{alg:algoCRP}
+			\begin{algorithmic}[1]
+				\REQUIRE $\forall \tau_i \in \tau : a_i \in [D_i,T_i]$
+				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
+				\REQUIRE $H$ is the hyperperiod of the system
+
+				\STATE Modify the $n_i$ and $a_i$ by prime decomposition so \\ that the
+				$n_i$ become pairwise coprime
+
+				\FORALL{$\tau_i \in \tau$}
+					\STATE $Mj \leftarrow \frac{H}{n_i}$
+					\STATE $invMj \leftarrow Mj^{-1} (mod \; n_i)$
+					\STATE $e_i \leftarrow (Mj \cdot invMj)$
+				\ENDFOR
+				\RETURN $\sum\limits_{\tau_i \in \tau}{a_i \cdot e_i} \; (mod \; H)$
+			\end{algorithmic}
+		\end{algorithm}
 
@@
 		combinations of $a_i$ values in the number of tasks, and resolving
-		exponentially many CRP is prohibitively slow. A better method for finding the
-		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
-		shown in Algorithm~\ref{alg:multiACRP} (note that $x^{-1} \; (mod \; y)$
-		means the modular inverse of $x$ in the naturals modulo $y$).
+		exponentially many CRP is prohibitively slow. A faster method for finding
+		the FPDIT consists in merging all these CRP instances into one problem
+		(finding all DITs), which can be solved faster by
+		Algorithm~\ref{alg:multiACRP}, as a significant part of the needed
+		intermediate results are shared between instances.
 
@@
 			\begin{algorithmic}[1]
-				\REQUIRE $\forall i: A_i$ is the set of possible $a_i$ values for
-					task $\tau_i$
+				\REQUIRE $\forall \tau_i \in \tau: A_i$ is the set of possible $a_i$ values
+				for $\tau_i$
+				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
 				\REQUIRE $H$ is the hyperperiod of the system
+
+				\STATE Modify the $n_i$ and $a_i$ by prime decomposition so \\ that the
+				$n_i$ become pairwise coprime
 
@@
 
-		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
-		speedup is achieved by first computing all possible terms for each task
-		then creating all possible DIT values by summing the terms in all possible
-		ways. The number of results is still exponential in the number of tasks, but
-		the only operation that is repeated exponentially many times is now a sum.
-		This allows us to profit from a high chance of having DITs when the deadlines
-		are close to the WCETs (and far from the periods), but with only a slight
-		increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.
+		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
+		computation of one modular inversion per $a_i$ value, which is done in linear
+		time with the number of tasks. However, to find all DITs
+		Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
+		combination of $a_i$ values, which is exponential in the number of tasks.
+		Algorithm~\ref{alg:multiACRP} is not faster in orders of
+		complexity as the computation of all DITs still requires an exponential number
+		of answers in the number of tasks, but it is nonetheless significantly faster
+		in practice. The running time of Algorithm~\ref{alg:multiACRP} is also less
+		sensitive to the number of different $a_i$ values per task, which means tasks
+		with deadlines significantly smaller than periods remain practical.
 

### 2013-09-17 python-simulation/mainNoFPDIT.py
python3 mod

@@ -2,65 +2,65 @@ import random
 import time
 import pylab
 
-from .Model import algorithms
-from .Model import cspace
-from .Model import Task
-from .Model import TaskGenerator
+from Model import algorithms
+from Model import cspace
+from Model import Task
+from Model import TaskGenerator
 
 
 def generateSystemArray(numberOfSystems, constrDeadlineFactor, tasksCnt, verbose=False):
-	systemArray = []
-	for i in range(numberOfSystems):
-		Umin = 0.25
-		Umax = 0.75
-		Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
-		n = tasksCnt
-		# maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
-		maxHyperT = -1
-		Tmin = 5
-		Tmax = 20
-		tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
-		if (verbose and numberOfSystems <= 10):
-			print(("Generated task system # ", i))
-			for task in tasks:
-					print(("\t", task))
-		systemArray.append(Task.TaskSystem(tasks))
-	return systemArray
+    systemArray = []
+    for i in range(numberOfSystems):
+        Umin = 0.25
+        Umax = 0.75
+        Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
+        n = tasksCnt
+        # maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
+        maxHyperT = -1
+        Tmin = 5
+        Tmax = 20
+        tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
+        if (verbose and numberOfSystems <= 10):
+            print(("Generated task system # ", i))
+            for task in tasks:
+                    print(("\t", task))
+        systemArray.append(Task.TaskSystem(tasks))
+    return systemArray
 
 if __name__ == '__main__':
[…]

### 2013-09-17 dit-paper_ieee.tex
removed a whitespace line
small things

@@
 	conditions in the case of small changes in task parameters, such as
-	different WCET values when porting a system to a different platform. The C-space describes the set of execution
+	different WCET values when porting a system to a different platform. The \mbox{C-space} describes the set of execution
 	times for which a system is feasible, which allows system designers to quickly
@@
 	test on the interval starting at $t_d$
-	and spanning an hyperperiod when $t_d$ exists is sufficient. A
+	and spanning an hyperperiod is sufficient when $t_d$ exists. A
 	numerical example is also given.
@@
 		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
-		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
-		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
+		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period, which is the exact time between two consecutive arrivals.
+		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
 		the following, we differentiate between \emph{synchronous systems} (where $O_i
@@
 			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
-			equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
+			equal to the maximum cumulated execution time of jobs of $\tau$ contained in the
 			closed interval $[t_1, t_2]$.
@@
 		values of $a_i$ if the following condition is respected:
-
 		%Review 3 : use ref to justify this formula
-		%TODO : change format so that the equation number is displayed correctly
-
 		\begin{equation}
@@
 		the following infinite number of constraints:
-
 		\begin{equation}
@@
 		\end{equation}
-
 		However, the method used in the synchronous case to remove redundancy does not

### 2013-09-17 dit-paper_ieee.tex
added knuth reference

--- 2013-09-17 dit-paper_ieee.tex
@@
 		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
-		moduli \cite{gauss1965disquisitiones}. (note that $x^{-1} \; (mod \; y)$
-		means the modular inverse of $x$ in the naturals modulo $y$)
+		moduli \cite{gauss1965disquisitiones,knuth1969art}. (note that $x^{-1} \; (mod
+		\; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
 

### 2013-09-17 dit-paper_ieee.tex
small reformulation

--- 2013-09-17 dit-paper_ieee.tex
@@
 		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period, which is the exact time between two consecutive arrivals.
-		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
+		The constrained deadline property implies that $D_i \leq T_i$. In
 		the following, we differentiate between \emph{synchronous systems} (where $O_i
-		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).
+		= 0$ for all tasks) and \emph{asynchronous systems} (which are not synchronous).
 
@@
 		The DBF test gives us a list of inequations on the WCET values of the task set
-		which together are a necessary and sufficient condition of feasibility. They
+		which, taken together, are a necessary and sufficient condition of feasibility. They
 		can all be written in the following way:
@@
 		\end{equation}
-		Note that for a given $t$, we have that the $n_i(t)$ are
+		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
 		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

### 2013-09-17 dit-paper_ieee.tex

@@
 		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
-		moduli \cite{gauss1965disquisitiones}. (note that $x^{-1} \; (mod \; y)$
-		means the modular inverse of $x$ in the naturals modulo $y$)
-
+		moduli \cite{gauss1965disquisitiones,knuth1969art}. (note that $x^{-1} \; (mod
+		\; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
 		\begin{algorithm}

### 2013-09-17 dit-paper_ieee.tex
small reformulations

@@
 		\end{equation}
-		which means that there could be systems with no FPDIT.
+		which means that systems where no such values of $a_i$ exists do not have a FPDIT.
 		We now present an example of such a system.\\
@@
 		(finding all DITs), which can be solved faster by
-		Algorithm~\ref{alg:multiACRP}, as a significant part of the needed
+		Algorithm~\ref{alg:multiACRP}, as a significant part of the
 		intermediate results are shared between instances.

### 2013-09-17 dit-paper_ieee.tex
theorem 1

--- 2013-09-17 dit-paper_ieee.tex
@@
 	conditions in the case of small changes in task parameters, such as
-	different WCET values when porting a system to a different platform. The \mbox{C-space} describes the set of execution
+	different WCET values when porting a system to a different platform. The C-space describes the set of execution
 	times for which a system is feasible, which allows system designers to quickly
@@
 	test on the interval starting at $t_d$
-	and spanning an hyperperiod is sufficient when $t_d$ exists. A
+	and spanning an hyperperiod when $t_d$ exists is sufficient. A
 	numerical example is also given.
@@
 		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
-		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period, which is the exact time between two consecutive arrivals.
-		The constrained deadline property implies that $D_i \leq T_i$. In
+		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
+		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
 		the following, we differentiate between \emph{synchronous systems} (where $O_i
-		= 0$ for all tasks) and \emph{asynchronous systems} (which are not synchronous).
+		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).
 
@@
 			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
-			equal to the maximum cumulated execution time of jobs of $\tau$ contained in the
+			equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
 			closed interval $[t_1, t_2]$.
@@
 		based on the DBF \cite{baruah1999generalized}
-
 		\begin{theorem} 
-			\begin{equation}
+			\begin{equation*}
 				\begin{array}{c}
 					\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
-					\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+					\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall t_1,t_2 \; s.t. \; 0 \leq t_1 \leq t_2
 				\end{array}
-			\end{equation}
+			\end{equation*} 
 		\end{theorem}
-
 	\subsection{C-space of synchronous systems}
@@
 		The DBF test gives us a list of inequations on the WCET values of the task set
-		which, taken together, are a necessary and sufficient condition of feasibility. They
+		which together are a necessary and sufficient condition of feasibility. They
 		can all be written in the following way:
@@
 		\end{equation}
-		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
+		Note that for a given $t$, we have that the $n_i(t)$ are
 		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

### 2013-09-18 dit-paper_ieee.tex
closed issue #29

--- 2013-09-17 dit-paper_ieee.tex
@@
 			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
-			equal to the maximum cumulated execution time of jobs of $\tau$ contained in the
+			equal to the cumulated execution time of jobs of $\tau$ contained in the
 			closed interval $[t_1, t_2]$.
@@
 
-		A necessary and sufficient condition of feasibility can easily be written
-		based on the DBF \cite{baruah1999generalized}
+		The following necessary and sufficient condition of feasibility
+		based on the DBF is given in \cite{baruah1999generalized}:
 
@@
 				\begin{array}{c}
-					\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
-					\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+					\tau \: \text{is feasible}  \iff
+					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
 				\end{array}
@@
 		\end{theorem}
+
+        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time.
+Therefore the system is unfeasible.
 
@@
 		combination of $a_i$ values, which is exponential in the number of tasks.
-		Algorithm~\ref{alg:multiACRP} is not faster in orders of
-		complexity as the computation of all DITs still requires an exponential number
+		Algorithm~\ref{alg:multiACRP} has the same theoretical complexity as the computation of all DITs still requires an exponential number
 		of answers in the number of tasks, but it is nonetheless significantly faster
@@
 
-		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
-		is thus still relevant. Therefore the C-space is still accurately described by
+		The description based on \cite{baruah1999generalized} and presented in Section \ref{sct:cspaceDescr} was general and
+		is still relevant. Therefore the C-space is still accurately described by
 		the following infinite number of constraints:
@@
 correct description of the C-Space, but it is not efficient. Redundant
-contraints are removed through a linear integer approach.
+constraints are removed through a linear integer approach.
 
@@
 
-	In other words, this figure
+	In other words, fig.~\ref{fig:sizeRatio}
 	evaluates the feasibility gain of adding random offsets to a synchronous task

### 2013-09-18 python-simulation/mainNoFPDIT.py

@@ -28,35 +28,28 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, tasksCnt, verbose
     return systemArray
 
 if __name__ == '__main__':
-    NUMBER_OF_SYSTEMS = 10
-    noFPDITpcts2 = []
-    noFPDITpcts3 = []
-    noFPDITpcts4 = []
-    CDFvalues = []
-    for constrDeadlineFactor in [1/(x * 0.1) for x in range(1, 11)]:
-        print(("CDF", constrDeadlineFactor))
-        systemArray2 = generateSystemArray(NUMBER_OF_SYSTEMS, constrDeadlineFactor, 2)
-        systemArray3 = generateSystemArray(NUMBER_OF_SYSTEMS, constrDeadlineFactor, 3)
-        systemArray4 = generateSystemArray(NUMBER_OF_SYSTEMS, constrDeadlineFactor, 4)
-        firstDITs2 = []
-        firstDITs3 = []
-        firstDITs4 = []
-        for i, tau in enumerate(systemArray2):
-            firstDITs2.append(algorithms.findFirstPeriodicDIT(tau))
-        for i, tau in enumerate(systemArray3):
-            firstDITs3.append(algorithms.findFirstPeriodicDIT(tau))
-        for i, tau in enumerate(systemArray4):
-            firstDITs4.append(algorithms.findFirstPeriodicDIT(tau))
-        noFPDITpcts2.append((100.0*len([x for x in firstDITs2 if x is None]))/len(firstDITs2))
-        noFPDITpcts3.append((100.0*len([x for x in firstDITs3 if x is None]))/len(firstDITs3))
-        noFPDITpcts4.append((100.0*len([x for x in firstDITs4 if x is None]))/len(firstDITs4))
-        print(("Percentage of system with no FPDIT:", noFPDITpcts2[-1], noFPDITpcts3[-1], noFPDITpcts4[-1], "%"))
-        CDFvalues.append(constrDeadlineFactor)
+    NUMBER_OF_SYSTEMS = 100
+    noFPDITpcts = {}
+    CDFvalues = [0.1, 0.3, 0.5, 0.7, 0.9, 1.0]
+    nValues = [2, 3, 4, 5, 10]
+    for taskCnt in nValues:
+        print("n", taskCnt)
+        noFPDITpcts[taskCnt] = {}
+        for constrDeadlineFactor in CDFvalues:
[…]

### 2013-09-18 dit-paper_ieee.tex

@@
 		based on the DBF is given in \cite{baruah1999generalized}:
-
 		\begin{theorem}
-			\begin{equation}
+			\begin{equation*}
 				\begin{array}{c}
 					\tau \: \text{is feasible}  \iff
-					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1, t_2 \mid  0 \leq t_1 \leq t_2
 				\end{array}
-			\end{equation}
+			\end{equation*}
 		\end{theorem}
-
         Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time.
@@
 		\begin{equation}
-			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
+			\sum_{i=1}^{n}  n_i(t_1, t_2) \cdot C_i \leq t_2 - t_1 \; \forall t_1,t_2 \mid 0 \leq t_1 \leq t_2
 		\end{equation}

### 2013-09-18 dit-paper_ieee.tex
spacing in formulas + ref to algorithm 1

@@
 		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
-		moduli \cite{gauss1965disquisitiones,knuth1969art}. (note that $x^{-1} \; (mod
-		\; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
+		moduli (Algorithm~\ref{alg:algoCRP}) \cite{gauss1965disquisitiones,knuth1969art}.
+		(note that $x^{-1} \; (mod \; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
 		\begin{algorithm}
@@
 					\STATE $Mj \leftarrow \frac{H}{n_i}$
-					\STATE $invMj \leftarrow Mj^{-1} (mod \; n_i)$
-					\STATE $e_i \leftarrow (Mj \cdot invMj)$
+					\STATE $invMj \leftarrow Mj^{-1} \; (mod \; n_i)$
+					\STATE $e_i \leftarrow Mj \cdot invMj$
 				\ENDFOR

### 2013-09-18 dit-paper_ieee.tex
Rewritten FPDIT existence condition and construction

@@
 		\end{equation}
-
-		This system is guaranteed to have at least one solution modulo $H$ for given
-		values of $a_i$ if the following condition is respected:
-		%Review 3 : use ref to justify this formula
+		This system is equivalent to an instance of the Chinese Remainder Problem
+		(CRP) where the goal is to find the value of $t_d$ such that it is congruent
+		to $a_i+O_i$ modulo $T_i$ for all tasks $\tau_i$ in $\tau$. We define $x_i =
+		a_i+O_i$ and $n_i = T_i$ for clarity in the context of the CRP. This problem
+		is guaranteed to have at least one solution modulo $H$ for given values of
+		$a_i$ if Condition~\ref{eq:CRPcond} is respected
+		\cite{knuth1969art}:
 		\begin{equation}
-			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i,j
+			\label{eq:CRPcond}
+			x_i \equiv x_j \; (\operatorname{mod} \; \operatorname{gcd}(n_i, n_j))
+			\; \forall \tau_i,\tau_j \in \tau
 		\end{equation}
-		which means that systems where no such values of $a_i$ exists do not have a FPDIT.
-		We now present an example of such a system.\\
-
-		\begin{center}
-			\begin{tabular}{|r|c|c|c|c|}
-				\hline
-							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
-				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
-				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
-			\end{tabular}
-		\end{center}
-
-		Here, the possible values of $a_1$ are 3 and 4, and the possible values
-		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
-		conditions must be fulfilled:
-		\[
-			\left[
-			\begin{array}{c}
-				3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
-				3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
-				4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
-				4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
-			\end{array}
-			\right.
-		\]
-		However neither is, which means the system has
-		no FPDIT (and no other DIT than $t=0$).
+		Condition~\ref{eq:CRPcond} means that DITs might still exist even though in
+		the general case task periods will not necessarily be pairwise coprime.
+% 		We now present an example of such a system.\\
+% 
+% 		\begin{center}
+% 			\begin{tabular}{|r|c|c|c|c|}
+% 				\hline
+% 							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
+% 				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
+% 				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
+% 			\end{tabular}
+% 		\end{center}
+% 
+% 		Here, the possible values of $a_1$ are 3 and 4, and the possible values
+% 		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
+% 		conditions must be fulfilled:
+% 		\[
+% 			\left[
+% 			\begin{array}{c}
+% 				3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
+% 				3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
+% 				4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
+% 				4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
+% 			\end{array}
+% 			\right.
+% 		\]
+% 		However neither is, which means the system has
+% 		no FPDIT (and no other DIT than $t=0$).
 
 	\subsection{Solving the modular system}
-		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
-		the FPDIT (if any), because for a given set of $a_i$ values the problem of
-		finding the corresponding DIT is an instance of the Chinese Remainder Problem
-		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
-		moduli (Algorithm~\ref{alg:algoCRP}) \cite{gauss1965disquisitiones,knuth1969art}.
-		(note that $x^{-1} \; (mod \; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
+		A sketch of the construction algorithm for $t_d$ can be found in
+		Algorithm~\ref{alg:algoCRP} (note that $x^{-1} \; (mod \; y)$ means the
+		modular inverse of $x$ in the naturals modulo $y$). In this paper we
+		concentrate on the latter part of the algorithm (after the modifications to
+		correct non-coprime periods, readers interested in the details of these
+		modifications should refer to \cite{knuth1969art}).		
 		\begin{algorithm}
@@
 				\REQUIRE $\forall \tau_i \in \tau : a_i \in [D_i,T_i]$
+				\REQUIRE $\forall \tau_i \in \tau : x_i = a_i+O_i$
 				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
@@
 
-				\STATE Modify the $n_i$ and $a_i$ by prime decomposition so \\ that the
+				\STATE Modify the $n_i$ and $x_i$ by prime decomposition so \\ that the
 				$n_i$ become pairwise coprime
@@
 				\ENDFOR
-				\RETURN $\sum\limits_{\tau_i \in \tau}{a_i \cdot e_i} \; (mod \; H)$
+				\RETURN $\sum\limits_{\tau_i \in \tau}{x_i \cdot e_i} \; (mod \; H)$
 			\end{algorithmic}
 		\end{algorithm}
-
-		%Review 3 : explain Gauss algorithm
-
-		However this is very inefficient as there are exponentially many different
-		combinations of $a_i$ values in the number of tasks, and resolving
-		exponentially many CRP is prohibitively slow. A faster method for finding
-		the FPDIT consists in merging all these CRP instances into one problem
-		(finding all DITs), which can be solved faster by
-		Algorithm~\ref{alg:multiACRP}, as a significant part of the
-		intermediate results are shared between instances.
+		Algorithm~\ref{alg:algoCRP} finds one DIT given one value of $a_i$ per task.
+		However using it in practice is very inefficient as there are
+		exponentially many different combinations of $a_i$ values in the number of
+		tasks, and resolving exponentially many CRP instances is prohibitively slow.
+		A faster method for finding the FPDIT consists in merging all these CRP
+		instances into one problem (finding all DITs), which can be solved faster by
+		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
+		results are shared between instances.
 
@@
 			\begin{algorithmic}[1]
-				\REQUIRE $\forall \tau_i \in \tau: A_i$ is the set of possible $a_i$ values
-				for $\tau_i$
+				\REQUIRE $\forall \tau_i \in \tau: X_i$ is the set of possible $a_i+O_i
+				\; \forall a_i \in [D_i,T_i]$ values for $\tau_i$
 				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
@@
 
-				\STATE Modify the $n_i$ and $a_i$ by prime decomposition so \\ that the
-				$n_i$ become pairwise coprime
+				\STATE Modify the $n_i$ and the content of the $X_i$ by prime
+				\\ decomposition so that the $n_i$ become pairwise coprime
 
@@
 					\STATE $taskTerms \leftarrow \text{empty list}$
-					\STATE $Mj \leftarrow \frac{H}{T_i}$
-					\STATE $invMj \leftarrow Mj^{-1} (mod \; T_i)$
-					\FORALL{$a_i \in A_i$}
-						\STATE append $(a_i \cdot Mj \cdot invMj)$ to $taskTerms$
+					\STATE $Mj \leftarrow \frac{H}{n_i}$
+					\STATE $invMj \leftarrow Mj^{-1} (mod \; n_i)$
+					\FORALL{$x_i \in X_i$}
+						\STATE append $(x_i \cdot Mj \cdot invMj)$ to $taskTerms$
 					\ENDFOR

### 2013-09-18 dit-paper_ieee.tex
rewritten FPDIT existence and construction

@@
 		\end{equation}
-		This system is equivalent to an instance of the Chinese Remainder Problem
-		(CRP) where the goal is to find the value of $t_d$ such that it is congruent
-		to $a_i+O_i$ modulo $T_i$ for all tasks $\tau_i$ in $\tau$. We define $x_i =
-		a_i+O_i$ and $n_i = T_i$ for clarity in the context of the CRP. This problem
-		is guaranteed to have at least one solution modulo $H$ for given values of
-		$a_i$ if Condition~\ref{eq:CRPcond} is respected
-		\cite{knuth1969art}:
+
+		This system is equivalent to multiple instances (one per combination of $a_i$
+		values) of the Chinese Remainder Problem (CRP) where the goal is to find the
+		value of $t_d$ such that it is congruent to $a_i+O_i$ modulo $T_i$ for all
+		tasks $\tau_i$ in $\tau$. To find the FPDIT it is to the best of our knowledge
+		necessary to solve the problem on all combinations of $a_i$ values then
+		compute the minimum solution. We define $x_i = a_i+O_i$ and $n_i = T_i$ for
+		clarity in the context of the CRP. One instance of this problem is guaranteed
+		to have at least one solution modulo $H$ for given values of $a_i$ if
+		Condition~\ref{eq:CRPcond} is satisfied \cite{knuth1969art}:
 		\begin{equation}
@@
 		\end{algorithm}
-		Algorithm~\ref{alg:algoCRP} finds one DIT given one value of $a_i$ per task.
-		However using it in practice is very inefficient as there are
+		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
+		values. However using it in practice is very inefficient as there are
 		exponentially many different combinations of $a_i$ values in the number of
@@
 
-				\STATE Modify the $n_i$ and the content of the $X_i$ by prime
-				\\ decomposition so that the $n_i$ become pairwise coprime
+				\STATE Modify $n_i$ and the content of $X_i$ by prime
+				\\ decomposition to get pairwise coprime $n_i$ values
 
@@
 		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
-		computation of one modular inversion per $a_i$ value, which is done in linear
-		time with the number of tasks. However, to find all DITs
-		Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
+		computation of one modular inversion per $a_i$ value, which is done in a
+		linear number of modular inversions per task. However, to
+		find all DITs Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
 		combination of $a_i$ values, which is exponential in the number of tasks.
-		Algorithm~\ref{alg:multiACRP} has the same theoretical complexity as the computation of all DITs still requires an exponential number
-		of answers in the number of tasks, but it is nonetheless significantly faster
-		in practice. The running time of Algorithm~\ref{alg:multiACRP} is also less
-		sensitive to the number of different $a_i$ values per task, which means tasks
-		with deadlines significantly smaller than periods remain practical.
+		Algorithm~\ref{alg:multiACRP} has the same theoretical complexity as the
+		computation of all DITs still requires an exponential number of answers in the
+		number of tasks, but it is nonetheless significantly faster in practice. The
+		running time of Algorithm~\ref{alg:multiACRP} is also less sensitive to the
+		number of different $a_i$ values per task, which means that this method
+		remains practical when tasks deadlines are much smaller than periods.
 

### 2013-09-18 dit-paper_ieee.tex
Close #19

--- 2013-09-18 dit-paper_ieee.tex
@@
 
-The general problem of redundancy of a new linear constraint $C \, X \leq d$ w.r.t.
+Previous sections give us a list of (integer) linear constraints accurately describing the C-space, composed of the DBF test applied to the required intervals.
+We now give a method to remove redundant constraints from this list.
+
+The general problem of redundancy of some linear constraint $C \, X \leq d$ w.r.t.
 a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the ILP presented in Fig.~\ref{fig:redILP}.
@@
 the simplex algorithm and a branch-and-cut approach.
-However, in our case the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within.
-A naive method would be to test each constraint against all the others.
+However, in our case the problem is not to test for redundancy of a particular constraint but to find all redundant constraints within a set.
+A naive method would be to test every constraint against all the others.
 We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.
@@
       \IF {$cstr$ is not redundant w.r.t. $S$}
-        \STATE $S \leftarrow cstr$
+        \STATE $S.push(cst)rcl$
       \ENDIF
     \ENDFOR
-    \STATE \COMMENT{$2^{nd}$ pass: test each $cstr$ against every other}
+    \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
     \FOR{$cstr$ \textbf{in} $S$}
-      \STATE Remove $cstr$ from $S$
+      \STATE $cstr$ = $S.pop()$
       \IF {$cstr$ is not redundant w.r.t. $S$}
-        \STATE Put $cstr$ back into $S$
+        \STATE $S.push(cstr)$
       \ENDIF

### 2013-09-19 dit-paper_ieee.tex
New NoFPDIT graph
Close #28 and reworded task generation and fig description for noFPDIT simulation

@@
 
-		The values of the $n_i$ are given by \cite{baruah1999generalized}
+		The values of the $n_i$ are given by \cite{baruah1990algorithms}
 		\begin{equation}
@@
 	\begin{itemize}
-		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters
+		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
 		\begin{itemize}
 			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
-			\item $n$ (number of tasks) equal to 3, 4 and 5.
+			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
 		\end{itemize}
@@
 	\begin{center}
-		\includegraphics[width=0.5\textwidth]{figs/nofpdit_3.png}
+		\includegraphics[width=0.5\textwidth]{figs/nofpdit_4.png}
 	\end{center}
@@
 
-	We observe that when the CDF tends to zero, few systems have a FPDIT.
+	We observe that when the CDF is close to zero, fewer systems have a FPDIT.
 	This is easily explained by the fact that

### 2013-09-20 dit-paper_ieee.tex
Explained the period range as requested in issue #21

@@
 		\end{itemize}
-		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
+		\item Choosing the $T_i$ uniformly between 5 and 20 (in order to have a manageable value of $H$), which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
 		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
@@
 	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
-	three tasks without synchronous instants were generated. The size of their
+	three tasks without synchronous instants were generated as described in Section~\ref{sct:noFPDITsimu}. The size of their
 	C-space (number of valid WCET vectors) was compared with that of the same

### 2013-09-20 dit-paper_ieee.tex
Removed emphasis on "strictly"
monoprocessor -> uniprocessor

@@
 			\item An \emph{idle time} is an instant $t$ at which each job that arrived
-			\emph{strictly} before $t$ has finished its execution.
+			strictly before $t$ has finished its execution.
 			\item A \emph{busy period} is a time interval between two consecutive idle times in
@@
 	\subsection{The DBF feasibility test}
-		We recall the necessary and sufficient feasability condition on monoprocessor
+		We recall the necessary and sufficient feasability condition on uniprocessor
 		platforms based on the demand-bound function \cite{baruah1999generalized,

### 2013-09-20 dit-paper_ieee.tex
Reworded

@@
 		\end{theorem}
-        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time.
-Therefore the system is unfeasible.
+        It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time.
+Therefore the system would be unfeasible.
 

### 2013-09-20 dit-paper_ieee.tex
rewording

@@
 
-		The DBF test gives us a list of inequations on the WCET values of the task set
-		which, taken together, are a necessary and sufficient condition of feasibility. They
-		can all be written in the following way:
+		The DBF test gives us the following list of inequations on the WCET values of the task set
+		which, taken together, are a necessary and sufficient condition of feasibility:
 		\begin{equation}
@@
 
-  To summarize, we reduced the description of the C-space from an infinite number
+  To summarize, the description of the C-space is reduced from an infinite number
   of constraints to only those where $t_1 = 0$, $t_2 \leqslant t_d$ and
@@
 	\label{sct:FPDITexist}
-
 		As in the synchronous case, the problem of existence of the FPDIT
@@
 		\end{equation}
+        Where $a \equiv b \; (mod \; n)$ means that $a$ and $b$ are congruent modulo $n$.
 
@@
 	\begin{itemize}
-		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
+		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with:
 		\begin{itemize}
-			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
-			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
+			\item The system utilization chosen uniformly between 0.25 and 0.75
+			\item The number of tasks set to several values (see Fig.~\ref{fig:noFPDIT})
 		\end{itemize}

### 2013-09-20 dit-paper_ieee.tex
typos

--- 2013-09-20 dit-paper_ieee.tex
@@
 	find the best platform for a given task set. This paper extends previous works
-	to generalize the description of the C-space for Earliest Deadline First
+	generalizing the description of the C-space for Earliest Deadline First
 	scheduling to systems with initial task offsets. The feasibility gain offered
@@
 	Finally, in section~\ref{sct:expCspaceGain}, we use a simulation to quantify the feasibility
-	gain of asynchronous system in terms of volume of the C-space.
+	gain of asynchronous systems in terms of volume of the C-space.
 
@@
 	\subsection{Model}
-		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
+		We consider a discrete timeline and tasks systems comprised of periodic
 		tasks with constrained deadlines on uniprocessor platforms. Each task
@@
 		\begin{itemize}
-			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$
+			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$ is called the task system
 			\item $H = \operatorname{lcm}(T_1, \cdots, T_{n})$
@@
 	\subsection{The DBF feasibility test}
-		We recall the necessary and sufficient feasability condition on uniprocessor
+		We recall the necessary and sufficient feasability condition on monoprocessor
 		platforms based on the demand-bound function \cite{baruah1999generalized,
@@
 		\end{theorem}
-        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time.
-Therefore the system is unfeasible.
+        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time.
+Therefore the system is not feasible.
 
@@
       which are redundant. While this does not harm the precision of the
-      test, a smaller description is preferred as it can greatly
+      test, a finite description is needed in practice. The description should also be as small as possible as this can greatly
       reduce the computation time of practical feasibility tests. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of constraints is given.
@@
   therefore not usable for the purposes of this paper. The
-  following concept, initially described by \cite{lipariaverage}, is thus introduced. It gives an upper bound for to the end of the busy period and does not depend on the execution times.
+  following concept, initially described by \cite{lipariaverage}, is thus introduced. It gives an upper bound for the end of the first busy period and does not depend on the execution times.
 
@@
 				\item In synchronous systems any $kH$ with $k \geqslant 0$ is a DIT and we
-					also have at least $t_d \leqslant H$.
+					also have $t_d \leqslant H$.
 			\end{itemize}
@@
 		The value of the first DIT can be found by solving the following modular
-		equation system:
+		equations system:
 		\begin{equation}

### 2013-09-23 dit-paper_ieee.tex

@@
 		\end{theorem}
-        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time.
-Therefore the system is not feasible.
+        It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time.
+Therefore the system would not be feasible.
 
@@
 	\begin{itemize}
-		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
+		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with:
 		\begin{itemize}
-			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
-			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
+			\item System utilization chosen uniformly between 0.25 and 0.75
+			\item The number of tasks set to several values (see Fig.~\ref{fig:noFPDIT})
 		\end{itemize}

### 2013-09-23 dit-paper_ieee.tex
minor changes

@@
 	evaluates the feasibility gain of adding random offsets to a synchronous task
-	set. It is assumed that a more advanced strategy to assign these offsets
-	would yield a greater difference.
+	set. It is assumed that a more advanced strategy to assign these offsets (such
+	as the ones from \cite{goossens2003scheduling}) would yield a
+	greater difference.
 
@@
 	sizes is rather long, the number of systems used to obtain average
-	results was rather low (1000), which is the likely cause of the spikes in the
+	results was rather low (5000), which is the likely cause of the spikes in the
 	data. Note that the value of the CDF has a greater influence on this ratio than

### 2013-09-24 python-simulation/Model/cspace.py
Moved cspace test into its own main

@@ -1,9 +1,7 @@
 from Model import algorithms
 
-import random
 import subprocess  # in order to launch GLPSOL
 import itertools
-import math
 import os.path
 import re
 
@@ -154,26 +152,6 @@ def testCVector(cspace, cvector):
     return True
 
 
-def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
-    systemArray = []
-    for i in range(numberOfSystems):
-        Umin = 0.25
-        Umax = 0.75
-        Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
-        n = 3
-        # maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
-        maxHyperT = -1
-        Tmin = 5
-        Tmax = 20
-        tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
-        if (verbose and numberOfSystems <= 10):
-            print("Generated task system # ", i)
-            for task in tasks:
-                    print("\t", task)
-        systemArray.append(Task.TaskSystem(tasks))
-    return systemArray
-
-
 class CSpaceConstraint(object):  # TODO : make the code use this lovely class
     def __init__(self, coeffs, t):
         self.coeffs = coeffs
@@ -199,7 +177,7 @@ class CSpaceConstraint(object):  # TODO : make the code use this lovely class
         self.writeRedundancyGLPSOLData(cspace, "redundant_temp.dat")
         p = subprocess.Popen(args=["glpsol", "-m", os.path.join("GLPK", "redundant.mod"), "-d", "redundant_temp.dat"], stdout=subprocess.PIPE)
         (output, err) = p.communicate()
-        reRes = re.search(r".*?Display\ statement\ at\ line\ 28.*?(?P<number>[0-9]+).*", output, re.DOTALL)
+        reRes = re.search(r".*?Display\ statement\ at\ line\ 28.*?(?P<number>[0-9]+).*", str(output), re.DOTALL)
         resultMaximization = int(reRes.group('number'))
         return resultMaximization <= self.t
 
[…]

### 2013-09-24 python-simulation/mainAsynchr.py

@@ -2,9 +2,9 @@ import random
 import time
 import pylab
 
-from .Model import algorithms
-from .Model import Task
-from .Model import TaskGenerator
+from Model import algorithms
+from Model import Task
+from Model import TaskGenerator
 
 
 def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):

### 2013-09-24 python-simulation/mainRedunComp.py

@@ -1,7 +1,7 @@
-from .Model import Task
-from .Model import TaskGenerator
-from .Model import algorithms
-from .Model import cspace
+from Model import Task
+from Model import TaskGenerator
+from Model import algorithms
+from Model import cspace
 
 import pylab
 
@@ -58,7 +58,7 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 	return systemArray
 
 if __name__ == '__main__':
-	systemArray = generateSystemArray(100, 1)
+	systemArray = generateSystemArray(10, 1)
 	cstrSizes = []
 	twoTimes = []
 	oneTimes = []

### 2013-09-24 python-simulation/mainSimu.py

@@ -8,7 +8,7 @@ import subprocess
 import sys
 
 # tau = systems.generateSystemArray(1, 0)[0]
-tau = systems.ImpPTEFTNonOptimal
+tau = systems.LongTransitive2
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()

### 2013-09-24 dit-paper_ieee.tex
size ratio n systems
Reworked conclusion

--- 2013-09-23 dit-paper_ieee.tex
@@
 	find the best platform for a given task set. This paper extends previous works
-	generalizing the description of the C-space for Earliest Deadline First
+	to generalize the description of the C-space for Earliest Deadline First
 	scheduling to systems with initial task offsets. The feasibility gain offered
@@
 	Finally, in section~\ref{sct:expCspaceGain}, we use a simulation to quantify the feasibility
-	gain of asynchronous systems in terms of volume of the C-space.
+	gain of asynchronous system in terms of volume of the C-space.
 
@@
 	\subsection{Model}
-		We consider a discrete timeline and tasks systems comprised of periodic
+		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
 		tasks with constrained deadlines on uniprocessor platforms. Each task
@@
 		\begin{itemize}
-			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$ is called the task system
+			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$
 			\item $H = \operatorname{lcm}(T_1, \cdots, T_{n})$
@@
 		\end{theorem}
-        It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time.
-Therefore the system would not be feasible.
+        It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time.
+Therefore the system would be unfeasible.
 
@@
       which are redundant. While this does not harm the precision of the
-      test, a finite description is needed in practice. The description should also be as small as possible as this can greatly
+      test, a smaller description is preferred as it can greatly
       reduce the computation time of practical feasibility tests. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of constraints is given.
@@
   therefore not usable for the purposes of this paper. The
-  following concept, initially described by \cite{lipariaverage}, is thus introduced. It gives an upper bound for the end of the first busy period and does not depend on the execution times.
+  following concept, initially described by \cite{lipariaverage}, is thus introduced. It gives an upper bound for to the end of the busy period and does not depend on the execution times.
 
@@
 				\item In synchronous systems any $kH$ with $k \geqslant 0$ is a DIT and we
-					also have $t_d \leqslant H$.
+					also have at least $t_d \leqslant H$.
 			\end{itemize}
@@
 		The value of the first DIT can be found by solving the following modular
-		equations system:
+		equation system:
 		\begin{equation}
@@
 		\begin{itemize}
-			\item System utilization chosen uniformly between 0.25 and 0.75
+			\item The system utilization chosen uniformly between 0.25 and 0.75
 			\item The number of tasks set to several values (see Fig.~\ref{fig:noFPDIT})
@@
 
+    % PRECISER : on ne genere pas de systyemes avec instants synchroes
+
 	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
@@
 
-In this paper, we presented a general approach to define the C-space of a constrained periodic task set for EDF on uniform platform.
+In this paper, we presented a general approach to concisely define the C-space of a constrained periodic task set for EDF on uniform platforms.
+We then used the C-space to quantify the feasibility gain given by random offset values, with a final result of about 10~\% more WCET values being feasible.
 Possible future works includes an extension to the study of systems with preemption costs or running on multiprocessor platforms, as the value of the DIT does not depend on preemptions or the number of processors.
 
-Future works could also repeat the simulation of section~\ref{sct:expCspaceGain} with the algorithm described in \cite{grenier2008pushing}, which determine offset values with optimal feasibility. The
-feasibility gain could then be expressed using the C-space.
+% A mettre quelque part : nombre de contraintes avant/apres dans les expériences (issue #20)
+
+Future works could also study the case of offset-free systems, where the offset values can be chosen.
+The performance of algorithms such as \cite{grenier2008pushing} and \cite{goossens2003scheduling} (although the latter depends on the execution times), which determine offset values with optimal feasibility, can be expressed using the C-space.
 

### 2013-09-24 dit-paper_ieee.tex

--- 2013-09-23 dit-paper_ieee.tex
@@
 	these systems roughly range from 0.95 in the worst case (high utilization, high
-	CDF) to 0.85 in the best case (low utilization, low CDF). As calculating those
-	sizes is rather long, the number of systems used to obtain average
-	results was rather low (5000), which is the likely cause of the spikes in the
-	data. Note that the value of the CDF has a greater influence on this ratio than
+	CDF) to 0.85 in the best case (low utilization, low CDF). Note that the value of the CDF has a greater influence on this ratio than
 	the system's total utilization, but less so when the CDF is lower. It is also

### 2013-09-25 dit-paper_ieee.tex
merge Laurent George

--- 2013-09-23 dit-paper_ieee.tex
@@
 \IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
-\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
+\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles / ECE\\
 tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
@@
 \IEEEauthorblockN{Laurent George}
-\IEEEauthorblockA{ECE Paris\\
-lgeorge@ece.fr}
+\IEEEauthorblockA{University of Paris-Est / ECE Paris\\
+lgeorge@ieee.org}
 \and
@@
 	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
-	conditions in the case of small changes in task parameters, such as
-	different WCET values when porting a system to a different platform. The \mbox{C-space} describes the set of execution
-	times for which a system is feasible, which allows system designers to quickly
-	find the best platform for a given task set. This paper extends previous works
+	conditions in the case of changes in task parameters, such as
+	different WCET values when porting a system to a different platform. The \mbox{C-space} defines the space of execution
+	times for which a system is feasible, which can help system designers to more easily check 
+	if a task set is feasible on a set of candidate platforms. This paper extends previous works
 	generalizing the description of the C-space for Earliest Deadline First
@@
 	by offsets is then expressed as the volume ratio between the C-space of an
-	asynchronous system and its corresponding synchronous system. The problem
+	asynchronous system and its corresponding synchronous system when offsets are randomly chosen. The problem
 	requires solving multiple similar instances of the Chinese Remainder Problem,
-	for which an algorithm efficient in this context is provided.
+	for which an efficient algorithm in this context is provided. We show that even for random offsets, the gain can reach 15%.
 \end{abstract}
@@
 	worst-case execution time of a job (WCET), a value highly dependent on the
-	platform on which the application is deployed. Feasibility conditions allow to
-	decide whether a system can be scheduled correctly (i.e. without violating any
+	platform on which the application is deployed. Feasibility conditions allow us to
+	decide whether a system can be correctly scheduled (i.e. without violating any
 	timeliness constraint) based on task parameters, including the WCET.
@@
 	The \emph{C-space} of a real-time system is, intuitively,
-	the set of WCET values for which this system would be feasible
-	\cite{bini2004schedulability,george2009characterization}. A precise and efficient description of the C-space of a system would allow to quickly decide
-	whether or not it is feasible on a given platform.
+	the space of WCET values for which this system is feasible
+	\cite{bini2004schedulability,george2009characterization}.
+A precise and efficient description of the C-space of a system would allow us to efficiently decide whether or not it is feasible on a set of candidate platforms.
 
@@
 	constrained systems, which has been mostly covered by \cite{george2009characterization}, is revisited.
-	This description is based on the DBF feasibility condition described in
+	This description is based on the Demand Bound Function (DBF) feasibility condition described in
 	\cite{baruah1999generalized,baruah1990algorithms} and is found with exponential complexity using
-	the notion of definitive idle times (DIT).
+	the notion of definitive idle times (DIT). The DIT notion provides a feasibility interval for EDF that does not depend of the WCET of the tasks.
 
@@
 
-		The following necessary and sufficient condition of feasibility
-		based on the DBF is given in \cite{baruah1999generalized}:
+		The following theorem is a necessary and sufficient condition of feasibility
+		based on the DBF, given in \cite{baruah1999generalized}:
 		\begin{theorem}
@@
 		\end{theorem}
-        It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time.
+        %It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ units of computation have to be done in $t_2 - t_1$ units of time.
 Therefore the system would not be feasible.
@@
   \begin{definition}
-    A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
+    A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ (if it exists) such that every job
     released strictly before instant $t$ has its absolute deadline before or at instant $t$.
@@
   \begin{definition}
-    The earliest DIT occurring in the system strictly after $t=0$ is called the
+    The earliest DIT (if it exists) occurring in the system strictly after $t=0$ is called the
     \textbf{first DIT} and is noted $t_d$.
@@
 
-		\begin{remark} (from the definitions):
+		\begin{remark} (from the definitions, if a DIT exist then):
 			\begin{itemize}
-				\item Contrary to other idle times, DITs are independent of the
+				\item Contrary to other idle times, a DIT is independent of the
 					scheduling or the execution times of the jobs.
@@
   is our ``best guess'' at an upper limit on the end of the busy period. As it was sufficient
-  to check the DBF test in intervals $[0, t]$ before the end of the busy period, it is
-  slightly more pessimistic but still correct to use the following condition:
+  to check the DBF test in intervals $[0, t]$ before the end of the first busy period. This time interval is WCETs dependant. A more general feasility condition valid for any WCET is as follows:
   \begin{equation}
@@
   values of $t_2$ correspond to job deadlines. Note that the number of
-  constraints is still exponential in the number of tasks in the worst-case ($t_d = H$).
+  constraints is still exponential in the number of tasks in the worst-case (which is when $t_d = H$).
 
@@
 		tasks $\tau_i$ in $\tau$. To find the FPDIT it is to the best of our knowledge
-		necessary to solve the problem on all combinations of $a_i$ values then
-		compute the minimum solution. We define $x_i = a_i+O_i$ and $n_i = T_i$ for
+		necessary to solve the problem on all combinations of $a_i$ values and then
+		to compute the minimum solution. We define $x_i = a_i+O_i$ and $n_i = T_i$ for
 		clarity in the context of the CRP. One instance of this problem is guaranteed
@@
 	\subsection{Solving the modular system}
-		A sketch of the construction algorithm for $t_d$ can be found in
+		A sketch of the construction algorithm to compute $t_d$ can be found in
 		Algorithm~\ref{alg:algoCRP} (note that $x^{-1} \; (mod \; y)$ means the
@@
 
+			As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the
+			\emph{incomplete period}, where all tasks are not in the system. Then, after
+			$O_{max}$ time units, every tasks is in the system and the \emph{transient
+			period} begins. Then, after $O_{max} + H$ time units, the system is faced
+			with the same pattern of arrival as in $O_{max}$. However, because in
+			$O_{max} + H$ every task is in the system and in $O_{max}$ some were missing,
+			the state of the system will be different. The \emph{stationary period} then
+			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
+			exact same situation it was at instant $O_{max} + H$.
+
 			\begin{figure}[h]
@@
 
-			As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the
-			\emph{incomplete period}, where all tasks are not in the system. Then, after
-			$O_{max}$ time units, every tasks is in the system and the \emph{transient
-			period} begins. Then, after $O_{max} + H$ time units, the system is faced
-			with the same pattern of arrival as in $O_{max}$. However, because in
-			$O_{max} + H$ every task is in the system and in $O_{max}$ some were missing,
-			the state of the system will be different. The \emph{stationary period} then
-			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
-			exact same situation it was at instant $O_{max} + H$.
-
 			For this reason, as shown by \cite{leung1982complexity}, it is sufficient (but pessimistic) to
@@
 			notion of cyclic idle times (denoted $t_c$), which are dependent of the execution
-			time and therefore cannot be used directly. Their interval is $[0, t_c + H]$ and is valid for
+			time and therefore cannot be used directly to characterize the C-Space. Their interval is $[0, t_c + H]$ and is valid for
 			every cyclic idle time $t_c$.
@@
 
-The general problem of redundancy of some linear constraint $C \, X \leq d$ w.r.t.
-a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the ILP presented in Fig.~\ref{fig:redILP}.
+The general problem of redundancy of some linear constraint $C \cdot X \leq d$
+w.r.t. a set of previous linear constraints $A \cdot X \leq B$ in an ILP can
+itself be written as the ILP presented in Fig.~\ref{fig:redILP}.
 
 \begin{figure}[h]
-$$z = \max C \, X$$
+$$z = \max C \cdot X$$
 s.t.
 \[
-\begin{array}{rccc}
-  A & X &\leq & B \\
-  C & X &\leq & d + 1
+\begin{array}{rcc}
+  A \cdot X &\leq & B \\
+  C \cdot X &\leq & d + 1
 \end{array}
+%\begin{array}{rccc}
+%  A & X &\leq & B \\
+%  C & X &\leq & d + 1
+%\end{array}
 \]
@@
 \]
-\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
+\caption{Redundancy of $C \cdot X \leq d$ w.r.t. $A \cdot X \leq B$ as an ILP}
 \label{fig:redILP}
@@
 	context of periodic tasks is that the critical instants of asynchronous systems
-	are at most as constraining for the C-space as a synchronous instant. For this
-	reason, modifying task offsets when possible during
+	can be less constraining for the C-space than synchronous instants (if offsets are chosen to prevent synchronous releases). For this reason, modifying task offsets when possible during
 	the design of a real-time system is a useful trick to fit a heavy periodic task set
@@
 	In other words, fig.~\ref{fig:sizeRatio}
-	evaluates the feasibility gain of adding random offsets to a synchronous task
-	set. It is assumed that a more advanced strategy to assign these offsets (such
-	as the ones from \cite{goossens2003scheduling}) would yield a
-	greater difference.
+	evaluates the feasibility gain of adding random offsets w.r.t. a synchronous task
+	set.
+We have chosen in this paper to generate offsets randomly but we did not consider offsets that eventually lead to synchronous releases.
+The problem of offset assignment has been considered for example in \cite{grenier2008pushing}.
+The problem of those heuristics is that they depend on WCETs.
+Finding offsets that maximize a C-space region is still an open problem.
 
@@
 	these systems roughly range from 0.95 in the worst case (high utilization, high
-	CDF) to 0.85 in the best case (low utilization, low CDF). As calculating those
-	sizes is rather long, the number of systems used to obtain average
-	results was rather low (5000), which is the likely cause of the spikes in the
-	data. Note that the value of the CDF has a greater influence on this ratio than
-	the system's total utilization, but less so when the CDF is lower. It is also
+	CDF) to 0.85 in the best case (low utilization, low CDF). Each point on the graph is based on an average over 5000 tests.
+	Note that the value of the CDF has a greater influence on this ratio than
+	the system's total utilization, but less so when the CDF is higher. It is also
 	important to note that even though a 0.95 ratio may not seem much, the
@@
 
-Future works could also repeat the simulation of section~\ref{sct:expCspaceGain} with the algorithm described in \cite{grenier2008pushing}, which determine offset values with optimal feasibility. The
-feasibility gain could then be expressed using the C-space.
+Future works could also repeat the simulation of section~\ref{sct:expCspaceGain} with the algorithm described in \cite{grenier2008pushing}, which determine offset values with optimal feasibility but for specific WCETs.
+We would like to study if those heuristics obtained for particular WCETs scenarios can be also interesting for any WCET in the C-Space.
 

### 2013-09-25 dit-paper_ieee.tex

@@
 	these systems roughly range from 0.95 in the worst case (high utilization, high
-	CDF) to 0.85 in the best case (low utilization, low CDF). Each point on the graph is based on an average over 5000 tests.
+	CDF) to 0.85 in the best case (low utilization, low CDF). Each point on the graph is an average over 5000 tests.
 	Note that the value of the CDF has a greater influence on this ratio than
@@
 
-In this paper, we presented a general approach to define the C-space of a constrained periodic task set for EDF on uniform platform.
+In this paper, we presented a general approach to concisely define the C-space of a constrained periodic task set for EDF on uniform platforms.
+We then used the C-space to quantify the feasibility gain given by random offset values, with a final result of about 10~\% more WCET values being feasible.
 Possible future works includes an extension to the study of systems with preemption costs or running on multiprocessor platforms, as the value of the DIT does not depend on preemptions or the number of processors.
@@
 We would like to study if those heuristics obtained for particular WCETs scenarios can be also interesting for any WCET in the C-Space.
+
+% A mettre quelque part : nombre de contraintes avant/apres dans les expériences (issue #20)
+
+% Future works could also study the case of offset-free systems, where the offset values can be chosen.
+The performance of algorithms such as \cite{grenier2008pushing} and \cite{goossens2003scheduling} (although the latter depends on the execution times), which determine offset values with optimal feasibility, can be expressed using the C-space.
 

### 2013-09-26 dit-paper_ieee.tex
added "Paris"
merge

@@
 \IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
-\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles / ECE\\
+\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles / ECE Paris\\
 tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
@@
 	requires solving multiple similar instances of the Chinese Remainder Problem,
-	for which an efficient algorithm in this context is provided. We show that even for random offsets, the gain can reach 15%.
+	for which an efficient algorithm in this context is provided. We show that even for random offsets, the gain can reach 15\%.
 \end{abstract}
@@
 		clarity in the context of the CRP. One instance of this problem is guaranteed
-		to have at least one solution modulo $H$ for given values of $a_i$ if
+		to have at least one solution modulo $H$ for given values of $a_i$ if and only if
 		Condition~\ref{eq:CRPcond} is satisfied \cite{knuth1969art}:

### 2013-09-26 python-simulation/Simulator/Drawer/PILDrawer.py

@@ -1,3 +1,5 @@
+from Simulator.Drawer.Drawer import Drawer
+
 from Model import algorithms
 
 from PIL import Image as img
@@ -7,17 +9,16 @@ from PIL import ImageDraw as draw
 import random
 import re
 
-class Drawer(object):
+class PILDrawer(Drawer):
     def __init__(self, simu, stop):
-        self.simu = simu
+        super().__init__(simu, stop)
         self.instantWidth = 20
         self.widthMargin = 20
         self.taskHeight = 50
         self.heightMargin = 20
         self.width = stop * self.instantWidth + 2 * self.widthMargin
         self.height = len(simu.system.tasks) * self.taskHeight + 2 * self.heightMargin
-        self.colors = ["rgb(" + ",".join([str(random.randint(0, 255)) for i in range(3)]) + ")" for j in range(self.simu.m)] + ["black"]  # black: preemption
-        self.drawnDeadlineMissCount = 0
+        self.colors = ["rgb(" + ",".join([str(random.randint(0, 255)) for i in range(3)]) + ")" for j in range(self.simu.m)]
 
         self.outImg = img.new("RGB", (self.width, self.height), "white")
         self.fontRoboto = ImageFont.truetype("res/Roboto-Medium.ttf", 9)
@@ -67,6 +68,9 @@ class Drawer(object):
         self.outDraw.line([x, y1, x, y2], fill="black", width=5)
         self.drawnDeadlineMissCount += 1
 
+    def getDrawnDeadlineMissCount(self):
+        return self.drawnDeadlineMissCount
+
     def drawOneExecutionUnit(self, taskNbr, CPUnbr, t, preemp):
         color = self.colors[CPUnbr]
         if preemp:
@@ -95,6 +99,9 @@ class Drawer(object):
                 else:
                     self.drawOneExecutionUnit(taskNbr, cpuNbr, t, preemp=False)
 
+    def terminate(self):
+        self.drawArrivalsAndDeadlines()
+
     def drawArrivalsAndDeadlines(self):
         for taskNbr, task in enumerate(self.simu.system.tasks):
             for t in range(task.O, self.simu.stop + 1, task.T):
@@ -113,27 +120,11 @@ def greyColor(color):
     rgb = colorRe.findall(color)
     assert len(rgb) == 3
     rgb = [int(s) for s in rgb]
[…]

### 2013-09-26 python-simulation/Simulator/Scheduler/Scheduler.py

@@ -1,5 +1,3 @@
-from . import Simulator
-
 import itertools
 import pdb
 
@@ -33,7 +31,7 @@ class SchedulerDP(object):
 
 class PTEDF(SchedulerDP):
     def __init__(self, tau):
-        super(PTEDF, self).__init__(tau)
+        super().__init__(tau)
         self.tau = tau
         self.prioOffset = max([task.alpha for task in tau.tasks])
 
@@ -96,7 +94,7 @@ class ArbitraryScheduler(SchedulerDP):
     format of userSchedule : userSchedule[t] = task to execute
     if t > len(userSchedule), userSchedule is assumed periodic"""
     def __init__(self, tau, userSchedule):
-        super(ArbitraryScheduler, self).__init__(tau)
+        super().__init__(tau)
         self.tau = tau
         self.userSchedule = userSchedule
 
@@ -108,7 +106,7 @@ class ArbitraryScheduler(SchedulerDP):
 class SpotlightEDF(SchedulerDP):
     def __init__(self, tau):
         """ Non-optimal algorithm taking preemption cost into account."""
-        super(SpotlightEDF, self).__init__(tau)
+        super().__init__(tau)
         self.prioOffset = max([task.alpha for task in tau.tasks])
 
     def priority(self, job, simu):
@@ -129,13 +127,13 @@ class SchedulerFJP(SchedulerDP):
 
 class EDF(SchedulerFJP):
     def priority(self, job, simu=None):
-        super(SchedulerFJP, self).priority(job, simu)
+        super().priority(job, simu)
         return 1 / job.deadline
 
 
 class SchedulerFTP(SchedulerFJP):
     def __init__(self, tau):
-        super(SchedulerFTP, self).__init__(tau)
+        super().__init__(tau)
         self.priorities = self.orderPriorities(tau.tasks)
 
     def orderPriorities(self, taskArray):
@@ -143,7 +141,7 @@ class SchedulerFTP(SchedulerFJP):
         pass
 
     def priority(self, job, simu=None):
-        super(SchedulerFTP, self).priority(job, simu)
+        super().priority(job, simu)
         for i, task in enumerate(reversed(self.priorities)):  # priorities is decreasing
             if job.task is task:
                 return i + 1  # prio = 0 is for idle cpu
@@ -156,7 +154,7 @@ class FixedPriority(SchedulerFTP):
     def __init__(self, tau, prioArray):
         """prioArray : list of priorities in the same order as tau.tasks"""
         self.prioArray = prioArray
[…]

### 2013-09-26 python-simulation/Simulator/Simulator.py

@@ -3,8 +3,8 @@ import pdb
 
 from Model.CPU import CPU
 from Model import algorithms
-from . import Drawer
-from .JobConfiguration import JobConfiguration
+from Simulator.Drawer import Drawer
+from Simulator.JobConfiguration import JobConfiguration
 
 
 def heappeek(heap):
@@ -46,7 +46,8 @@ class Simulator(object):  # Global multiprocessing only
         heapify(self.activeJobsHeap)
 
         if drawing:
-            self.drawer = Drawer.Drawer(self, stop)
+            from Simulator.Drawer import PILDrawer
+            self.drawer = PILDrawer.PILDrawer(self, stop)
         else:
             self.drawer = Drawer.EmptyDrawer(self, stop)
 
@@ -232,7 +233,7 @@ class Simulator(object):  # Global multiprocessing only
             self.incrementTime()
             self.drawer.drawInstant(self.t)
 
-            if len(self.deadlineMisses) > self.drawer.drawnDeadlineMissCount:
+            if len(self.deadlineMisses) > self.drawer.getDrawnDeadlineMissCount():
                 # new deadline miss
                 assert len(self.deadlineMisses) > 0
                 missT, job = self.deadlineMisses[-1]
@@ -243,7 +244,7 @@ class Simulator(object):  # Global multiprocessing only
                     break
             if stopAtStableConfig and self.isStable:
                 break
-        self.drawer.drawArrivalsAndDeadlines()
+        self.drawer.terminate()
 
     def success(self):
         assert self.t >= 0, "Simulator.success: call run() first"

### 2013-09-26 python-simulation/mainSimulatorTest.py

@@ -1,4 +1,5 @@
-from Simulator import Simulator, Scheduler, ChooseKeepEDF, PALLF
+from Simulator import Simulator
+from Simulator.Scheduler import Scheduler, ChooseKeepEDF, PALLF
 from Model import algorithms
 import systems
 
@@ -46,7 +47,7 @@ class TestSimulator(unittest.TestCase):
         self.checkResult(tau, PALLF.PALLF(tau), True)
         self.checkResult(tau, Scheduler.PTEDF(tau), True)
 
-        sim = Simulator.Simulator(tau, stop=5, nbrCPUs=1, scheduler=Scheduler.EDF(tau), abortAndRestart=False)
+        sim = Simulator.Simulator(tau, stop=5, nbrCPUs=1, scheduler=Scheduler.EDF(tau), abortAndRestart=False, drawing=False)
         sim.run()
         self.assertEquals(sim.t, 6)
         blockedJob = sim.mostPrioritaryJob()

### 2013-09-26 dit-paper_ieee.tex
explained system modification for coprime n_i

@@
 		Algorithm~\ref{alg:algoCRP} (note that $x^{-1} \; (mod \; y)$ means the
-		modular inverse of $x$ in the naturals modulo $y$). In this paper we
-		concentrate on the latter part of the algorithm (after the modifications to
-		correct non-coprime periods, readers interested in the details of these
-		modifications should refer to \cite{knuth1969art}).
+		modular inverse of $x$ in the naturals modulo $y$). The congruences must
+		first be modified in order to obtain pairwise coprime moduli. Each $n_i$
+		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m = n_i$.
+		Each original constraint $t_d \equiv x_i \; (mod \; n_i)$ is replaced by the
+		equivalent set
+		\begin{equation*}
+			\begin{split}
+				t_d \equiv x_i 	& \; (mod \; p^{k_1}_1) \\
+				t_d \equiv x_i 	& \; (mod \; p^{k_2}_2) \\
+								& \vdots \\
+				t_d \equiv x_i 	& \; (mod \; p^{k_m}_m) \\
+			\end{split}
+		\end{equation*}
+		This operation might create duplicate constraints, which are removed. As shown
+		in \cite{knuth1969art}, the resulting system can be solved using
+		Algorithm~\ref{alg:algoCRP}.
+
 		\begin{algorithm}
@@
 			\begin{algorithmic}[1]
-				\REQUIRE $\forall \tau_i \in \tau : a_i \in [D_i,T_i]$
-				\REQUIRE $\forall \tau_i \in \tau : x_i = a_i+O_i$
-				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
 				\REQUIRE $H$ is the hyperperiod of the system
-
-				\STATE Modify the $n_i$ and $x_i$ by prime decomposition so \\ that the
-				$n_i$ become pairwise coprime
-
 				\FORALL{$\tau_i \in \tau$}
@@
 		\end{algorithm}
+
+		%TODO change algo 2 with respect to explanation of coprime n_i
+
 		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$

### 2013-09-26 dit-paper_ieee.tex
Shortened the article length (goal : strictly less than 7 pages) (Issue #18) Fixed #20 by adding a reference to the initial and final number of constraints in most cases

--- 2013-09-26 dit-paper_ieee.tex
@@
 
-	The \emph{C-space} of a real-time system is, intuitively,
+	The \mbox{C-space} of a real-time system is, intuitively,
 	the space of WCET values for which this system is feasible
@@
 
-		Furthermore, the following notations are used:
+		Furthermore, we define:
 		\begin{itemize}
@@
     The earliest DIT (if it exists) occurring in the system strictly after $t=0$ is called the
-    \textbf{first DIT} and is noted $t_d$.
+    \textbf{first DIT}, denoted $t_d$.
   \end{definition}
 
-		\begin{remark} (from the definitions, if a DIT exist then):
+		\begin{remark} (from previous definitions):
 			\begin{itemize}
-				\item Contrary to other idle times, a DIT is independent of the
+				\item Contrary to other idle times, DITs are independent of the
 					scheduling or the execution times of the jobs.
@@
 				\item In a feasible system, the first DIT happens after the end of the
-					first busy period.
+					first busy period if it exists.
 				\item In synchronous systems any $kH$ with $k \geqslant 0$ is a DIT and we
@@
 
-		The value of the first DIT can be found by solving the following modular
-		equations system:
-		\begin{equation}
-			\begin{split}
-				 t_d = \min(& \{ t \; s.t. \; t > 0 \; and \\
-						& \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]: t \equiv a_i \;
-						(mod \; T_i) \})
-			\end{split}
-		\end{equation}
-  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.
+		% The value of the first DIT can be found by solving the following modular
+		% equations system:
+		% \begin{equation}
+		% 	\begin{split}
+		% 		 t_d = \min(& \{ t \; s.t. \; t > 0 \; and \\
+		% 				& \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]: t \equiv a_i \;
+		% 				(mod \; T_i) \})
+		% 	\end{split}
+		% \end{equation}
+  The authors of \cite{george2009characterization} give a method to find the value of $t_d$ for cases in which periods are pairwise coprime.
 
@@
 	\begin{center}
-		\includegraphics[width=0.5\textwidth]{figs/nofpdit_4.png}
+		\includegraphics[width=0.4\textwidth]{figs/nofpdit_4.png}
 	\end{center}
@@
 
-Such a linear problem can be solved by e.g.
-the simplex algorithm and a branch-and-cut approach.
+Such a linear problem can be solved by a branch-and-bound approach \cite{nemhauser1988integer}.
 However, in our case the problem is not to test for redundancy of a particular constraint but to find all redundant constraints within a set.
-A naive method would be to test every constraint against all the others.
-We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.
+A naive algorithm would consist of testing every constraint against all others.
+We present Algorithm \ref{alg:prunRedun}, which has the same theoretical complexity but is more efficient when most of the constraints are redundant.
+Indeed, most of the system we generated had a final C-space description size of less than five constraints, even if the initial description often contained more than a thousand.
 
@@
 
-After doing this, no redundant constraints are left. However, this algorithm
-takes an exponential time in the number of constraints. An efficient initial
-description of $CSPACE$, as given by the methods described in previous
-sections, is therefore preferred.
+This algorithm
+has an exponential complexity in the number of constraints. The initial description
+of the C-space should thus be as concise as possible.
 
@@
 $[O_{max}, O_{max} + 2H]$ otherwise. This set of constraints is a
-correct description of the C-Space, but it is not efficient. Redundant
+correct but redundant description of the C-Space. Redundant
 constraints are removed through a linear integer approach.
@@
 
-Let us now consider the same system but with a synchronous pattern of arrival.
-
-    \begin{center}
-    \begin{tabular}{|r|c|c|c|c|}
-     \hline
-      & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
-     \hline
-     $\tau_1$ & 0 & $C_1$ & 7 & 15\\
-     \hline
-     $\tau_2$ & 0 & $C_2$ & 2 & 5\\
-     \hline
-    \end{tabular}
-    \end{center}
-
+Let us now consider the same system but with a synchronous pattern of arrival ($O_1 = O_2 = 0$).
 The first DIT happens at time $t_d = 7$.
@@
 \begin{center}
-  \includegraphics[width=0.5\textwidth]{figs/cspace_example.png}
+  \includegraphics[width=0.3\textwidth]{figs/cspace_example.png}
   \caption{C-space of an asynchronous system and its corresponding synchronous system}
@@
 
-    % PRECISER : on ne genere pas de systyemes avec instants synchroes
-
 	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
@@
 	set.
-We have chosen in this paper to generate offsets randomly but we did not consider offsets that eventually lead to synchronous releases.
-The problem of offset assignment has been considered for example in \cite{grenier2008pushing}.
-The problem of those heuristics is that they depend on WCETs.
-Finding offsets that maximize a C-space region is still an open problem.
+Offsets eventually leading to synchronous releases have been discarded.
+The problem of offset assignment has been considered for example in \cite{grenier2008pushing} in the case of fixed WCET values.
+To the best of our knowledge, finding offsets maximizing a C-space region is an open problem.
 
@@
 		\begin{center}
-			\includegraphics[width=0.5\textwidth]{figs/sizeratio.png}
+			\includegraphics[width=0.4\textwidth]{figs/sizeratio.png}
 			\caption{C-space size ratio between asynchronous and equivalent synchronous
@@
 	designer of the system. Using the asynchronous C-space instead will relax some
-	constraints and therefore add new acceptable solutions that will dominate solutions that were previously non-dominated,
+	constraints and therefore add new acceptable and dominating solutions,
 	increasing the quality of the C-space border.
@@
 
-Future works could also repeat the simulation of section~\ref{sct:expCspaceGain} with the algorithm described in \cite{grenier2008pushing}, which determine offset values with optimal feasibility but for specific WCETs.
-We would like to study if those heuristics obtained for particular WCETs scenarios can be also interesting for any WCET in the C-Space.
-
-% A mettre quelque part : nombre de contraintes avant/apres dans les expériences (issue #20)
+Future works could also repeat the simulation of section~\ref{sct:expCspaceGain} with the algorithm described in \cite{grenier2008pushing}, which determine offset values with optimal feasibility for given WCET values.
+We could like to study if those heuristics obtained for particular WCETs scenarios can also be interesting for any WCET in the \mbox{C-Space}.
 

### 2013-09-27 dit-paper_ieee.tex

@@
 		necessary to solve the problem on all combinations of $a_i$ values and then
-		to compute the minimum solution. We define $x_i = a_i+O_i$ and $n_i = T_i$ for
-		clarity in the context of the CRP. One instance of this problem is guaranteed
-		to have at least one solution modulo $H$ for given values of $a_i$ if and only if
+		to compute the minimum solution. We define $A_i = [D_i,T_i]$, $X_i = \{x_i
+		= a_i+O_i \mid a_i \in A_i\}$ and $n_i = T_i$ for clarity in the context of
+		the CRP.
+		One instance of this problem is guaranteed to have at least one solution modulo $H$ for given values of $a_i$ if and only if
 		Condition~\ref{eq:CRPcond} is satisfied \cite{knuth1969art}:
@@
 		first be modified in order to obtain pairwise coprime moduli. Each $n_i$
-		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m = n_i$.
-		Each original constraint $t_d \equiv x_i \; (mod \; n_i)$ is replaced by the
-		equivalent set
+		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m = n_i$
+		with $k_j$ the highest integer s.t. $p^{k_j}_j$ divides $n_i \; \forall j
+		\; \mid 1 \leqslant j \leqslant m$. Each original constraint $t_d \equiv x_i
+		\; (mod \; n_i)$ is replaced by the equivalent set
 		\begin{equation*}
@@
 		\end{equation*}
-		This operation might create duplicate constraints, which are removed. As shown
-		in \cite{knuth1969art}, the resulting system can be solved using
-		Algorithm~\ref{alg:algoCRP}.
+		This operation (later called constraint \emph{factorisation}) might create
+		duplicate constraints, which are removed.
+		As shown in \cite{knuth1969art}, the resulting system can be solved using
+		Algorithm~\ref{alg:algoCRP}. For ease of reading, we call $C$ the set of
+		resulting constraints $c$ each written $t_d \equiv x_c \; (mod \;
+		p_c)$.
 
@@
 				\REQUIRE $H$ is the hyperperiod of the system
-				\FORALL{$\tau_i \in \tau$}
-					\STATE $Mj \leftarrow \frac{H}{n_i}$
-					\STATE $invMj \leftarrow Mj^{-1} \; (mod \; n_i)$
-					\STATE $e_i \leftarrow Mj \cdot invMj$
+				\FORALL{$c \in C$}
+					\STATE $Mc \leftarrow \frac{H}{p_c}$
+					\STATE $invMc \leftarrow Mc^{-1} \; (mod \; p_c)$
+					\STATE $e_c \leftarrow Mc \cdot invMc$
 				\ENDFOR
-				\RETURN $\sum\limits_{\tau_i \in \tau}{x_i \cdot e_i} \; (mod \; H)$
+				\RETURN $\sum\limits_{c \in C}{x_c \cdot e_c} \; (mod \; H)$
 			\end{algorithmic}
@@
 		exponentially many different combinations of $a_i$ values in the number of
-		tasks, and resolving exponentially many CRP instances is prohibitively slow.
+		tasks (the cartesian product of all the $A_i$ sets), and resolving
+		exponentially many CRP instances is prohibitively slow.
 		A faster method for finding the FPDIT consists in merging all these CRP
@@
 		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
-		results are shared between instances.
-
-		%Review 3 : add formal complexity assessment of this algorithm
+		results are shared between instances. The first part consisting in splitting
+		all constraints into sets of constraints with prime power moduli is slightly
+		different. We define for each task $\tau_i$ and $a_j \in A_i$ :
+		$C_{ij}$ is the set of constraints resulting from the factorisation of $t_d
+		\equiv a_j+O_i \; (mod \; n_i)$ of the form $t_d \equiv x_c
+		\; (mod \; p_c)$ if named $c$. We define $C = \cup\limits_{\tau_i \in \tau,
+		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in
+		constraints of $C$ and $C_{p}$ the subset of $C$ containing all constraints
+		$c$ with $p_c = p$.
 
@@
 			\begin{algorithmic}[1]
-				\REQUIRE $\forall \tau_i \in \tau: X_i$ is the set of possible $a_i+O_i
-				\; \forall a_i \in [D_i,T_i]$ values for $\tau_i$
-				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
 				\REQUIRE $H$ is the hyperperiod of the system
 
-				\STATE Modify $n_i$ and the content of $X_i$ by prime
-				\\ decomposition to get pairwise coprime $n_i$ values
-
-				\STATE $sumchunks \leftarrow \text{empty list}$
-				\FORALL{$\tau_i \in \tau$}
+				\STATE $sumchunks \leftarrow \text{empty map}$
+				\FORALL{$p \in P$}
 					\STATE $taskTerms \leftarrow \text{empty list}$
-					\STATE $Mj \leftarrow \frac{H}{n_i}$
-					\STATE $invMj \leftarrow Mj^{-1} (mod \; n_i)$
-					\FORALL{$x_i \in X_i$}
-						\STATE append $(x_i \cdot Mj \cdot invMj)$ to $taskTerms$
+					\STATE $Mp \leftarrow \frac{H}{p}$
+					\STATE $invMp \leftarrow Mp^{-1} (mod \; p)$
+					\FORALL{$c \in C_p$}
+						\STATE append $(x_c \cdot Mp \cdot invMp)$ to $taskTerms$
 					\ENDFOR
-					\STATE $sumchunks[i] \leftarrow taskTerms$
+					\STATE $sumchunks[p] \leftarrow taskTerms$
 				\ENDFOR
@@
 				\STATE append $0$ to $results$
-				\FORALL{$\tau_i \in \tau$}
+				\FORALL{$p \in P$}
 					\STATE $newresults \leftarrow \text{empty list}$
-					\FORALL{$chunk \in sumchunks[i]$}
+					\FORALL{$chunk \in sumchunks[p]$}
 						\FORALL{$r \in results$}
@@
 
+		This method ``forgets'' the link between generated constraints and the tasks
+		(with the associated $A_i$) they come from. Constraints are instead grouped by their
+		primal power modulo $p$ and each $p$ is associated with a set of $x_c$ values
+		for $c$ in $C_p$, acting similarly as the $A_i$ set of each task. Due to this
+		simplification, Algorithm~\ref{alg:multiACRP} might output ``false''
+		solutions. This isn't a major drawback as checking whether a solution is
+		correct can be done in linear time in the number of tasks (for each task
+		$\tau_i$, check whether at least one $a \in A_i$ satisfies $t_d \equiv a \;
+		(mod \; T_i)$) and the only interesting result is the minimum $t_d$ which
+		means that using a minimum heap structure containing the results we only need
+		to check solutions for correctness until the first (hence minimum) correct
+		solution is found.
+
 		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
-		computation of one modular inversion per $a_i$ value, which is done in a
-		linear number of modular inversions per task. However, to
+		computation of one modular inversion per constraint and per $a_i$ value, which
+		is done in a linear number of modular inversions per task. However, to
 		find all DITs Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
@@
 		running time of Algorithm~\ref{alg:multiACRP} is also less sensitive to the
-		number of different $a_i$ values per task, which means that this method
+		size of the $A_i$ sets per task, which means that this method
 		remains practical when tasks deadlines are much smaller than periods.

### 2013-09-27 dit-paper_ieee.tex
hotfix

@@
 		\equiv a_j+O_i \; (mod \; n_i)$ of the form $t_d \equiv x_c
-		\; (mod \; p_c)$ if named $c$. We define $C = \cup\limits_{\tau_i \in \tau,
+		\; (mod \; p_c)$ if named $c$. We define $C = \bigcup\limits_{\tau_i \in \tau,
 		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in

### 2013-09-27 beamer/dit-paper-presentation.tex

@@
 Systems using Definitive Idle Times}
-\author{Thomas Chapeaux \inst{1} \and Paul Rodriguez \inst{1} \and Laurent George \inst{2} \and Joël Goossens \inst{1}}
+\author{Thomas~Chapeaux~\inst{1}~\inst{2} \and Paul~Rodriguez~\inst{1}~\inst{2} \and Laurent~George~\inst{2} \and Joël~Goossens~\inst{1}}
 \institute[shortinst]{\inst{1} Université Libre de Bruxelles \and %
@@
 	\begin{frame}{Model}
-		Tasks, jobs, OCDT
+  \begin{block}{Definition}
+  Systems with real-time constraints. (e.g. ABS, VOD, etc)
+  \end{block}
+  \textbf{Model:} Set of tasks $\tau_i = (O_i, T_i, D_i, C_i)$ generating jobs $J_{i,j}$, with
+      \begin{itemize}
+      \item $O_i$ : arrival of the first job
+      \item $T_i$ : time between two jobs
+      \item $D_i$ : relative deadline
+      \item $C_i$ : execution time
+    \end{itemize}
+
+  \begin{columns}[c] % the "c" option specifies center vertical alignment
+  \column{.4\textwidth}
+\begin{center}
+\begin{tabular}{|r|c|c|c|c|}
+ \hline
+  & $O_i$ & $T_i$ & $D_i$ & $C_i$ \\
+ \hline
+ $\tau_1$ & 1 & 2 & 6 & 10\\
+ \hline
+ $\tau_2$ & 0 & 3 & 5 & 5\\
+ \hline
+\end{tabular}
+\end{center}
+
+  \column{.6\textwidth} % column designated by a command
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{figs/RTsystem_example.png}
+\caption{A task system}
+\label{fig:llf}
+\end{figure}
+  \end{columns}
 \end{frame}
@@
 
-	\begin{frame}{Related Works}
-	This one and this one
+    \subsubsection{The C-space}
+
+    \begin{frame}{Definition of the C-space}
+        \begin{block}{Definition}
+            The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
+        \end{block}
+
+        A region of $\mathbb{N}_0^n$ such as the C-space can be described by a list of parametric linear constraints (called the \emph{formulation}), such as those given by the DBF test.
+    \end{frame}
+
+    \begin{frame}{Removing Redundancies in the C-space of synchronous system}
+
     \end{frame}
@@
 	\begin{frame}{Definition of the FPDIT}
-		Even without knowing the WCETs in advance, we can define the following notions:
+		We define the following notions, which do not depend on the WCET values:
 		\begin{block}{Definition}
@@
 
-\section{C-space}
-
-	\subsection{Definition}
-
-	\begin{frame}{Definition of the C-space}
-		\begin{block}{Definition}
-			The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
-		\end{block}
-
-		A region of $\mathbb{N}_0^n$ such as the C-space can be described by a list of parametric linear constraints (called the \emph{formulation}).
-	\end{frame}
-
-	\subsection{Redundancies}
-
-		\subsubsection{General approach}
-
-		\begin{frame}{Redundancies}
-			Infinite number of constraints...
-
-			However: arrival and deadlines, feasibility interval, ILP
-
-			The sequel will concentrate on obtaining a short feasibility interval
-		\end{frame}
-
-		\subsubsection{Synchronous systems}
-
-		\begin{frame}{Redundancy in synchronous systems}
-			[0, t] is a critical instant, 0 is the worst-case
-		\end{frame}
-
-		\subsubsection{Asynchronous systems}
+\section{C-space of asynchronous system}
 
@@
 
-	\subsection{Numerical Example}
+\section{Numerical Example}
 

### 2013-09-27 dit-paper_ieee.tex
knuth ref + clearer contribution
Added require to Algo Modified Gauss Algorithm
hotfix

@@
 		\; \mid 1 \leqslant j \leqslant m$. Each original constraint $t_d \equiv x_i
-		\; (mod \; n_i)$ is replaced by the equivalent set
+		\; (mod \; n_i)$ is replaced by the equivalent set \cite{knuth1969art}
 		\begin{equation*}
@@
 
-		%TODO change algo 2 with respect to explanation of coprime n_i
-
 		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
@@
 		exponentially many CRP instances is prohibitively slow.
-		A faster method for finding the FPDIT consists in merging all these CRP
-		instances into one problem (finding all DITs), which can be solved faster by
+		In this paper a faster method for finding the FPDIT is proposed. It consists
+		in merging all these CRP instances into one problem (finding all DITs), which can be solved faster by
 		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
@@
 		different. We define for each task $\tau_i$ and $a_j \in A_i$ :
-		$C_{ij}$ is the set of constraints resulting from the factorisation of $t_d
-		\equiv a_j+O_i \; (mod \; n_i)$ of the form $t_d \equiv x_c
-		\; (mod \; p_c)$ if named $c$. We define $C = \bigcup\limits_{\tau_i \in \tau,
+		$D_{ij}$ the set of constraints $c$ of the form $t_d \equiv x_c
+		\; (mod \; p_c)$ resulting from the factorisation of $t_d
+		\equiv a_j+O_i \; (mod \; n_i)$. We define $C = \bigcup\limits_{\tau_i \in \tau,
 		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in

### 2013-09-29 dit-paper_ieee.tex
multi A crp description rewrite

@@
 		first be modified in order to obtain pairwise coprime moduli. Each $n_i$
-		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m = n_i$
+		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m$
 		with $k_j$ the highest integer s.t. $p^{k_j}_j$ divides $n_i \; \forall j
@@
 		\end{equation*}
-		This operation (later called constraint \emph{factorisation}) might create
+		This operation might create
 		duplicate constraints, which are removed.
@@
 		Algorithm~\ref{alg:algoCRP}. For ease of reading, we call $C$ the set of
-		resulting constraints $c$ each written $t_d \equiv x_c \; (mod \;
-		p_c)$.
+		resulting constraints. We define two functions on the set of
+		constraints. Assuming contraint $c$ of the form $t_d \equiv x \; (mod \; p)$,
+		we have $p(c) = p$ and $x(c) = x$
 
@@
 				\FORALL{$c \in C$}
-					\STATE $Mc \leftarrow \frac{H}{p_c}$
-					\STATE $invMc \leftarrow Mc^{-1} \; (mod \; p_c)$
+					\STATE $Mc \leftarrow \frac{H}{p(c)}$
+					\STATE $invMc \leftarrow Mc^{-1} \; (mod \; p(c))$
 					\STATE $e_c \leftarrow Mc \cdot invMc$
 				\ENDFOR
-				\RETURN $\sum\limits_{c \in C}{x_c \cdot e_c} \; (mod \; H)$
+				\RETURN $\sum\limits_{c \in C}{x(c) \cdot e_c} \; (mod \; H)$
 			\end{algorithmic}
@@
 		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
-		results are shared between instances. The first part consisting in splitting
-		all constraints into sets of constraints with prime power moduli is slightly
-		different. We define for each task $\tau_i$ and $a_j \in A_i$ :
-		$D_{ij}$ the set of constraints $c$ of the form $t_d \equiv x_c
-		\; (mod \; p_c)$ resulting from the factorisation of $t_d
-		\equiv a_j+O_i \; (mod \; n_i)$. We define $C = \bigcup\limits_{\tau_i \in \tau,
-		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in
-		constraints of $C$ and $C_{p}$ the subset of $C$ containing all constraints
-		$c$ with $p_c = p$.
-
+		results are shared between instances. First, the same $C$ set is obtained,
+		but instead of one $x_i$ value per task, all variants in $X_i$ spawn a set of
+		constraints. All the duplicate and useless constraints are removed. Then we
+		define $P$ the set of all powers of prime numbers appearing as moduli in the
+		congruences (the $p_j^{k_j}$ values). For all $p \in P$, we define $C_p$ the set of
+		constraints where $p$ is the modulo.
 		\begin{algorithm}
@@
 			\begin{algorithmic}[1]
+                \REQUIRE $P$, $C_{p}$, $x(c)$: as defined above
 				\REQUIRE $H$ is the hyperperiod of the system
 
-				\STATE $sumchunks \leftarrow \text{empty map}$
+				\STATE $sumchunks \leftarrow \text{empty mapping}$
 				\FORALL{$p \in P$}
@@
 					\FORALL{$c \in C_p$}
-						\STATE append $(x_c \cdot Mp \cdot invMp)$ to $taskTerms$
+						\STATE append $(x(c) \cdot Mp \cdot invMp)$ to $taskTerms$
 					\ENDFOR
@@
 		\end{algorithm}
-
-		This method ``forgets'' the link between generated constraints and the tasks
-		(with the associated $A_i$) they come from. Constraints are instead grouped by their
-		primal power modulo $p$ and each $p$ is associated with a set of $x_c$ values
-		for $c$ in $C_p$, acting similarly as the $A_i$ set of each task. Due to this
-		simplification, Algorithm~\ref{alg:multiACRP} might output ``false''
-		solutions. This isn't a major drawback as checking whether a solution is
-		correct can be done in linear time in the number of tasks (for each task
-		$\tau_i$, check whether at least one $a \in A_i$ satisfies $t_d \equiv a \;
-		(mod \; T_i)$) and the only interesting result is the minimum $t_d$ which
-		means that using a minimum heap structure containing the results we only need
-		to check solutions for correctness until the first (hence minimum) correct
-		solution is found.
-
-		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
-		computation of one modular inversion per constraint and per $a_i$ value, which
+		In the first loop over $P$ of Algorithm~\ref{alg:multiACRP}, all the
+		required intermediate values are computed. In the second loop, those
+		intermediate values are added in every possible way. Both
+		Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
+		computation of one modular inversion per constraint, which
 		is done in a linear number of modular inversions per task. However, to
@@
 		computation of all DITs still requires an exponential number of answers in the
-		number of tasks, but it is nonetheless significantly faster in practice. The
-		running time of Algorithm~\ref{alg:multiACRP} is also less sensitive to the
-		size of the $A_i$ sets per task, which means that this method
-		remains practical when tasks deadlines are much smaller than periods.
+		number of tasks, but it is nonetheless significantly faster in practice. One
+		drawback of Algorithm~\ref{alg:multiACRP} is that the replacement of each
+		constraint by sets of constraints with powers of primes as moduli is not
+		equivalent. Algorithm~\ref{alg:multiACRP} might ouput values that are not
+		DITs. However, as we only need the FPDIT, it remains practical to check those
+		solutions one by one from the lowest to the highest, and stop as soon as the
+		first correct result is found.
 

### 2013-09-30 dit-paper_ieee.tex
Less than 6 pages. You are now closed #18

@@
 \IEEEauthorblockA{Universit\'{e} Libre de Bruxelles / ECE Paris\\
+ Avenue Franklin Roosevelt 50\\
+ 1050 Brussels, Belgium\\
 tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
@@
 \IEEEauthorblockA{University of Paris-Est / ECE Paris\\
+Quai de Grenelle, 37\\
+75015 Paris\\
 lgeorge@ieee.org}
@@
 \IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
+ Avenue Franklin Roosevelt 50\\
+ 1050 Brussels, Belgium\\
 joel.goossens@ulb.ac.be}
@@
   Even then, the number of constraints to consider is exponential in the number
-  of tasks. While it has been shown that constraints that cover intervals ending
+  of tasks. While it has been shown \cite{baruah1990algorithms} that constraints that cover intervals ending
   after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
@@
   For synchronous systems in which the execution times are not known, the first DIT $t_d$
-  is our ``best guess'' at an upper limit on the end of the busy period. As it was sufficient
-  to check the DBF test in intervals $[0, t]$ before the end of the first busy period. This time interval is WCETs dependant. A more general feasility condition valid for any WCET is as follows:
+  is an upper limit on the end of the busy period regardless of the WCET values. As it was sufficient
+  to check the DBF test in intervals $[0, t]$ before the end of the first busy period, a condition valid for any WCET is as follows:
   \begin{equation}
@@
 		\; \mid 1 \leqslant j \leqslant m$. Each original constraint $t_d \equiv x_i
-		\; (mod \; n_i)$ is replaced by the equivalent set \cite{knuth1969art}
+		\; (mod \; n_i)$ is replaced by the following equivalent set of constraints \cite{knuth1969art}:
 		\begin{equation*}
@@
 		This operation might create
-		duplicate constraints, which are removed.
-		As shown in \cite{knuth1969art}, the resulting system can be solved using
-		Algorithm~\ref{alg:algoCRP}. For ease of reading, we call $C$ the set of
+		duplicate constraints, which are removed. We call $C$ the set of
 		resulting constraints. We define two functions on the set of
-		constraints. Assuming contraint $c$ of the form $t_d \equiv x \; (mod \; p)$,
-		we have $p(c) = p$ and $x(c) = x$
+		constraints, assuming contraint $c$ of the form $t_d \equiv x \; (mod \; p)$
+		we have $p(c) = p$ and $x(c) = x$. As shown in \cite{knuth1969art}, the resulting system can be solved
+        using Algorithm~\ref{alg:algoCRP}.
 
@@
 		exponentially many CRP instances is prohibitively slow.
-		In this paper a faster method for finding the FPDIT is proposed. It consists
+
+		We propose a faster method for finding the FPDIT which consists
 		in merging all these CRP instances into one problem (finding all DITs), which can be solved faster by
@@
 		but instead of one $x_i$ value per task, all variants in $X_i$ spawn a set of
-		constraints. All the duplicate and useless constraints are removed. Then we
+		constraints. All duplicate and useless constraints are removed. We then
 		define $P$ the set of all powers of prime numbers appearing as moduli in the
@@
 		constraints where $p$ is the modulo.
+
 		\begin{algorithm}
@@
 		computation of all DITs still requires an exponential number of answers in the
-		number of tasks, but it is nonetheless significantly faster in practice. One
-		drawback of Algorithm~\ref{alg:multiACRP} is that the replacement of each
+		number of tasks, but it is nonetheless significantly faster in practice.
+
+        One drawback of Algorithm~\ref{alg:multiACRP} is that the replacement of each
 		constraint by sets of constraints with powers of primes as moduli is not
-		equivalent. Algorithm~\ref{alg:multiACRP} might ouput values that are not
+		equivalent. Algorithm~\ref{alg:multiACRP} might output values that are not
 		DITs. However, as we only need the FPDIT, it remains practical to check those
@@
 		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
-		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}.
+		\item Choosing the $D_i$ uniformly in the interval \mbox{$[T_i - CDF \cdot (T_i - C_i), T_i]$}, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}.
 It allows us to generate systems where the deadlines are closer to the period.
@@
 
-	The number of tasks and the constrained Deadline Factor is shown to have a direct influence on the density of FPDIT.
+	The number of tasks and the Constrained Deadline Factor is shown to have a direct influence on the density of FPDIT.
 Indeed, Fig~\ref{fig:noFPDIT} show the percentage of systems having no FPDIT for different values of CDF.
@@
 
-			As shown in Fig. \ref{fig:asyncBehavior}, the system begins in the
+			The system begins in the
 			\emph{incomplete period}, where all tasks are not in the system. Then, after
-			$O_{max}$ time units, every tasks is in the system and the \emph{transient
+			$O_{max}$ time units, every task has arrived in the system and the \emph{transient
 			period} begins. Then, after $O_{max} + H$ time units, the system is faced
@@
 			$O_{max} + H$ every task is in the system and in $O_{max}$ some were missing,
-			the state of the system will be different. The \emph{stationary period} then
+			the state of the system may differ. The \emph{stationary period} then
 			begins. At instant $O_{max} + 2H$ it is guaranteed that the system is in the
@@
 
-			\begin{figure}[h]
-				\[
-					\begin{array}{r||c|c|c|l}
-									& \text{Incomplete} & \text{Transient}	& \text{Stationary} & \cdots \\
-						\text{Name} & \text{period} 	& \text{period} 	& \text{period}  	& \\ \hline
-						\text{size} & O_{max} 			& H 				& H 				& \cdots \\ \hline
-						t \geqslant & 0 				& O_{max} 			& O_{max} + H 		& \cdots
-					\end{array}
-				\]
-				\begin{center}
-				\caption{Behavior of an asynchronous system under EDF.}
-				\label{fig:asyncBehavior}
-				\end{center}
-			\end{figure}
-
-			For this reason, as shown by \cite{leung1982complexity}, it is sufficient (but pessimistic) to
-			check for
+			% For this reason, as shown by \cite{leung1982complexity}, it is sufficient (but pessimistic) to
+			As shown in \cite{leung1982complexity}, it is sufficient to
+            apply the demand-bound function test in
 			intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length
 			in the number of tasks. A better interval is given in \cite{choquet2004minimal} using the
-			notion of cyclic idle times (denoted $t_c$), which are dependent of the execution
-			time and therefore cannot be used directly to characterize the C-Space. Their interval is $[0, t_c + H]$ and is valid for
-			every cyclic idle time $t_c$.
+			notion of cyclic idle times (denoted $t_c$), which are idle times occurring at fixed intervals of
+            length $H$ and whose value depends of the tasks execution
+			time, therefore they cannot be used directly to characterize the C-Space. Their interval is
+            $[0, t_c + H]$ and is valid for every cyclic idle time $t_c$.
 
-			In the following section, we extend the latter interval using the previously defined notion
-			of periodic DIT, a particular case of cyclic idle times which does not depend on the execution
+			In the following section, we show how the latter interval can be used with the previously defined
+            notion of periodic DIT, a particular case of cyclic idle times which does not depend on the execution
 			times.
@@
 
-The FPDIT, if it exists, must occur in the transient period.
-Indeed, it cannot occur in the incomplete period by definition ($t_d > O_{max}$) and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transient period at instant $t_d - k H$ (a contradiction).
+The FPDIT, if it exists, must occur after in the transient period.
+Indeed, $t_d > O_{max}$ by definition, and if it occurred in the $k^{th}$ stationary period, another DIT should have occurred in the transient period at instant $t_d - k H$ (a contradiction).
 
-As the FPDIT happens when all tasks are in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$) (A rigorous proof is given in \cite{choquet2004minimal} for any cyclic idle time).
+Despite $t_d$ being in the theoretical transient period, the system will be in the same state at instant $t_d + H$ (A rigorous proof is given in \cite{choquet2004minimal} for any cyclic idle time).
 We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$ if the FPDIT exists.
-This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.
+This will always be a smaller interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.
 
@@
 The study interval using the FPDIT is thus $[15, 30]$, which contains 11 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $15 \leqslant a < d \leqslant 30$.
-Those intervals are
-$[15, 17]$, $[15, 22]$, $[15, 27]$, $[15, 30]$, $[20, 22]$, $[20, 27]$, $[20, 30]$, $[23, 27]$, $[23, 30]$, $[25, 27]$ and $[25, 30]$.
 For comparison, the original study interval of $[O_{max}, O_{max} + 2H]$ is $[8, 38]$ which yields 57 intervals.
@@
 	\end{equation}
-The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.
 
@@
 $$
-This time, the C-space only contains 8 points: $(1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$.
 
-Fig.
-\ref{fig:cspaceComp} shows the two C-spaces in the plane.
-The dark gray region is the C-space of the synchronous system and the light gray region is the surface gain given by the asynchronous system.
+We see that the offsets allow three more points to be in the C-space ($(C_1, C_2) = (4, 2), (5, 2), (6, 1)$).
 
-\begin{figure}[h]
-\begin{center}
-  \includegraphics[width=0.3\textwidth]{figs/cspace_example.png}
-  \caption{C-space of an asynchronous system and its corresponding synchronous system}
-  \label{fig:cspaceComp}
-\end{center}
-\end{figure}
+% \begin{figure}[h]
+% \begin{center}
+%   \includegraphics[width=0.3\textwidth]{figs/cspace_example.png}
+%   \caption{C-space of an asynchronous system and its corresponding synchronous system}
+%   \label{fig:cspaceComp}
+% \end{center}
+% \end{figure}
 

### 2013-10-02 beamer/dit-paper-presentation.tex
I hadn't done a COMMIT in some time so here it is

@@
 
+\begin{frame}
+    \tableofcontents[currentsection]
+\end{frame}
+
 	\subsection{Real-time systems}
@@
       \item $O_i$ : arrival of the first job
-      \item $T_i$ : time between two jobs
+      \item $T_i$ : time between two job arrivals
       \item $D_i$ : relative deadline
@@
 
+    \subsection{Feasibility}
+
 	\begin{frame}{Feasibility}
-		We define feasibility...
+		\begin{block}{Feasibility}
+        A task set is said to be \textbf{feasible} if there exists a schedule such that every job in the task set completes before its deadline is reached.
+        \end{block}
+
+        \begin{block}{Feasibility}
+        A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
+        \end{block}
+
+        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is EDF-schedulable.
 	\end{frame}
 
-	\begin{frame}{DBF test}
-		\begin{block}{Definition}
-			The \textbf{demand-bound function (DBF)}
-			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
-			equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
-			closed interval $[t_1, t_2]$.
-		\end{block}
-
-		Mathematically,
-		\[
-			\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
-		\]
-		where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
-		and deadlines are both in the closed interval $[t_1, t_2]$.
-
-		The values of the $n_i$ are given by \cite{baruah1999generalized}
-
-		CNS of feasibility: $\dbf{t1, t2} \leqslant t2 - t1$
-	\end{frame}
-
-	\subsection{Related works}
-
-    \subsubsection{The C-space}
+    \subsection{C-space}
 
@@
 
-        A region of $\mathbb{N}_0^n$ such as the C-space can be described by a list of parametric linear constraints (called the \emph{formulation}), such as those given by the DBF test.
+        \begin{itemize}
+            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints
+            \item An efficient description allows us to quickly  whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
+        \end{itemize}
+
     \end{frame}
 
-    \begin{frame}{Removing Redundancies in the C-space of synchronous system}
+	\section{Related works}
+
+\begin{frame}
+    \tableofcontents[currentsection]
+\end{frame}
+
+    \subsection{Demand-bound function}
+
+    \begin{frame}{Demand-bound function feasibility test}
+        \begin{block}{Definition}
+            The \textbf{demand-bound function (DBF)}
+            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
+            the maximal cumulated execution time of jobs of $\tau$ contained in the
+            closed interval $[t_1, t_2]$.
+        \end{block}
+        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
+        where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
+        and deadlines are both in the closed interval $[t_1, t_2]$.
+
+        ~\\
+
+        The following has been shown to be a necessary and sufficient condition of feasibility (called DBF test in the following): $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$
+
+    \end{frame}
+
+    \subsection{C-space of synchronous systems}
+
+    \begin{frame}{Description using the DBF test}
+    The DBF test gives us a set of constraints
+    $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$
+
+    \begin{itemize}
+        \item Every constraint is linear in the $C_i$ values
+        \item Every constraint is necessary
+        \item Their conjunction is sufficient
+        \pause
+        \item But we have an infinite number of constraints!
+        \item $\Rightarrow$ Removing redundancy
+    \end{itemize}
+    \end{frame}
+
+    \begin{frame}{Removing redundancy for synchronous system}
+
+    The authors of \cite{george2009characterization} obtain an efficient description of the C-space by
+    \begin{itemize}
+        \item Removing constraints in which $t_1 > 0$
+        \item Removing constraints in which $t_2$ is not a deadline or $t_2 > H$ (where $H = LCM(T_i)$)
+    \end{itemize}
+
+    ~\\
+    \pause
+
+    They also define the notion of \textbf{definitive idle times (DIT)} and show that the first one happens at a time $0 < t_d \leqslant H$.
+Finally they show that all constraints where $t_2 > t_d$ are also redundant.
+
+    ~\\
+    \pause
+
+    The remaining constraints are thus the DBF test on intervals $[0, t]$, where $t$ is a deadline and $0 < t \leqslant t_d$.
+The remaining redundancies are removed by an algorithm based on the simplex.
 
@@
 
-	Extension of the previous results
+	In this paper, we
+    \begin{itemize}
+        \item Introduce the notion of \textbf{first periodic DIT (FPDIT)} as a generalization of the notion of DIT
+        \item Provide an algorithm to find an efficient description of the C-space for any periodic system
+        \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
+    \end{itemize}
 
@@
 	\begin{frame}{Definition of the FPDIT}
-		We define the following notions, which do not depend on the WCET values:
-		\begin{block}{Definition}
-			A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
-			released strictly before instant $t$ has its absolute deadline before or at instant $t$.
-		\end{block}
 		\begin{block}{Definition}
@@
 
-	\end{frame}
-
-	\subsection{Existence and value}
-
-	\begin{frame}{Existence and value}
-		The FPDIT is a time $t_d$ for which
-		\[
+        The FPDIT is the smallest $t_d$ such as:
+       \begin{equation}
             \begin{array}{l}
-				\forall i \; :\\
+                \forall \tau_i \in \tau, \exists a_i \in [D_i,T_i] \; :\\
                 \left\{
@@
                         t_d > O_i \\
-						t_d - O_i \equiv a_i \; (mod \; T_i) \\
-						a_i \in [D_i, T_i]
+                        t_d - O_i \equiv a_i \; (mod \; T_i)
+                        \\
                     \end{array}
@@
             \end{array}
-		\]
+            \label{eq:FPDIT}
+        \end{equation}
 
-		This system is guaranteed to have at least one solution modulo $H$ for given
-		values of $a_i$ if the following condition is respected:
+        For given values of $a_i$, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ if the following condition is respected:
         \[
@@
 
-		Note that in the synchronous case $t_d = H$ is always a solution ($a_i = T_i$)
+	\end{frame}
+
+	\subsection{Finding the FPDIT value}
+
+	\begin{frame}{Existence and value}
+
 	\end{frame}
@@
 
+\bibliographystyle{IEEEtran}
+\bibliography{dit-paper}
+
 \end{document}

### 2013-10-02 dit-paper_ieee.tex
I hadn't done a COMMIT in some time so here it is

@@
 		\end{equation}
-		where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ which arrival times
+		where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
 		and deadlines are both in the closed interval $[t_1, t_2]$.

### 2013-10-02 beamer/dit-paper-presentation.tex
more beamer tentative change of nofpdit graph definition

@@
 \usepackage{pgfpages}
+\usepackage{algorithm}
+\usepackage[noend]{algorithmic}
 
@@
 \begin{frame}
-	\tableofcontents
+    \tableofcontents[hideothersubsections]
 \end{frame}
@@
 \begin{frame}
-    \tableofcontents[currentsection]
+    \tableofcontents[currentsection, hideothersubsections]
 \end{frame}
@@
     \begin{frame}
-    \tableofcontents[currentsection]
+    \tableofcontents[currentsection, hideothersubsections]
     \end{frame}
@@
 
+    \begin{frame}
+        \tableofcontents[currentsection, hideothersubsections]
+    \end{frame}
+
 	\subsection{Definition}
@@
 
+	\end{frame}
+
+	\subsection{Finding the FPDIT value}
+
+    \begin{frame}{Finding the FPDIT - Chinese Remainder Theorem}
         For given values of $a_i$, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ if the following condition is respected:
@@
 
+        ...
     \end{frame}
 
-	\subsection{Finding the FPDIT value}
+    \begin{frame}{Finding the FPDIT value}
 
-	\begin{frame}{Existence and value}
+        \begin{algorithm}[H]
+            \caption{Gauss's CRP Algorithm}
+            \label{alg:algoCRP}
+            \begin{algorithmic}[1]
+                \REQUIRE $C$ the set of constraint $c$  $\left( t_d \equiv x(c) \; (\operatorname{mod} \; p(c)) \right)$
+                \REQUIRE $H$ the hyperperiod of the system
+                \FORALL{$c \in C$}
+                    \STATE $Mc \leftarrow \frac{H}{p(c)}$
+                    \STATE $invMc \leftarrow Mc^{-1} \; (mod \; p(c))$
+                    \STATE $e_c \leftarrow Mc \cdot invMc$
+                \ENDFOR
+                \RETURN $\sum\limits_{c \in C}{x(c) \cdot e_c} \; (mod \; H)$
+            \end{algorithmic}
+        \end{algorithm}
+
+    \end{frame}
+
+    \subsection{Frequency of existence}
+
+    \begin{frame}{Frequency of existence of the FPDIT}
+
+    \begin{columns}[c]
+        \column{0.4\textwidth}
+
+        Systems were generated by
+        \begin{itemize}
+            \item Generating O
+            \item Generating T
+            \item Generating D
+        \end{itemize}
+
+        \column{0.6\textwidth}
+        \includegraphics[width=\textwidth]{figs/nofpdit_4.png}
+
+    \end{columns}
 
@@
 
-	\begin{frame}{Redundancy in asynchronous systems}
+    \begin{frame}
+    \tableofcontents[currentsection, hideothersubsections]
+    \end{frame}
+
+	\begin{frame}{Initial description}
 		[$t_d$, $t_d + H$] is a feasibility interval
@@
 \section{Numerical Example}
-
 	\begin{frame}{Example}

### 2013-10-02 python-simulation/mainNoFPDIT.py

@@ -1,11 +1,28 @@
 import random
-import time
 import pylab
+import math
 
 from Model import algorithms
-from Model import cspace
 from Model import Task
 from Model import TaskGenerator
+
+from Helper import myAlgebra
+
+
+def generateSystemArray2(numberOfSystems, constrDeadlineFactor, tasksCnt):
+    systemArray = []
+    for i in range(numberOfSystems):
+        tasks = []
+        T = []
+        for j in range(tasksCnt):
+            T.append(random.randint(5, 20))
+        H = myAlgebra.lcmArray(T)
+        for j in range(tasksCnt):
+            O = random.randint(0, H)
+            D = random.randint(math.floor(H - constrDeadlineFactor * H), H)
+            tasks.append(Task.Task(O, 1, D, T[j]))
+        systemArray.append(Task.TaskSystem(tasks))
+    return systemArray
 
 
 def generateSystemArray(numberOfSystems, constrDeadlineFactor, tasksCnt, verbose=False):
@@ -28,7 +45,7 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, tasksCnt, verbose
     return systemArray
 
 if __name__ == '__main__':
-    NUMBER_OF_SYSTEMS = 10000
+    NUMBER_OF_SYSTEMS = 100
     noFPDITpcts = {}
     CDFvalues = [0.1, 0.3, 0.5, 0.7, 0.9, 1.0]
     nValues = [2, 3, 4, 5, 7, 10]
@@ -38,7 +55,7 @@ if __name__ == '__main__':
         noFPDITpcts[taskCnt] = {}
         for constrDeadlineFactor in CDFvalues:
             print("cdf", constrDeadlineFactor)
-            systemArray = generateSystemArray(NUMBER_OF_SYSTEMS, constrDeadlineFactor, taskCnt)
+            systemArray = generateSystemArray2(NUMBER_OF_SYSTEMS, constrDeadlineFactor, taskCnt)
             firstDitsCnt = 0
             for i, tau in enumerate(systemArray):
                 if algorithms.findFirstDIT(tau) is None:

### 2013-10-02 python-simulation/mainNoFPDIT.py
More printage

@@ -70,4 +70,6 @@ if __name__ == '__main__':
             noFPDITpcts[taskCnt][constrDeadlineFactor] = (100*firstDitsCnt)/NUMBER_OF_SYSTEMS
 
     with open("noFPDIT_results.pickle", "wb") as output:
+        print("Writing result to memory...")
         pickle.dump((noFPDITpcts, CDFvalues, nValues, NUMBER_OF_SYSTEMS), output, pickle.HIGHEST_PROTOCOL)
+        print("Done.")

### 2013-10-02 beamer/dit-paper-presentation.tex
added stuff

@@
 
+    % \subsection{Cyclic Idle Times}
+
+    % \begin{frame}{Cyclic Idle Times}
+
+    % \end{frame}
+
 	\subsection{Our work}
@@
         \begin{itemize}
-            \item Generating O
-            \item Generating T
-            \item Generating D
+            \item Choosing $T_i$ in [5, 20]
+            \item Choosing $O_i$ in [0, $H$]
+            \item Choosing $D_i$ in [$T_i - CDF * T_i$, $T_i$]
         \end{itemize}
@@
 
+    \subsection{Initial description}
+
 	\begin{frame}{Initial description}
-		[$t_d$, $t_d + H$] is a feasibility interval
+		The C-space is still accurately described by the following infinity of constraints:
+
+        $$\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall t_1 \leqslant  t_2$$
+
+        As in the synchronous case,
+        \begin{itemize}
+            \item Every constraint is necessary
+            \item Their conjunction is sufficient
+            \item Most of them are redundant.
+        \end{itemize}
+        However the method used to remove redundancies will be different.
 	\end{frame}
 
-\section{Numerical Example}
+    \subsection{Removing redundancies}
+
+    \begin{frame}{Feasibility study interval}
+
+        The authors of \cite{leung1982complexity} have shown that for asynchronous systems, it sufficient to check the DBF test in intervals $[t_1, t_2]$ where $0 \leqslant t_1 \leqslant t_2$.
+
+        ~\\
+
+        Furthermore, by definition of the demand-bound function, it is sufficient to check only intervals where $t_1$ is an arrival and $t_2$ is a deadline.
+
+    \end{frame}
+
+    \begin{frame}{Using the FPDIT}
+
+        If a FPDIT exists,
+
+    \end{frame}
+
+    \subsection{Example}
+
     \begin{frame}{Example}
 		Table, OCDT, figure
+	\end{frame}
+
+\section{Feasibility gain of offset}
+
+    \begin{frame}
+    \tableofcontents[currentsection, hideothersubsections]
+    \end{frame}
+
+    \begin{frame}{Experiment}
+
+        We want to express the feasibility gain of random offsets as the ratio
+
+        $$\frac{V(\tau)}{V(\tau')}$$
+
+        Where
+        \begin{itemize}
+            \item $\tau$ is a synchronous system
+            \item $\tau'$ is $\tau$ with added offsets
+            \item $V(\tau)$ is the size of the C-space of $\tau$
+        \end{itemize}
+
+    \end{frame}
+
+    \begin{frame}{Result}
+
+        \includegraphics[width=0.9\textwidth]{figs/sizeratio.png}
+
+    \end{frame}
+
+\section{Future Works}
+
+    \begin{frame}{Future Works}
+
+    \begin{itemize}
+        \item Further ways of reducing redundancy before applying the simplex
+        \item Other metrics to quantify the quality of the C-space
+        \item Extension to multiprocessor scheduling
+    \end{itemize}
+
     \end{frame}

### 2013-10-03 beamer/dit-paper-presentation.tex
yep yep yep

@@
 	\begin{frame}{Model}
-  \begin{block}{Definition}
+  \begin{block}{Real-Time Systems}
   Systems with real-time constraints. (e.g. ABS, VOD, etc)
   \end{block}
-  \textbf{Model:} Set of tasks $\tau_i = (O_i, T_i, D_i, C_i)$ generating jobs $J_{i,j}$, with
+  \textbf{Model:} $\tau$ set of $n$ tasks $\tau_i = (O_i, C_i, D_i, T_i)$ generating jobs $J_{i,j}$
       \begin{itemize}
       \item $O_i$ : arrival of the first job
+      \item $C_i$ : execution time
+      \item $D_i$ : relative deadline
       \item $T_i$ : time between two job arrivals
-      \item $D_i$ : relative deadline
-      \item $C_i$ : execution time
     \end{itemize}
@@
  \hline
-  & $O_i$ & $T_i$ & $D_i$ & $C_i$ \\
+  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
  \hline
@@
 
-        \begin{block}{Feasibility}
+        \begin{block}{Feasibility by a scheduling policy}
         A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
@@
     \begin{frame}{Definition of the C-space}
-        \begin{block}{Definition}
+        \begin{block}{C-space}
             The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
@@
     \begin{frame}{Demand-bound function feasibility test}
-        \begin{block}{Definition}
+        \begin{block}{Demand-bound function}
             The \textbf{demand-bound function (DBF)}
@@
     The DBF test gives us a set of constraints
-    $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$
+    $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$
 
@@
         \item Their conjunction is sufficient
-        \pause
+        % \pause
         \item But we have an infinite number of constraints!
@@
     ~\\
-    \pause
+    % \pause
 
@@
 
-	In this paper, we
+	In the article, we
     \begin{itemize}
@@
 	\begin{frame}{Definition of the FPDIT}
-		\begin{block}{Definition}
+        \begin{block}{Definitive Idle Time}
+            A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ (if it exists) such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.
+        \end{block}
+
+        \begin{block}{First Periodic DIT}
 			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
@@
         The FPDIT is the smallest $t_d$ such as:
-       \begin{equation}
+       \[
             \begin{array}{l}
@@
             \end{array}
-            \label{eq:FPDIT}
-        \end{equation}
+        \]
 
@@
 
-    \begin{frame}{Finding the FPDIT - Chinese Remainder Theorem}
-        For given values of $a_i$, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ if the following condition is respected:
-        \[
-            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
-            T_j)) \; \forall i,j
-        \]
-
-        ...
-    \end{frame}
-
-    \begin{frame}{Finding the FPDIT value}
+    \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
+        For given values of $a_i$, if the periods are pairwise coprime, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ given by:
 
@@
             \begin{algorithmic}[1]
-                \REQUIRE $C$ the set of constraint $c$  $\left( t_d \equiv x(c) \; (\operatorname{mod} \; p(c)) \right)$
+                \REQUIRE $C$ the set of constraint $c$ : $\left( t_d \equiv x(c) \; (\operatorname{mod} \; p(c)) \right)$
                 \REQUIRE $H$ the hyperperiod of the system
@@
         \end{algorithm}
+
+    \end{frame}
+
+    \begin{frame}{Non-pairwise co-prime moduli}
+        If the periods are non-pairwise co-prime, the system has a FPDIT if and only if the following condition is respected:
+        \[
+            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
+            T_j)) \; \forall i,j
+        \]
+
+        Then each equation $t_d \equiv x \; (\operatorname{mod} \; p)$ with $p = p_1^{b_1} \cdots p_k^{b_k}$ (where each $p_i$ is prime), can be replaced by the system:
+
+       \[
+            \begin{array}{l}
+                \left\{
+                    \begin{array}{l}
+                         t_d \equiv x \; (mod \; p_1^{b_1}) \\
+                         \cdots \\
+                         t_d \equiv x \; (mod \; p_k^{b_k})
+                    \end{array}
+                \right.
+            \end{array}
+        \]
+
+        Equations with the same $p_i$ can be replaced by only the one of highest $b_i$. The new system now has pairwise co-prime moduli.
 
@@
         \column{0.6\textwidth}
-        \includegraphics[width=\textwidth]{figs/nofpdit_4.png}
+        \includegraphics[width=1.2\textwidth]{figs/nofpdit_5.png}
 
@@
 	\begin{frame}{Initial description}
-		The C-space is still accurately described by the following infinity of constraints:
+		The C-space is still accurately described by the following infinite number of constraints:
 
@@
 
+    \begin{frame}{Redundancy as an ILP (I)}
+
+    We can define the redundancy of a linear constraint $C \cdot X \leqslant d$ with regards to a set of $k$ linear constraints $A \cdot X \leqslant B$ as the following Integer Linear Problem (ILP):
+
+    \begin{columns}[c]
+        \column{0.1\textwidth}
+        \column{0.3\textwidth}
+
+        \begin{block}{Redundancy ILP}
+
+        \begin{center}
+        $z = \max \left( C \cdot X \right)$
+
+        s.t.
+
+        $
+        \begin{array}{rcc}
+          A \cdot X &\leq & B \\
+          C \cdot X &\leq & d + 1
+        \end{array}
+        $
+        \end{center}
+
+        \end{block}
+
+        \column{0.1\textwidth}
+
+        \column{0.5\textwidth}
+
+        \begin{center}with\end{center}
+        \[
+          \begin{array}{ccc}
+            A & : & [n,k] \text{ matrix}\\
+            B \; \text{and} \; C & : & [n,1] \text{ matrix}\\
+            X & : & [1,n] \text{ matrix}\\
+            d & : & \text{integer}
+          \end{array}
+        \]
+    \end{columns}
+        \begin{itemize}
+            \item If $z = d + 1$, the constraint is redundant
+            % \item Can be solved with a branch-and-bound approach
+            \item Complexity (one test): exponential in the size of the set
+            \item Each constraint of the set must be tested
+        \end{itemize}
+
+    \end{frame}
+
+    \begin{frame}{Redundancy as an ILP (II)}
+
+        \begin{algorithm}[H]
+            \caption{Removing redundant constraints}
+            \label{alg:pruneCspace}
+          \begin{algorithmic}[1]
+            \STATE $CSPACE$ : set of constraints
+            \STATE $S \leftarrow \emptyset$
+            \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
+            \FOR{$cstr$ \textbf{in} $CSPACE$}
+              \IF {$cstr$ is not redundant w.r.t. $S$}
+                \STATE $S.push(cstr)$
+              \ENDIF
+            \ENDFOR
+            \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
+            \FOR{$cstr$ \textbf{in} $S$}
+              \STATE $cstr$ = $S.pop()$
+              \IF {$cstr$ is not redundant w.r.t. $S$}
+                \STATE $S.push(cstr)$
+              \ENDIF
+            \ENDFOR
+            \RETURN{S}
+            \end{algorithmic}
+        \end{algorithm}
+
+    \end{frame}
+
     \begin{frame}{Feasibility study interval}
 
-        The authors of \cite{leung1982complexity} have shown that for asynchronous systems, it sufficient to check the DBF test in intervals $[t_1, t_2]$ where $0 \leqslant t_1 \leqslant t_2$.
+        The authors of \cite{leung1982complexity} have shown that for asynchronous systems, it sufficient to check the DBF test in intervals $[t_1, t_2]$ where $$O_{max} \leqslant t_1 < t_2 \leqslant O_{max} + 2 \cdot H$$
 
-        ~\\
+        Indeed, it can be shown that at instant $O_{max} + 2 \cdot H$ at the latest, the system enters a periodic behavior.
+If follows that if no deadlines have been missed before it, no future deadline misses can occur.
 
-        Furthermore, by definition of the demand-bound function, it is sufficient to check only intervals where $t_1$ is an arrival and $t_2$ is a deadline.
+    \end{frame}
+
+    \begin{frame}{Arrivals and deadlines}
+
+        By definition of the demand-bound function, it is sufficient to check only intervals where $t_1$ is an arrival and $t_2$ is a deadline.
+
+        \begin{block}{Demand-bound function}
+            The \textbf{demand-bound function (DBF)}
+            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
+            the maximal cumulated execution time of jobs of $\tau$ contained in the
+            closed interval $[t_1, t_2]$.
+        \end{block}
 
@@
 
-        If a FPDIT exists,
+        The authors of \cite{choquet2004minimal} define the notion of \emph{cyclic idle times}, the first of which marks the start of the periodic behavior of the system.
+They prove that if $t_c$ is a cyclic idle time and there are no deadline miss in the interval $[t_c, t_c + H]$, then the system is feasible.
+
+        ~\\
+
+        However the existence and position of the cyclic idle times depend on the values of the $C_i$ and are therefore not accessible when describing the C-space.
+
+        ~\\
+
+        By definition, if the FPDIT exists it will also be a cyclic idle time. It follows that the interval $[t_d, t_d + H]$ is sufficient.
 
@@
 
-    \begin{frame}{Example}
-		Table, OCDT, figure
+    \begin{frame}{Example (I)}
+        \[
+        \begin{array}{|r|c|c|c|c|}
+         \hline
+          & O_i & C_i & D_i & T_i \\
+         \hline
+         \tau_1 & 8 & C_1 & 7 & 15\\
+         \hline
+         \tau_2 & 0 & C_2 & 2 & 5\\
+         \hline
+        \end{array}
+        \]
+
+        \includegraphics[width=\textwidth]{figs/CspaceExampleArrDead.png}
+
+        \begin{itemize}
+            \item $H = 15$
+            \item The FPDIT happens at $t_d = 15$
+            \item Our study interval is $[15, 30]$ which yields 11 constraints
+            \item Without the FPDIT, the interval would be $[8, 38]$ (57 constraints)
+        \end{itemize}
     \end{frame}
 
-\section{Feasibility gain of offset}
+    \begin{frame}{Example (II)}
+
+    We remove the remaining redundancies with the ILP:
+    $$
+        \left\{
+            \begin{array}{cccccc}
+                & & & C_2 & \leqslant & 2 \\
+                C_1 & + & & C_2 & \leqslant & 7
+            \end{array}
+        \right.
+    $$
+
+    The C-space of the corresponding synchronous system is:
+    $$
+    \left\{
+      \begin{array}{cccccc}
+        & & & C_2 & \leqslant & 2 \\
+        C_1 & + & 2 & C_2 & \leqslant & 7
+      \end{array}
+    \right.
+    $$
+
+    \begin{columns}[c]
+
+    \column{0.5\textwidth}
+
+    \includegraphics[width=\textwidth]{figs/cspace_example.png}
+
+    \column{0.5\textwidth}
+
+    The offsets allow three more $C_i$ values to be feasible.
+
+    \end{columns}
+
+    \end{frame}
+
+\section{Feasibility gain of random offsets}
 
@@
 
-        \includegraphics[width=0.9\textwidth]{figs/sizeratio.png}
+        \begin{columns}[c]
+
+        \column{0.5\textwidth}
+
+            \includegraphics[width=1.2\textwidth]{figs/sizeratio.png}
+
+        \column{0.5\textwidth}
+
+            \begin{itemize}
+                \item Around 10\% of amelioration for high-utilization systems
+                \item Gain not highly dependent of utilization or CDF
+            \end{itemize}
+
+        \end{columns}
 

### 2013-10-03 python-simulation/Helper/systems.py

@@ -271,6 +271,12 @@ tasks.append(Task.Task(0, 1, 6, 6, alpha=2))
 tasks.append(Task.Task(0, 6, 12, 12, alpha=2))
 ImpPTEFTNonOptimal = Task.TaskSystem(tasks)
 
+# DITPaperExample
+tasks = []
+tasks.append(Task.Task(8, 0, 7, 15, alpha=0))
+tasks.append(Task.Task(0, 0, 2, 5, alpha=0))
+DITPaperExample = Task.TaskSystem(tasks)
+
 
 # test
 tasks = []

### 2013-10-03 python-simulation/mainSimu.py

@@ -1,4 +1,6 @@
 from Model import algorithms
+from Model import TaskGenerator
+from Model import Task
 from Simulator import Simulator
 from Simulator.Scheduler import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
 from Helper import systems
@@ -6,8 +8,8 @@ from Helper import systems
 import subprocess
 import sys
 
-# tau = systems.generateSystemArray(1, 0)[0]
-tau = systems.SmallExample
+# tau = Task.TaskSystem(TaskGenerator.generateTasks(0.7, 3, 33750, 5, 20))
+tau = systems.DITPaperExample
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()
@@ -24,10 +26,10 @@ stop = Omax + 10 * H
 
 print(("stop", stop))
 
-# scheduler = Scheduler.EDF(tau)
+scheduler = Scheduler.EDF(tau)
 # scheduler = Scheduler.SpotlightEDF(tau)
 # scheduler = ChooseKeepEDF.ChooseKeepEDF(tau)
-scheduler = Scheduler.PTEDF(tau)
+# scheduler = Scheduler.PTEDF(tau)
 # scheduler = PALLF.PALLF(tau)
 # scheduler = Scheduler.ArbitraryScheduler(tau, systems.mpanaSchedule)
 # scheduler = LBLScheduler.LBLEDF(tau)

### 2013-10-04 beamer/dit-paper-presentation.tex
renamed module to lowercase (crazy convention following while we can)

@@
 
-	\section{Related works}
+	\section{Previous works}
 
@@
         \begin{block}{Demand-bound function}
-            The \textbf{demand-bound function (DBF)}
+            The \textbf{demand-bound function (DBF)} \cite{baruah1999generalized,
+        baruah1990algorithms}
             defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
@@
     \begin{frame}{Description using the DBF test}
-    The DBF test gives us a set of constraints
+    The DBF test gives us a set of constraints to describe the C-space
     $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$
@@
         \begin{block}{Definitive Idle Time}
-            A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ (if it exists) such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.
+            A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.
         \end{block}
@@
     \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
-        For given values of $a_i$, if the periods are pairwise coprime, equation~(\ref{eq:FPDIT}) has one solution modulo $H$ given by:
+        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by:
 
@@
     \begin{frame}{Non-pairwise co-prime moduli}
-        If the periods are non-pairwise co-prime, the system has a FPDIT if and only if the following condition is respected:
+        If the periods are non-pairwise co-prime, the system has a DIT for given values of $a_i$ if and only if the following condition is respected:
         \[
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{amsalpha}
 \bibliography{dit-paper}

### 2013-10-04 python-simulation/test/testTask.py

@@ -1,4 +1,4 @@
-from Model.Task import Task, TaskSystem
+from model.Task import Task, TaskSystem
 
 import unittest
 

### 2013-10-04 python-simulation/paper-paedf/paper-paedf.tex
further modification to lowercase stuff

@@
 
-\title{Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor systems}
+\title{Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor periodic systems}
 \author{Thomas Chapeaux}
@@
 
+...
+
 \section{Model}
@@
 
-        OCDT model with per-task
+        The results presented in this section use the assumption that preemption times are negligible.\\
 
-        Constrained deadline
+        We use an extension of Liu and Layland model presented in \cite{Liu:2000:RS:518501} to formalize real-time systems.
+This model represents such systems by a set of \textbf{tasks} generating \textbf{jobs}, where a job is a whole entity of computation with a given time of arrival and a given deadline.\\
 
-        EDF is optimal
+        \subsubsection{Tasks and jobs}
+
+        Tasks are used to model recurring jobs. They are denoted as the tuple $\tau_i = (O_i, T_i, D_i, C_i)$, where
+        \begin{itemize}
+            \item $i = \{1,2,...\}$ is an unique identifier for the task.
+            \item $O_i$ is the minimal time at which the first job of the tasks is generated.
+            \item $T_i$ is the minimal time between two job generations.
+            \item $D_i$ is the relative deadline of its job.
+            \item $C_i$ is the execution time of its job.
+        \end{itemize}
+
+        A task $\tau_i$ generates jobs, denoted as the tuple $J_{i,j} = (a_{i, j}, d_{i,j}, c_{i,j})$ where :
+        \begin{itemize}
+            \item $j = \{1,2,...\}$ is an unique identifier for the job within $\tau_i$.
+            \item $a_{i,j} = O_i + (j-1) \cdot T_i$ is the arrival time (or \emph{activation time}) of the job.
+            \item $d_{i,j} = a_{i,j} + D_i$ is an absolute deadline at which the job must be completed.
+            \item $c_{i,j} = C_i$ is the time it takes to complete the job (\emph{execution time}).
+        \end{itemize}
+
+        We also assume a discrete time, meaning that we consider that time passes one unit (sometimes called \emph{clock tick}) at a time.
+This means that the values listed above must be integers and that jobs will execute for whole units.\\
+
+        In this paper, we only consider \textbf{constrained deadline} systems, where $D_i \leqslant T_i \; \forall i$, and sometimes the particular case of \textbf{implicit deadline} systems, where $D_i = T_i$.\\
+
+        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (which are not synchronous).
+
+        \subsubsection{Schedule and feasibility}
+
+        A scheduling policy is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are released and unfinished jobs present in the system.
+It is said to be \textbf{preemptive} if it allows the processor to begin computation of a new job when the currently computed job is still unfinished.\\
+
+        A system is said to be \textbf{schedulable by a scheduling policy} if it exists a scheduling policy such that every job in the task set completes before its deadline is reached.
+A system schedulable by at least one scheduling policy is said to be \textbf{feasible}.\\
+
+        The authors of \cite{liu1973scheduling} have shown that the EDF (Earliest Deadline First) scheduling policy, in which jobs are prioritized according to their absolute deadline, is optimal, meaning that any feasible system is schedulable by EDF.\\
+
+        \subsubsection{Feasibility Analysis}
+
+        For implicit task systems, $U_{tot} \leqslant 1$ is a necessary and sufficient condition of feasibility.\\
+
+        For (a)synchronous constrained deadline systems, $[O_{max}, O_{max} + 2 \cdot H]$ (with $O_{max}$ being the maximal task offset and $H$ the LCM of periods) is a feasibility interval for EDF.
 
@@
 
-        Preemption model (add parameters alpha and atomic preemption recovery period)
+        We now consider that preemption costs are not negligible. We thus define a parameter $\alpha$, constant for all tasks of a system, called the preemption cost.\\
+
+        Once a previously preempted job is chosen for computation by the scheduling policy, it enters an uninterruptible preemption recovery period.\\
+
+        [figure]\\
 
@@
 
+    In this section, we show that the EDF scheduling policy, optimal when the preemption costs are negligible, is less adapted to our model with costly preemptions.
+
     \subsection{Non-optimality}
 
+        Consider the following task system
+
+        \begin{center}
+            \begin{tabular}{|r|c|c|c|c|c|}
+                \hline
+                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
+                $\tau_1$    & 0     & 3     & 6    & 6     & 2     \\ \hline
+                $\tau_2$    & 1     & 2     & 4    & 4     & 2     \\ \hline
+            \end{tabular}
+        \end{center}
+
+        When scheduled by EDF, this job miss a deadline\\
+
+        [figure]\\
+
+        However, there exists a schedule which does not miss any deadline:\\
+
+        [figure]\\
+
+        EDF is thus non-optimal.
+
     \subsection{Anomalies}
+
+        Consider the following system
+
+        \begin{center}
+            \begin{tabular}{|r|c|c|c|c|c|}
+                \hline
+                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
+                $\tau_1$    & 0     & 3     & 6    & 6     & 2     \\ \hline
+                $\tau_2$    & 1     & 2     & 4    & 4     & 2     \\ \hline
+            \end{tabular}
+        \end{center}
+
+    \subsection{Other properties of constrained deadline systems}
 

### 2013-10-04 python-simulation/helper/findFPDIT.py

@@ -1,4 +1,4 @@
-from Helper import myAlgebra
+from helper import myAlgebra
 
 import math
 import heapq
@@ -39,7 +39,7 @@ def findFPDIT(tau):
     Omax = max([task.O for task in tau.tasks])
     congruenceDict = {}
     primeDict = {}
-    
+
     for task in tau.tasks:
         pFactors = myAlgebra.primeFactors(task.T)
         primalPowers = [pow(t,pFactors.count(t)) for t in set(pFactors)]
@@ -72,7 +72,7 @@ def findFPDIT(tau):
     ppSet = set()
     for t in tgsList:
         ppSet.update(t.pList)
-        
+
     for pp in ppSet:
         for task in tau.tasks:
             taskPList = congruenceDict[task].pList
@@ -82,8 +82,8 @@ def findFPDIT(tau):
                     newTaskPList.append(pp)
                 else:
                     newTaskPList.append(taskp)
-            congruenceDict[task].pList = newTaskPList 
-    	
+            congruenceDict[task].pList = newTaskPList
+
     allResults = multiCRP(congruenceDict)
 
     if not allResults:
@@ -113,8 +113,8 @@ def findFPDIT(tau):
             alreadyTested = idleTuple[1]
 
     return tIdle
-    
-    
+
+
 def multiCRP(congruenceDict):
     tgsList = congruenceDict.values()
     ppSet = set()
@@ -133,7 +133,7 @@ def multiCRP(congruenceDict):
                 invMi = myAlgebra.modinv(Mi, p)
                 tgsSum += (x * Mi * invMi) % H
             tgsSumList[cnt] = tgsSum
-        sumChunks[t] = tgsSumList 
+        sumChunks[t] = tgsSumList
 
 #   calculate the sums from the precomputed terms
     results = [0]
@@ -147,7 +147,7 @@ def multiCRP(congruenceDict):
         results = newResults
 
     return [r % H for r in results]
-    
-    
+
+
 if __name__ == '__main__':
     pass

### 2013-10-04 python-simulation/helper/systems.py

@@ -1,6 +1,6 @@
 import random
-from Model import Task
-from Model import TaskGenerator
+from model import Task
+from model import TaskGenerator
 
 
 def generateSystemArray(numberOfSystems, constrDeadlineFactor, n=4, preemptionCost=2, verbose=False):
@@ -125,8 +125,8 @@ tasks.append(Task.Task(20, 10, 50, 50, alpha=23))
 LongTransitive = Task.TaskSystem(tasks)
 tasks = []
 tasks.append(Task.Task(0, 5, 10, 10, alpha=1))
-tasks.append(Task.Task(4, 1, 1, 10))
-tasks.append(Task.Task(6, 4, 10, 10))
+tasks.append(Task.Task(4, 1, 1, 10, alpha=1))
+tasks.append(Task.Task(6, 4, 10, 10, alpha=1))
 LongTransitive2 = Task.TaskSystem(tasks)
 
 # FailByTransitive
@@ -280,8 +280,7 @@ DITPaperExample = Task.TaskSystem(tasks)
 
 # test
 tasks = []
-tasks.append(Task.Task(0, 9, 45, 45, alpha=2))
-tasks.append(Task.Task(0, 1, 6, 6, alpha=2))
-tasks.append(Task.Task(0, 6, 12, 12, alpha=2))
+tasks.append(Task.Task(0, 1, 6, 8, alpha=0))
+tasks.append(Task.Task(0, 1, 12, 13, alpha=0))
 
 test = Task.TaskSystem(tasks)

### 2013-10-04 python-simulation/main.py

@@ -3,8 +3,8 @@ import random
 
 import pylab  # http://matplotlib.org/
 
-from Task import Task, TaskGenerator
-from Model import algorithms
+from model.Task import Task, TaskGenerator
+from model import algorithms
 from functools import reduce
 
 

### 2013-10-04 python-simulation/mainAsyncExample.py

@@ -1,7 +1,7 @@
-from Model import Task
-from Model import TaskGenerator
-from Model import algorithms
-from Model import cspace
+from model import Task
+from model import TaskGenerator
+from model import algorithms
+from model import cspace
 
 import random
 import time

### 2013-10-04 python-simulation/mainAsynchr.py

@@ -2,10 +2,10 @@ import random
 import time
 # import pylab
 
-from Model import algorithms
-from Model import Task
-from Model import TaskGenerator
-from Model import cspace
+from model import algorithms
+from model import Task
+from model import TaskGenerator
+from model import cspace
 
 
 def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):

### 2013-10-04 python-simulation/mainCspace.py

@@ -1,8 +1,9 @@
-from Model import Task
-from Model import TaskGenerator
-from Model import cspace as cs
-from Model import algorithms
+from model import Task
+from model import TaskGenerator
+from model import cspace as cs
+from model import algorithms
 import random
+from helper import systems
 
 def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
     systemArray = []
@@ -25,55 +26,54 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
 
 tasks = []
 #                      0, C, D, T
-tasks.append(Task.Task(0, 1, 5, 7))
-tasks.append(Task.Task(0, 1, 7, 11))
-tasks.append(Task.Task(0, 1, 10, 13))
+tasks.append(Task.Task(0, 1, 6, 8))
+tasks.append(Task.Task(0, 1, 12, 13))
 tau = Task.TaskSystem(tasks)
 print(tau)
 tau_Cspace = cs.Cspace(tau)
-tau_Cspace_noredun = tau_Cspace.removeRedundancy()
+tau_Cspace_noredun = tau_Cspace.removeRedundancy(verbose=True)
 
 print("FINAL CSPACE")
 for cstr in tau_Cspace_noredun:
     print(cstr)
 print(len(tau_Cspace), "=>", len(tau_Cspace_noredun), "constraints left")
 
-tasks = []
-#                      0, C, D, T
-tasks.append(Task.Task(5, 1, 1, 3))
-tasks.append(Task.Task(0, 4, 4, 8))
-tau = Task.TaskSystem(tasks)
-tau_Cspace = cs.Cspace(tau)
-assert cs.testCVector(tau_Cspace, [task.C for task in tau.tasks]) is False
+# tasks = []
+# #                      0, C, D, T
+# tasks.append(Task.Task(5, 1, 1, 3))
+# tasks.append(Task.Task(0, 4, 4, 8))
+# tau = Task.TaskSystem(tasks)
+# tau_Cspace = cs.Cspace(tau)
+# assert cs.testCVector(tau_Cspace, [task.C for task in tau.tasks]) is False
 
-# "TEST2"
+# # "TEST2"
 
-tasks = []
-tasks.append(Task.Task(0, 1, 73, 154))
-tasks.append(Task.Task(0, 1, 381, 825))
-tasks.append(Task.Task(0, 1, 381, 400))
-tau = Task.TaskSystem(tasks)
[…]

### 2013-10-04 python-simulation/mainNoFPDIT.py

@@ -3,11 +3,11 @@ import math
 import concurrent.futures
 import pickle
 
-from Model import algorithms
-from Model import Task
-from Model import TaskGenerator
+from model import algorithms
+from model import Task
+from model import TaskGenerator
 
-from Helper import myAlgebra
+from helper import myAlgebra
 
 
 def generateSystemArray2(numberOfSystems, constrDeadlineFactor, tasksCnt):

### 2013-10-04 python-simulation/mainRedunComp.py

@@ -1,7 +1,7 @@
-from Model import Task
-from Model import TaskGenerator
-from Model import algorithms
-from Model import cspace
+from model import Task
+from model import TaskGenerator
+from model import algorithms
+from model import cspace
 
 import pylab
 

### 2013-10-04 python-simulation/mainSimu.py

@@ -1,15 +1,15 @@
-from Model import algorithms
-from Model import TaskGenerator
-from Model import Task
-from Simulator import Simulator
-from Simulator.Scheduler import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
-from Helper import systems
+from model import algorithms
+from model import TaskGenerator
+from model import Task
+from simulator import Simulator
+from simulator.scheduler import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
+from helper import systems
 
 import subprocess
 import sys
 
 # tau = Task.TaskSystem(TaskGenerator.generateTasks(0.7, 3, 33750, 5, 20))
-tau = systems.DITPaperExample
+tau = systems.LongTransitive2
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()

### 2013-10-04 python-simulation/mainSimuComp.py

@@ -1,8 +1,8 @@
-from Model import algorithms
-from Model import Task, TaskGenerator
-from Simulator import Simulator
-from Simulator.Scheduler import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
-from Helper import systems
+from model import algorithms
+from model import Task, TaskGenerator
+from simulator import Simulator
+from simulator.Scheduler import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
+from helper import systems
 
 import random
 import pylab

### 2013-10-04 python-simulation/model/Task.py

@@ -1,7 +1,7 @@
 import math
-from Helper import myAlgebra
-from Model import Job
-from Model import cspace
+from helper import myAlgebra
+from model import Job
+from model import cspace
 
 import array
 import heapq

### 2013-10-04 python-simulation/model/TaskGenerator.py

@@ -1,6 +1,6 @@
 import math
 import random
-from . import Task
+from model import Task
 from functools import reduce
 
 

### 2013-10-04 python-simulation/model/algorithms.py

@@ -1,8 +1,8 @@
 import itertools
 import math
 
-from Helper import myAlgebra
-from Model import newChineseRemainder
+from helper import myAlgebra
+from model import newChineseRemainder
 from functools import reduce
 
 

### 2013-10-04 python-simulation/model/cspace.py

@@ -1,4 +1,4 @@
-from Model import algorithms
+from model import algorithms
 
 import subprocess  # in order to launch GLPSOL
 import itertools

### 2013-10-04 python-simulation/model/newChineseRemainder.py

@@ -1,6 +1,6 @@
-from Helper import myAlgebra
-# from Model import Task
-# from Model import TaskGenerator
+from helper import myAlgebra
+# from model import Task
+# from model import TaskGenerator
 
 import math
 import heapq
@@ -196,7 +196,7 @@ def oldCRLoop(systems):
 
 # def benchmarkNewChineseRemainder():
 # #   systems = [Task.TaskSystem(TaskGenerator.generateTasks(1, 3, 554400, 2, 7, False)) for i in range(1000)]
-# 
+#
 #     cProfile.run('benchmark_main()', 'CRstats')
 #     p = pstats.Stats('CRstats')
 #     p.strip_dirs()

### 2013-10-04 python-simulation/simulator/Simulator.py

@@ -1,10 +1,10 @@
 from heapq import heapify, heappop, heappush
 import pdb
 
-from Model.CPU import CPU
-from Model import algorithms
-from Simulator.Drawer import Drawer
-from Simulator.JobConfiguration import JobConfiguration
+from model.CPU import CPU
+from model import algorithms
+from simulator.drawer import Drawer
+from simulator.JobConfiguration import JobConfiguration
 
 
 def heappeek(heap):
@@ -46,7 +46,7 @@ class Simulator(object):  # Global multiprocessing only
         heapify(self.activeJobsHeap)
 
         if drawing:
-            from Simulator.Drawer import PILDrawer
+            from simulator.drawer import PILDrawer
             self.drawer = PILDrawer.PILDrawer(self, stop)
         else:
             self.drawer = Drawer.EmptyDrawer(self, stop)

### 2013-10-04 python-simulation/simulator/drawer/PILDrawer.py

@@ -1,6 +1,6 @@
-from Simulator.Drawer.Drawer import Drawer
+from simulator.drawer.Drawer import Drawer
 
-from Model import algorithms
+from model import algorithms
 
 from PIL import Image as img
 from PIL import ImageFont
@@ -8,6 +8,7 @@ from PIL import ImageDraw as draw
 
 import random
 import re
+
 
 class PILDrawer(Drawer):
     def __init__(self, simu, stop):

### 2013-10-04 python-simulation/simulator/scheduler/ChooseKeepEDF.py

@@ -1,4 +1,4 @@
-from . import Scheduler
+from simulator.scheduler import Scheduler
 
 
 class ChooseKeepEDF(Scheduler.SchedulerDP):

### 2013-10-04 python-simulation/simulator/scheduler/LBLScheduler.py

@@ -1,4 +1,4 @@
-from Simulator.Scheduler import Scheduler
+from simulator.scheduler import Scheduler
 
 
 class LBLScheduler(Scheduler.SchedulerDP):

### 2013-10-04 python-simulation/simulator/scheduler/PALLF.py

@@ -1,4 +1,4 @@
-from . import Scheduler
+from simulator.scheduler import Scheduler
 
 
 class PALLF(Scheduler.SchedulerDP):

### 2013-10-04 python-simulation/simulator/scheduler/Scheduler.py

@@ -1,6 +1,6 @@
 import itertools
 import pdb
-from Helper import myAlgebra
+from helper import myAlgebra
 
 
 class SchedulerDP(object):
@@ -175,7 +175,7 @@ class ExhaustiveFixedPriority(FixedPriority):
         super().__init__(tau, feasiblePriorities)
 
     def exhaustiveSearch(self):
-        from Simulator.Simulator import Simulator
+        from simulator.Simulator import Simulator
         taskArray = self.tau.tasks
         priorities = [i for i in range(0, len(taskArray))]
         self.foundFeasible = False

### 2013-10-04 python-simulation/test/testAlgorithms.py

@@ -1,8 +1,8 @@
 import unittest
 import random
 
-from Model import algorithms as algo
-from Model.Task import Task, TaskSystem
+from model import algorithms as algo
+from model.Task import Task, TaskSystem
 
 
 class TestAlgorithms(unittest.TestCase):
@@ -82,7 +82,7 @@ class TestAlgorithms(unittest.TestCase):
         self.assertFalse(algo.dbfTest(tau))
 
     def test_randomYAfindFPDIT(self):
-        from Model import TaskGenerator
+        from model import TaskGenerator
         for i in range(1000):
             Utot = random.randint(25, 100) / 100
             n = random.randint(2, 5)

### 2013-10-04 python-simulation/test/testFindFPDIT.py

@@ -1,9 +1,9 @@
 import unittest
 import random
 
-from Model.Task import Task, TaskSystem
-from Model import algorithms, TaskGenerator
-from Helper import findFPDIT
+from model.Task import Task, TaskSystem
+from model import algorithms, TaskGenerator
+from helper import findFPDIT
 
 class TestFindFPDIT(unittest.TestCase):
     def setUp(self):
@@ -25,4 +25,4 @@ class TestFindFPDIT(unittest.TestCase):
         tasks.append(Task(6, 1, 8, 8, 0))
         tau = TaskSystem(tasks)
 #         self.assertEquals(findFPDIT.findFPDIT(tau), algorithms.findFirstDIT(tau))
-            
+

### 2013-10-04 python-simulation/test/testMyAlgebra.py

@@ -1,6 +1,6 @@
 import unittest
 
-from Helper import myAlgebra as mAlg
+from helper import myAlgebra as mAlg
 
 
 class TestMyAlgebra(unittest.TestCase):

### 2013-10-04 python-simulation/test/testSimulator.py

@@ -1,6 +1,6 @@
-from Simulator import Simulator
-from Simulator.Scheduler import Scheduler, ChooseKeepEDF, PALLF
-from Helper import systems
+from simulator import Simulator
+from simulator.scheduler import Scheduler, ChooseKeepEDF, PALLF
+from helper import systems
 
 import unittest
 

### 2013-10-04 python-simulation/paper-paedf/paper-paedf.tex
added content to tex

@@
 
-        A scheduling policy is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are released and unfinished jobs present in the system.
+        A scheduling policy (or \emph{algorithm}) is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are released and unfinished jobs present in the system.
 It is said to be \textbf{preemptive} if it allows the processor to begin computation of a new job when the currently computed job is still unfinished.\\
@@
 \section{Performance of EDF with preemption cost}
+% Rename section to something like "Old results do not old, bitch"
 
@@
 
+        \subsubsection{Longer transitive period}
         Consider the following system
@@
                             & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
-                $\tau_1$    & 0     & 3     & 6    & 6     & 2     \\ \hline
-                $\tau_2$    & 1     & 2     & 4    & 4     & 2     \\ \hline
+                $\tau_1$    & 0     & 5     & 10   & 10    & 1     \\ \hline
+                $\tau_2$    & 4     & 1     & 1    & 10    & 1     \\ \hline
+                $\tau_3$    & 6     & 4     & 10   & 10    & 1     \\ \hline
             \end{tabular}
@@
 
+        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet. This only happens at instant $O_{max} + 4 \cdot H$.\\
+
+        Figure.
+
+        \subsubsection{Deadline miss in transitive, not in periodic}
+
     \subsection{Other properties of constrained deadline systems}
 
-\section{PA-EDF: an amelioration}
+    In this section, we present other results which do not hold under the costly preemption assumption.
+
+        \subsubsection{Idling dominate non-idling}
+
+        Consider the following system
+
+        \begin{center}
+            \begin{tabular}{|r|c|c|c|c|c|}
+                \hline
+                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
+                $\tau_1$    & 0     & 3     & 8    & 8     & 2     \\ \hline
+                $\tau_2$    & 0     & 3     & 5    & 8     & 2     \\ \hline
+                $\tau_3$    & 1     & 1     & 1    & 8     & 2     \\ \hline
+            \end{tabular}
+        \end{center}
+
+        And consider the following schedule which shows that it is feasible with an idling scheduling policy.
+
+        [figure]
+
+        However, it is easy to see that no non-idling algorithm can successfully schedule this system: at $t=0$, a non-idling algorithm has to choose between the first job of $\tau_1$ and $\tau_2$ for execution, whichever is chosen will then be preempted by the first job of $\tau_3$ (if not, it will miss its deadline in $t=2$).
+Then, at $t=2$, there will be $3+2+2=7$ units of computation left to compute before the deadline at $t=8$, the system will thus certainly miss a deadline.
+
+        \subsubsection{Dynamic dominate fixed-job}
+
+        \subsubsection{u < 0.69 is not sufficient}
+
+        \subsubsection{Require Claivoyance}
+
+        \subsubsection{Preemption can happen anywhere}
+
+\section{PA-EDF: an extension of EDF for costly preemption}
 

### 2013-10-07 python-simulation/simulator/drawer/CairoDrawer.py
More abstraction level in Drawer the goal is to have another drawer based on pycairo which will output vectorized picture

@@ -1,0 +1,46 @@
+from simulator.drawer.Drawer import PictureDrawer
+
+import cairo
+
+import math
+
+
+class CairoDrawer(PictureDrawer):
+    def __init__(self, simu, stop):
+        super().__init__(simu, stop)
+
+    def custom_init(self):
+        self.surface = cairo.ImageSurface(cairo.FORMAT_ARGB32, self.width, self.height)
+        self.ctx = cairo.Context(self.surface)
+
+    def black():
+        return (1, 1, 1)
+
+    def grey(self):
+        return (0.6, 0.6, 0.6)
+
+    def drawLine(self, x1, y1, x2, y2, width=1, color=black()):
+        self.ctx.set_source_rgb(color)
+        self.ctx.set_line_width(width)
+        self.ctx.move_to(x1, y1)
+        self.ctx.line_to(x2, y2)
+
+    def greyColor(self, color):
+        return tuple((c // 2 for c in color))
+
+    def drawRectangle(self, x1, y1, x2, y2, fillColor, outlineColor):
+        self.ctx.set_source_rgb(outlineColor)
+        width = x2 - y2
+        height = y2 - y1
+        self.ctx.rectangle(x1, y1, width, height)
+        self.ctx.set_source_rgb(fillColor)
+        self.ctx.fill()
+
+    def drawCircle(self, xC, yC, rad, color):
+        self.ctx.set_source_rgb(color)
+        self.ctx.arc(xC, yC, rad, 0, 2 * math.pi)
+
+    def drawArrow(self, x1, y1, x2, y2, color):
+        self.drawLine(x1, y1, x2, y2, width=2, color=color)
+        r = 2
+        self.drawCircle(x2, y2, r, color)

### 2013-10-07 python-simulation/simulator/drawer/Drawer.py

@@ -25,7 +25,7 @@ class Drawer(object):
         raise NotImplementedError("Drawer: attempted to call abstract method")
 
     def terminate(self):
-        """Called right before displaying results, with no other call in between"""
+        """Called at the end of the simulation"""
         raise NotImplementedError("Drawer: attempted to call abstract method")
 
 
@@ -52,3 +52,4 @@ class EmptyDrawer(Drawer):
 
     def terminate(self):
         pass
+

### 2013-10-07 python-simulation/simulator/drawer/PILDrawer.py

@@ -1,6 +1,4 @@
-from simulator.drawer.Drawer import Drawer
-
-from model import algorithms
+from simulator.drawer.PictureDrawer import PictureDrawer
 
 from PIL import Image as img
 from PIL import ImageFont
@@ -10,122 +8,40 @@ import random
 import re
 
 
-class PILDrawer(Drawer):
+class PILDrawer(PictureDrawer):
     def __init__(self, simu, stop):
         super().__init__(simu, stop)
-        self.instantWidth = 20
-        self.widthMargin = 20
-        self.taskHeight = 50
-        self.heightMargin = 20
-        self.width = stop * self.instantWidth + 2 * self.widthMargin
-        self.height = len(simu.system.tasks) * self.taskHeight + 2 * self.heightMargin
-        self.colors = ["rgb(" + ",".join([str(random.randint(0, 255)) for i in range(3)]) + ")" for j in range(self.simu.m)]
 
+    def custom_init(self):
+        self.colors = ["rgb(" + ",".join([str(random.randint(0, 255)) for i in range(3)]) + ")" for j in range(self.simu.m)]
         self.outImg = img.new("RGB", (self.width, self.height), "white")
         self.fontRoboto = ImageFont.truetype("res/Roboto-Medium.ttf", 9)
         self.outDraw = draw.Draw(self.outImg)
 
-        self.drawGrid(stop)
-        self.drawArrivalsAndDeadlines()
+    def greyColor(self, color):
+        colorRe = re.compile('\d+')
+        rgb = colorRe.findall(color)
+        assert len(rgb) == 3
+        rgb = [int(s) for s in rgb]
+        rgbGrey = [c // 2 for c in rgb]
+        return "rgb(" + ",".join([str(c) for c in rgbGrey]) + ")"
 
-    def getTaskNbr(self, task):
-        taskNbr = None
-        for i, eachTask in enumerate(self.simu.system.tasks):
-            if eachTask is task:
-                taskNbr = i
-                break
-        return taskNbr
+    def drawArrow(self, x1, y1, x2, y2, color):
+        self.drawLine(x1, y1, x2, y2, color=color, width=2)
+        r = 2
+        self.drawCircle(x2, y2, r, color)
 
-    def drawGrid(self, stop):
-        self.outDraw.line([self.widthMargin, self.height - self.heightMargin, self.widthMargin + self.instantWidth * stop, self.height - self.heightMargin], fill="black")
-        # - horizontal lines to separate tasks
[…]

### 2013-10-07 python-simulation/simulator/drawer/PictureDrawer.py

@@ -1,0 +1,131 @@
+from simulator.drawer.Drawer import Drawer
+
+from model import algorithms
+
+
+class PictureDrawer(Drawer):
+    """Abstract Drawer which display a single picture of the execution when it stops"""
+    def __init__(self, simu, stop):
+        super().__init__(simu, stop)
+        self.instantWidth = 20
+        self.widthMargin = 20
+        self.taskHeight = 50
+        self.heightMargin = 20
+        self.width = stop * self.instantWidth + 2 * self.widthMargin
+        self.height = len(simu.system.tasks) * self.taskHeight + 2 * self.heightMargin
+
+        self.custom_init()
+
+        self.drawGrid(stop)
+        self.drawArrivalsAndDeadlines()
+
+    def custom_init(self):
+        """Used to initialize custom drawing libraries and such"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def black():
+        """return a representation of the color black that can be used by methods"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def grey(self):
+        """return a representation of the color black that can be used by methods"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def drawLine(self, x1, y1, x2, y2, width, color):
+        """draw a line between (x1, y1) and (x2, y2) on the final picture"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def drawRectangle(self, x1, y1, x2, y2, fillColor, outlineColor):
+        """draw a rectangle parallel to the axes whose top-left corner is (x1, y1) and bottom-right corner is (x2, y2)"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def drawArrow(self, x1, y1, x2, y2, color):
+        """draw an arrow from (x1, y1) to (x2, y2)"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def getTaskNbr(self, task):
+        taskNbr = None
+        for i, eachTask in enumerate(self.simu.system.tasks):
+            if eachTask is task:
+                taskNbr = i
+                break
+        return taskNbr
+
+    def drawGrid(self, stop):
[…]

### 2013-10-07 python-simulation/paper-paedf/paper-paedf.tex
now with some figs

@@
 
-        Once a previously preempted job is chosen for computation by the scheduling policy, it enters an uninterruptible preemption recovery period.\\
+        Once a previously preempted job is chosen for computation by the scheduling policy, it enters an uninterruptible preemption recovery period, as seen in Fig.~\ref{fig:prp}.\\
 
-        [figure]\\
+        \begin{figure}[h]
+        \begin{center}
+            \includegraphics[width=\textwidth]{figs/atomicpreemption_example.png}
+            \caption{Schedule of a system with $\alpha=2$. At t $t=6$, the preemption recovery period is not interrupted even though a job with higher priority is activated}
+            \label{fig:prp}
+        \end{center}
+        \end{figure}
 
@@
 
-        [figure]\\
+        \begin{figure}[h]
+        \begin{center}
+            \includegraphics{figs/edfNonOptimal_EDF.png}
+            \caption{A system scheduled by EDF where a deadline is missed}
+            \label{fig:edfnonoptimal_edf}
+        \end{center}
+        \end{figure}
 
@@
 
-        [figure]\\
+        \begin{figure}[h]
+        \begin{center}
+            \includegraphics{figs/edfNonOptimal_PALLF.png}
+            \caption{The system of Fig.~\ref{fig:edfnonoptimal_edf} with a different schedule in which no deadline is missed}
+            \label{fig:edfnonoptimal_pallf}
+        \end{center}
+        \end{figure}
 

### 2013-10-08 python-simulation/paper-paedf/paper-paedf.tex
added more example to the article about examples

@@
 \usepackage{graphicx}
+\usepackage{float}
 %\usepackage[section]{placeins}
@@
         We use an extension of Liu and Layland model presented in \cite{Liu:2000:RS:518501} to formalize real-time systems.
-This model represents such systems by a set of \textbf{tasks} generating \textbf{jobs}, where a job is a whole entity of computation with a given time of arrival and a given deadline.\\
+This model represents such systems by a set of \textbf{tasks} generating \textbf{jobs}, where a job is a whole entity of computation with a given time of arrival and a given deadline.
 
@@
 
-        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (which are not synchronous).
+        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (which are not synchronous).\\
+
+        To summarize, Fig.~\ref{fig:rt_ex} shows an example of real-time system in our model.
+
+        \begin{figure}[H]
+        \begin{center}
+            \includegraphics{figs/RTsystem_example.png}
+            \caption{A task system. Annotations will be removed in later figures}
+            \label{fig:rt_ex}
+        \end{center}
+        \end{figure}
 
@@
 
-        The authors of \cite{liu1973scheduling} have shown that the EDF (Earliest Deadline First) scheduling policy, in which jobs are prioritized according to their absolute deadline, is optimal, meaning that any feasible system is schedulable by EDF.\\
+        The authors of \cite{liu1973scheduling} have shown that the EDF (Earliest Deadline First) scheduling policy, in which jobs are prioritized according to their absolute deadline, is optimal, meaning that any feasible system is schedulable by EDF.
 
@@
 
-        \begin{figure}[h]
+        \begin{figure}[H]
         \begin{center}
@@
 
-        Meumeu is FTP-optimal (equivalent to ExhaustiveFTP)
+        The authors of \cite{meumeu2007extending} (TOCHECK) propose an unnamed (we use PA-RMA to refer to it) fixed-priority-optimal scheduling policy for synchronous implicit deadline systems.
 
 \section{Performance of EDF with preemption cost}
-% Rename section to something like "Old results do not old, bitch"
+% Rename section to something like "Old results do not hold, bitch"
 
@@
 
-        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet. This only happens at instant $O_{max} + 4 \cdot H$.\\
+        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet.
+This only happens at instant $O_{max} + 4 \cdot H$, as seen on Fig.~\ref{fig:edf_longtransitive}.\\
 
-        Figure.
+        \begin{figure}[H]
+        \begin{center}
+            \centerline{\includegraphics[width=1.4\textwidth]{figs/longTransitive2_EDF.png}}
+            \caption{Scheduling of a system where the periodic behavior does not happen until $O_{max} + 4 \cdot H$}
+            \label{fig:edf_longtransitive}
+        \end{center}
+        \end{figure}
 
@@
 
-        And consider the following schedule which shows that it is feasible with an idling scheduling policy.
+        And consider the following schedule of fig.~\ref{fig:mustidle_pallf} which shows that it is feasible with an idling scheduling policy.
 
-        [figure]
+        \begin{figure}[H]
+        \begin{center}
+            \includegraphics[scale=0.7]{figs/mustIdle_PALLF.png}
+            \caption{A system scheduled by an idling algorithm. $t=0$ is an idle instant even though a job of $\tau_1$ is active}
+            \label{fig:mustidle_pallf}
+        \end{center}
+        \end{figure}
 
-        However, it is easy to see that no non-idling algorithm can successfully schedule this system: at $t=0$, a non-idling algorithm has to choose between the first job of $\tau_1$ and $\tau_2$ for execution, whichever is chosen will then be preempted by the first job of $\tau_3$ (if not, it will miss its deadline in $t=2$).
-Then, at $t=2$, there will be $3+2+2=7$ units of computation left to compute before the deadline at $t=8$, the system will thus certainly miss a deadline.
+        However, it is easy to see that no non-idling algorithm can successfully schedule this system: at $t=0$, a non-idling algorithm has to choose between $j_{1,1}$ and $j_{2,1}$ for execution, whichever is chosen will then be preempted by $j_{3,1}$ (if not, it will miss its deadline in $t=2$).\\
+
+        Which means that at $t=2$, there will either be \mbox{$(c_{1,1} - 1) +c_{2,1} + \alpha = 7$} or \mbox{$c_{1,1} + (c_{2,1} -1) + \alpha = 7$} units of computation left to compute (including preemptions recovery) before the deadline at $t=8$, the system will thus certainly miss a deadline.
 
@@
 
-        \subsubsection{u < 0.69 is not sufficient}
+        Consider the following system
 
-        \subsubsection{Require Claivoyance}
+        \begin{center}
+            \begin{tabular}{|r|c|c|c|c|c|}
+                \hline
+                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
+                $\tau_1$    & 0     & 4     & 8    & 8     & 1     \\ \hline
+                $\tau_2$    & 0     & 1     & 5    & 8     & 1     \\ \hline
+                $\tau_3$    & 3     & 1     & 1    & 8     & 1     \\ \hline
+                $\tau_4$    & 5     & 1     & 1    & 8     & 1     \\ \hline
+            \end{tabular}
+        \end{center}
 
-        \subsubsection{Preemption can happen anywhere}
+        And a successful schedule of it in Fig.~\ref{fig:dponly_pallf}.
+
+        \begin{figure}[H]
+        \begin{center}
+            \includegraphics[scale=0.7]{figs/dponly_palff.png}
+            \caption{A system scheduled by a dynamic algorithm. The priorities of $j_{1,1}$ and $j_{2,1}$ change between $t=0$ and $t=4$}
+            \label{fig:dponly_pallf}
+        \end{center}
+        \end{figure}
+
+        Furthermore, it can be shown that the schedule of fig.~\ref{fig:dponly_pallf} is the only successful schedule possible.
+However no fixed-priority algorithm (either at the task of the job level) can produce it, which shows that dynamic algorithms are necessary when considering the preemption cost.
+
+        % \subsubsection{$u < 0.69$ is not sufficient}
+
+        \subsubsection{Require clairvoyance}
+
+        Consider the following the following system
+
+        \begin{center}
+            \begin{tabular}{|r|c|c|c|c|c|}
+                \hline
+                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
+                $\tau_1$    & 22    & 2     & 2    & 24    & 1     \\ \hline
+                $\tau_2$    & 0     & 5     & 12   & 12    & 1     \\ \hline
+                $\tau_3$    & 4     & 5     & 6    & 12    & 1     \\ \hline
+                $\tau_4$    & 9     & 1     & 1    & 24    & 1     \\ \hline
+            \end{tabular}
+        \end{center}
+
+        And a successful schedule of it
+
+        \begin{figure}[H]
+        \begin{center}
+            \includegraphics[scale=0.7]{figs/clairvoyance_example.png}
+            \caption{A system scheduled by a clairvoyant algorithm. Different decisions have to be taken at $t=4$ and $t=16$ even though the state of the system is identical}
+            \label{fig:clairvoyance}
+        \end{center}
+        \end{figure}
+
+        \subsubsection{Preemption at non-arrivals}
+
+        As we have shown previously, an optimal algorithm has to update priority of the jobs dynamically.
+This can be very heavy if done at each instant, and one could wonder if updating the priority only at arrivals of job would be sufficient.
+We show by an example that this is not the case.\\
+
+        Consider the following system
+
+        \begin{center}
+            \begin{tabular}{|r|c|c|c|c|c|}
+                \hline
+                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
+                $\tau_1$    & 0     & 3     & 6    & 6     & 1     \\ \hline
+                $\tau_2$    & 3     & 1     & 1    & 6     & 1     \\ \hline
+                $\tau_3$    & 1     & 1     & 3    & 6     & 1     \\ \hline
+            \end{tabular}
+        \end{center}
+
+        And the only valid schedule of it
+
+        \begin{figure}[H]
+        \begin{center}
+            \includegraphics[scale=0.7]{figs/mpana.png}
+            \caption{A valid schedule of a system. Note that the preemption occurs at $t=2$ which is not a job arrival time}
+            \label{fig:mpana}
+        \end{center}
+        \end{figure}
+
+        Indeed, if the preemption of $j_{1,1}$ happens at $t=1$, $j_{3,1}$ will finish its execution at $t=1$ and the instant $t=3$ will be used for a preemption recovery period which will be immediately followed by another preemption, leading to a deadline miss at $t=6$.
+Similarly, if $j_{1,1}$ continues its execution without preemption, either $j_{2,1}$ or $j_{3,1}$ will have to miss its deadline at $t=4$.
+The proposed schedule is thus the only valid and require a priority update at $t=2$.
 

### 2013-10-08 python-simulation/helper/systems.py
brought the cairodrawer to an usable state further drawer refactoring are in the works...

@@ -95,7 +95,7 @@ tasks.append(Task.Task(4, 1, 1, 11))
 tasks.append(Task.Task(6, 4, 11, 11))
 EDFFailTransitiveNotPeriodic = Task.TaskSystem(tasks)
 
-# DPOnly (preemptTime = 1)
+# DPOnly
 tasks = []
 tasks.append(Task.Task(0, 4, 8, 8, alpha=1))
 tasks.append(Task.Task(0, 1, 5, 8, alpha=1))

### 2013-10-08 python-simulation/mainSimu.py

@@ -8,8 +8,8 @@ from helper import systems
 import subprocess
 import sys
 
-# tau = Task.TaskSystem(TaskGenerator.generateTasks(0.7, 3, 33750, 5, 20))
-tau = systems.LongTransitive2
+# tau = Task.TaskSystem(TaskGenerator.generateTasks(0.7, 3, 33750, 5, 20, constrDeadlineFactor=0))
+tau = systems.MustPreemptAtNoArrival
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()
@@ -26,12 +26,12 @@ stop = Omax + 10 * H
 
 print(("stop", stop))
 
-scheduler = Scheduler.EDF(tau)
+# scheduler = Scheduler.EDF(tau)
 # scheduler = Scheduler.SpotlightEDF(tau)
 # scheduler = ChooseKeepEDF.ChooseKeepEDF(tau)
 # scheduler = Scheduler.PTEDF(tau)
 # scheduler = PALLF.PALLF(tau)
-# scheduler = Scheduler.ArbitraryScheduler(tau, systems.mpanaSchedule)
+scheduler = Scheduler.ArbitraryScheduler(tau, systems.mpanaSchedule)
 # scheduler = LBLScheduler.LBLEDF(tau)
 
 # scheduler = Scheduler.FixedPriority(tau, [1, 2, 3])
@@ -55,7 +55,6 @@ except AssertionError:
     raise
 finally:
     if "linux" in sys.platform:
-        simu.drawer.outImg.save("out.png")
-        subprocess.Popen(['shotwell', 'out.png'])
+        subprocess.Popen(['eog', simu.drawer.outputName()])
     elif "win" in sys.platform:
         simu.drawer.outImg.show()

### 2013-10-08 python-simulation/simulator/Simulator.py

@@ -46,8 +46,10 @@ class Simulator(object):  # Global multiprocessing only
         heapify(self.activeJobsHeap)
 
         if drawing:
+            from simulator.drawer import CairoDrawer
             from simulator.drawer import PILDrawer
-            self.drawer = PILDrawer.PILDrawer(self, stop)
+            self.drawer = CairoDrawer.CairoDrawer(self, stop)
+            # self.drawer = PILDrawer.PILDrawer(self, stop)
         else:
             self.drawer = Drawer.EmptyDrawer(self, stop)
 

### 2013-10-08 python-simulation/simulator/drawer/CairoDrawer.py

@@ -1,8 +1,9 @@
-from simulator.drawer.Drawer import PictureDrawer
+from simulator.drawer.PictureDrawer import PictureDrawer
 
 import cairo
 
 import math
+import random
 
 
 class CairoDrawer(PictureDrawer):
@@ -10,37 +11,69 @@ class CairoDrawer(PictureDrawer):
         super().__init__(simu, stop)
 
     def custom_init(self):
-        self.surface = cairo.ImageSurface(cairo.FORMAT_ARGB32, self.width, self.height)
+        self.surface = cairo.SVGSurface("out.svg", self.width, self.height)
         self.ctx = cairo.Context(self.surface)
 
-    def black():
+    def randomColor(self):
+        return tuple((random.random() for i in range(3)))
+
+    def black(self):
+        return (0, 0, 0)
+
+    def white(self):
         return (1, 1, 1)
 
-    def grey(self):
+    def gray(self):
         return (0.6, 0.6, 0.6)
 
-    def drawLine(self, x1, y1, x2, y2, width=1, color=black()):
-        self.ctx.set_source_rgb(color)
+    def blue(self):
+        return (0, 0, 1)
+
+    def red(self):
+        return (1, 0, 0)
+
+    def drawLine(self, x1, y1, x2, y2, width, color):
+        self.ctx.set_source_rgb(*color)
         self.ctx.set_line_width(width)
         self.ctx.move_to(x1, y1)
         self.ctx.line_to(x2, y2)
+        self.ctx.stroke()
 
     def greyColor(self, color):
-        return tuple((c // 2 for c in color))
+        return tuple((c / 2 for c in color))
 
     def drawRectangle(self, x1, y1, x2, y2, fillColor, outlineColor):
-        self.ctx.set_source_rgb(outlineColor)
-        width = x2 - y2
+        self.ctx.set_source_rgb(*outlineColor)
+        width = x2 - x1
         height = y2 - y1
         self.ctx.rectangle(x1, y1, width, height)
-        self.ctx.set_source_rgb(fillColor)
+        self.ctx.stroke_preserve()
+        self.ctx.set_source_rgb(*fillColor)
         self.ctx.fill()
+        # self.ctx.set_source_rgb(*outlineColor)
+        # self.ctx.rectangle(x1, y1, width, height)
 
     def drawCircle(self, xC, yC, rad, color):
-        self.ctx.set_source_rgb(color)
[…]

### 2013-10-08 python-simulation/simulator/drawer/PILDrawer.py

@@ -13,10 +13,12 @@ class PILDrawer(PictureDrawer):
         super().__init__(simu, stop)
 
     def custom_init(self):
-        self.colors = ["rgb(" + ",".join([str(random.randint(0, 255)) for i in range(3)]) + ")" for j in range(self.simu.m)]
         self.outImg = img.new("RGB", (self.width, self.height), "white")
         self.fontRoboto = ImageFont.truetype("res/Roboto-Medium.ttf", 9)
         self.outDraw = draw.Draw(self.outImg)
+
+    def randomColor(self):
+        return "rgb(" + ",".join([str(random.randint(0, 255)) for i in range(3)]) + ")"
 
     def greyColor(self, color):
         colorRe = re.compile('\d+')
@@ -27,21 +29,40 @@ class PILDrawer(PictureDrawer):
         return "rgb(" + ",".join([str(c) for c in rgbGrey]) + ")"
 
     def drawArrow(self, x1, y1, x2, y2, color):
-        self.drawLine(x1, y1, x2, y2, color=color, width=2)
+        self.drawLine(x1, y1, x2, y2, width=2, color=color)
         r = 2
         self.drawCircle(x2, y2, r, color)
 
-    def black():
+    def drawText(self, xT, yT, text, color):
+        self.outDraw.text((xT, yT), str(text), font=self.fontRoboto, fill=color)
+
+    def black(self):
         return "black"
 
-    def grey(self):
+    def white(self):
+        return "white"
+
+    def gray(self):
         return "gray"
 
-    def drawLine(self, x1, y1, x2, y2, width=1, color=black()):
+    def red(self):
+        return "red"
+
+    def blue(self):
+        return "blue"
+
+    def drawLine(self, x1, y1, x2, y2, width, color):
         self.outDraw.line([x1, y1, x2, y2], width=width, fill=color)
 
     def drawRectangle(self, x1, y1, x2, y2, fillColor, outlineColor):
         self.outDraw.rectangle([x1, y1, x2, y2], outline=outlineColor, fill=fillColor)
 
     def drawCircle(self, xC, yC, rad, color):
-        self.outDraw.ellipse([xC - rad, yC - rad, xC + rad, yC + rad], outline="black", fill=color)
+        self.outDraw.ellipse([xC - rad, yC - rad, xC + rad, yC + rad], fill=color)
+
+    def terminate(self):
+        super().terminate()
+        self.outImg.save("out.png")
+
+    def outputName(self):
+        return "out.png"

### 2013-10-08 python-simulation/simulator/drawer/PictureDrawer.py

@@ -7,15 +7,17 @@ class PictureDrawer(Drawer):
     """Abstract Drawer which display a single picture of the execution when it stops"""
     def __init__(self, simu, stop):
         super().__init__(simu, stop)
+        self.colors = [self.randomColor() for j in range(self.simu.m)]
         self.instantWidth = 20
         self.widthMargin = 20
-        self.taskHeight = 50
+        self.taskHeight = 40
         self.heightMargin = 20
         self.width = stop * self.instantWidth + 2 * self.widthMargin
         self.height = len(simu.system.tasks) * self.taskHeight + 2 * self.heightMargin
 
         self.custom_init()
 
+        self.drawRectangle(0, 0, self.width, self.height, self.white(), self.white())
         self.drawGrid(stop)
         self.drawArrivalsAndDeadlines()
 
@@ -23,12 +25,28 @@ class PictureDrawer(Drawer):
         """Used to initialize custom drawing libraries and such"""
         raise NotImplementedError("PictureDrawer: attempted to call abstract method")
 
-    def black():
+    def randomColor(self):
+        """return a random color that can be used by methdos"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def black(self):
         """return a representation of the color black that can be used by methods"""
         raise NotImplementedError("PictureDrawer: attempted to call abstract method")
 
-    def grey(self):
+    def white(self):
         """return a representation of the color black that can be used by methods"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def gray(self):
+        """return a representation of the color gray that can be used by methods"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def red(self):
+        """return a representation of the color red that can be used by methods"""
+        raise NotImplementedError("PictureDrawer: attempted to call abstract method")
+
+    def blue(self):
+        """return a representation of the color blue that can be used by methods"""
         raise NotImplementedError("PictureDrawer: attempted to call abstract method")
 
     def drawLine(self, x1, y1, x2, y2, width, color):
@@ -43,6 +61,14 @@ class PictureDrawer(Drawer):
         """draw an arrow from (x1, y1) to (x2, y2)"""
[…]

### 2013-10-08 python-simulation/mainCspace.py
Made the cspace main script more userfriendly

@@ -1,79 +1,29 @@
+from helper import systems
 from model import Task
-from model import TaskGenerator
 from model import cspace as cs
 from model import algorithms
-import random
-from helper import systems
 
-def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
-    systemArray = []
-    for i in range(numberOfSystems):
-        Umin = 0.25
-        Umax = 0.75
-        Utot = 1.0*random.randint(int(Umin*100), int(Umax*100))/100
-        n = 3
-        maxHyperT = 554400  # PPCM(2, 3, 5, 6, 8, 9, 10, 12, 14, 15, 16, 18, 20, 22, 24, 25, 28, 30, 32)
-        # maxHyperT = -1
-        Tmin = 5
-        Tmax = 20
-        tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
-        if (verbose and numberOfSystems <= 10):
-            print("Generated task system # ", i)
-            for task in tasks:
-                    print("\t", task)
-        systemArray.append(Task.TaskSystem(tasks))
-    return systemArray
 
-tasks = []
-#                      0, C, D, T
-tasks.append(Task.Task(0, 1, 6, 8))
-tasks.append(Task.Task(0, 1, 12, 13))
-tau = Task.TaskSystem(tasks)
+# tasks = []
+# tasks.append(Task.Task(O, C, D, T))
+# tasks.append(Task.Task(O, C, D, T))
+# tau = Task.TaskSystem(tasks)
+
+tau = systems.Meumeu
+
 print(tau)
-tau_Cspace = cs.Cspace(tau)
-tau_Cspace_noredun = tau_Cspace.removeRedundancy(verbose=True)
-
-print("FINAL CSPACE")
-for cstr in tau_Cspace_noredun:
+print("cspace...")
+cspace = cs.Cspace(tau)
+print("found ", len(cspace), "constraints")
+print("remove redun...")
+cspace_noredun = cspace.removeRedundancy()
+print(len(cspace), "=>", len(cspace_noredun), "constraints left")
+for cstr in cspace_noredun:
     print(cstr)
-print(len(tau_Cspace), "=>", len(tau_Cspace_noredun), "constraints left")
-
-# tasks = []
[…]

### 2013-10-08 python-simulation/model/cspace.py

@@ -158,8 +158,8 @@ class CSpaceConstraint(object):  # TODO : make the code use this lovely class
         self.t = t
 
     def __repr__(self):
-        reprStr = "+ ".join([str(a) + "*x" + str(i+1) + '\t' for i, a in enumerate(self.coeffs)])
-        reprStr += " <= " + str(self.t)
+        reprStr = "\t+\t".join([str(a) + "\tx" + str(i+1) for i, a in enumerate(self.coeffs)])
+        reprStr += "\t<=\t" + str(self.t)
         return reprStr
 
     def isRedundant(self, cspace):

### 2013-10-09 python-simulation/simulator/scheduler/Scheduler.py
Added LLF algorithm (finally)

@@ -30,6 +30,20 @@ class SchedulerDP(object):
         return myAlgebra.nextPeriodic(t, task.T, task.O)
 
 
+class LLF(SchedulerDP):
+    def __init__(self, tau):
+        super().__init__(tau)
+        self.prioOffset = max([task.C for task in tau.tasks]) + 1
+        self.tau = tau
+
+    def priority(self, job, simu):
+        slackTime = max(0, job.deadline - (simu.t + job.computationLeft()))
+        return 1 / (self.prioOffset + slackTime)
+
+    def preemptEqualPriorities(self):
+        return False
+
+
 class PTEDF(SchedulerDP):
     def __init__(self, tau):
         super().__init__(tau)

### 2013-10-09 python-simulation/mainSimu.py
new versions of main integrating LLF

@@ -8,8 +8,8 @@ from helper import systems
 import subprocess
 import sys
 
-# tau = Task.TaskSystem(TaskGenerator.generateTasks(0.7, 3, 33750, 5, 20, constrDeadlineFactor=0))
-tau = systems.EDFNonOptimal
+tau = Task.TaskSystem(TaskGenerator.generateTasks(0.7, 3, 33750, 5, 20, constrDeadlineFactor=0))
+# tau = systems.EDFNonOptimal
 
 Omax = max([task.O for task in tau.tasks])
 H = tau.hyperPeriod()
@@ -26,7 +26,8 @@ stop = Omax + 4 * H
 
 print(("stop", stop))
 
-scheduler = Scheduler.EDF(tau)
+# scheduler = Scheduler.EDF(tau)
+scheduler = Scheduler.LLF(tau)
 # scheduler = Scheduler.SpotlightEDF(tau)
 # scheduler = ChooseKeepEDF.ChooseKeepEDF(tau)
 # scheduler = Scheduler.PTEDF(tau)

### 2013-10-09 python-simulation/mainSimuComp.py

@@ -1,7 +1,7 @@
 from model import algorithms
 from model import Task, TaskGenerator
 from simulator import Simulator
-from simulator.Scheduler import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
+from simulator.scheduler import Scheduler, ChooseKeepEDF, PALLF, LBLScheduler
 from helper import systems
 
 import random
@@ -12,7 +12,7 @@ domin_scores = {}
 results = {}
 NUMBER_OF_SYSTEMS = 100
 uRange = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]
-schedulers = [Scheduler.EDF, Scheduler.PTEDF]
+schedulers = [Scheduler.LLF, Scheduler.PTEDF]
 names = ["EDF", "PA-EDF"]
 
 failures = []

### 2013-10-09 python-simulation/paper-paedf/paper-paedf.tex
added an introduction to the PA-EDF section
preliminary description of PA-EDF

@@
 
-        The results presented in this section use the assumption that preemption times are negligible.\\
+        The results presented in this section assumes that preemption times are negligible.\\
 
         We use an extension of Liu and Layland model presented in \cite{Liu:2000:RS:518501} to formalize real-time systems.
-This model represents such systems by a set of \textbf{tasks} generating \textbf{jobs}, where a job is a whole entity of computation with a given time of arrival and a given deadline.
+This model represents such systems by a set of \textbf{tasks} $\tau = \{\tau_1, \cdots, \tau_n\}$ generating \textbf{jobs}, where a job is an entity of computation with a given arrival time, execution time and deadline.
 
@@
 
-        A task $\tau_i$ generates jobs, denoted as the tuple $J_{i,j} = (a_{i, j}, d_{i,j}, c_{i,j})$ where :
+        A task $\tau_i$ generates jobs, denoted as the tuple $j_{i,j} = (a_{i, j}, d_{i,j}, c_{i,j})$ where :
         \begin{itemize}
@@
 
-        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (which are not synchronous).\\
+        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (which are not synchronous).
+For synchronous systems, we assume without loss of generality that $O_i = 0 \; \forall i$.\\
 
@@
             \includegraphics{figs/RTsystem_example.png}
-            \caption{A task system. Annotations will be removed in later figures}
+            \caption{A task system, with our notation highlighted}
             \label{fig:rt_ex}
@@
 
-        A scheduling policy (or \emph{algorithm}) is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are released and unfinished jobs present in the system.
-It is said to be \textbf{preemptive} if it allows the processor to begin computation of a new job when the currently computed job is still unfinished.\\
+        A scheduling policy (or \emph{algorithm}) is...\\
+
+        A scheduling policy is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are active (i.e.
+released and unfinished) jobs present in the system.
+Such instants are then called \textbf{idled instants}.
+They are not to be confused with \emph{idle times}, another important concept in feasibility analysis which is not discussed here.\\
+
+        A scheduling policy is said to be \textbf{preemptive} if it allows the processor to begin computation of a new job when the currently computed job is still unfinished.\\
 
@@
             \includegraphics[width=\textwidth]{figs/atomicpreemption_example.png}
-            \caption{Schedule of a system with $\alpha=2$. At t $t=6$, the preemption recovery period is not interrupted even though a job with higher priority is activated}
+            \caption{EDF schedule of a system with $\alpha=2$. At t $t=6$, the preemption recovery period is not interrupted even though a job with higher priority is activated}
             \label{fig:prp}
@@
 
-    In this section, we show that the EDF scheduling policy, optimal when the preemption costs are negligible, is less adapted to our model with costly preemptions.
+    In this section, we show that the EDF scheduling policy, optimal when the preemption costs are negligible, loses this property in our model with costly preemptions.
 
@@
 
+        A property of EDF in systems where preemptions costs are negligible is that it does not require knowledge of future arrivals of jobs (or \textbf{clairvoyance}).
+This allows EDF to also be an optimal scheduler for \emph{sporadic} systems, where the period of a task is the \emph{minimal} time between two consecutive arrival of its jobs.
+We now show that an optimal scheduler for our model would not have that property.\\
+
         Consider the following the following system
@@
 
+    In previous sections, we have shown that EDF is not optimal when including preemption costs.
+To the best of our knowledge, there is no known optimal algorithm in that case.
+This section presents an algorithm which, while not being optimal, is an improvement over the EDF algorithm.
+
+    \subsection{Idling behavior}
+
+        While we have shown by example that idling may sometimes be necessary, an efficient scheduling algorithm has to minimize the number of idled units, as each idled unit is a lost unit when considering the execution of the jobs (they can be seen as an increase of the load of the system).
+For this reason, we propose in this section a general method to determine if an idled unit is beneficial.\\
+
+        Idled units are a direct consequence of the preemption recovery period, which means that each preemption increased the load of the system by $\alpha$ time unit.
+The intuition is thus that if we idle for a duration $d < \alpha$ to prevent a preemption, the resulting load increase would be smaller, and the idled unit would then be beneficial.
+The sequel express this intuition in formal terms.\\
+
+        We define the \textbf{earliest preemptive arrival of a job} $epa(j_{i,j}, t)$ as the earliest arrival strictly after $t$ of another job with higher priority.
+Similarly, the \textbf{minimal termination time } $mtt(j_{i,j}, t)$ of a job is the instant at which the job will end if it was given maximal priority at time $t$.
+An idled unit is then beneficial at time $t$ if, for each active job $j_{i,j}$ we have
+        \begin{itemize}
+            \item $j_{i,j}$ was not executing at time $t-1$
+            \item it will certainly be preempted: $epa(j_{i,j}, t) < mtt(j_{i,j}, t)$
+            \item this preemption will add more load than idling would: $epa(j_{i,j}, t) - t < \alpha$
+        \end{itemize}
+
+        The main setback of this approach is that it remains to find an accurate method to compute the \emph{epa} values.
+
+    \subsection{Limiting preemptions}
+
+        As we saw, each preemption adds $\alpha$ time units to the load of the system.
+Limiting the number of preemptions, i.e.
+detecting and preventing unnecessary preemptions, is thus an efficient behavior of a scheduling algorithm.\\
+
+        A preemption is not necessary at instant $t$ when job $j_{i,j}$ was executing at instant $t-1$ and is not finished if:
+        \begin{itemize}
+            \item every other active job has a laxity equal or smaller than $mtt(j_{i,j}, t)$
+            \item this property holds for every job arriving before the next idle time.
+        \end{itemize}
+
+        The main setback is that it remains to find an accurate method to find idle times in our model.
+
 \nocite{*}

### 2013-10-09 python-simulation/mainSimuComp.py
added failure gathering

@@ -42,9 +42,9 @@ def oneTest(utilization):
 
 domin_scores = {}
 scores = {}
-NUMBER_OF_SYSTEMS = 100
+NUMBER_OF_SYSTEMS = 1
 uRange = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0]
-schedulers = [Scheduler.EDF, PALLF.PALLF]
+schedulers = [Scheduler.EDF, Scheduler.PTEDF]
 names = ["EDF", "PA-EDF"]
 
 failures = []
@@ -71,6 +71,8 @@ for f in futures:
                 otherSuccess = otherSuccess or success[otherSched]
             if success[sched] and not otherSuccess:
                 domin_scores[u][sched] += 1
+    if success[schedulers[1]] and not success[schedulers[0]]:
+        failures.append(tau)
 
 
 with open("mainSimuComp_results.pickle", "wb") as output:

### 2013-10-09 python-simulation/paper-paedf/paper-paedf.tex
finished PA-EDF chapter (somewhat)

@@
 \usepackage{float}
+\usepackage{theorem}
+\usepackage{algorithm}
+\usepackage[noend]{algorithmic}
 %\usepackage[section]{placeins}
+
+\newtheorem{theorem}{Theorem}
 
@@
 
-    \subsection{Idling behavior}
+    \subsection{Algorithm}
+
+    \subsubsection{Limiting preemptions}
+    \label{sct:limPreemp}
+
+        As we saw, each preemption adds $\alpha$ time units to the load of the system.
+Limiting the number of preemptions, i.e.
+detecting and preventing unnecessary preemptions, is thus an efficient behavior of a scheduling algorithm.\\
+
+        \begin{theorem}
+            \label{the:limPreemp}
+            A preemption is not necessary at instant $t$ when job $j_{i,j}$ was executing at instant $t-1$ if:
+            \begin{itemize}
+                \item every other active job has a laxity equal or smaller than $c_{i,j}^{LEFT}$
+                \item this property holds for every job arriving before the next idle time.
+            \end{itemize}
+            where $c_{i,j}^{LEFT}$ is the remaining execution time of job $j_{i,j}$.
+        \end{theorem}
+
+        The main setback is that it remains to find an accurate method to find idle times in our model.
+Also, if the condition is not fulfilled, we cannot know if a preemption would really be beneficial (EXAMPLE?).
+
+    \subsubsection{Idling behavior}
+    \label{sct:idlBehav}
 
@@
         Idled units are a direct consequence of the preemption recovery period, which means that each preemption increased the load of the system by $\alpha$ time unit.
-The intuition is thus that if we idle for a duration $d < \alpha$ to prevent a preemption, the resulting load increase would be smaller, and the idled unit would then be beneficial.
-The sequel express this intuition in formal terms.\\
+The intuition is thus that if we idle for a duration $d < \alpha$ to prevent a preemption, the resulting load increase would be smaller, and the idled unit would then be beneficial.\\
 
-        We define the \textbf{earliest preemptive arrival of a job} $epa(j_{i,j}, t)$ as the earliest arrival strictly after $t$ of another job with higher priority.
-Similarly, the \textbf{minimal termination time } $mtt(j_{i,j}, t)$ of a job is the instant at which the job will end if it was given maximal priority at time $t$.
-An idled unit is then beneficial at time $t$ if, for each active job $j_{i,j}$ we have
-        \begin{itemize}
-            \item $j_{i,j}$ was not executing at time $t-1$
-            \item it will certainly be preempted: $epa(j_{i,j}, t) < mtt(j_{i,j}, t)$
-            \item this preemption will add more load than idling would: $epa(j_{i,j}, t) - t < \alpha$
-        \end{itemize}
+        Theorem~\ref{the:limPreemp} gave us a method to determine if a preemption was necessary at a given instant.
+Note that if the condition is not fulfilled and the busy job continues executing, the condition will stay unfulfilled at later instant.
+We use it to give the following idling condition.
 
-        The main setback of this approach is that it remains to find an accurate method to compute the \emph{epa} values.
+        \begin{theorem}
+            An active job $j_{i,j}$ at idle instant $t$ is eligible for execution if, according to theorem~\ref{the:limPreemp}, a preemption will not be necessary at instant $t + \alpha$ if it is chosen at instant $t$.
+        \end{theorem}
 
-    \subsection{Limiting preemptions}
+        If every active job is not eligible for execution, it is better to idle.
 
-        As we saw, each preemption adds $\alpha$ time units to the load of the system.
-Limiting the number of preemptions, i.e.
-detecting and preventing unnecessary preemptions, is thus an efficient behavior of a scheduling algorithm.\\
+    \subsubsection{Job priority}
 
-        A preemption is not necessary at instant $t$ when job $j_{i,j}$ was executing at instant $t-1$ and is not finished if:
-        \begin{itemize}
-            \item every other active job has a laxity equal or smaller than $mtt(j_{i,j}, t)$
-            \item this property holds for every job arriving before the next idle time.
-        \end{itemize}
+        Our algorithm is a dynamic algorithm which computes a priority $p(j_{i,j}, t)$ for each job at each instant.
+We consider that if the most prioritary job has a priority inferior to 0, it is better to idle.
 
-        The main setback is that it remains to find an accurate method to find idle times in our model.
+        \begin{algorithm}[H]
+            \begin{algorithmic}[1]
+                \IF{$t$ is an idle instant}
+                    \IF{$j_{i,j}$ would be preempted at $t + \alpha$ (see Algo.~\ref{alg:PAEDFpreemp})}
+                        \RETURN $- \infty$
+                    \ELSE
+                        \RETURN $1 / d_{i,j}$
+                    \ENDIF
+                \ELSIF{$j_{i,j}$ is a busy job}
+                    \IF {$j_{i,j}$ must be preempted now (see Algo.~\ref{alg:PAEDFpreemp})}
+                        \RETURN $- \infty$
+                    \ELSE
+                        \RETURN 1
+                    \ENDIF
+                \ENDIF
+                \RETURN $1 / d_{i,j}$
+            \end{algorithmic}
+                \caption{Priority of job $j_{i,j}$ at time $t$ with PA-EDF}
+                \label{alg:prio}
+            \end{algorithm}
+
+        The algorithm follows the conclusion of sections \ref{sct:limPreemp} and \ref{sct:idlBehav}. To determine if a preemption is necessary at instant $t$, it uses Algorithm~\ref{alg:PAEDFpreemp}.
+
+        \begin{algorithm}[H]
+            \begin{algorithmic}[1]
+            \STATE cumulCompLeft $\leftarrow$ compLeft($j$)
+            \FORALL {active jobs $j'$ s.t. $j'.deadline \leqslant j.deadline$}
+                \IF {$j'$ was preempted}
+                    \STATE lax $\leftarrow j'.deadline - t - j'.compLeft$ - $\alpha_j'$
+                \ELSE
+                    \STATE lax $\leftarrow j'.deadline - t - j'.compLeft$
+                \ENDIF
+                \IF {lax $<$ cumulCompLeft}
+                    \RETURN True
+                \ELSE
+                    \STATE cumulCompLeft += compLeft($j'$)
+                \ENDIF
+            \ENDFOR
+            \RETURN False
+            \end{algorithmic}
+                \caption{Should job $j$ be preempted at time $t$?}
+                \label{alg:PAEDFpreemp}
+            \end{algorithm}
+
+        Note that this is not an exact algorithm, but it has an $O(n)$ complexity.\\
+
+    \subsection{Example}
+
+        Fig.~\ref{fig:paedf_example} gives an example of the following system scheduled by PA-EDF
+
+        \begin{center}
+            \begin{tabular}{|r|c|c|c|c|c|}
+                \hline
+                            & $O_i$ & $C_i$ & $D_i$ & $T_i$ & $\alpha_i$ \\ \hline
+                $\tau_3$    & 0     & 26    & 45    & 45    & 2     \\ \hline
+                $\tau_2$    & 2     & 3     & 20    & 20    & 2     \\ \hline
+                $\tau_1$    & 0     & 1     & 12    & 12    & 2     \\ \hline
+            \end{tabular}
+        \end{center}
+
+        \begin{figure}[H]
+        \begin{center}
+            \centerline{\includegraphics[scale=0.6]{figs/PAEDF_example.png}}
+            \caption{Example of a system scheduled by PA-EDF}
+            \label{fig:paedf_example}
+        \end{center}
+        \end{figure}
+
+        Note that at $t=2$, the algorithm anticipates the arrival of $j_{2,1}$ at $t=3$ and thus correctly schedules an idle instant.
+Between $t=22$ and $t=24$, $j_{3,1}$ continues its execution when EDF would have caused a preemption.
+At $t=12$, however, the algorithm detects that a preemption is necessary.
 
 \nocite{*}
-\bibliographystyle{plain}
+\bibliographystyle{amsalpha}
 \bibliography{paper-paedf}

### 2013-10-09 python-simulation/mainH_VS_DIT.py
Renamed main to make place for a true main

@@ -3,7 +3,7 @@ import random
 
 import pylab  # http://matplotlib.org/
 
-from model.Task import Task, TaskGenerator
+from model import Task, TaskGenerator
 from model import algorithms
 from functools import reduce
 
@@ -21,7 +21,7 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, verbose=False):
         Tmax = 25
         tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
         if (verbose and numberOfSystems <= 10):
-            print(("Generated task system # ", i))
+            print("Generated task system # ", i)
             for task in tasks:
                     print(("\t", task))
         systemArray.append(Task.TaskSystem(tasks))
@@ -80,19 +80,19 @@ def test(numberOfSystems, constrDeadlineFactor):
     for i in range(len(systemArray)):
         assert ditResults[i] == hyperTResults[i]
 
-    print(("== Test Results (on " + str(numberOfSystems) + " tasks system)"))
+    print("== Test Results (on " + str(numberOfSystems) + " tasks system)")
     if (verbose and len(systemArray) <= 10):
         for i in range(len(systemArray)):
-            print(("=== System", i))
-            print(("\tbusy period:", busyPeriods[i]))
-            print(("\tfirst DIT:", firstDITs[i]))
-            print(("\tPPCM:", hyperTs[i]))
+            print("=== System", i)
+            print("\tbusy period:", busyPeriods[i])
+            print("\tfirst DIT:", firstDITs[i])
+            print("\tPPCM:", hyperTs[i])
     print("\tAlgorithms performance (upper limit computation + dbf test)")
-    print(("\t\tTime with busy period:", bpMedium - bpStart, "+", bpStop - bpMedium, " = ", bpStop - bpStart, "s"))
-    print(("\t\tTime with DIT:", ditMedium - ditStart, "+", ditStop - ditMedium, " = ", ditStop - ditStart, "s"))
-    print(("\t\tTime with hyperT:", hyperTMedium - hyperTStart, "+", hyperTStop - hyperTMedium, " = ", hyperTStop - hyperTStart, "s"))
[…]

### 2013-10-11 ideas_lipari/ideas_lipari.tex
One-paged LaTeX file for one line of text

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage{listings}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{theorem}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
%\usepackage[section]{placeins}

\newtheorem{property}{Property}
\newtheorem{assumption}{Assumption}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\newtheorem{constraint}{Constraint}
\newtheorem{corollary}{Corollary}
\newtheorem{condition}{Condition}
\newcommand{\dbf}[1]{\operatorname{dbf}(#1)}

\definecolor{grey}{rgb}{0.9,0.9,0.9}

\lstset{
language=Python,
basicstyle=\footnotesize\fontfamily{pcr},
backgroundcolor=\color{grey},
numbers=left,
numberstyle=\tiny,
numbersep=5pt,
showstringspaces=false,
tabsize=2,
breaklines=true
}

\setlength{\parindent}{0pt}

\title{Removing Redundancy in the Set of Constraints given by the DBF Test for Asynchronous Periodic System with Constrained Deadlines}
\author{Thomas Chapeaux}
\date{Summer 2013}
%opening
\sloppy
\begin{document}
\maketitle

\tableofcontents

% \newpage

% \begin{abstract}

% \end{abstract}

\newpage

\section{The DBF test}

Let $\tau$ be a set of tasks $\tau_i = (O_i, C_i, D_i, T_i)$ where $D_i \leqslant T_i$.

\begin{definition}
    The \textbf{demand-bound function (DBF)}
    defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
    equal to the cumulated execution time of jobs of $\tau$ contained in the
    closed interval $[t_1, t_2]$.
\end{definition}

Mathematically,
\begin{equation}
    \dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
\end{equation}
where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
and deadlines are both in the closed interval $[t_1, t_2]$.\\

The values of the $n_i$ are given by
\begin{equation}
    n_i(t_1, t_2) = \max
    \left( 0,
        \left\lfloor
            \frac{t_2 - O_i - D_i}{T_i}
        \right\rfloor -
        \left\lceil
            \frac{t_1 - O_i}{T_i}
        \right\rceil + 1
    \right)
\end{equation}

We have the following property

\begin{theorem}
    \label{theo:DBFtest}
    \begin{equation*}
        \begin{array}{c}
            \tau \: \text{is feasible}  \iff
            \dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1, t_2 \mid  0 \leq t_1 \leq t_2
        \end{array}
    \end{equation*}
\end{theorem}

However this theorem require to check the condition for an infinite number of intervals. As it turns out, only a small fraction of those conditions are necessary.

\section{Removing redundancy}

    \subsection{State of the art}

Based on previous results, we know that it is not necessary to check the condition of Theorem~\ref{theo:DBFtest} for intervals
\begin{itemize}
    \item where $t_2 > O_{max} + 2 \cdot H$
    \item where $t_1$ is not an arrival time or $t_2$ is not a deadline
\end{itemize}

Furthermore, if there is a periodic DIT at instant $t_d < O_{max} + H$, it is sufficient to check the condition for intervals such that $t_d \leqslant t_1 < t_2 \leqslant t_d + H$.\\

This already reduce the size of the set of conditions to test to a manageable size. However, in most cases there
is still redundancy in the set of conditions after applying those results, which can causes a loss of efficiency. Further analytical detection of redundancy is thus required.

    \subsection{Separation by DIT}

If there is another DIT $t_{d'}$ such that $t_d < t_{d'} < t_d + H$, then it is not necessary to check the condition in intervals where $t_1 < t_{d'} < t_2$.\\

This require to computation of every DIT modulo $H$.

% \nocite{*}
% \bibliographystyle{amsalpha}
% \bibliography{paper-paedf}

\end{document}

### 2013-10-11 python-simulation/model/algorithms.py
added Lipari's idea to calculate DIT value

@@ -35,6 +35,24 @@ def YAfindFPDIT(tau):
     return None
 
 
+def LIPARIfindFPDIT(tau):
+    omax = tau.omax()
+    H = tau.hyperPeriod()
+    arrivals = {}
+    deadlines = {}
+    for task in tau.tasks:
+        arrivals[task] = task.O
+        deadlines[task] = task.O + task.D
+    aMin = 0
+    while(aMin <= omax + H):
+        d_next, task_d_next = min([(task.D, task) for task in tau.tasks])
+        arrivals[task_d_next] += task_d_next.T
+        aMin = min([arrivals[task] for task in tau.tasks])
+        if aMin >= d_next:
+            return d_next
+    return None
+
+
 def findFirstPeriodicDIT(tau):
     # Requires to solve several system of modular equations
 

### 2013-10-11 python-simulation/model/cspace.py
Constraints now know the exact [a,d] interval which yielded it (and print it)

@@ -35,7 +35,7 @@ class Cspace(object):
             # for each arrival and each deadline, create an equation
             self.constraints = []
             for a, d in tau.dbf_intervals(lowerLimit, upperLimit):
-                constraint = CSpaceConstraint([algorithms.completedJobCount(t, a, d) for t in tau.tasks], d - a)
+                constraint = CSpaceConstraint([algorithms.completedJobCount(t, a, d) for t in tau.tasks], a, d)
                 self.constraints.append(constraint)
 
     def __getitem__(self, key):
@@ -152,14 +152,17 @@ def testCVector(cspace, cvector):
     return True
 
 
-class CSpaceConstraint(object):  # TODO : make the code use this lovely class
-    def __init__(self, coeffs, t):
+class CSpaceConstraint(object):
+    def __init__(self, coeffs, a, d):
         self.coeffs = coeffs
-        self.t = t
+        self.a = a
+        self.d = d
+        self.t = d - a
 
     def __repr__(self):
         reprStr = "\t+\t".join([str(a) + "\tx" + str(i+1) for i, a in enumerate(self.coeffs)])
         reprStr += "\t<=\t" + str(self.t)
+        reprStr += "\t[" + str(self.a) + ", " + str(self.d) + "]"
         return reprStr
 
     def isRedundant(self, cspace):

### 2013-10-11 python-simulation/paper-paedf/paper-paedf.tex
Renamed main to make place for a true main
Corrections by L.G.

@@
 
-\title{Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor periodic systems}
+\title{Improving success ratio of EDF when taking into account the preemption cost in uniprocessor periodic systems}
 \author{Thomas Chapeaux}
@@
         \end{itemize}
-
+h
         We also assume a discrete time, meaning that we consider that time passes one unit (sometimes called \emph{clock tick}) at a time.
@@
 
-        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (which are not synchronous).
+        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (general case of unconstrained offset).
 For synchronous systems, we assume without loss of generality that $O_i = 0 \; \forall i$.\\
@@
 
-        \subsubsection{Feasibility Analysis}
+        \subsubsection{Feasibility Analysis with no preemption cost}
+
+        % TODO: add reference to cyclic idles times
 
@@
     \subsection{Preemption Cost}
+
+        % TODO : présenter différents modèles et justifier celui qu'on utilise
 
@@
 
-    \subsection{Non-optimality}
+    \subsection{Non-optimality of EDF}
 
@@
 
-    \subsection{Anomalies}
+    \subsection{Scheduling anomalies w.r.t. the state of the art}
+
+        % TODO: Introduction
 
@@
 
-        \subsubsection{Deadline miss in transitive, not in periodic}
+        \subsubsection{Deadline miss in transient, not in permanent}
 
     \subsection{Other properties of constrained deadline systems}
+
+    % TODO: présenter les résultats sous forme de Lemmes
 
@@
         \subsubsection{Dynamic dominate fixed-job}
+        % TODO: expliquer dynamic et fixed-priority job in the introduction
 
@@
 
-\section{PA-EDF: an extension of EDF for costly preemption}
+\section{PA-EDF: an extension of EDF with preemption cost}
+
+    %TODO : comparer avec les approches de limited preemptions (Marko Bertogna)
+    %TODO : Introduire la notion d'alpha-horizon
+    %TODO : essayer un algorithme "exhaustif" sur base de cet horizon
 

### 2013-12-16 beamer/dit-paper-presentation.tex
further modification to lowercase stuff
SBESC version of DIT paper presentation

@@
   \begin{block}{Real-Time Systems}
-  Systems with real-time constraints. (e.g. ABS, VOD, etc)
+  Systems with timeliness constraints. (e.g. ABS, VOD, etc)
   \end{block}
@@
       \item $O_i$ : arrival of the first job
-      \item $C_i$ : execution time
+      \item $C_i$ : worst-case execution time (WCET)
       \item $D_i$ : relative deadline
@@
 
-        \begin{block}{Feasibility by a scheduling policy}
-        A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
-        \end{block}
+        % \begin{block}{Feasibility by a scheduling policy}
+        % A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
+        % \end{block}
 
-        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is EDF-schedulable.
+        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is correctly scheduled by EDF.
 	\end{frame}
@@
         \begin{itemize}
-            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints
-            \item An efficient description allows us to quickly  whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
+            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints on the $C_i$.
+            \item An efficient description allows us to decide whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
         \end{itemize}
@@
         baruah1990algorithms}
-            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
+            of a task set $\tau$, denoted $\dbf{t_1, t_2}$, is
             the maximal cumulated execution time of jobs of $\tau$ contained in the
@@
         $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
-        where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
-        and deadlines are both in the closed interval $[t_1, t_2]$.
+        where $n_i(t_1, t_2)$ is the number of jobs of $\tau_i$ in the interval $[t_1, t_2]$.
 
@@
     \begin{itemize}
-        \item Every constraint is linear in the $C_i$ values
-        \item Every constraint is necessary
-        \item Their conjunction is sufficient
+        \item Every constraint is linear in the $C_i$ values.
+        \item We have an infinite number of constraints!
+        \item Every constraint is a necessary condition of feasibility.
+        \item Their conjunction is a sufficient condition of feasibility.
         % \pause
-        \item But we have an infinite number of constraints!
-        \item $\Rightarrow$ Removing redundancy
+        \item $\Rightarrow$ We must find a way of removing redundancies in the constraints.
     \end{itemize}
@@
 
-    \begin{frame}{Removing redundancy for synchronous system}
+    \begin{frame}{Removing redundancy for synchronous systems}
 
@@
         \item Introduce the notion of \textbf{first periodic DIT (FPDIT)} as a generalization of the notion of DIT
-        \item Provide an algorithm to find an efficient description of the C-space for any periodic system
+        \item Provide an algorithm to find an efficient description of the C-space for any periodic constrained deadline systems
         \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
@@
     \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
-        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by:
+        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by :
 
@@
         \]
+		The CRP is then solved by constructing an equivalent system with pairwise co-prime moduli.\\
 
-        Then each equation $t_d \equiv x \; (\operatorname{mod} \; p)$ with $p = p_1^{b_1} \cdots p_k^{b_k}$ (where each $p_i$ is prime), can be replaced by the system:
+		~\\
 
-       \[
-            \begin{array}{l}
-                \left\{
-                    \begin{array}{l}
-                         t_d \equiv x \; (mod \; p_1^{b_1}) \\
-                         \cdots \\
-                         t_d \equiv x \; (mod \; p_k^{b_k})
-                    \end{array}
-                \right.
-            \end{array}
-        \]
+		In the asynchronous case, it is thus possible to have systems where no FPDIT exists.
+        %Then each equation $t_d \equiv x \; (\operatorname{mod} \; p)$ with $p = p_1^{b_1} \cdots p_k^{b_k}$ (where each $p_i$ is prime), can be replaced by the system:
 
-        Equations with the same $p_i$ can be replaced by only the one of highest $b_i$. The new system now has pairwise co-prime moduli.
+       %\[
+       %     \begin{array}{l}
+       %         \left\{
+       %             \begin{array}{l}
+       %                  t_d \equiv x \; (mod \; p_1^{b_1}) \\
+       %                  \cdots \\
+       %                  t_d \equiv x \; (mod \; p_k^{b_k})
+       %             \end{array}
+       %         \right.
+       %     \end{array}
+       % \]
+
+        %Equations with the same $p_i$ can be replaced by only the one of highest $b_i$. The new system now has pairwise co-prime moduli.
 
@@
 
-\section{C-space of asynchronous system}
+\section{C-space of asynchronous systems}
 
@@
         \begin{itemize}
-            \item Every constraint is necessary
-            \item Their conjunction is sufficient
+            \item Every constraint is a necessary condition.
+            \item Their conjunction is a sufficient condition.
             \item Most of them are redundant.
@@
     \subsection{Removing redundancies}
-
-    \begin{frame}{Redundancy as an ILP (I)}
-
-    We can define the redundancy of a linear constraint $C \cdot X \leqslant d$ with regards to a set of $k$ linear constraints $A \cdot X \leqslant B$ as the following Integer Linear Problem (ILP):
-
-    \begin{columns}[c]
-        \column{0.1\textwidth}
-        \column{0.3\textwidth}
-
-        \begin{block}{Redundancy ILP}
-
-        \begin{center}
-        $z = \max \left( C \cdot X \right)$
-
-        s.t.
-
-        $
-        \begin{array}{rcc}
-          A \cdot X &\leq & B \\
-          C \cdot X &\leq & d + 1
-        \end{array}
-        $
-        \end{center}
-
-        \end{block}
-
-        \column{0.1\textwidth}
-
-        \column{0.5\textwidth}
-
-        \begin{center}with\end{center}
-        \[
-          \begin{array}{ccc}
-            A & : & [n,k] \text{ matrix}\\
-            B \; \text{and} \; C & : & [n,1] \text{ matrix}\\
-            X & : & [1,n] \text{ matrix}\\
-            d & : & \text{integer}
-          \end{array}
-        \]
-    \end{columns}
-        \begin{itemize}
-            \item If $z = d + 1$, the constraint is redundant
-            % \item Can be solved with a branch-and-bound approach
-            \item Complexity (one test): exponential in the size of the set
-            \item Each constraint of the set must be tested
-        \end{itemize}
-
-    \end{frame}
-
-    \begin{frame}{Redundancy as an ILP (II)}
-
-        \begin{algorithm}[H]
-            \caption{Removing redundant constraints}
-            \label{alg:pruneCspace}
-          \begin{algorithmic}[1]
-            \STATE $CSPACE$ : set of constraints
-            \STATE $S \leftarrow \emptyset$
-            \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
-            \FOR{$cstr$ \textbf{in} $CSPACE$}
-              \IF {$cstr$ is not redundant w.r.t. $S$}
-                \STATE $S.push(cstr)$
-              \ENDIF
-            \ENDFOR
-            \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
-            \FOR{$cstr$ \textbf{in} $S$}
-              \STATE $cstr$ = $S.pop()$
-              \IF {$cstr$ is not redundant w.r.t. $S$}
-                \STATE $S.push(cstr)$
-              \ENDIF
-            \ENDFOR
-            \RETURN{S}
-            \end{algorithmic}
-        \end{algorithm}
-
-    \end{frame}
 
@@
 
+    \begin{frame}{Redundancy as an ILP (I)}
+
+    We can define the redundancy of a linear constraint $DBF' \cdot C \leqslant t_2 - t_1$ with regards to the set of $k$ linear constraints $DBF \cdot C \leqslant T$ as the following Integer Linear Problem (ILP):
+
+    \begin{columns}[c]
+        \column{0.5\textwidth}
+
+        \begin{block}{Redundancy ILP}
+
+        % \begin{center}
+        $z = \max \left( DBF' \cdot C \right)$
+
+        s.t. $DBF  \cdot C \leq T$
+
+        %$
+        % \begin{array}{ccccc}
+        % DBF  & \cdot & C &\leq & T \\
+        % DBF' & \cdot & C &\leq & t_2 - t_1 + 1
+        % \end{array}
+        %$
+        % \end{center}
+
+        \end{block}
+
+        \column{0.4\textwidth}
+
+        % \begin{center}with\end{center}
+        \[
+          \begin{array}{ccc}
+            DBF & : & [n,k] \text{ matrix}\\
+            DBF' \; \text{and} \; T & : & [n,1] \text{ matrices}\\
+            C & : & [1,n] \text{ matrix}\\
+            t_2 \; \text{and} \; t_1 & : & \text{integers}
+          \end{array}
+        \]
+    \end{columns}
+        \begin{itemize}
+            \item If $z \leqslant t_2 - t_1$, the constraint is redundant
+            % \item Can be solved with a branch-and-bound approach
+            \item Complexity (one test): exponential in the size of the set
+            \item Each constraint of the set must be tested
+        \end{itemize}
+
+    \end{frame}
+
+    \begin{frame}{Redundancy as an ILP (II)}
+
+        \begin{algorithm}[H]
+            \caption{Removing redundant constraints}
+            \label{alg:pruneCspace}
+          \begin{algorithmic}[1]
+            \STATE $CSPACE$ : set of constraints
+            \STATE $S \leftarrow \emptyset$
+            \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
+            \FOR{$cstr$ \textbf{in} $CSPACE$}
+              \IF {$cstr$ is not redundant w.r.t. $S$}
+                \STATE $S.push(cstr)$
+              \ENDIF
+            \ENDFOR
+            \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
+            \FOR{$cstr$ \textbf{in} $S$}
+              \STATE $cstr$ = $S.pop()$
+              \IF {$cstr$ is not redundant w.r.t. $S$}
+                \STATE $S.push(cstr)$
+              \ENDIF
+            \ENDFOR
+            \RETURN{S}
+            \end{algorithmic}
+        \end{algorithm}
+    \end{frame}
+
+	\begin{frame}{Redundancy removal summary}
+
+		To summarize, a finite number of constraints is given by applying the DBF test to intervals:
+		\begin{itemize}
+			\item beginning at a job arrival,
+			\item ending at a job deadline,
+			\item strictly contained in
+			\begin{itemize}
+				\item $[t_d, t_d + H]$ if there exists a FPDIT at $t_d$
+				\item $[O_{max}, O_{max} + 2 \cdot H]$ otherwise
+			\end{itemize}
+		\end{itemize}
+
+		Remaining redundancies are removed with a general ILP approach.
+
+	\end{frame}
+
     \subsection{Example}
@@
 
-    We remove the remaining redundancies with the ILP:
+    We remove the remaining redundancies with the ILP approach:
     $$
@@
     \begin{itemize}
-        \item Further ways of reducing redundancy before applying the simplex
+        \item Further ways of reducing redundancy before applying the ILP approach
         \item Other metrics to quantify the quality of the C-space

### 2013-12-16 beamer/dit-paper-presentation_v2.tex
SBESC version of DIT paper presentation

--- 2013-10-04 beamer/dit-paper-presentation.tex
@@
 \usepackage{algorithm}
+\usepackage{color}
 \usepackage[noend]{algorithmic}
@@
 \author{Thomas~Chapeaux~\inst{1}~\inst{2} \and Paul~Rodriguez~\inst{1}~\inst{2} \and Laurent~George~\inst{2} \and Joël~Goossens~\inst{1}}
-\institute[shortinst]{\inst{1} Université Libre de Bruxelles \and %
-                      \inst{2} ECE Paris}
+\institute[shortinst]{\inst{1} Université Libre de Bruxelles \\ Belgium \and %
+                      \inst{2} ECE Paris \\ France}
 \date{July 2013}
@@
 \begin{frame}
-    \tableofcontents[hideothersubsections]
+    \tableofcontents[hideallsubsections]
 \end{frame}
@@
 \begin{frame}
-    \tableofcontents[currentsection, hideothersubsections]
+    \tableofcontents[currentsection, hideallsubsections]
 \end{frame}
 
-	\subsection{Real-time systems}
+% 	\subsection{Real-time systems}
 
@@
     \end{itemize}
+  We consider periodic systems with constrained deadline on uniprocessor platforms.
 
@@
 \begin{figure}[h]
-\includegraphics[width=\textwidth]{figs/RTsystem_example.png}
-\caption{A task system}
+\includegraphics[width=0.7\textwidth]{figs/RTsystem_example.png}
 \label{fig:llf}
@@
   \end{columns}
+
 \end{frame}
@@
 
-	\begin{frame}{Feasibility}
+    \subsection{Motivation}
+
+    \begin{frame}{Motivation}
+
         \begin{block}{Feasibility}
@@
 
-        \begin{block}{Feasibility by a scheduling policy}
-        A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
-        \end{block}
+        \begin{itemize}
+            % \begin{columns}[c]
+            % \column{.1\textwidth}
+            % \column{.4\textwidth}
+            %     \begin{tabular}{|r|c|c|c|c|}
+            %      \hline
+            %       & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
+            %      \hline
+            %      $\tau_1$ & 1 & 2 & 6 & 10\\
+            %      \hline
+            %      $\tau_2$ & 0 & 3 & 5 & 5\\
+            %      \hline
+            %     \end{tabular}
+            % \column{.5\textwidth}
+            %     \includegraphics[width=\textwidth]{figs/RTsystem_example.png}
+            % \end{columns}
+            \item When implementing a system on different platform, the $C_i$ values may vary. How can we efficiently check if a system is feasible on a given platform?
 
-        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is EDF-schedulable.
+            \item Most feasibility tests assume specific values of the $C_i$, which means that they must be applied once for each candidate platform.
+
+            \item Our solution is to provide a description of the space of feasible execution times which can be  used to efficiently test any platform.
+        \end{itemize}
     \end{frame}
@@
         \begin{block}{C-space}
-            The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
+            The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any point $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
         \end{block}
 
+\begin{columns}[c]
+    \column{0.5\textwidth}
         \begin{itemize}
-            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints
-            \item An efficient description allows us to quickly  whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
+            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints on the $C_i$.
+            \item Example:
+            \begin{tabular}{|r|c|c|c|c|}
+             \hline
+              & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
+             \hline
+             $\tau_1$ & 1 & ? & 6 & 10\\
+             \hline
+             $\tau_2$ & 0 & ? & 5 & 5\\
+             \hline
+            \end{tabular}
+        \end{itemize}
+    \column{0.5\textwidth}
+        \begin{center}
+        \begin{figure}
+            \includegraphics[width=0.9\textwidth]{figs/cspace_example_2.png}
+            \caption{C-space containing 17 possible $C_i$ values}
+        \end{figure}
+        \end{center}
+
+    \end{columns}
+    \end{frame}
+
+    \begin{frame}{C-space of synchronous systems}
+
+    \begin{itemize}
+        \item The authors of \cite{george2009characterization} obtain an efficient description of the C-space of synchronous systems based on the DBF test\cite{baruah1990algorithms}, a necessary and sufficient condition of feasibility for constrained deadline systems.
+        \item However, synchronous systems are a worst-case with regards to feasibility, i.e.
+some unfeasible synchronous systems become feasible if specific offsets are added.
+In the literature (e.g.
+\cite{goossens2003scheduling}), the benefits of offsets are confirmed.
+        \item This motivates a description of the C-space for asynchronous systems.
+
     \end{itemize}
 
-    \end{frame}
+% a necessary and sufficient condition of feasibility:$$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leqslant t_2 - t_1 \; \; \forall t_1 \leq t_2$$
+%         where $n_i(t_1, t_2)$ is the number of jobs of $\tau_i$ in the interval $[t_1, t_2]$.
 
-	\section{Previous works}
+%     ~\\
 
-    \begin{frame}
-    \tableofcontents[currentsection, hideothersubsections]
-    \end{frame}
+%     The description is given by the DBF test on intervals $[0, t]$, where $t$ is a deadline and $0 < t \leqslant H$ (with $H = LCM(T_i)$).
 
-    \subsection{Demand-bound function}
+%     ~\\
 
-    \begin{frame}{Demand-bound function feasibility test}
-        \begin{block}{Demand-bound function}
-            The \textbf{demand-bound function (DBF)} \cite{baruah1999generalized,
-        baruah1990algorithms}
-            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
-            the maximal cumulated execution time of jobs of $\tau$ contained in the
-            closed interval $[t_1, t_2]$.
-        \end{block}
-        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
-        where $n_i(t_1, t_2)$ is the number of jobs of task $\tau_i$ whose arrival times
-        and deadlines are both in the closed interval $[t_1, t_2]$.
-
-        ~\\
-
-        The following has been shown to be a necessary and sufficient condition of feasibility (called DBF test in the following): $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$
+%     The remaining redundancies are removed by an algorithm based on the simplex (with exponential worst-case complexity).
 
     \end{frame}
-
-    \subsection{C-space of synchronous systems}
-
-    \begin{frame}{Description using the DBF test}
-    The DBF test gives us a set of constraints to describe the C-space
-    $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$
-
-    \begin{itemize}
-        \item Every constraint is linear in the $C_i$ values
-        \item Every constraint is necessary
-        \item Their conjunction is sufficient
-        % \pause
-        \item But we have an infinite number of constraints!
-        \item $\Rightarrow$ Removing redundancy
-    \end{itemize}
-    \end{frame}
-
-    \begin{frame}{Removing redundancy for synchronous system}
-
-    The authors of \cite{george2009characterization} obtain an efficient description of the C-space by
-    \begin{itemize}
-        \item Removing constraints in which $t_1 > 0$
-        \item Removing constraints in which $t_2$ is not a deadline or $t_2 > H$ (where $H = LCM(T_i)$)
-    \end{itemize}
-
-    ~\\
-    % \pause
-
-    They also define the notion of \textbf{definitive idle times (DIT)} and show that the first one happens at a time $0 < t_d \leqslant H$.
-Finally they show that all constraints where $t_2 > t_d$ are also redundant.
-
-    ~\\
-    % \pause
-
-    The remaining constraints are thus the DBF test on intervals $[0, t]$, where $t$ is a deadline and $0 < t \leqslant t_d$.
-The remaining redundancies are removed by an algorithm based on the simplex.
-
-    \end{frame}
-
-    % \subsection{Cyclic Idle Times}
-
-    % \begin{frame}{Cyclic Idle Times}
-
-    % \end{frame}
 
@@
     \begin{itemize}
-        \item Introduce the notion of \textbf{first periodic DIT (FPDIT)} as a generalization of the notion of DIT
-        \item Provide an algorithm to find an efficient description of the C-space for any periodic system
+        \item Introduce the notion of \textbf{First Periodic Definitive Idle Times}, which provides a study interval independent of the execution times.
+        \item Extend the description of the C-space for asynchronous periodic constrained deadline systems
         \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
@@
     \begin{frame}
-        \tableofcontents[currentsection, hideothersubsections]
+        \tableofcontents[currentsection, hideallsubsections]
     \end{frame}
@@
 
+        \begin{columns}[c]
+        \column{0.5\textwidth}
+
+        \includegraphics<1>[width=\textwidth]{figs/DIT_example.png}
+        \includegraphics<2>[width=\textwidth]{figs/DIT_example_2.png}
+
+        \column{0.5\textwidth}
+
         The FPDIT is the smallest $t_d$ such as:
@@
         \]
+        \end{columns}
 
@@
 
-	\subsection{Finding the FPDIT value}
+    \subsection{Possible non-existence}
 
-    \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
-        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by:
+    \begin{frame}{Possible non-existence}
 
-        \begin{algorithm}[H]
-            \caption{Gauss's CRP Algorithm}
-            \label{alg:algoCRP}
-            \begin{algorithmic}[1]
-                \REQUIRE $C$ the set of constraint $c$ : $\left( t_d \equiv x(c) \; (\operatorname{mod} \; p(c)) \right)$
-                \REQUIRE $H$ the hyperperiod of the system
-                \FORALL{$c \in C$}
-                    \STATE $Mc \leftarrow \frac{H}{p(c)}$
-                    \STATE $invMc \leftarrow Mc^{-1} \; (mod \; p(c))$
-                    \STATE $e_c \leftarrow Mc \cdot invMc$
-                \ENDFOR
-                \RETURN $\sum\limits_{c \in C}{x(c) \cdot e_c} \; (mod \; H)$
-            \end{algorithmic}
-        \end{algorithm}
+    \begin{itemize}
+        \item In asynchronous systems, it is possible for a system to not have any FPDIT. Example:
+        \begin{center}
+            \includegraphics[width=.6\textwidth]{figs/nofpdit_example.png}
+        \end{center}
+        \item In fact, a system has a FPDIT if and only if the following condition is fulfilled for some value of $a_i$:
 
-    \end{frame}
-
-    \begin{frame}{Non-pairwise co-prime moduli}
-        If the periods are non-pairwise co-prime, the system has a DIT for given values of $a_i$ if and only if the following condition is respected:
             \[
@@
 
-        Then each equation $t_d \equiv x \; (\operatorname{mod} \; p)$ with $p = p_1^{b_1} \cdots p_k^{b_k}$ (where each $p_i$ is prime), can be replaced by the system:
-
-       \[
-            \begin{array}{l}
-                \left\{
-                    \begin{array}{l}
-                         t_d \equiv x \; (mod \; p_1^{b_1}) \\
-                         \cdots \\
-                         t_d \equiv x \; (mod \; p_k^{b_k})
-                    \end{array}
-                \right.
-            \end{array}
-        \]
-
-        Equations with the same $p_i$ can be replaced by only the one of highest $b_i$. The new system now has pairwise co-prime moduli.
+        \item Note that in synchronous systems ($O_i = 0 \; \forall i$), the hyperiod $H = LCM(T_i)$ is always a DIT.
+    \end{itemize}
 
@@
     \begin{columns}[c]
+        \column{0.6\textwidth}
+
+        \includegraphics[width=1\textwidth]{figs/nofpdit_5.png}
+
         \column{0.4\textwidth}
-
         Systems were generated by
@@
 
-        \column{0.6\textwidth}
-        \includegraphics[width=1.2\textwidth]{figs/nofpdit_5.png}
+    \end{columns}
 
-    \end{columns}
+    FPDIT are less frequent in systems with a high number of tasks or a low CDF.
 
@@
 
-\section{C-space of asynchronous system}
+\section{C-space of asynchronous systems}
 
     \begin{frame}
-    \tableofcontents[currentsection, hideothersubsections]
+        \tableofcontents[currentsection, hideallsubsections]
     \end{frame}
@@
 	\begin{frame}{Initial description}
-		The C-space is still accurately described by the following infinite number of constraints:
+		The C-space is accurately described by the following infinite number of constraints:
 
-        $$\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall t_1 \leqslant  t_2$$
+        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall t_1 \leqslant  t_2$$
+        where $n_i(t_1, t_2)$ is the number of jobs of $\tau_i$ whose release time and deadline are both strictly included the interval $[t_1, t_2]$.
 
-        As in the synchronous case,
+        ~\\
+
+        Based on previous results, a sufficient description is given by intervals $[t_1, t_2]$ where
         \begin{itemize}
-            \item Every constraint is necessary
-            \item Their conjunction is sufficient
-            \item Most of them are redundant.
+            \item $t_1$ is an arrival
+            \item $t_2$ is a deadline
+            \item $0 \leqslant t_1 < t_2 \leqslant O_{max} + 2 \cdot H$ (where $H = LCM(T_i)$)
         \end{itemize}
-        However the method used to remove redundancies will be different.
 	\end{frame}
@@
 
-    \begin{frame}{Redundancy as an ILP (I)}
+    \begin{frame}{Using the FPDIT}
 
-    We can define the redundancy of a linear constraint $C \cdot X \leqslant d$ with regards to a set of $k$ linear constraints $A \cdot X \leqslant B$ as the following Integer Linear Problem (ILP):
+        If the FPDIT exists, we can use the constraints given by the DBF test on intervals $[t_1, t_2]$ such that
+        $$t_d \leqslant t_1 < t_2 \leqslant t_d + H$$
+        which is a smaller interval than $[0, O_{max} + 2 \cdot H]$
 
-    \begin{columns}[c]
-        \column{0.1\textwidth}
-        \column{0.3\textwidth}
+    \end{frame}
 
-        \begin{block}{Redundancy ILP}
+    \begin{frame}{Redundancy as an ILP}
 
-        \begin{center}
-        $z = \max \left( C \cdot X \right)$
+    We can define the redundancy of a linear constraint with regards to the set of $k$ linear constraints as an Integer Linear Problem.
 
-        s.t.
-
-        $
-        \begin{array}{rcc}
-          A \cdot X &\leq & B \\
-          C \cdot X &\leq & d + 1
-        \end{array}
-        $
-        \end{center}
-
-        \end{block}
-
-        \column{0.1\textwidth}
-
-        \column{0.5\textwidth}
-
-        \begin{center}with\end{center}
-        \[
-          \begin{array}{ccc}
-            A & : & [n,k] \text{ matrix}\\
-            B \; \text{and} \; C & : & [n,1] \text{ matrix}\\
-            X & : & [1,n] \text{ matrix}\\
-            d & : & \text{integer}
-          \end{array}
-        \]
-    \end{columns}
         \begin{itemize}
-            \item If $z = d + 1$, the constraint is redundant
+            % \item If $z \leqslant t_2 - t_1$, the constraint is redundant
             % \item Can be solved with a branch-and-bound approach
-            \item Complexity (one test): exponential in the size of the set
             \item Each constraint of the set must be tested
+            \item The worst-case complexity of each test is exponential in $k$
+            \item In the paper, we propose a two-pass approach to reduce the number of constraints.
         \end{itemize}
@@
     \end{frame}
-
-    \begin{frame}{Redundancy as an ILP (II)}
-
-        \begin{algorithm}[H]
-            \caption{Removing redundant constraints}
-            \label{alg:pruneCspace}
-          \begin{algorithmic}[1]
-            \STATE $CSPACE$ : set of constraints
-            \STATE $S \leftarrow \emptyset$
-            \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
-            \FOR{$cstr$ \textbf{in} $CSPACE$}
-              \IF {$cstr$ is not redundant w.r.t. $S$}
-                \STATE $S.push(cstr)$
-              \ENDIF
-            \ENDFOR
-            \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
-            \FOR{$cstr$ \textbf{in} $S$}
-              \STATE $cstr$ = $S.pop()$
-              \IF {$cstr$ is not redundant w.r.t. $S$}
-                \STATE $S.push(cstr)$
-              \ENDIF
-            \ENDFOR
-            \RETURN{S}
-            \end{algorithmic}
-        \end{algorithm}
-
-    \end{frame}
-
-    \begin{frame}{Feasibility study interval}
-
-        The authors of \cite{leung1982complexity} have shown that for asynchronous systems, it sufficient to check the DBF test in intervals $[t_1, t_2]$ where $$O_{max} \leqslant t_1 < t_2 \leqslant O_{max} + 2 \cdot H$$
-
-        Indeed, it can be shown that at instant $O_{max} + 2 \cdot H$ at the latest, the system enters a periodic behavior.
-If follows that if no deadlines have been missed before it, no future deadline misses can occur.
-
-    \end{frame}
-
-    \begin{frame}{Arrivals and deadlines}
-
-        By definition of the demand-bound function, it is sufficient to check only intervals where $t_1$ is an arrival and $t_2$ is a deadline.
-
-        \begin{block}{Demand-bound function}
-            The \textbf{demand-bound function (DBF)}
-            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
-            the maximal cumulated execution time of jobs of $\tau$ contained in the
-            closed interval $[t_1, t_2]$.
-        \end{block}
-
-    \end{frame}
-
-    \begin{frame}{Using the FPDIT}
-
-        The authors of \cite{choquet2004minimal} define the notion of \emph{cyclic idle times}, the first of which marks the start of the periodic behavior of the system.
-They prove that if $t_c$ is a cyclic idle time and there are no deadline miss in the interval $[t_c, t_c + H]$, then the system is feasible.
-
-        ~\\
-
-        However the existence and position of the cyclic idle times depend on the values of the $C_i$ and are therefore not accessible when describing the C-space.
-
-        ~\\
-
-        By definition, if the FPDIT exists it will also be a cyclic idle time. It follows that the interval $[t_d, t_d + H]$ is sufficient.
-
-    \end{frame}
-
     \subsection{Example}
@@
          \hline
+         \tau_2 & 0 & C_2 & 2 & 5\\
+         \hline
          \tau_1 & 8 & C_1 & 7 & 15\\
-         \hline
-         \tau_2 & 0 & C_2 & 2 & 5\\
          \hline
@@
 
+    \begin{frame}{Example (II) ILP first pass}
+
+    \begin{columns}[c]
+    \column{.45\textwidth}
+        \begin{center}
+            \includegraphics[width=\textwidth]{figs/CspaceExampleArrDead_restricted.png}
+        \end{center}
+
+        The DBF test:
+        $$\sum_{i=1}^{n} n_i(t_1, t_2) \cdot C_i \leqslant t_2 - t_1 \; \; \forall t_1 \leq t_2$$
+
+    \column{.55\textwidth}
+        \[
+        \left\{
+            \begin{array}{cccccccc}
+                0 & C_1 & + & 1 & C_2 & \leqslant & 17 - 15 & (x) \\
+                \pause
+                    \color{gray} 0 &
+                    \color{gray} C_1 &
+                    \color{gray} + &
+                    \color{gray} 2 &
+                    \color{gray} C_2 &
+                    \color{gray} \leqslant &
+                    \color{gray} 22 - 15 & \\
+                \pause
+                    \color{gray} 0 &
+                    \color{gray} C_1 &
+                    \color{gray} + &
+                    \color{gray} 3 &
+                    \color{gray} C_2 &
+                    \color{gray} \leqslant &
+                    \color{gray} 27 - 15 & \\
+                \pause
+                1 & C_1 & + & 3 & C_2 & \leqslant & 30 - 15 & (x) \\
+                \pause
+                    \color{gray} 0 &
+                    \color{gray} C_1 &
+                    \color{gray} + &
+                    \color{gray} 1 &
+                    \color{gray} C_2 &
+                    \color{gray} \leqslant &
+                    \color{gray} 22 - 20 & \\
+                    \color{gray} 0 &
+                    \color{gray} C_1 &
+                    \color{gray} + &
+                    \color{gray} 2 &
+                    \color{gray} C_2 &
+                    \color{gray} \leqslant &
+                    \color{gray} 27 - 20 & \\
+                1 & C_1 & + & 2 & C_2 & \leqslant & 30 - 20 & (x) \\
+                    \color{gray} 0 &
+                    \color{gray} C_1 &
+                    \color{gray} + &
+                    \color{gray} 1 &
+                    \color{gray} C_2 &
+                    \color{gray} \leqslant &
+                    \color{gray} 27 - 23 & \\
+                1 & C_1 & + & 1 & C_2 & \leqslant & 30 - 23 & (x) \\
+                    \color{gray} 0 &
+                    \color{gray} C_1 &
+                    \color{gray} + &
+                    \color{gray} 1 &
+                    \color{gray} C_2 &
+                    \color{gray} \leqslant &
+                    \color{gray} 27 - 25 & \\
+                    \color{gray} 0 &
+                    \color{gray} C_1 &
+                    \color{gray} + &
+                    \color{gray} 1 &
+                    \color{gray} C_2 &
+                    \color{gray} \leqslant &
+                    \color{gray} 30 - 25 & \\
+            \end{array}
+        \right.
+        \]
+    \end{columns}
+    \end{frame}
+
     \begin{frame}{Example (II)}
 
-    We remove the remaining redundancies with the ILP:
+    We remove the remaining redundancies with a second exhaustive pass:
     $$
@@
     \begin{frame}
-    \tableofcontents[currentsection, hideothersubsections]
+        \tableofcontents[currentsection, hideallsubsections]
     \end{frame}
@@
 
-        We want to express the feasibility gain of random offsets as the ratio
+        Because the synchronous release is known to be the worst-case feasibility-wise, we know that random offset can only improve the feasibility of a system.
+
+        ~\\
+
+        We express this feasibility gain given as the ratio
 
@@
             \begin{itemize}
-                \item Around 10\% of amelioration for high-utilization systems
+                \item Around 10\% of improvement for high-utilization systems
                 \item Gain not highly dependent of utilization or CDF
+                \item For random offsets!
             \end{itemize}
@@
 
+    \begin{frame}
+        \tableofcontents[currentsection, hideallsubsections]
+    \end{frame}
+
     \begin{frame}{Future Works}
@@
     \begin{itemize}
-        \item Further ways of reducing redundancy before applying the simplex
-        \item Other metrics to quantify the quality of the C-space
-        \item Extension to multiprocessor scheduling
+        \item Further ways of reducing redundancy before applying the ILP approach: We often a lot of constraints before applying the ILP approach and far less afterwards.
+It is our belief that further theoretical results would allow to remove a lot of redundant constraints beforehand.
+        \item Other metrics to quantify the quality of the C-space: Rather than the volume of the C-space, a study of the size or the minimal distance of its border may be more relevant.
+        \item Using the C-space to study the impact of offsets on feasibility. Are there \emph{optimal} offset values for a given system?
+        %\item Extension to multiprocessor scheduling: The values of the DITs do not depend on the number of processor.
     \end{itemize}
+
+    \end{frame}
+
+\begin{frame}
+
+    \begin{center}
+    \huge Abrigado!
+
+    ~\\
+
+    \normalsize Any questions?
+    \end{center}
 

### 2013-12-16 python-simulation/helper/systems.py
Added ability to generate synchronous systems

@@ -3,7 +3,7 @@ from model import Task
 from model import TaskGenerator
 
 
-def generateSystemArray(numberOfSystems, constrDeadlineFactor, n=4, preemptionCost=2, verbose=False):
+def generateSystemArray(numberOfSystems, constrDeadlineFactor, synchronous=False, n=4, preemptionCost=2, verbose=False):
 	systemArray = []
 	for i in range(numberOfSystems):
 		Umin = 0.55
@@ -13,7 +13,7 @@ def generateSystemArray(numberOfSystems, constrDeadlineFactor, n=4, preemptionCo
 		# maxHyperT = -1
 		Tmin = 3
 		Tmax = 50
-		tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, preemptionCost=preemptionCost, synchronous=False, constrDeadlineFactor=constrDeadlineFactor)
+		tasks = TaskGenerator.generateTasks(Utot, n, maxHyperT, Tmin, Tmax, preemptionCost=preemptionCost, synchronous=synchronous, constrDeadlineFactor=constrDeadlineFactor)
 		if (verbose and numberOfSystems <= 10):
 			print(("Generated task system # ", i))
 			for task in tasks:
@@ -280,7 +280,7 @@ DITPaperExample = Task.TaskSystem(tasks)
 
 # test
 tasks = []
-tasks.append(Task.Task(0, 1, 6, 8, alpha=0))
-tasks.append(Task.Task(0, 1, 12, 13, alpha=0))
+tasks.append(Task.Task(2, 1, 3, 4, alpha=0))
+tasks.append(Task.Task(0, 1, 3, 4, alpha=0))
 
 test = Task.TaskSystem(tasks)

### 2014-01-06 paper-paedf/paper-paedf.tex
Moved other unrelated papers to root (don't worry everyone I know what I'm doing. maybe.)

--- 2013-10-11 python-simulation/paper-paedf/paper-paedf.tex
@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{hyperref}
@@
 \usepackage{float}
-\usepackage{theorem}
+% \usepackage{theorem}
 \usepackage{algorithm}
@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{lemme}{Lemme}
 
@@
 
-\title{Improving success ratio of EDF when taking into account the preemption cost in uniprocessor periodic systems}
+\title{Improving success ratio of EDF when taking into account preemption costs in uniprocessor periodic systems}
 \author{Thomas Chapeaux}
@@
         \end{itemize}
-h
+
         We also assume a discrete time, meaning that we consider that time passes one unit (sometimes called \emph{clock tick}) at a time.
@@
 
-        A scheduling policy is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are active (i.e.
-released and unfinished) jobs present in the system.
+        A scheduling policy is said to be \textbf{idling} if it is not work-conserving, i.e.
+it allows instants at which no jobs are executing even when there are active jobs (i.e.
+released and unfinished) in the system.
 Such instants are then called \textbf{idled instants}.
@@
 
-        A system is said to be \textbf{schedulable by a scheduling policy} if it exists a scheduling policy such that every job in the task set completes before its deadline is reached.
+        A system is said to be \textbf{schedulable} if it exists a scheduling policy such that every job in the task set completes before its deadline is reached.
 A system schedulable by at least one scheduling policy is said to be \textbf{feasible}.\\
@@
 
-        For (a)synchronous constrained deadline systems, $[O_{max}, O_{max} + 2 \cdot H]$ (with $O_{max}$ being the maximal task offset and $H$ the LCM of periods) is a feasibility interval for EDF.
+        For (a)synchronous constrained deadline systems, $U_{tot}$ is still a necesary condition, but is not sufficient.
+When that condition is fulfilled, $[O_{max}, O_{max} + 2 \cdot H]$ (with $O_{max}$ being the maximal task offset and $H$ the LCM of periods) is a feasibility interval for EDF.
 
@@
 
-        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet.
-This only happens at instant $O_{max} + 4 \cdot H$, as seen on Fig.~\ref{fig:edf_longtransitive}.\\
+        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet even if $U_{tot} \leqslant 1$.
+Indeed, the periodic behavior begins at instant $O_{max} + 4 \cdot H$, as seen on Fig.~\ref{fig:edf_longtransitive}.\\
 
@@
 
-        \subsubsection{Idling dominate non-idling}
+        \subsubsection{Idling strictly dominates non-idling}
 
+        Non-idling (or work-conserving) algorithms are a special case of idling algorithms.
+In the free preemption model, EDF was a non-idling optimal algorithm, which proved that the idling algorithms did not offer any advantage with regards to schedulability.
+
+        \begin{lemme}
+        With the costly preemption assumption, there are constrained deadline systems schedulable by an idling algorithm and not schedulable by any non-idling algorithm.
+        \end{lemme}
+
+        \begin{proof}
         Consider the following system
@@
         Which means that at $t=2$, there will either be \mbox{$(c_{1,1} - 1) +c_{2,1} + \alpha = 7$} or \mbox{$c_{1,1} + (c_{2,1} -1) + \alpha = 7$} units of computation left to compute (including preemptions recovery) before the deadline at $t=8$, the system will thus certainly miss a deadline.
+
+        \end{proof}
 
